### 2014-08-18 ms/figure.tex
first

\documentclass[12pt, preprint]{aastex}
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citep and citep
\usepackage{amsmath}	% for \iint
\usepackage{bbm}
\usepackage[breaklinks]{hyperref}	% for blackboard bold numbers
\usepackage{hyperref}
\hypersetup{colorlinks}
\usepackage{color}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\hypersetup{ colorlinks,
linkcolor=darkblue,
filecolor=darkgreen,
urlcolor=darkred,
citecolor=darkblue }
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

\begin{document}
\author{
  Mohammadjavad~Vakili\altaffilmark{1},
  David~W.~Hogg\altaffilmark{1,2,3}
\altaffiltext{1}{Center for Cosmology and Particle Physics, New York University}
\altaffiltext{2}{Center for Data Science, New York University}
\altaffiltext{3}{Max-Planck-Institut f\"ur Astronomie}
}

\title{Towards fast and optimal centroiding of stars}

\begin{abstract}

We present a 3$\times$3 method for estimating the centroid of stars in astronomical images. After simulating a large number of stars in a wide range of scales, both in signal-to-noise-ratio and full width at half maxima, we compare the results of our model to those obtained from the centroiding method implemented in
SDSS photometric pipeline, as well as $\chi^{2}$ PSF fitting. Comparison of the median centroid error, binned on signal-to-noise-ratio, resulting from the proposed technique to the Cramer-Rao lower bound on the variance of centroid estimates, suggests that, the 3$\times$3 polynomial hack provides accurate estimates of centroid in certain subsets of the parameter space, and that SDSS trick is able to deliver an unbiased estimate in a wide range of parameters.

\end{abstract}

\section{Introduction}

A common practice in astronomy is taking imaging data, and then finding the coordinates of various light sources across the sky. Having access to unbiased estimate of the center of point sources, convolved with telescope point spread function (and atmospheric PSF in case of ground based telescopes) and pixel response function, is crucial in further steps of astronomical image processing. For instance, proper measurement of the shape of galaxies requires interpolating the PSF from the position of sparsely located stars across the image to the position of galaxies. The accuracy of the PSF estimation therefore, depends on how accurately we know the centroid of stars.

Ideally, we want a centroiding procedure that provides measurements as accurate as possible, without putting a huge computational burden on the photometric pipeline. Reducing the computational cost becomes even more important in large surveys, where we want to estimate the centroid of thousands of point sources detected on the focal plane.

Reaching the optimal precision however, is limited by the presence of noise; both sky noise and CCD readout noise. Variance of the centroid estimate, will always have a theoretically set lower bound, known as the Cramer-Rao lower bound (hereafter denoted by CRLB) which has an inverse relation with the signal-to-noise-ratio. Thus, of particular interest is devising a fast method that returns less biased estimate of centroids especially in a realistic range of signal-to-noise ratios.

To date, a number of softwares have been designed for the purpose of extracting astronomical sources and making catalogs. One of these softwares is SExtractor \citep{sex}, whose centroiding method involves first, finding the zeroth moment of the object as a first order estimate, and then iteratively correcting the centroid by computing the zeroth order moment of the object weighted by a Gaussian window function, until the correction falls below a particular threshold value. The width of the Gaussian window function is set by the object's half light radius.

Another examples are DAOPHOT \citep{daophot} and DOPHOT \citep{dophot} which both assume analytic models for the stellar PSF profiles with centroid coordinates being free parameters of these models. DAOPHOT (DoPHOT) finds the centroid by fitting a Gaussian (power law) PSF to the light profile of stars.

In this paper, we propose to find the centroid of stars by fitting a second order polynomial to the $3\times3$ pixels around the brightest pixel of stars. We focus on studying the accuracy of this model by comparing the centroid measurement errors with the ones obtained from the method used in SDSS. In order to do so, we apply these methods to a large number of simulated stars with different noise and size realizations.

This paper is structured as follows. In section \ref{sec:model}, we give a brief overview of the methods used in our investigation. In section \ref{sec:data}, we discuss the simulated data. In section \ref{sec:results}, we compare the results of our centroid measurement with those of SDSS method, once for a fixed set of full width at half maxima, and once for a set of fixed signal-to-noise-ratios. Finally, we discuss and conclude in \ref{sec:discussion}.

\section{Model}\label{sec:model}

In order to find the centroid of a star, we fit a simple 2d polynomial $I(x,y)=a+bx+cy+dx^2+exy+fy^2$ to the $3\times3$ patch centered on the brightest pixel of the
image. Upon constructing a universal 9$\times$6 design matrix
\[
A=
  \begin{bmatrix}
    1 & x_{1} & y_{1} & x_{1}^{2} & x_{1}y_{1} & y_{1}^{2}\\
    . & . & . & . & . & . \\
    . & . & . & . & . & . \\
    . & . & . & . & . & . \\
    1 & x_{9} & y_{9} & x_{9}^{2} & x_{9}y_{9} & y_{9}^{2}\\
  \end{bmatrix},
\]
the free parameters of the model $\{a,b,c,d,e,f\}$ (hereafter compactly denoted by $\mathbf{X}$) can be determined by 
\beq
\mathbf{X} = (A^{T}A)^{-1}A^{T}\mathbf{Z},
\eeq  
where $\mathbf{Z}$ is given by $(I_{1},...,I_{9})^{T}$, with $I_{i}$ denoting the brightness of the $i-$th pixel. Afterwards, the best fit parameters can be used to compute the centroid coordinate
\[
  \begin{bmatrix}
    x_{c}\\
    y_{c}\\
  \end{bmatrix} = \begin{bmatrix}
    2d & e\\
    e & 2f\\
  \end{bmatrix}^{-1}\begin{bmatrix}
    -b\\
    -c\\
  \end{bmatrix}.
\]

Let us smooth the image of the star with a Gaussian PSF with a FWHM equal to that of PSF at that location. Now Consider any row or column of the 3$\times$3 patch around the brightest pixel of the smooth image and let us denote the brightness of these three pixels by $\{f_{-},f_{0},f_{+}\}$. The fundamental assumption behind the model implemented in SDSS photometric pipeline \citep{sdss} is that these brightness values are in fact the function $f(x) = A\exp((x-x_{c})^{2}/2\beta^{2})$ evaluated at $x=-1,0,+1$; with $x_{c}$ being the position of centroid. Knowing the value of $f$ at $\{-1,0,1\}$, expanding $f(x)$ up to fourth order in $x$ leads to
\beq
x = \frac{s}{d}(1+k\frac{d}{4A}(1-(s/d)^{2})),
\eeq
where $k \simeq 4/3$, and
\beq
\begin{array}{l}
s:=(f_{+}-f_{0})/2, \nonumber\\
d:=2f_{0} - (f_{+}+f_{0}), \nonumber\\
A = f_{0} +s^{2}/2d.
\label{def}
\end{array}
\eeq

Now if we apply this method to every column and row of the 3$\times$3 patch, we will find three local maxima for three rows $\{(x_{-},-1), (x_{0},0),(x_{+},1)\}$, and three local maxima for three columns $\{(-1,y_{-}), (0,y_{0}),(1,y_{+})\}$. It is important to note that since the image has been smoothed, the covariance matrix between different pixels is not zero. Therefore, there is an uncertianty associated with any of these local maxima. Then, the centroid is estimated by finding the intersection of a line fitted to three maxima corresponding to rows, and another curve fitted to three maxima corresponding to columns. Figure [\ref{ex}] demonstrates the performances of the discussed models in centroiding simulated stars with known true centroids.

\section{Simulated data}\label{sec:data}

In order to test the accuracy of the two models and compare them against each other, we need to simulate a large set of stars for which we know the exact position of centroids. Furthermore, we uniformly draw the centroids within sub-pixel regions.

We use the Moffat profile \citep{moffat} for our simulations. Moffat profile is an analytic model for stellar PSFs which has broader wings than a simple Gaussian model. The surface brightness of the Moffat profile is given by
\beq
I(r) = \frac{f(\beta -1)}{\pi \alpha^{2}}[1+(r/\alpha)^{2}]^{-\beta},
\label{mof}
\eeq
where $f$ is the total flux, and $\alpha$ is the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$) being $2\alpha\sqrt{2^{1/\beta}-1}$. The radial light profile of the stars generated in our simulations are shown in Figure[\ref{moffat}].

We want to investigate the performance of the two models introduced in section \ref{sec:model} for different background noise levels, and also different values of $\gamma$. For further simplicity, we set the flux of all stars to one. Per pixel uncertainties are assumed to be uncorrelated Gaussian (resulting in a diagonal covariance matrix), and we only study the sky dominated regime. Therefore the covariance matrix is simply given by $\sigma^{2}I$.

Moreover, it is more useful to work with the signal-to-noise ratio instead of the variance of the Gaussian noise. This is due to the fact that at the same noise level, simulated stars with different values of $\gamma$ have different signal-to-noise-ratios.

First, let us find an analytic expression for $S/N$. We define $S/N$ as the ratio of the mean and variance of the distribution which the flux estimator is drawn from. Assume that the total flux from the point source is $f$, and that the PSF at the $i$-th pixel is given by $P_{i}$. Therefore the brightness of the $i$-th pixel is drawn from a Gaussian distribution $p(I_{i}) = \mathcal{N}(fP_{i},\sigma^{2})$.

The optimal estimator of flux (an estimator which saturates Cramer-Rao bound), is the weighted average $\tilde{f}=\sum_{i}I_{i}P_{i}$. Knowing the distribution of $I_{i}$, it can be shown that 
\beq
p(\tilde{f}) = \mathcal{N}(f , \frac{\sigma^{2}}{\sum_{i}P_{i}^{2}}),
\eeq  
which leads to
\beq
\begin{array}{l}
S/N $=$ \frac{\sqrt{\sum_{i} P_{i}^{2}}}{\sigma}.
\end{array}
\label{snr}
\eeq

Note that (\ref{snr}) is valid in the limit of sky-dominated star images, and that is the limit we are interested in. In the case of our simulations the expression (\ref{snr}) can be analytically expressed in terms of $\sigma$, $\gamma$, and also $\beta$. We fix $\beta$ at the fiducial value of 2.5. In this case we have
\beq
S/N = \frac{0.478}{\sigma \gamma}.
\label{snr2}
\eeq

Equation (\ref{snr2}) implies that for stars with the same flux $f$ and background noise level $\sigma$, those with bigger size have lower $S/N$ and therefore, we expect to obtain more biased estimates for larger $\gamma$.

In this work, we study the relation between error in centroid measurement and $\gamma$ at fixed $S/N$ and vice versa. In the first experiment, we generate Moffat profiles centered randomly in the sub-pixel region inside the central pixel of a 17$\times$17 image, at four different full width at half maxima of 2, 2.8, 4, and 5.6 pixels with signal-to-noise ratio ranging from 5 to 150. In the second experiment, we generate Moffat profiles with $\gamma$ ranging from 2 to 6, with four different signal-to-noise-ratios of 5, 50, 100, 150.

In addition to the two centroiding method discussed in the previous sections, we compute the error in centroid measurement from fitting the exact analytic PSF model to the data by minimizing $\chi^{2}$. In both experiments, we compare the error with the quantity

\beq
\rho := \frac{\gamma}{SNR}
\eeq

In order to do so, after computing the error $\Delta x = \sqrt{(x_{t}-x_{c})^2 + (y_{t}-y_{c})^2}$ for each model, we compute the median in bins of $S/N$. The closer the median error is to $\rho$, the less biased the centroid estimate is. This quantity is, in fact, the Cramer-Rao lower bound (hereafter CRLB). In statistics, CRLB sets a lower bound for the point estimate of a variable. This lower bound can be analytically calculayed from the log-likelihood function

\beq
var(\hat{\theta}) \geq \langle (\frac{\partial \log \mathcal{L}}{\partial \theta})^{2}\rangle^{-1},
\eeq

where here $\theta$ is the centroid coordinate, and the dependence of likelihood on centroid $\theta$ comes through (\ref{mof}). Taking the derivative of the log-likelihood w.r.t the centroid coordiantes, yields

\beq
\sum_{a=1}^{2} \langle \delta x_{a}^{2} \rangle = \frac{(2\beta + 1)\pi \gamma \sigma}{4 \beta (\beta-1)^{2}(2^{1/\beta}-1)^{1.5}},
\eeq

where, in the case of $\beta = 2.5$, is given by $0.4\gamma^{2}\sigma$ which is approximately equal to $\rho$.

Theoretically, we expect the median error resulting from the exact PSF fitting method to be arbitrarily close to CRLB. This is due to the fact that, we find the centroid by fitting the model that used to generate the data. In this case, the log-likelihood can be written as

\beq
\log \mathcal{L}(\theta) = -\frac{1}{2\sigma^{2}}\sum_{\mathbf{p}}(f(\mathbf{x}_{\mathbf{p}},\theta_{t})+ n(\mathbf{x}_{\mathbf{p}}) - f(\mathbf{x}_{\mathbf{p}},\theta)),
\label{like}
\eeq

where $\theta$ encompasses all the free parameters of the model (with $\theta_{t}$ denoting the true value of the parameters), and $n(\mathbf{x}_{\mathbf{p}})$ is the uncorrelated Gaussian noise map with variance $\sigma^{2}$. Upon expanding (\ref{like}) around the true parameter, and assuming that the the point estimate is close to the true value, it can be shown that the covariance of the parameters $\hat{\theta}$ is given by the inverse Fisher information matrix

\beq
F_{ij} = \sum_{\mathbf{p}}\frac{\partial f(\mathbf{x}_{\mathbf{p}},\theta_{t})}{\partial \theta_{i}}\frac{\partial f(\mathbf{x}_{\mathbf{p}},\theta_{t})}{\partial \theta_{j}},
\eeq 
whose inverse is CRLB.

\section{Results}\label{sec:results}

\subsection{Experiment 1}

Results of the first experiment are shown in Figures[\ref{1}], [\ref{2}], [\ref{22}], [\ref{3}]. As we expected, for all three methods, median error gets larger for fainter stars. This error is even larger as $\gamma$ gets larger. In order to have a better understanding of the performance of these models, the plots are made in logarithmic scale. As it can be seen in [\ref{3}], the difference between the median error and the CRLB (hereafter denoted by $\Delta$) in the case of PSF fitting is quite negligible. Furthermore, it is evident that in the case of 3$\times$3 polynomial method [\ref{1}], there are certain ranges of signal-to-noise ratio, where $\Delta$ is bigger than the one obtained from SDSS trick [\ref{2}], when we center the smoothing kernel on the center of the brightest pixel of the star, for different values of $\gamma$. On the other hand, when the smoothing kernel in the SDSS method [\ref{22}], is centered on the true centroid, the resulting bias is relatively close to CRLB. Moreover, $\Delta$ shrinks significantly, as $\gamma$ becomes smaller.

We repeat the same experiment, this time assigning random ellipticities between 0 and 0.2 to the simulated stars. We did not observe any particular change in the behavior of error as a function of signal-to-noise-ratio for the polynomial (Figure [\ref{111}]). However, as can be seen in figure [\ref{222}], centroiding elliptical Moffat profiles with the SDSS method in the presence of noise, results in relatively larger errors.

\subsection{Experiment 2}

Behavior of $\Delta x$ as a function of $\gamma$ for different values of $S/N$ is shown in Figures [\ref{4}], [\ref{5}], [\ref{6}]. Again, by decreasing noise level of the background sky, $\Delta x$ becomes smaller at all ranges of $\gamma$. Interestingly, as observed in results of both methods, in the cases of $S/N = 100, 150$, $\Delta x$ does not increase with $\gamma$ monotonically. In fact, there exist a minimum error around $\gamma$ $\sim$ 3 pixels. Also, at $S/N = 5$, where the image of stars are dominated by noise, we do not observe any considerable variation in $\Delta x$.

\subsection{Experiment 3}

In the last experiment, we study bias as a function of the ellipticity of the simulated stars for different values of $\gamma$, and signal-to-noise-ratio. As it can be seen in Figures [\ref{7}], [\ref{8}], [\ref{9}], the variation of bias with ellipticity is almost negligible for all three methods. Furthermore, the bias arising from the SDSS method is slightly higher than the one obtained from the polynomial method at $\gamma = 4$.

\section{Discussion}\label{sec:discussion}

In this work, we proposed a method for centroiding stars based on a 3$\times$3 method. Employing this technique into large scale astronomical surveys can considerably reduce the computational cost of initial astrometry of these surveys. This method can be roughly thousand times faster than centroiding through model fitting. The advantage of this method becomes more pronounced in PSF estimation in which all we need as an input is the centroid of stars and some lower dimensional representation of the postage stamp of stars.

Comparison of this method with centroiding method of SDSS photo pipeline suggests that there are ranges of size and noise level in which, the error arising from this method is close to the theoretically set CRLB than the error obtained from SDSS method. However, in a wide range of scales, the error from SDSS trick is relatively smaller.

However, it is important to note that, at the very faint end of stars, the bias resulting from both method can be significantly large. This can be largely attributed to the fact that any estimate obtained from this method, tends to be inside the brightest pixel of the image, which is not necessarily the case for the true centroid when the signal-to-noise-ratio is low.

The advantage of SDSS trick over the polynomial model is that, it assumes a more realistic model for the light profile of stars. On the other hand, in order for this model to achieve significantly better results, one has to estimate the FWHM of the star in advance.

Furthermore, in this investigation we narrowed our focus on data simulated from a very specific model. Although there are various cases where Moffat profiles provide reasonable representation of point spread function, these models are not generic enough to let us reach a more general conclusion.

Another important, and untapped, area of study would be devising a model that infers the centroid of stars and point spread function (in its full extent, not at the catalog level) across an astronomical image simultaneously.

\begin{thebibliography}{70}

\bibitem[Bertin \& Arnouts (1996)]{sex} Bertin, E., Arnouts, S. \ 1996  Astronomy and Astrophysics Supplement Series, 117, 393-404
\bibitem[Lupton etal. (2001)]{sdss} Lupton, R. etal. \ 2001  arXiv: astro-ph/0101420
\bibitem[Schechter etal. (1993)]{dophot} Schechter, P. L., Mateo, M., Saha, A. \ 1993 \pasp, 1342-1353
\bibitem[Stetson (1987)]{daophot} Stetson, P. B. \ 1987, \pasp, 191-222
\bibitem[Trujillo etal. (2001)]{moffat} Trujillo, I., et al. \ 2001 \mnras, 977-985

\end{thebibliography}

\clearpage

\begin{figure}[!htb]
\minipage{.5\textwidth}
  \includegraphics[width=\linewidth]{exaple_cen0.png}
\endminipage
\minipage{.5\textwidth}
  \includegraphics[width=\linewidth]{example_cen1.png}
\endminipage
\caption{Demonstration of the performance of SDSS and polynomial method on finding the centroid on the 3$\times$3 patch around the brightest pixel, with the true centroid, and centroid estimate from the polynomial method markerd by $+$, $\wedge$ respectively; and the centroid estimate from SDSS trick (shown by $\star$) given by the intersection of two curves.}\label{ex}
\end{figure}

\begin{figure}[!htb]
\minipage{1\textwidth}
  \includegraphics[width=\linewidth]{moffat.png}
\endminipage
\caption{The radial light profile of stars used in this study, with FWHM of 2(star), 2.8(circle), 4(pentagon), and 5.6(square) pixels. The parameter $\beta$ is set to $2.5$.}\label{moffat}
\end{figure}

\begin{figure}[!htb]
\minipage{1\textwidth}
  \includegraphics[width=\linewidth]{map_20_50.png}
\endminipage

\minipage{1\textwidth}
  \includegraphics[width=\linewidth]{map_4_50.png}
\endminipage
\caption{Demonstration of the centroid bias resulting from: \emph{left}: polynomial, and \emph{right}: SDSS tricks as a function of subpixel position of centroid. Top  (bottom) color maps are obtained from taking the median bias of different noise realization of a Moffat profiles with FWHM = 2 (4) pixels, and signal-to-noise of 50.}\label{map}
\end{figure}

\begin{figure}[!htb]
\minipage{1\textwidth}
  \includegraphics[width=\linewidth]{map_2_100.png}
\endminipage

\minipage{1\textwidth}
  \includegraphics[width=\linewidth]{map_4_10.png}
\endminipage
\caption{Demonstration of the centroid bias resulting from: \emph{left}: polynomial, and \emph{right}: SDSS tricks as a function of subpixel position of centroid. Top  (bottom) color maps are obtained from taking the median bias of different noise realization of a Moffat profiles with FWHM = 2 (4) pixels, and signal-to-noise of 10.}\label{map2}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{poly_snr.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from polynomial method and the signal-to-noise ratio of stars with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{1}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{sdss_without_knowing_true_pixel.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from SDSS method, when the center of the smoothing kernel is the center of the brightest pixel of star, and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{2}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{sdss_fwhm_true_pixel.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from SDSS method, when the center of the smoothing kernel is the true centroid of star, and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{22}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{psf_snr.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from PSF fitting method and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{3}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{epoly_fwhm.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement of elliptical PSF profiles from polynomial method and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{111}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{esdss_fwhm_notruth.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement of elliptical PSF profiles from SDSS method and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{222}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{poly_fwhm.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from polynomial method and the FWHM of stars with signal-to-noise-ratio of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right). In each scatter plot, the blue line represents the median of data points, and the green line represents $\rho$.}\label{4}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{sdss_fwhm.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from SDSS method and the FWHM of stars with signal-to-noise-ratio of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right). In each scatter plot, the blue line represents the median of data points, and the green line represents $\rho$.}\label{5}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{psf_fwhm.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from PSF fitting method and the FWHM of stars with signal-to-noise-ratio of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right). In each scatter plot, the blue line represents the median of data points, and the green line represents $\rho$.}\label{6}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{poly_ellipticity.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the polynomial method and the ellipticity of stars with ($S/N$, $\gamma$) of : (100, 2) (upper left), (20, 2) (upper right), (100, 4) (lower left), and (20, 4) (lower right). In each scatter plot, the blue line represents the median of data points.}\label{7}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{sdss_ellipticity.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the sdss method and the ellipticity of stars with ($S/N$, $\gamma$) of : (100, 2) (upper left), (20, 2) (upper right), (100, 4) (lower left), and (20, 4) (lower right). In each scatter plot, the blue line represents the median of data points.}\label{8}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{psf_ellipticity.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the PSF fitting method and the ellipticity of stars with ($S/N$, $\gamma$) of : (100, 2) (upper left), (20, 2) (upper right), (100, 4) (lower left), and (20, 4) (lower right). In each scatter plot, the blue line represents the median of data points.}\label{9}
\end{figure}

\end{document}

### 2014-08-18 script/test_snr.py

@@ -1,0 +1,150 @@
+#!/usr/bin/env python
+
+
+
+"""
+Goal: This code tests centroiding of a set of 
+normalized moffat profiles with a given FWHM and beta
+in a given range of signal-to-noise-ratios,
+using three different models:
+SDSS method, Polynomial method, 
+and PSF fitting method.
+
+Dependencies: numpy, profile.py,
+              poly.py, sdss.py
+Author: Mohammadjavad Vakili (July and August 2014)
+"""
+
+import centererr
+import numpy as np
+import sys
+
+
+
+if __name__ == '__main__':
+    from optparse import OptionParser
+    o = OptionParser()
+    #o.set_usage('%prog [options]')
+    #o.set_description(__doc__)
+
+    o.add_option('-m', '--method', dest='method', default='poly',
+        help='Set the centroiding method, polynomial or sdss or fitting, default: polynomial')
+    o.add_option('-f', '--fwhm', dest='fwhm', default= 2., type='float',
+        help='FWHM of the moffat profile, default: 2')
+    o.add_option('-b', '--beta', dest='beta', default= 2.5, type='float',
+        help='Dimensionless parameter of Moffat profile, default: 2.5')
+    
+    o.add_option('--smin', dest='smin', default=5., type='float',
+        help='Minimum S/N in experiment, default: 10.0')
+    o.add_option('--smax', dest='smax', default=150, type='float',
+        help='Maximum S/N in experiment, default: 150.0')
+    o.add_option('--size', dest='size', default=17, type='int',
+        help='size of the postage_stamp')
+    o.add_option('--sample', dest='sample', default=20000, type='int',
+        help='number of stars in experiment')
+    opts, args = o.parse_args(sys.argv[1:])
+
+
+    #ifn=args[0]
+    
+    if not (opts.size is None):
+        size = opts.size
+    
+    if not (opts.fwhm is None):
+        fwhm = opts.fwhm
+
+    if not (opts.smin is None):
+        smin = opts.smin
+
+    if not (opts.smax is None):
+        smax = opts.smax
+
+    if not (opts.sample is None):
+        sample = opts.sample
+
+    if not (opts.beta is None):
+        beta = opts.beta
+    
+    
[…]

### 2014-08-18 setup.py

@@ -1,0 +1,20 @@
+from setuptools import setup
+import os, sys, glob
+
+__version__ = '0.1'
+
+setup(name = 'centererr',
+      version = __version__,
+      description = 'Centroiding Stars',
+      long_description = 'Centroiding Stars with SDSS, POLYNOMIAL, PSF FITTING',
+      author='MJ Vakili',
+      author_email='mjvakili@nyu.edu',
+      url='',
+      platforms=['*nix'],
+      license='GPL',
+      requires = ['scipy','numpy'],
+      provides = ['centererr'],
+      package_dir = {'centererr':'src'},
+      packages = ['centererr'],
+      scripts=glob.glob('script/*.py'),
+)

### 2014-08-18 src/__init__.py

@@ -1,0 +1,5 @@
+"""
+A module interface to shapelet functions
+"""
+import fitting, poly, profile, sdss
+

### 2014-08-18 src/fitting.py

@@ -1,0 +1,40 @@
+import numpy as np
+import scipy.optimize as op
+
+def Moffat(data , FWHM , b , x0 , y0 , x , y ):
+   
+    
+    a = FWHM/(2.*np.sqrt(2**(1./b) - 1.))
+    r = ((x-x0)**2. +(y-y0)**2.)**.5
+    return ((b - 1.)*(1. + (r/a)**2.)**(-1.*b))/(a*np.pi)
+
+
+
+def lnlike(theta , I , x , y):
+
+    FWHM , b , x0 , y0 = theta
+    model = Moffat(I , FWHM , b, x0 , y0 , x ,y)
+    inv_sigma2 = 1.
+    return -0.5*(np.sum((I-model)**2*inv_sigma2 - np.log(inv_sigma2)))
+
+
+
+def fitting_centroid(I):
+    size = I.shape[0]
+    x = np.linspace(0.5, size - .5, size)
+    y = x[:,np.newaxis]
+    FWHM_true = I.shape[0]/4.
+    b_true = 2.5
+    x0_true = I.shape[0]/2.
+    y0_true = I.shape[0]/2.
+    size = I.shape[0]
+    x = np.linspace(0.5, size - .5, size)
+    y = x[:,np.newaxis]
+    nll = lambda *args: -lnlike(*args)
+    results = op.minimize(nll , [FWHM_true , b_true , x0_true , y0_true] , args = (I , x , y))
+    FWHM_ml , b_ml , x0_ml , y0_ml = results["x"]
+
+    return x0_ml , y0_ml
+
+if __name__ == "__main__":
+    print 'fitting main'

### 2014-08-18 src/poly.py

@@ -1,0 +1,81 @@
+import numpy as np
+
+def design(degree = 2):
+  
+  """This function evaluates the
+     entries of the 9by6 design
+     matrix used in 2nd order
+     polynomial centroiding"""
+
+  nx = np.array([-1. , 0. , 1.])
+  ny = nx[:,np.newaxis]
+  npix = 9
+  
+  #brightness = image.flatten()
+  
+  xv , yv =  np.meshgrid(np.array(nx) , np.array(ny))
+  xc , yc =  xv.flatten() , yv.flatten()
+  
+  A = np.zeros((npix , 6))
+  
+  A[:,0] = (xc**0.)*(yc**0.)
+  A[:,1] = (xc**1.)*(yc**0.)
+  A[:,2] = (xc**0.)*(yc**1.)
+  A[:,3] = (xc**2.)*(yc**0.)
+  A[:,4] = (xc**1.)*(yc**1.)    
+  A[:,5] = (xc**0.)*(yc**2.)
+ 
+
+  return A
+
+
+def regression( A , obs):
+
+  X1 = np.dot(np.transpose(A) , A) 
+  X2 = np.linalg.inv(X1)
+  X3 = np.dot(X2 , np.transpose(A))
+  X = np.dot(X3 , obs)
+
+  return X
+
+def BP(data):
+
+  size = data.shape[0]
+  zero = size/2
+  
+  bp = np.where((data==data.max())) #brightest pixel in the smoothed image
+  cen = [bp[0][0] , bp[1][0]]
+
+  k = data[cen[0]-1:cen[0]+2,cen[1]-1:cen[1]+2]
+ 
+  if (k.shape!= 3):
+     cen = [size/2 , size/2]
+     k = data[cen[0]-1:cen[0]+2,cen[1]-1:cen[1]+2]
+     cen = [size/2 , size/2]
+  return cen
+   
+
+def poly_centroid(data , design):
+
+  size = data.shape[0]
+  zero = size/2
+  
+  bp = np.where((data==data.max())) #brightest pixel in the smoothed image
+  cen = [bp[0][0] , bp[1][0]]
+
+  k = data[cen[0]-1:cen[0]+2,cen[1]-1:cen[1]+2]
+ 
+  if (k.shape!= 3):
+     cen = [size/2 , size/2]
+     k = data[cen[0]-1:cen[0]+2,cen[1]-1:cen[1]+2]
+     
+  X = regression(design , k.flatten())
+  a , b , c, d , e , f = X
[…]

### 2014-08-18 src/profile.py

@@ -1,0 +1,41 @@
+import numpy as np
+
+
+def makeMoffat(size , FWHM =3 , b = 2.5 , e = 0 , center = None ):
+
+    #x = np.arange(0, size, 1, float)
+    #y = x[:,np.newaxis]
+    x = np.linspace(0.5, size-.5 , size)
+    y = x[:,np.newaxis]
+
+    if center is None:
+        x0 = y0 = size / 2.
+    else:
+        x0 = center[0]
+        y0 = center[1]
+    
+    a = FWHM/(2.*np.sqrt(2**(1./b) - 1.))
+    r = ((x-x0)**2. + ((y-y0)**2.)*(1. + np.abs(e))**2./(1. - np.abs(e))**2.)**.5
+    
+    return ((b - 1.)*(1. + (r/a)**2.)**(-1.*b))/(np.pi*(a**2.))
+
+def makeGaussian(size , FWHM =3 , e = 0 , center = None):
+
+    #x = np.arange(0, size, 1, float)
+    #y = x[:,np.newaxis]
+    x = np.linspace(0.5, size-.5 , size)
+    y = x[:,np.newaxis]
+
+    if center is None:
+        x0 = y0 = size / 2.
+    else:
+        x0 = center[0]
+        y0 = center[1]
+    
+    
+    r = ((x-x0)**2. + ((y-y0)**2.)*(1. + np.abs(e))**2./(1. - np.abs(e))**2.)**.5
+    factor = 1./(2.*np.pi*FWHM**2.)   
+    return factor*np.exp((-1.*r**2.)/(2*FWHM**2.))
+
+if __name__ == "__main__":
+    print 'profile main'

### 2014-08-18 src/sdss.py

@@ -1,0 +1,150 @@
+import numpy as np
+from scipy import signal
+
+import profile
+
+def lupton(x , f , sigma):
+  
+
+  """
+  Implementation of Lupton algorithm for 
+  finding the centroid and centroid error
+  of a 3by1 vector in the presence of
+  uncorrelated additive Gaussian noise
+  with variance sigma and smoothing kernel
+  with fwhm = f
+  
+  -----------------------------------------
+  inputs: 
+          x = 3by1 vector,
+          f = FWHM of smoothing kernel,
+          sigma = background noise.
+  -----------------------------------------
+
+  output: 
+          x0 = centroid of the 3by1 vector x
+          varx0 = varianc of x0 
+  
+  """          
+
+  a , b , c = x[0] , x[1] , x[2]
+  k = 1.33
+  s = (c - a)/2.
+  d = 2.* b - (a + c)
+  A = b + (s**2.)/(2.*d)
+  y = 1. - 4.*(s/d)**2.
+  
+  x0 = (s/d)*(1. + k*d*y/4.*A)    #Lupton 1d centroid estimate
+  
+  var_s = (sigma**2.)*(1. - np.exp(f**-2.))/(8.*np.pi*f**2.)
+  var_d = (sigma**2.)*(3. + np.exp(f**-2.) - 4.*np.exp(.25*f**-2.))/(2.*np.pi*f**2.)
+  varx = var_s*(1./d + k*(1-12.*s**2./d**2.)/(4*A))**2. + var_d*(s/d**2. - (8.*k*s**2.)/(4.*A*d**3.))**2.
+  
+  return x0 , varx
+
+
+def lupton_2d(I , f , s):
+  
+  """
+  Implementation of Lupton algorithm in 2D
+  --------------------------------------------
+  inputs:
+         I = 3by3 numpy array
+         f = FWHM of the smoothing kernel
+         s = variance of the background noise
+  --------------------------------------------
+
+  output:
+         x & y coordinate of the centroid estimate of I
+  -------------------------------------------- 
+
+  """
+  
+  mx_plus , mx_zero , mx_minus = lupton(I[:,2] ,f,s)[0] , lupton(I[:,1],f,s)[0] , lupton(I[:,0],f,s)[0]
[…]

### 2014-08-18 setup.py
Update setup.py

@@ -11,7 +11,7 @@ setup(name = 'centererr',
       author_email='mjvakili@nyu.edu',
       url='',
       platforms=['*nix'],
-      license='GPL',
+      license='',
       requires = ['scipy','numpy'],
       provides = ['centererr'],
       package_dir = {'centererr':'src'},

### 2014-08-18 src/sdss.py
Update sdss.py

@@ -126,7 +126,7 @@ def sdss_centroid(data , f , sigma):
   """
   size = data.shape[0]
   zero = size/2
-  kernel = profile.makeGaussian(17 , f , 0 , np.array([zero,zero]))
+  kernel = profile.makeGaussian(size , f , 0 , np.array([zero,zero]))
   
   smoothed_image = signal.convolve2d(data , kernel , mode = "same")
   

### 2014-08-21 script/test_fwhm.py
Create test_fwhm.py

@@ -1,0 +1,174 @@
+#!/usr/bin/env python
+
+
+
+"""
+Goal: This code tests centroiding of a set of 
+normalized moffat profiles with a given SNR and beta
+in a given range of full width at half maxima,
+using four different models:
+SDSS method, Polynomial method, 
+and round PSF fitting method, 
+and elliptical PSF fitting.
+
+Dependencies: numpy
+              
+Author: Mohammadjavad Vakili (July and August 2014)
+"""
+
+import centererr
+import numpy as np
+import sys
+
+
+
+if __name__ == '__main__':
+    from optparse import OptionParser
+    o = OptionParser()
+    #o.set_usage('%prog [options]')
+    #o.set_description(__doc__)
+
+    o.add_option('-m', '--method', dest='method', default='poly',
+        help='Set the centroiding method, polynomial or sdss or fitting, or efitting, default: polynomial')
+    o.add_option('-s', '--snr', dest='snr', default= 150, type='float',
+        help='SNR, default: 150')
+    o.add_option('-b', '--beta', dest='beta', default= 2.5, type='float',
+        help='Dimensionless parameter of Moffat profile, default: 2.5')
+    
+    o.add_option('--fmin', dest='fmin', default=2., type='float',
+        help='Minimum fwhm in experiment, default: 2.')
+    o.add_option('--fmax', dest='fmax', default=5.6, type='float',
+        help='Maximum fwhm in experiment, default: 5.6')
+    o.add_option('--size', dest='size', default=17, type='int',
+        help='size of the postage_stamp')
+    o.add_option('--sample', dest='sample', default=20000, type='int',
+        help='number of stars in experiment')
+    opts, args = o.parse_args(sys.argv[1:])
+
+
+    #ifn=args[0]
+    
+    if not (opts.size is None):
+        size = opts.size
+    
+    if not (opts.snr is None):
+        snr = opts.snr
+
+    if not (opts.fmin is None):
+        fmin = opts.fmin
+
+    if not (opts.fmax is None):
+        fmax = opts.fmax
+
+    if not (opts.sample is None):
+        sample = opts.sample
+
+    if not (opts.beta is None):
+        beta = opts.beta
+    
[…]

### 2014-08-21 script/test_snr.py
added elliptical psf

@@ -6,12 +6,13 @@
 Goal: This code tests centroiding of a set of 
 normalized moffat profiles with a given FWHM and beta
 in a given range of signal-to-noise-ratios,
-using three different models:
+using four different models:
 SDSS method, Polynomial method, 
-and PSF fitting method.
+and Round PSF fitting method, and 
+Elliptical PSF fitting.
 
-Dependencies: numpy, profile.py,
-              poly.py, sdss.py
+Dependencies: numpy
+              
 Author: Mohammadjavad Vakili (July and August 2014)
 """
 

### 2014-08-21 src/__init__.py
Update __init__.py

@@ -1,5 +1,5 @@
 """
 A module interface to shapelet functions
 """
-import fitting, poly, profile, sdss
+import efitting, fitting, poly, profile, sdss
 

### 2014-08-21 src/efitting.py
Create efitting.py

@@ -1,0 +1,41 @@
+import numpy as np
+import scipy.optimize as op
+
+def Moffat(data , FWHM , b , e , x0 , y0 , x , y ):
+   
+    
+    a = FWHM/(2.*np.sqrt(2**(1./b) - 1.))
+    r = ((x-x0)**2. + ((y-y0)**2.)*(1. + np.abs(e))**2./(1. - np.abs(e))**2.)**.5
+    return ((b - 1.)*(1. + (r/a)**2.)**(-1.*b))/(a*np.pi)
+
+
+
+def lnlike(theta , I , x , y):
+
+    FWHM , b , e , x0 , y0 = theta
+    model = Moffat(I , FWHM , b, e , x0 , y0 , x ,y)
+    inv_sigma2 = 1.
+    return -0.5*(np.sum((I-model)**2*inv_sigma2 - np.log(inv_sigma2)))
+
+
+
+def fitting_centroid(I):
+    size = I.shape[0]
+    x = np.linspace(0.5, size - .5, size)
+    y = x[:,np.newaxis]
+    FWHM_true = I.shape[0]/4.
+    b_true = 2.5
+    e_true = 0.1
+    x0_true = I.shape[0]/2.
+    y0_true = I.shape[0]/2.
+    size = I.shape[0]
+    x = np.linspace(0.5, size - .5, size)
+    y = x[:,np.newaxis]
+    nll = lambda *args: -lnlike(*args)
+    results = op.minimize(nll , [FWHM_true , b_true , e_true , x0_true , y0_true] , args = (I , x , y))
+    FWHM_ml , b_ml , e_ml , x0_ml , y0_ml = results["x"]
+
+    return x0_ml , y0_ml
+
+if __name__ == "__main__":
+    print 'efitting main'

### 2014-08-21 src/sdss.py
Update sdss.py

@@ -95,7 +95,7 @@ def lupton_2d(I , f , s):
 def BP(data , f):
 
   size = data.shape[0]
-  zero = size/2
+  zero = size/2 + .5
   kernel = profile.makeGaussian(17 , f , 0 , np.array([zero,zero]))
   smoothed_image = signal.convolve2d(data , kernel , mode = "same")
   data = smoothed_image/np.sum(smoothed_image)
@@ -125,7 +125,7 @@ def sdss_centroid(data , f , sigma):
 
   """
   size = data.shape[0]
-  zero = size/2
+  zero = size/2 + .5
   kernel = profile.makeGaussian(size , f , 0 , np.array([zero,zero]))
   
   smoothed_image = signal.convolve2d(data , kernel , mode = "same")

### 2014-08-25 ms/figure.tex
Update figure.tex

@@
 \usepackage{color}
+\usepackage{morefloats}
 \definecolor{darkred}{rgb}{0.5,0,0}
@@
 We present a 3$\times$3 method for estimating the centroid of stars in astronomical images.
-After simulating a large number of stars in a wide range of scales, both in signal-to-noise-ratio and full width at half maxima, we compare the results of our model to those obtained from the centroiding method implemented in
+After simulating a large number of stars in a wide range of scales, in signal-to-noise-ratio, full width at half maxima, and ellipticity, we compare the results of our model to those obtained from the centroiding method implemented in
 SDSS photometric pipeline, as well as $\chi^{2}$ PSF fitting.
-Comparison of the median centroid error, binned on signal-to-noise-ratio, resulting from the proposed technique to the Cramer-Rao lower bound on the variance of centroid estimates, suggests that, the 3$\times$3 polynomial hack provides accurate estimates of centroid in certain subsets of the parameter space, and that SDSS trick is able to deliver an unbiased estimate in a wide range of parameters.
+Comparison of the median centroid bias, binned on signal-to-noise-ratio, resulting from the proposed technique to the Cramer-Rao lower bound on the variance of centroid estimates, suggests that, the 3$\times$3 polynomial trick, once modified by smoothing the image with a Gaussian kernel, is able to deliver unbiased estimates of centroid at a wide range of values in the parameter space.
+Furthermore, we show that at low signal-to-noise-ratios, the unmodified polynomial method gives rise bias on centroid estimate comparable to the Cramer-Rao lower bound.
 
@@
 
-In order to find the centroid of a star, we fit a simple 2d polynomial $I(x,y)=a+bx+cy+dx^2+exy+fy^2$ to the $3\times3$ patch centered on the brightest pixel of the
-image. Upon constructing a universal 9$\times$6 design matrix
-\[
-A=
+In order to find the centroid of a star, we fit a simple 2d polynomial $P(x,y)=a+bx+cy+dx^2+exy+fy^2$ to the $3\times3$ patch centered on the brightest pixel of the
+image.
+We apply this method to star images in the sky-dominated regime.
+In this regime, the covariance matrix of pixel uncertianties is given by $\sigma^{2}\mathbf{I}$, where $\sigma^{2}$ is variance of the uncorrelated Gaussian noise, and $\mathbf{I}$ is a 9$\times$9 identity matrix.
+Upon constructing a universal 9$\times$6 design matrix
+
+\begin{equation}
+    \mathbf{A} = 
     \begin{bmatrix}
-    1 & x_{1} & y_{1} & x_{1}^{2} & x_{1}y_{1} & y_{1}^{2}\\
+        1 & x_{1} & y_{1} & x_{1}^{2} & x_{1}y_{1} & y_{1}^{2} \\
         . & . & . & . & . & .  \\
@@
         . & . & . & . & . & .  \\
-    1 & x_{9} & y_{9} & x_{9}^{2} & x_{9}y_{9} & y_{9}^{2}\\
+        1 & x_{9} & y_{9} & x_{9}^{2} & x_{9}y_{9} & y_{9}^{2}
     \end{bmatrix},
-\]
+\end{equation}
+
 the free parameters of the model $\{a,b,c,d,e,f\}$ (hereafter compactly denoted by $\mathbf{X}$) can be determined by 
 \beq
-\mathbf{X} = (A^{T}A)^{-1}A^{T}\mathbf{Z},
+\mathbf{X} = (\mathbf{A}^{T}\mathbf{A})^{-1}\mathbf{A}^{T}\mathbf{Z},
+\label{linearfit}
 \eeq
-where $\mathbf{Z}$ is given by $(I_{1},...,I_{9})^{T}$, with $I_{i}$ denoting the brightness of the $i-$th pixel. Afterwards, the best fit parameters can be used to compute the centroid coordinate
-\[
+where $\mathbf{Z}$ is given by $(I_{1},...,I_{9})^{T}$, with $I_{i}$, denotes the brightness of the $i-$th pixel. Afterwards, the best fit parameters can be used to compute the centroid coordinate
+
+\beq
   \begin{bmatrix}
@@
       y_{c}\\
-  \end{bmatrix} = \begin{bmatrix}
+  \end{bmatrix} = 
+  \begin{bmatrix}
       2d & e\\
       e & 2f\\
-  \end{bmatrix}^{-1}\begin{bmatrix}
+  \end{bmatrix}^{-1}
+  \begin{bmatrix}
       -b\\
@@
   \end{bmatrix}.
-\]
-
-Let us smooth the image of the star with a Gaussian PSF with a FWHM equal to that of PSF at that location.
-Now Consider any row or column of the 3$\times$3 patch around the brightest pixel of the smooth image and let us denote the brightness of these three pixels by $\{f_{-},f_{0},f_{+}\}$.
-The fundamental assumption behind the model implemented in SDSS photometric pipeline \citep{sdss} is that these brightness values are in fact the function $f(x) = A\exp((x-x_{c})^{2}/2\beta^{2})$ evaluated at $x=-1,0,+1$; with $x_{c}$ being the position of centroid.
-Knowing the value of $f$ at $\{-1,0,1\}$, expanding $f(x)$ up to fourth order in $x$ leads to
-\beq
-x = \frac{s}{d}(1+k\frac{d}{4A}(1-(s/d)^{2})),
-\eeq
-where $k \simeq 4/3$, and
-\beq
-\begin{array}{l}
-s:=(f_{+}-f_{0})/2, \nonumber\\
-d:=2f_{0} - (f_{+}+f_{0}), \nonumber\\
-A = f_{0} +s^{2}/2d.
-\label{def}
-\end{array}
+\label{center}
 \eeq
 
-Now if we apply this method to every column and row of the 3$\times$3 patch, we will find three local maxima for three rows $\{(x_{-},-1), (x_{0},0),(x_{+},1)\}$, and three local maxima for three columns $\{(-1,y_{-}), (0,y_{0}),(1,y_{+})\}$.
-It is important to note that since the image has been smoothed, the covariance matrix between different pixels is not zero.
+Now, we modify the polynomial method by smoothing the image of the star with a Gaussian kernel whose FWHM is equal to that of PSF at that location of image.
+Then we apply the same polynomial method to the 3$\times$3 patch around the brightest pixel of the smoothed image.
+The important difference between the previous approach and the modified method is that, there are non-zero covariances among the uncertainties of brightness of the different pixels of the smoothed image.
+That is, the covariance matrix $\mathbf{C}$ is non-diagonal.
+It can be shown that after smoothing, elements of the covariance matrix are given by
+
+\begin{eqnarray}
+\mathbf{C}_{ij} &=& \frac{\sigma^{2}}{4\pi w^{2}} \exp(-\frac{r_{ij}^{2}}{4\pi w^{2}}),\\
+r_{ij}^{2} &=& (x_{i} - x_{j})^{2} + (y_{i} - y_{j})^{2},
+\end{eqnarray}
+where $w$ is the FWHM of star, and $x_{i}$ , $y_{i}$ are the $x$, and $y$ coordinates of the $i$-th pixel respectively.
+In the presence of the non-diagonal covariance matrix $\mathbf{C}$, equation (\ref{linearfit}) needs to be modified in the following way
+\beq
+\mathbf{X} = [\mathbf{A}^{T}\mathbf{C}^{-1}\mathbf{A}]^{-1}[\mathbf{A}^{T}\mathbf{C}^{-1}\mathbf{Z}].
+\label{linearfit2}
+\eeq
+
+Therefore, for a given star and its corresponding smoothing kernel, the outcome of equation (\ref{linearfit2}) can be plugged into equation (\ref{center}) to find the centroid estimate of the star.
+Hereafter, we call this method the modified polynomial method.
+
+Now, let us give a brief overview of centroiding method implemented in SDSS photometric pipeline \citep{sdss}: Consider any row or column of the 3$\times$3 patch around the brightest pixel of the smooth image and let us denote the brightness of these three pixels by $\{I_{-},I_{0},I_{+}\}$.
+The fundamental assumption behind the model is that these brightness values are in fact the function $P(x) = Q\exp((x-x_{c})^{2}/2\beta^{2})$ evaluated at $x=-1,0,+1$; with $x_{c}$ being the position of centroid.
+Knowing the value of $P$ at $\{-1,0,1\}$, expanding $P(x)$ up to fourth order in $x$ leads to
+\beq
+x = \frac{s}{t}(1+k\frac{t}{4Q}(1-(s/t)^{2})),
+\eeq
+where k = 1.33, and
+
+\begin{eqnarray}
+s&=&(I_{+}-I_{-})/2, \\
+t &=&2I_{0} - (I_{+}+I_{-}), \\
+Q &=& I_{0} +s^{2}/2t.
+\label{def}
+\end{eqnarray}
+
+If we apply this method to every column and row of the 3$\times$3 patch around the brightest pixel of the smoothed image, we will find three local maxima for three rows $\{(x_{-},-1)$, $(x_{0},0)$, $(x_{+},1)\}$, and three local maxima for three columns $\{(-1,y_{-})$, $(0,y_{0})$, $(1,y_{+})\}$.
+It is important to note that, since the image has been smoothed, the covariance matrix between different pixels is not zero.
 Therefore, there is an uncertianty associated with any of these local maxima.
-Then, the centroid is estimated by finding the intersection of a line fitted to three maxima corresponding to rows, and another curve fitted to three maxima corresponding to columns.
-Figure [\ref{ex}] demonstrates the performances of the discussed models in centroiding simulated stars with known true centroids.
+The centroid is then estimated by finding the intersection of a line fitted to three maxima corresponding to rows, and another curve fitted to three maxima corresponding to columns.
+
+Figures [\ref{ex}] demonstrates the performances of the modified polynomial, and SDSS method in centroiding the simulated stars with known true centroids.
 
@@
 \beq
-I(r) = \frac{f(\beta -1)}{\pi \alpha^{2}}[1+(r/\alpha)^{2}]^{-\beta},
+P(r) = \frac{F(\beta -1)}{\pi \alpha^{2}}[1+(r/\alpha)^{2}]^{-\beta},
 \label{mof}
 \eeq
-where $f$ is the total flux, and $\alpha$ is the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$) being $2\alpha\sqrt{2^{1/\beta}-1}$.
+where $F$ is the total flux, $\beta$ is a dimensionless paramter, and $\alpha$ is the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$) being $2\alpha\sqrt{2^{1/\beta}-1}$.
 The radial light profile of the stars generated in our simulations are shown in Figure[\ref{moffat}].
@@
 Per pixel uncertainties are assumed to be uncorrelated Gaussian (resulting in a diagonal covariance matrix), and we only study the sky dominated regime.
-Therefore the covariance matrix is simply given by $\sigma^{2}I$.
 
@@
 
-In this work, we study the relation between error in centroid measurement and $\gamma$ at fixed $S/N$ and vice versa.
-In the first experiment, we generate Moffat profiles centered randomly in the sub-pixel region inside the central pixel of a 17$\times$17 image, at four different full width at half maxima of 2, 2.8, 4, and 5.6 pixels with signal-to-noise ratio ranging from 5 to 150.
-In the second experiment, we generate Moffat profiles with $\gamma$ ranging from 2 to 6, with four different signal-to-noise-ratios of 5, 50, 100, 150.
+In this work, we study the relation between bias in centroid measurement and $\gamma$ at fixed $S/N$ and vice versa.
+In the first experiment, we generate Moffat profiles centered randomly in the sub-pixel region inside the central pixel of a 17$\times$17 image, at four different full width at half maxima of 2, 2.8, 4, and 5.6 pixels with signal-to-noise ratio ranging from 10 to 150.
+In the second experiment, we generate Moffat profiles with $\gamma$ ranging from 2 to 6, with four different signal-to-noise-ratios of 10, 50, 100, 150.
 
-In addition to the two centroiding method discussed in the previous sections, we compute the error in centroid measurement from fitting the exact analytic PSF model to the data by minimizing $\chi^{2}$.
-In both experiments, we compare the error with the quantity
+In addition to the centroiding methods discussed in the previous sections, we compute the bias in centroid measurement from, $(i)$ fitting the exact analytic PSF model and $(ii)$ fitting a round PSF to the data by minimizing $\chi^{2}$.
+In both experiments, we compare the bias with the quantity
 
@@
 
-In order to do so, after computing the error $\Delta x = \sqrt{(x_{t}-x_{c})^2 + (y_{t}-y_{c})^2}$ for each model, we compute the median in bins of $S/N$.
-The closer the median error is to $\rho$, the less biased the centroid estimate is.
+In order to do so, after computing the bias $\Delta x = \sqrt{(x_{t}-x_{c})^2 + (y_{t}-y_{c})^2}$ for each model, we compute the median in bins of $S/N$.
+The closer the median bias is to $\rho$, the less biased the centroid estimate is.
 This quantity is, in fact, the Cramer-Rao lower bound (hereafter CRLB).
@@
 
-where here $\theta$ is the centroid coordinate, and the dependence of likelihood on centroid $\theta$ comes through (\ref{mof}).
+where $\theta$ compactly denotes the centroid coordinate, and the dependence of likelihood on centroid $\theta$ comes through (\ref{mof}).
 Taking the derivative of the log-likelihood w.r.t the centroid coordiantes, yields
@@
 
-Theoretically, we expect the median error resulting from the exact PSF fitting method to be arbitrarily close to CRLB.
+Theoretically, we expect the median bias resulting from the exact PSF fitting method to be arbitrarily close to CRLB.
 This is due to the fact that, we find the centroid by fitting the model that used to generate the data.
@@
 
-Results of the first experiment are shown in Figures[\ref{1}], [\ref{2}], [\ref{22}], [\ref{3}].
-As we expected, for all three methods, median error gets larger for fainter stars.
-This error is even larger as $\gamma$ gets larger.
-In order to have a better understanding of the performance of these models, the plots are made in logarithmic scale.
-As it can be seen in [\ref{3}], the difference between the median error and the CRLB (hereafter denoted by $\Delta$) in the case of PSF fitting is quite negligible.
-Furthermore, it is evident that in the case of 3$\times$3 polynomial method [\ref{1}], there are certain ranges of signal-to-noise ratio, where $\Delta$ is bigger than the one obtained from SDSS trick [\ref{2}], when we center the smoothing kernel on the center of the brightest pixel of the star, for different values of $\gamma$.
-On the other hand, when the smoothing kernel in the SDSS method [\ref{22}], is centered on the true centroid, the resulting bias is relatively close to CRLB.
-Moreover, $\Delta$ shrinks significantly, as $\gamma$ becomes smaller.
+Results of the first experiment, in the case of zero ellipticity, are shown in Figures [\ref{1}], [\ref{4}], [\ref{7}], [\ref{10}], and [\ref{13}].
+As we expected, for all methods, median bias becomes larger for fainter stars.
+This bias is even larger as $\gamma$ gets larger.
+As it can be seen in figures [\ref{10}] and [\ref{13}], the difference between the median bias and the CRLB (hereafter denoted by $\Delta$) in the case of PSF fitting is quite negligible.
+Furthermore, it is evident that in the case of 3$\times$3 polynomial method [\ref{1}], there are certain ranges of signal-to-noise ratio (higher than 10), where $\Delta$ is bigger than the one obtained from SDSS trick [\ref{7}].
+However, in a wide range of $\gamma$, and $S/N$, the bias from the modified polynomial method [\ref{4}] is comparable to that of SDSS method.
 
-We repeat the same experiment, this time assigning random ellipticities between 0 and 0.2 to the simulated stars.
-We did not observe any particular change in the behavior of error as a function of signal-to-noise-ratio for the polynomial (Figure [\ref{111}]).
-However, as can be seen in figure [\ref{222}], centroiding elliptical Moffat profiles with the SDSS method in the presence of noise, results in relatively larger errors.
+We repeat the same experiment, this time with assigning non-zero ellipticities of 0.1, and 0.2 to the simulated stars.
+We keep the orientation of all stars fixed.
+As it can be seen, in figures [\ref{2}],[\ref{3}],[\ref{5}],[\ref{6}],[\ref{8}],[\ref{9}],[\ref{11}],[\ref{12}],[\ref{14}],[\ref{15}], centroid measurements of stars with smaller $\gamma$ give rise to larger bias than the centroid measurements of stars with bigger $\gamma$.
 
@@
 
-Behavior of $\Delta x$ as a function of $\gamma$ for different values of $S/N$ is shown in Figures [\ref{4}], [\ref{5}], [\ref{6}].
+Behavior of bias as a function of $\gamma$ for different values of $S/N$, and different ellipticities, is shown in figures [\ref{16}], [\ref{17}], [\ref{18}], [\ref{19}], [\ref{20}], [\ref{21}], [\ref{22}], [\ref{23}], [\ref{24}], [\ref{25}], [\ref{26}], [\ref{27}], [\ref{28}], [\ref{29}], [\ref{30}].
 Again, by decreasing noise level of the background sky, $\Delta x$ becomes smaller at all ranges of $\gamma$.
-Interestingly, as observed in results of both methods, in the cases of $S/N = 100, 150$, $\Delta x$ does not increase with $\gamma$ monotonically.
-In fact, there exist a minimum error around $\gamma$ $\sim$ 3 pixels.
-Also, at $S/N = 5$, where the image of stars are dominated by noise, we do not observe any considerable variation in $\Delta x$.
+Also, in the case of non-zero ellipticities, again, we observe that centroiding stars with smaller $\gamma$ leads to larger bias.
 
-\subsection{Experiment 3}
-
-In the last experiment, we study bias as a function of the ellipticity of the simulated stars for different values of $\gamma$, and signal-to-noise-ratio.
-As it can be seen in Figures [\ref{7}], [\ref{8}], [\ref{9}], the variation of bias with ellipticity is almost negligible for all three methods.
-Furthermore, the bias arising from the SDSS method is slightly higher than the one obtained from the polynomial method at $\gamma = 4$.
+Interstingly, at $S/N=10$, the bias from the polynomial method, is fairly comparable to CRLB at all three ellipticities.
+At higher $S/N$ however, the bias from the polynomial method is significantly larger than CRLB [\ref{16}], [\ref{17}], [\ref{18}].
+On the other hand, the bias from the modified polynomial methods (see figures [\ref{19}], [\ref{20}], [\ref{21}]), and SDSS method (see figures [\ref{22}], [\ref{23}], [\ref{24}]), are smaller than that of polynomial method in signal-to-noise-ratios higher than 10, and in a wide range of $\gamma$.
 
@@
 
-In this work, we proposed a method for centroiding stars based on a 3$\times$3 method.
+In this work, we proposed a method for centroiding stars based on fitting a low order polynomial to a 3$\times$3 patch of star images.
 Employing this technique into large scale astronomical surveys can considerably reduce the computational cost of initial astrometry of these surveys.
-This method can be roughly thousand times faster than centroiding through model fitting.
-The advantage of this method becomes more pronounced in PSF estimation in which all we need as an input is the centroid of stars and some lower dimensional representation of the postage stamp of stars.
+The advantage of this method becomes more pronounced in PSF estimation in which we need to estimate the centroid of stars, and we can compute these estimates with a few number of algebraic operations.
 
-Comparison of this method with centroiding method of SDSS photo pipeline suggests that there are ranges of size and noise level in which, the error arising from this method is close to the theoretically set CRLB than the error obtained from SDSS method.
-However, in a wide range of scales, the error from SDSS trick is relatively smaller.
+This method can be roughly thousand times faster than centroiding through model fitting, and requires fewer operations than the method implemented in SDSS photo pipeline.
+Moreover, we presented a modified version of the model, in which before applying the polynomial fitting, we smooth the image with a Gaussian kernel.
+Comparison of the modified method with centroiding method of SDSS photo pipeline suggests that in wide ranges of size and noise level of the background sky, the bias arising from this method is close to the theoretically set CRLB, and comparable to, ans in some cases smaller than, the bias obtained from SDSS method.
 
-However, it is important to note that, at the very faint end of stars, the bias resulting from both method can be significantly large.
-This can be largely attributed to the fact that any estimate obtained from this method, tends to be inside the brightest pixel of the image, which is not necessarily the case for the true centroid when the signal-to-noise-ratio is low.
+However, it is important to note that, without smoothing the image, the bias from the polynomial method can be larger.
+This can be attributed to the fact that any estimate obtained from application of this method to the smoothed image, tends to make use of more information about the brightness of the pixels out of the 3$\times$3
+patch around the brightest pixel of the original image.
 
-The advantage of SDSS trick over the polynomial model is that, it assumes a more realistic model for the light profile of stars.
-On the other hand, in order for this model to achieve significantly better results, one has to estimate the FWHM of the star in advance.
-
-Furthermore, in this investigation we narrowed our focus on data simulated from a very specific model.
+In this investigation we narrowed our focus on a set of data simulated from a very specific model.
 Although there are various cases where Moffat profiles provide reasonable representation of point spread function, these models are not generic enough to let us reach a more general conclusion.
-
 Another important, and untapped, area of study would be devising a model that infers the centroid of stars and point spread function (in its full extent, not at the catalog level) across an astronomical image simultaneously.
@@
 \minipage{.5\textwidth}
-  \includegraphics[width=\linewidth]{exaple_cen0.png}
+  \includegraphics[width=\linewidth]{4025.pdf}
 \endminipage
 \minipage{.5\textwidth}
-  \includegraphics[width=\linewidth]{example_cen1.png}
+  \includegraphics[width=\linewidth]{4050.pdf}
 \endminipage
-\caption{Demonstration of the performance of SDSS and polynomial method on finding the centroid on the 3$\times$3 patch around the brightest pixel, with the true centroid, and centroid estimate from the polynomial method markerd by $+$, $\wedge$ respectively; and the centroid estimate from SDSS trick (shown by $\star$) given by the intersection of two curves.}\label{ex}
+
+\minipage{.5\textwidth}
+  \includegraphics[width=\linewidth]{10025.pdf}
+\endminipage
+\minipage{.5\textwidth}
+  \includegraphics[width=\linewidth]{10050.pdf}
+\endminipage
+\caption{Demonstration of the performance of SDSS and modified polynomial method on finding the centroid around the brightest pixel, from top to bottom, and from left to right: for a star image with $S/N=40$ and $\gamma = 2.5$, $S/N=40$ and $\gamma = 5$, $S/N=100$ and $\gamma = 2.5$, and $S/N=100$ and $\gamma = 5$.
+In each plot, the true centroid, and the centroid estimate from the modified polynomial method are markerd by $*$, $\wedge$ respectively; and the centroid estimate from SDSS trick is given by intersection of the two curves.}\label{ex}
 \end{figure}
@@
 \minipage{1\textwidth}
-  \includegraphics[width=\linewidth]{map_20_50.png}
+\includegraphics[width=\linewidth]{map-1000-5.png}
 \endminipage
@@
 \minipage{1\textwidth}
-  \includegraphics[width=\linewidth]{map_4_50.png}
+\includegraphics[width=\linewidth]{map-100-5.png}
 \endminipage
-\caption{Demonstration of the centroid bias resulting from: \emph{left}: polynomial, and \emph{right}: SDSS tricks as a function of subpixel position of centroid.
-Top  (bottom) color maps are obtained from taking the median bias of different noise realization of a Moffat profiles with FWHM = 2 (4) pixels, and signal-to-noise of 50.}\label{map}
+\caption{Demonstration of the centroid bias resulting from \emph{left}: the modified polynomial method, and \emph{right}: SDSS method applied to Moffat profiles with $\gamma=5$ pixels, as a function of subpixel position of centroid.
+Top, and bottom maps are obtained from taking the median bias of different noise realization of a simulated star with signal-to-noise-ratio of 10$^{3}$, and 10$^{2}$ respectively.}\label{map}
 \end{figure}
@@
 \minipage{1\textwidth}
-  \includegraphics[width=\linewidth]{map_2_100.png}
+  \includegraphics[width=\linewidth]{map-1000-25.png}
 \endminipage
@@
 \minipage{1\textwidth}
-  \includegraphics[width=\linewidth]{map_4_10.png}
+  \includegraphics[width=\linewidth]{map-100-25.png}
 \endminipage
-\caption{Demonstration of the centroid bias resulting from: \emph{left}: polynomial, and \emph{right}: SDSS tricks as a function of subpixel position of centroid.
-Top  (bottom) color maps are obtained from taking the median bias of different noise realization of a Moffat profiles with FWHM = 2 (4) pixels, and signal-to-noise of 10.}\label{map2}
+\caption{Demonstration of the centroid bias resulting from \emph{left}: the modified polynomial method, and \emph{right}: SDSS method applied to Moffat profiles with $\gamma=2.5$ pixels, as a function of subpixel position of centroid.
+Top, and bottom maps are obtained from taking the median bias of different noise realization of a simulated star with signal-to-noise-ratio of 10$^{3}$, and 10$^{2}$ respectively.}\label{map}
 \end{figure}
@@
  \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{poly_snr.png}
+  \includegraphics[width=\linewidth]{poly_bias(snr)_e=00.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from polynomial method and the signal-to-noise ratio of stars with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{1}
+\caption{Scatter plots showing the relation between bias in centroid measurement from the polynomial method and the signal-to-noise ratio of stars with $e=0$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{1}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{sdss_without_knowing_true_pixel.png}
+  \includegraphics[width=\linewidth]{poly_bias(snr)_e=01.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from SDSS method, when the center of the smoothing kernel is the center of the brightest pixel of star, and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{2}
+\caption{Scatter plots showing the relation between bias in centroid measurement from the polynomial method and the signal-to-noise ratio of stars with $e=0.1$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{2}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{sdss_fwhm_true_pixel.png}
+  \includegraphics[width=\linewidth]{poly_bias(snr)_e=02.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from SDSS method, when the center of the smoothing kernel is the true centroid of star, and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{22}
+\caption{Scatter plots showing the relation between bias in centroid measurement from the polynomial method and the signal-to-noise ratio of stars with $e=0.2$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{3}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{psf_snr.png}
+  \includegraphics[width=\linewidth]{smoothpoly_bias(snr)_e=00.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from PSF fitting method and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{3}
+\caption{Scatter plots showing the relation between bias in centroid measurement from the modified polynomial method and the signal-to-noise ratio of stars with $e=0$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{4}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{epoly_fwhm.png}
+  \includegraphics[width=\linewidth]{smoothpoly_bias(snr)_e=01.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement of elliptical PSF profiles from polynomial method and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{111}
+\caption{Scatter plots showing the relation between bias in centroid measurement from the modified polynomial method and the signal-to-noise ratio of stars with $e=0.1$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{5}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{esdss_fwhm_notruth.png}
+  \includegraphics[width=\linewidth]{smoothpoly_bias(snr)_e=02.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement of elliptical PSF profiles from SDSS method and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{222}
+\caption{Scatter plots showing the relation between bias in centroid measurement from the modified polynomial method and the signal-to-noise ratio of stars with $e=0.2$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{6}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{poly_fwhm.png}
+  \includegraphics[width=\linewidth]{sdss_bias(snr)_e=00.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from polynomial method and the FWHM of stars with signal-to-noise-ratio of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
-In each scatter plot, the blue line represents the median of data points, and the green line represents $\rho$.}\label{4}
+\caption{Scatter plots showing the relation between bias in centroid measurement from the SDSS method and the signal-to-noise ratio of stars with $e=0$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{7}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{sdss_fwhm.png}
+  \includegraphics[width=\linewidth]{sdss_bias(snr)_e=01.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from SDSS method and the FWHM of stars with signal-to-noise-ratio of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
-In each scatter plot, the blue line represents the median of data points, and the green line represents $\rho$.}\label{5}
+\caption{Scatter plots showing the relation between bias in centroid measurement from the SDSS method and the signal-to-noise ratio of stars with $e=0.1$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{8}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{psf_fwhm.png}
+  \includegraphics[width=\linewidth]{sdss_bias(snr)_e=02.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from PSF fitting method and the FWHM of stars with signal-to-noise-ratio of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
-In each scatter plot, the blue line represents the median of data points, and the green line represents $\rho$.}\label{6}
+\caption{Scatter plots showing the relation between bias in centroid measurement from the SDSS method and the signal-to-noise ratio of stars with $e=0.2$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{9}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{poly_ellipticity.png}
+  \includegraphics[width=\linewidth]{roundpsf_bias(snr)_e=00.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the polynomial method and the ellipticity of stars with ($S/N$, $\gamma$) of : (100, 2) (upper left), (20, 2) (upper right), (100, 4) (lower left), and (20, 4) (lower right).
-In each scatter plot, the blue line represents the median of data points.}\label{7}
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting a round PSF to stars, and the signal-to-noise ratio of stars with $e=0$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{10}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{sdss_ellipticity.png}
+  \includegraphics[width=\linewidth]{roundpsf_bias(snr)_e=01.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the sdss method and the ellipticity of stars with ($S/N$, $\gamma$) of : (100, 2) (upper left), (20, 2) (upper right), (100, 4) (lower left), and (20, 4) (lower right).
-In each scatter plot, the blue line represents the median of data points.}\label{8}
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting a round PSF to stars, and the signal-to-noise ratio of stars with $e=0.1$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{11}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{psf_ellipticity.png}
+  \includegraphics[width=\linewidth]{roundpsf_bias(snr)_e=02.pdf}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the PSF fitting method and the ellipticity of stars with ($S/N$, $\gamma$) of : (100, 2) (upper left), (20, 2) (upper right), (100, 4) (lower left), and (20, 4) (lower right).
-In each scatter plot, the blue line represents the median of data points.}\label{9}
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting a round PSF to stars, and the signal-to-noise ratio of stars with $e=0.2$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{12}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{ellipticalpsf_bias(snr)_e=00.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting an elliptical PSF to stars, and the signal-to-noise ratio of stars with $e=0$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{13}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{ellipticalpsf_bias(snr)_e=01.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting an elliptical PSF to stars, and the signal-to-noise ratio of stars with $e=0.1$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{14}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{ellipticalpsf_bias(snr)_e=02.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting an elliptical PSF to stars, and the signal-to-noise ratio of stars with $e=0.2$, and FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{15}
+\end{figure}
+
+\begin{figure}[!htb]
+
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{poly_bias(fwhm)_e=00.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from the polynomial method and FWHM of stars with $e=0$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{16}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{poly_bias(fwhm)_e=01.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from the polynomial method and FWHM of stars with $e=0.1$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{17}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{poly_bias(fwhm)_e=02.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from the polynomial method and FWHM of stars with $e=0.2$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{18}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{smoothpoly_bias(fwhm)_e=00.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from the modified polynomial method and FWHM of stars with $e=0$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{19}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{smoothpoly_bias(fwhm)_e=01.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from the modified polynomial method and FWHM of stars with $e=0.1$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{20}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{smoothpoly_bias(fwhm)_e=02.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from the modified polynomial method and FWHM of stars with $e=0.2$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{21}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{sdss_bias(fwhm)_e=00.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from the SDSS method and FWHM of stars with $e=0$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{22}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{sdss_bias(fwhm)_e=01.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from the SDSS method and FWHM of stars with $e=0.1$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{23}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{sdss_bias(fwhm)_e=02.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from the SDSS method and FWHM of stars with $e=0.2$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{24}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{roundpsf_bias(fwhm)_e=00.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting a round PSF to stars, and FWHM of stars with $e=0$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{25}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{roundpsf_bias(fwhm)_e=01.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting a round PSF to stars, and FWHM of stars with $e=0.1$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{26}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{roundpsf_bias(fwhm)_e=02.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting a round PSF to stars, and FWHM of stars with $e=0.2$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{27}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{ellipticalpsf_bias(fwhm)_e=00.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting an elliptical PSF to stars, and FWHM of stars with $e=0$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{28}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{ellipticalpsf_bias(fwhm)_e=01.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting an elliptical PSF to stars, and FWHM of stars with $e=0.1$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{29}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{ellipticalpsf_bias(fwhm)_e=02.pdf}
+\endminipage
+\caption{Scatter plots showing the relation between bias in centroid measurement from fitting an elliptical PSF to stars, and FWHM of stars with $e=0.2$, with $S/N$  of : 10 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green dashed line represents $\rho$.}\label{30}
 \end{figure}

### 2014-12-01 src/spoly.py
Update spoly.py

@@ -88,7 +88,7 @@ def spoly_centroid(data , A , f , sigma):
   
   image = smoothed_image#/np.sum(smoothed_image)
   
-  bp = np.where((image==image.max())) #brightest pixel in the smoothed image
+  bp = np.where(image==image.max()) #brightest pixel in the smoothed image
   cen = [bp[1][0] , bp[0][0]]
 
   k = image[cen[1]-1:cen[1]+2,cen[0]-1:cen[0]+2]
@@ -101,11 +101,12 @@ def spoly_centroid(data , A , f , sigma):
   
      a , b , c, d , e , f = X
      matrix = np.array([[2.*d , e],[e , 2.*f]])
-     #matrix = matrix + (np.max(np.abs(matrix))/10.)*np.array([[1,0],[0,1]])
-     
+     #matrix = matrix + (np.max(np.abs(matrix))/1000.)*np.array([[1,0],[0,1]])
+     matrix = matrix + (sigma/1000.)*np.array([[1,0],[0,1]])
      vector = np.array([-1.*b , -1.*c])
      center = np.dot(np.linalg.inv(matrix) , vector)
      #center = (c*e - b*f)/(2.*d*f - 2.*e**2.) , (b*e - c*d)/(2.*d*f - 2.*e**2.)   
   return np.array(cen) + np.array([.5,.5]) + center
 
 if __name__ == "__main__":
+    print 'spoly main'

### 2014-12-01 ms/figure.tex
Update figure.tex

--- 2014-08-18 ms/figure.tex
@@
 We present a 3$\times$3 method for estimating the centroid of stars in astronomical images.
-After simulating a large number of stars in a wide range of scales, both in signal-to-noise-ratio and full width at half maxima, we compare the results of our model to those obtained from the centroiding method implemented in
-SDSS photometric pipeline, as well as $\chi^{2}$ PSF fitting.
-Comparison of the median centroid error, binned on signal-to-noise-ratio, resulting from the proposed technique to the Cramer-Rao lower bound on the variance of centroid estimates, suggests that, the 3$\times$3 polynomial hack provides accurate estimates of centroid in certain subsets of the parameter space, and that SDSS trick is able to deliver an unbiased estimate in a wide range of parameters.
+After simulating a large number of stars in a wide range of scales, in signal-to-noise-ratio, and full width at half maxima, we compare the results of our method to those obtained from the fourth order approximation method implemented in SDSS photometric pipeline, as well as finding the centroid by fitting the exact PSF model used to generate the simulated data.
+Comparison of the median squared error in centroid measurement, resulting from the proposed techniques to the Cramer-Rao lower bound of centroid estimates, suggests that, the 3$\times$3 polynomial trick, once modified by smoothing the image with a Gaussian kernel, is able to deliver sufficiently accurate estimates of centroid over a wide range of values in the parameter space.
 
@@
 A common practice in astronomy is taking imaging data, and then finding the coordinates of various light sources across the sky.
-Having access to unbiased estimate of the center of point sources, convolved with telescope point spread function (and atmospheric PSF in case of ground based telescopes) and pixel response function, is crucial in further steps of astronomical image processing.
+Finding unbiased estimate of the center of point sources, convolved with telescope point spread function (and atmospheric PSF in case of ground based telescopes) and pixel response function, is crucial to further steps of astronomical image processing.
 For instance, proper measurement of the shape of galaxies requires interpolating the PSF from the position of sparsely located stars across the image to the position of galaxies.
@@
 
-Reaching the optimal precision however, is limited by the presence of noise; both sky noise and CCD readout noise.
+Reaching the optimal measurement of the centroid of stars however, is limited by the lack of knowledge about the exact shape of PSF, and also presence of noise; both sky noise and CCD readout noise.
 Variance of the centroid estimate, will always have a theoretically set lower bound, known as the Cramer-Rao lower bound (hereafter denoted by CRLB) which has an inverse relation with the signal-to-noise-ratio.
-Thus, of particular interest is devising a fast method that returns less biased estimate of centroids especially in a realistic range of signal-to-noise ratios.
+Thus, of particular interest is devising a fast method that returns less biased estimate of centroids in a realistic range of signal-to-noise ratios.
 
@@
 
-In this paper, we propose to find the centroid of stars by fitting a second order polynomial to the $3\times3$ pixels around the brightest pixel of stars.
-We focus on studying the accuracy of this model by comparing the centroid measurement errors with the ones obtained from the method used in SDSS.
+In this paper, we propose to find the centroid of stars by smoothing the image of stars by a Gaussian kernel, and fitting a second order polynomial to the $3\times3$ pixels around the brightest pixel of smoothed image.
+We focus on studying the accuracy of this model by comparing the centroid measurement errors with the ones obtained from the approximate method used in SDSS.
 In order to do so, we apply these methods to a large number of simulated stars with different noise and size realizations.
@@
 
-In order to find the centroid of a star, we fit a simple 2d polynomial $I(x,y)=a+bx+cy+dx^2+exy+fy^2$ to the $3\times3$ patch centered on the brightest pixel of the
-image. Upon constructing a universal 9$\times$6 design matrix
-\[
-A=
+In order to find the centroid of a star, we fit a simple 2d polynomial $P(x,y)=a+bx+cy+dx^2+exy+fy^2$ to the $3\times3$ patch centered on the brightest pixel of the
+image.
+We apply this method to star images in the sky-dominated regime.
+In this regime, the covariance matrix of pixel uncertianties is simply given by $\sigma^{2}\mathbf{I}$, where $\sigma^{2}$ is variance of the uncorrelated Gaussian noise, and $\mathbf{I}$ is a 9$\times$9 identity matrix.
+Upon constructing a universal 9$\times$6 design matrix
+
+\begin{equation}
+    \mathbf{A} = 
     \begin{bmatrix}
-    1 & x_{1} & y_{1} & x_{1}^{2} & x_{1}y_{1} & y_{1}^{2}\\
+        1 & x_{1} & y_{1} & x_{1}^{2} & x_{1}y_{1} & y_{1}^{2} \\
         . & . & . & . & . & .  \\
@@
         . & . & . & . & . & .  \\
-    1 & x_{9} & y_{9} & x_{9}^{2} & x_{9}y_{9} & y_{9}^{2}\\
+        1 & x_{9} & y_{9} & x_{9}^{2} & x_{9}y_{9} & y_{9}^{2}
     \end{bmatrix},
-\]
+\end{equation}
 the free parameters of the model $\{a,b,c,d,e,f\}$ (hereafter compactly denoted by $\mathbf{X}$) can be determined by 
 \beq
-\mathbf{X} = (A^{T}A)^{-1}A^{T}\mathbf{Z},
+\mathbf{X} = (\mathbf{A}^{T}\mathbf{A})^{-1}\mathbf{A}^{T}\mathbf{Z},
+\label{linearfit}
 \eeq
-where $\mathbf{Z}$ is given by $(I_{1},...,I_{9})^{T}$, with $I_{i}$ denoting the brightness of the $i-$th pixel. Afterwards, the best fit parameters can be used to compute the centroid coordinate
-\[
+where $\mathbf{Z}$ is given by $(I_{1},...,I_{9})^{T}$, with $I_{i}$, being the brightness of the $i-$th pixel of the 3$\times$3 patch.
+Afterwards, the best fit parameters can be used to compute the centroid coordinate
+
+\beq
   \begin{bmatrix}
@@
   \end{bmatrix}.
-\]
-
-Let us smooth the image of the star with a Gaussian PSF with a FWHM equal to that of PSF at that location.
-Now Consider any row or column of the 3$\times$3 patch around the brightest pixel of the smooth image and let us denote the brightness of these three pixels by $\{f_{-},f_{0},f_{+}\}$.
-The fundamental assumption behind the model implemented in SDSS photometric pipeline \citep{sdss} is that these brightness values are in fact the function $f(x) = A\exp((x-x_{c})^{2}/2\beta^{2})$ evaluated at $x=-1,0,+1$; with $x_{c}$ being the position of centroid.
-Knowing the value of $f$ at $\{-1,0,1\}$, expanding $f(x)$ up to fourth order in $x$ leads to
-\beq
-x = \frac{s}{d}(1+k\frac{d}{4A}(1-(s/d)^{2})),
-\eeq
-where $k \simeq 4/3$, and
-\beq
-\begin{array}{l}
-s:=(f_{+}-f_{0})/2, \nonumber\\
-d:=2f_{0} - (f_{+}+f_{0}), \nonumber\\
-A = f_{0} +s^{2}/2d.
-\label{def}
-\end{array}
+\label{center}
 \eeq
 
-Now if we apply this method to every column and row of the 3$\times$3 patch, we will find three local maxima for three rows $\{(x_{-},-1), (x_{0},0),(x_{+},1)\}$, and three local maxima for three columns $\{(-1,y_{-}), (0,y_{0}),(1,y_{+})\}$.
-It is important to note that since the image has been smoothed, the covariance matrix between different pixels is not zero.
+Now, we modify the simple polynomial method explained above, by smoothing the image of the star with a Gaussian kernel with a given width (2 pixels in this study).
+Then we apply the same polynomial method to the 3$\times$3 patch around the brightest pixel of the smoothed image.
+The important difference between the previous approach and the modified method is that, there are non-zero covariances among the uncertainties of the brightness of different pixels of the smoothed image.
+That is, the covariance matrix $\mathbf{C}$ is non-diagonal.
+It can be shown that after smoothing, elements of the covariance matrix are given by
+\begin{eqnarray}
+\mathbf{C}_{ij} &=& \frac{\sigma^{2}}{4\pi w^{2}} \exp(-\frac{r_{ij}^{2}}{4\pi w^{2}}),\\
+r_{ij}^{2} &=& (x_{i} - x_{j})^{2} + (y_{i} - y_{j})^{2},
+\label{nondiagonal}
+\end{eqnarray}
+where $w$ is width of the kernel, and $x_{i}$ , $y_{i}$ are the $x$, and $y$ coordinates of the $i$-th pixel respectively.
+In the presence of the non-diagonal covariance matrix $\mathbf{C}$, equation (\ref{linearfit}) needs to be modified in the following way
+\beq
+\mathbf{X} = [\mathbf{A}^{T}\mathbf{C}^{-1}\mathbf{A}]^{-1}[\mathbf{A}^{T}\mathbf{C}^{-1}\mathbf{Z}].
+\label{linearfit2}
+\eeq
+
+Therefore, for a given star and a smoothing kernel, the outcome of equation (\ref{linearfit2}) can be plugged into equation (\ref{center}) to find the centroid estimate of the star.
+Hereafter, we call this method the modified polynomial method.
+
+Now, let us give a brief overview of centroiding method implemented in SDSS photometric pipeline \citep{sdss}: Consider any row or column of the 3$\times$3 patch around the brightest pixel of the smooth image and let us denote the brightness of these three pixels by $\{I_{-},I_{0},I_{+}\}$.
+The fundamental assumption behind the technique is that these brightness values can be approximated by the function $P(x) = Q\exp((x-x_{c})^{2}/2\beta^{2})$ evaluated at $x=-1,0,+1$; with $x_{c}$ being the position of centroid.
+Knowing the value of $P$ at $\{-1,0,1\}$, expanding $P(x)$ up to fourth order in $x$ leads to
+\beq
+x = \frac{s}{t}(1+k\frac{t}{4Q}(1-(s/t)^{2})),
+\eeq
+where k = 1.33, and
+
+\begin{eqnarray}
+s&=&(I_{+}-I_{-})/2, \\
+t &=&2I_{0} - (I_{+}+I_{-}), \\
+Q &=& I_{0} +s^{2}/2t.
+\label{def}
+\end{eqnarray}
+
+If we apply this method to every column and row of the 3$\times$3 patch around the brightest pixel of the smoothed image, we will find three local maxima for three rows $\{(x_{-},-1)$, $(x_{0},0)$, $(x_{+},1)\}$, and three local maxima for three columns $\{(-1,y_{-})$, $(0,y_{0})$, $(1,y_{+})\}$.
+It is important to note that, since the image has been smoothed, the covariance matrix between different pixels is not zero.
 Therefore, there is an uncertianty associated with any of these local maxima.
-Then, the centroid is estimated by finding the intersection of a line fitted to three maxima corresponding to rows, and another curve fitted to three maxima corresponding to columns.
-Figure [\ref{ex}] demonstrates the performances of the discussed models in centroiding simulated stars with known true centroids.
-
-\section{Simulated data}\label{sec:data}
+The centroid is then estimated by finding the intersection of two curves, one fitted to three maxima corresponding to rows, and the other fitted to three maxima corresponding to columns.
+\section{Simulations and Tests}\label{sec:data}
 
@@
 We use the Moffat profile \citep{moffat} for our simulations.
-Moffat profile is an analytic model for stellar PSFs which has broader wings than a simple Gaussian model.
+Moffat profile is an analytic model for stellar PSFs.
+It has broader wings than a simple Gaussian model.
 The surface brightness of the Moffat profile is given by
 \beq
-I(r) = \frac{f(\beta -1)}{\pi \alpha^{2}}[1+(r/\alpha)^{2}]^{-\beta},
+I(r) = \frac{F(\beta -1)}{\pi \alpha^{2}}[1+(r/\alpha)^{2}]^{-\beta},
 \label{mof}
 \eeq
-where $f$ is the total flux, and $\alpha$ is the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$) being $2\alpha\sqrt{2^{1/\beta}-1}$.
-The radial light profile of the stars generated in our simulations are shown in Figure[\ref{moffat}].
+where $F$ is the total flux, $\beta$ is a dimensionless paramter, and $\alpha$ is the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$) being $2\alpha\sqrt{2^{1/\beta}-1}$.
+We want to investigate the performance of the two models introduced in section \ref{sec:model} for different background noise levels, and also different values of $\gamma$.
+For further simplicity, we set the flux of all stars in our simulations to unity.
+Per pixel uncertainties are assumed to be uncorrelated Gaussian, and we only study the sky dominated regime.
 
-We want to investigate the performance of the two models introduced in section \ref{sec:model} for different background noise levels, and also different values of $\gamma$.
-For further simplicity, we set the flux of all stars to one.
-Per pixel uncertainties are assumed to be uncorrelated Gaussian (resulting in a diagonal covariance matrix), and we only study the sky dominated regime.
-Therefore the covariance matrix is simply given by $\sigma^{2}I$.
+Moreover, it is more convenient to work with the signal-to-noise ratio (hereafter denoted by SNR) instead of the variance of the Gaussian noise.
+This is due to the fact that at the same noise level, simulated stars with different values of $\gamma$ have different SNRs.
 
-Moreover, it is more useful to work with the signal-to-noise ratio instead of the variance of the Gaussian noise.
-This is due to the fact that at the same noise level, simulated stars with different values of $\gamma$ have different signal-to-noise-ratios.
-
-First, let us find an analytic expression for $S/N$.
-We define $S/N$ as the ratio of the mean and variance of the distribution which the flux estimator is drawn from.
+First, let us find an analytic expression for SNR.
+We define SNR as the ratio of the mean and variance of the distribution which the flux estimator is drawn from.
 Assume that the total flux from the point source is $f$, and that the PSF at the $i$-th pixel is given by $P_{i}$.
@@
 \eeq  
-which leads to
+which leads us to
 \beq
 \begin{array}{l}
-S/N $=$ \frac{\sqrt{\sum_{i} P_{i}^{2}}}{\sigma}.
+\text{SNR} $=$ \frac{\sqrt{\sum_{i} P_{i}^{2}}}{\sigma}.
 \end{array}
@@
 
-Note that (\ref{snr}) is valid in the limit of sky-dominated star images, and that is the limit we are interested in.
-In the case of our simulations the expression (\ref{snr}) can be analytically expressed in terms of $\sigma$, $\gamma$, and also $\beta$.
+Note that (\ref{snr}) is valid in the limit of sky-dominated images, and that is the limit we are interested in.
+In the case of our simulations, the expression (\ref{snr}) can be analytically expressed in terms of $\sigma$, $\gamma$, and also $\beta$.
 We fix $\beta$ at the fiducial value of 2.5.
@@
 \beq
-S/N = \frac{0.478}{\sigma \gamma}.
+\text{SNR} = \frac{0.478}{\sigma \gamma}.
 \label{snr2}
@@
 
-Equation (\ref{snr2}) implies that for stars with the same flux $f$ and background noise level $\sigma$, those with bigger size have lower $S/N$ and therefore, we expect to obtain more biased estimates for larger $\gamma$.
+Equation (\ref{snr2}) implies that for stars with the same flux $f$ and background noise level $\sigma$, those with bigger effective size have lower SNR.
+In this work, we study the relation between error in centroid measurement and $\gamma$ at fixed SNR, and vice versa.
+In the first experiment, we generate 100000 Moffat profiles centered randomly in the sub-pixel region inside the central pixel of a 17$\times$17 image, at four different full width at half maxima of 2, 2.8, 4, and 5.6 pixels with SNR ranging from 5 to 150.
+In the second experiment, we generate the same number of Moffat profiles with $\gamma$ ranging from 2 pixels to 6 pixels, with four different SNR values of 5, 50, 100, 150.
 
-In this work, we study the relation between error in centroid measurement and $\gamma$ at fixed $S/N$ and vice versa.
-In the first experiment, we generate Moffat profiles centered randomly in the sub-pixel region inside the central pixel of a 17$\times$17 image, at four different full width at half maxima of 2, 2.8, 4, and 5.6 pixels with signal-to-noise ratio ranging from 5 to 150.
-In the second experiment, we generate Moffat profiles with $\gamma$ ranging from 2 to 6, with four different signal-to-noise-ratios of 5, 50, 100, 150.
+In addition to the centroiding methods discussed in the previous sections, we compute the error from fitting the PSF model with the exact $\gamma$.
+That is, we find the best estimates of flux and centroid by optimizing the $\chi^{2}$.
 
-In addition to the two centroiding method discussed in the previous sections, we compute the error in centroid measurement from fitting the exact analytic PSF model to the data by minimizing $\chi^{2}$.
-In both experiments, we compare the error with the quantity
+In order to test the accuracy of each model, we need to compare the mean squared error to the Cramer-Rao lower bound (hereafter CRLB).
+That is, after finding the centroid error for each model, we compute the mean in bins of $S/N$ (bins of $\gamma$ in the second experiment).
+The closer the mean bias is to the CRLB, the more accurate the centroid estimate is.
 
+In practice however, instead of mean squared error, we work with the median squared error.
+The reason is that, at the faint end of our simulations (SNR $\leq$ 10), the unmodified polynomial method leads to some catastrophic failures which could skew the mean squared centroid error of the sample.
+Thus, we use median squared error as a less biased representative of the performance of different centroiding techniques.
+
+In statistics, CRLB sets a lower bound for the variance of the point estimator of a variable.
+Let us assume that the data is generated from the analytic model $f(\mathbf{x}, \{\theta\})$, where the vector $\mathbf{x}$ denotes coordinate, and $\{\theta\}$ represents parameters of the model.
+CRLB of the  estimator of the parameter $\theta_{i}$ can be computed from the inverse of the Fisher information information matrix
 \beq
-\rho := \frac{\gamma}{SNR}
+\text{CRLB}[\hat{\theta}_{i}] = (F^{-1})_{ii}, 
+\label{crlb}
+\eeq
+where the elements of the Fisher matrix can be computed according to
+\beq
+F_{ij} = \left \langle -\frac{\partial^{2} \ln \mathcal{L}}{\partial \theta_{i}\partial \theta_{j}} \right \rangle,   
+\label{fisher}
+\eeq
+where $\ln \mathcal{L}$ is the log-likelihood function (or Log probability density function of the observations) and is given by $-\chi^{2}/2$: 
+\beq
+\chi^{2} = \sigma^{-2}\sum_{\mathbf{p}}\big [ f(\mathbf{x}_{\mathbf{p}},\{\theta_{t}\})+ n(\mathbf{x}_\mathbf{p}) - f(\mathbf{x}_{\mathbf{p}},\{\theta\}) \big ]^{2},
+\label{lik}
+\eeq
+in which summation is over all pixels, ${\theta_{t}}$ represents the set of parameters used to generate the data, and $n(\mathbf{x}_{\mathbf{p}})$ is uncorrelated Gaussian noise map
+\begin{eqnarray}
+\langle n(\mathbf{x}) \rangle &=& 0, \\
+\langle n(\mathbf{x_{p}})n(\mathbf{x_{p^{\prime}}}) \rangle &=& \sigma^{2}\delta_{\mathbf{p}\mathbf{p}^{\prime}}. 
+\end{eqnarray}
+
+Combining (\ref{fisher}) and (\ref{lik}) yields
+\beq
+F_{ij} = \sigma^{-2}\sum_{\mathbf{p}}\frac{\partial f(\mathbf_{x}_{\mathbf{p}} , \{\theta_{t}\})}{\partial \theta_{i}}\frac{\partial f(\mathbf_{x}_{\mathbf{p}} , \{\theta_{t}\})}{\partial \theta_{j}}.
 \eeq
 
-In order to do so, after computing the error $\Delta x = \sqrt{(x_{t}-x_{c})^2 + (y_{t}-y_{c})^2}$ for each model, we compute the median in bins of $S/N$.
-The closer the median error is to $\rho$, the less biased the centroid estimate is.
-This quantity is, in fact, the Cramer-Rao lower bound (hereafter CRLB).
-In statistics, CRLB sets a lower bound for the point estimate of a variable.
-This lower bound can be analytically calculayed from the log-likelihood function
-
+Assuming the model (\ref{mof}) with $\beta = 2.5$, it can be shown that the inverse of the Fisher matrix is given by
 \beq
-var(\hat{\theta}) \geq \langle (\frac{\partial \log \mathcal{L}}{\partial \theta})^{2}\rangle^{-1},
+  F^{-1} \simeq 0.6846 \frac{\gamma}{\text{SNR}} 
+  \begin{pmatrix}
+      1 & 0\\
+      0 & 1\\
+  \end{pmatrix}.
+\label{crlbmoffat}
 \eeq
 
-where here $\theta$ is the centroid coordinate, and the dependence of likelihood on centroid $\theta$ comes through (\ref{mof}).
-Taking the derivative of the log-likelihood w.r.t the centroid coordiantes, yields
+Equation (\ref{crlbmoffat}) implies that for different noise realizations of a moffat PSF at a given SNR and $\gamma$, an optimal centroiding technique delivers estimates whose mean (in this study, median) squared error along each axis is less than or equal to $0.6846 \gamma/\text{SNR}$.
 
+Moreover, it is worth investigating cases where we do not know the exact PSF model, or the model we use to find the centroid is slightly wrong.
+For instance, let us consider a set of images of stars generated from elliptical Moffat profile
 \beq
-\sum_{a=1}^{2} \langle \delta x_{a}^{2} \rangle = \frac{(2\beta + 1)\pi \gamma \sigma}{4 \beta (\beta-1)^{2}(2^{1/\beta}-1)^{1.5}},
+P(r) = \frac{F(\beta - 1)}{\pi a_{1}a_{2}}\Big[1+\Big(\frac{x}{a_{1}}\Big)^{2}+\Big(\frac{y}{a_{2}}\Big)^{2}\Big]^{-\beta},
 \eeq    
+where $a_{1}$ is the major axis, $a_{2}$ is the minor axis, and for simplicity we have assumed that the major axis is along the $x$ axis.
+In this case, the CRLB associated with  the $x$ component of centroid is given by $0.6846 a_{1}/\text{SNR}$, and the CRLB associated with the $y$ component is given by $0.6846 a_{2}/\text{SNR}$.
 
-where, in the case of $\beta = 2.5$, is given by $0.4\gamma^{2}\sigma$ which is approximately equal to $\rho$.
-
-Theoretically, we expect the median error resulting from the exact PSF fitting method to be arbitrarily close to CRLB.
-This is due to the fact that, we find the centroid by fitting the model that used to generate the data.
-In this case, the log-likelihood can be written as
-
-\beq
-\log \mathcal{L}(\theta) = -\frac{1}{2\sigma^{2}}\sum_{\mathbf{p}}(f(\mathbf{x}_{\mathbf{p}},\theta_{t})+ n(\mathbf{x}_{\mathbf{p}}) - f(\mathbf{x}_{\mathbf{p}},\theta)),
-\label{like}
-\eeq
-
-where $\theta$ encompasses all the free parameters of the model (with $\theta_{t}$ denoting the true value of the parameters), and $n(\mathbf{x}_{\mathbf{p}})$ is the uncorrelated Gaussian noise map with variance $\sigma^{2}$.
-Upon expanding (\ref{like}) around the true parameter, and assuming that the the point estimate is close to the true value, it can be shown that the covariance of the parameters $\hat{\theta}$ is given by the inverse Fisher information matrix
-
-\beq
-F_{ij} = \sum_{\mathbf{p}}\frac{\partial f(\mathbf{x}_{\mathbf{p}},\theta_{t})}{\partial \theta_{i}}\frac{\partial f(\mathbf{x}_{\mathbf{p}},\theta_{t})}{\partial \theta_{j}},
-\eeq 
-whose inverse is CRLB.
+We also generate a set of elliptical Moffat profiles with $e=0.2$, and $a_{1} = 2.8$ pixels, with signal-to-noise ratios ranging from 5 to 150.
+In addition to the exact (elliptical) PSF model, we use circular PSF model with $\gamma = \sqrt{a_{1}a_{2}}$ to find the centroid of these stars.
 
@@
 
-Results of the first experiment are shown in Figures[\ref{1}], [\ref{2}], [\ref{22}], [\ref{3}].
-As we expected, for all three methods, median error gets larger for fainter stars.
-This error is even larger as $\gamma$ gets larger.
-In order to have a better understanding of the performance of these models, the plots are made in logarithmic scale.
-As it can be seen in [\ref{3}], the difference between the median error and the CRLB (hereafter denoted by $\Delta$) in the case of PSF fitting is quite negligible.
-Furthermore, it is evident that in the case of 3$\times$3 polynomial method [\ref{1}], there are certain ranges of signal-to-noise ratio, where $\Delta$ is bigger than the one obtained from SDSS trick [\ref{2}], when we center the smoothing kernel on the center of the brightest pixel of the star, for different values of $\gamma$.
-On the other hand, when the smoothing kernel in the SDSS method [\ref{22}], is centered on the true centroid, the resulting bias is relatively close to CRLB.
-Moreover, $\Delta$ shrinks significantly, as $\gamma$ becomes smaller.
+Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}].
+As we expected, for all methods, median squared error becomes larger for fainter stars, and for stars with larger $\gamma$.
+As it can be seen in figure [\ref{1}], centroid estimate obtained from the polynomial method does not saturate the CRLB unless at smaller values of SNR.
 
-We repeat the same experiment, this time assigning random ellipticities between 0 and 0.2 to the simulated stars.
-We did not observe any particular change in the behavior of error as a function of signal-to-noise-ratio for the polynomial (Figure [\ref{111}]).
-However, as can be seen in figure [\ref{222}], centroiding elliptical Moffat profiles with the SDSS method in the presence of noise, results in relatively larger errors.
+The modified polynomial centroiding however, is able to deliver median squared error arbitrarily close to the CRLB in all ranges of SNR.
+At $\gamma = 2$ the modified centroiding estimate does not saturates the CRLB, but as $\gamma$ gets larger, centroid estimates of this techniques saturate and eventually, get lower than the CRLB.
+The median error from the SDSS method shows similar behaviour to that of modified polynomial method.
+See figures [\ref{2}], [\ref{3}].
+And finally, the centroid estimates from the exact fitting the exact PSF model give rise to a median error that is always below the CRLB [\ref{4}].
 
@@
 
-Behavior of $\Delta x$ as a function of $\gamma$ for different values of $S/N$ is shown in Figures [\ref{4}], [\ref{5}], [\ref{6}].
-Again, by decreasing noise level of the background sky, $\Delta x$ becomes smaller at all ranges of $\gamma$.
-Interestingly, as observed in results of both methods, in the cases of $S/N = 100, 150$, $\Delta x$ does not increase with $\gamma$ monotonically.
-In fact, there exist a minimum error around $\gamma$ $\sim$ 3 pixels.
-Also, at $S/N = 5$, where the image of stars are dominated by noise, we do not observe any considerable variation in $\Delta x$.
+Behavior of error as a function of $\gamma$ for different values of SNR, is shown in figures [\ref{5}], [\ref{6}], [\ref{7}], and [\ref{8}]. 
+By decreasing noise level of the background sky, $\Delta x$ becomes smaller at all ranges of $\gamma$.
 
-\subsection{Experiment 3}
+The polynomial method fails to saturate the CRLB except in simulations with SNR of 5.
+The modified polynomial method, and the SDSS method result in  median squared error always lower than CRLB, except in simulated stars with small $\gamma$.
+As we expect, the median error from fitting the exact PSF model always saturates the CRLB.
 
-In the last experiment, we study bias as a function of the ellipticity of the simulated stars for different values of $\gamma$, and signal-to-noise-ratio.
-As it can be seen in Figures [\ref{7}], [\ref{8}], [\ref{9}], the variation of bias with ellipticity is almost negligible for all three methods.
-Furthermore, the bias arising from the SDSS method is slightly higher than the one obtained from the polynomial method at $\gamma = 4$.
+\subsection{Elliptical PSF}
+
+In the last experiment, we compare the performances of the modified polynomial method, and SDSS method, with fitting the exact PSF model to the elliptical Moffat profiles, and also with fitting a circular PSF model.
+
+The median error from the modified polynomial and SDSS methods are very close to the CRLB.
+But only by fitting an approximate (circular) PSF profile, or eventually by fitting an exact PSF model, one can saturate the CRLB.
+However, it is important to note that centroiding errors of all four methods are extremely close to each other.
 
@@
 
-In this work, we proposed a method for centroiding stars based on a 3$\times$3 method.
+In this work, we proposed a method for centroiding stars based on fitting a low order polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel.
 Employing this technique into large scale astronomical surveys can considerably reduce the computational cost of initial astrometry of these surveys.
-This method can be roughly thousand times faster than centroiding through model fitting.
-The advantage of this method becomes more pronounced in PSF estimation in which all we need as an input is the centroid of stars and some lower dimensional representation of the postage stamp of stars.
+The advantage of this method becomes more pronounced in PSF estimation in which we need to know the centroid of stars accurately, but at the same time, with fewer number of algebraic operations.
 
-Comparison of this method with centroiding method of SDSS photo pipeline suggests that there are ranges of size and noise level in which, the error arising from this method is close to the theoretically set CRLB than the error obtained from SDSS method.
-However, in a wide range of scales, the error from SDSS trick is relatively smaller.
+This method can roughly be thousand times faster than centroiding through model fitting, and requires fewer operations than the method implemented in SDSS photo pipeline.
+More importantly, it requires no prior knowledge about the shape of the PSF.
 
-However, it is important to note that, at the very faint end of stars, the bias resulting from both method can be significantly large.
-This can be largely attributed to the fact that any estimate obtained from this method, tends to be inside the brightest pixel of the image, which is not necessarily the case for the true centroid when the signal-to-noise-ratio is low.
+Comparison of this technique with the centroiding method based on a fourth-order approximation implemented in SDSS photo pipeline suggests that in wide ranges of size and noise level of the background sky, the error arising from this method is close to the theoretically set CRLB, and comparable to the error obtained from SDSS method.
 
-The advantage of SDSS trick over the polynomial model is that, it assumes a more realistic model for the light profile of stars.
-On the other hand, in order for this model to achieve significantly better results, one has to estimate the FWHM of the star in advance.
+Although having a reasonable PSF model should always deliver better centroid estimates, one can achieve sensibly accurate results by employing this simple 3$\times$3 method without making any assumption about the PSF model.
 
-Furthermore, in this investigation we narrowed our focus on data simulated from a very specific model.
+In this investigation we narrowed our focus on a set of data simulated from a very specific model.
 Although there are various cases where Moffat profiles provide reasonable representation of point spread function, these models are not generic enough to let us reach a more general conclusion.
-
 Another important, and untapped, area of study would be devising a model that infers the centroid of stars and point spread function (in its full extent, not at the catalog level) across an astronomical image simultaneously.
+This is beyond the scope of this study.
 
@@
 \begin{figure}[!htb]
-\minipage{.5\textwidth}
-  \includegraphics[width=\linewidth]{exaple_cen0.png}
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{snr_poly.png}
 \endminipage
-\minipage{.5\textwidth}
-  \includegraphics[width=\linewidth]{example_cen1.png}
-\endminipage
-\caption{Demonstration of the performance of SDSS and polynomial method on finding the centroid on the 3$\times$3 patch around the brightest pixel, with the true centroid, and centroid estimate from the polynomial method markerd by $+$, $\wedge$ respectively; and the centroid estimate from SDSS trick (shown by $\star$) given by the intersection of two curves.}\label{ex}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{1\textwidth}
-  \includegraphics[width=\linewidth]{moffat.png}
-\endminipage
-\caption{The radial light profile of stars used in this study, with FWHM of 2(star), 2.8(circle), 4(pentagon), and 5.6(square) pixels. The parameter $\beta$ is set to $2.5$.}\label{moffat}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{1\textwidth}
-  \includegraphics[width=\linewidth]{map_20_50.png}
-\endminipage
-
-\minipage{1\textwidth}
-  \includegraphics[width=\linewidth]{map_4_50.png}
-\endminipage
-\caption{Demonstration of the centroid bias resulting from: \emph{left}: polynomial, and \emph{right}: SDSS tricks as a function of subpixel position of centroid.
-Top  (bottom) color maps are obtained from taking the median bias of different noise realization of a Moffat profiles with FWHM = 2 (4) pixels, and signal-to-noise of 50.}\label{map}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{1\textwidth}
-  \includegraphics[width=\linewidth]{map_2_100.png}
-\endminipage
-
-\minipage{1\textwidth}
-  \includegraphics[width=\linewidth]{map_4_10.png}
-\endminipage
-\caption{Demonstration of the centroid bias resulting from: \emph{left}: polynomial, and \emph{right}: SDSS tricks as a function of subpixel position of centroid.
-Top  (bottom) color maps are obtained from taking the median bias of different noise realization of a Moffat profiles with FWHM = 2 (4) pixels, and signal-to-noise of 10.}\label{map2}
+\caption{Scatter plots showing the relation between error in centroid measurement from the polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{1}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{poly_snr.png}
+  \includegraphics[width=\linewidth]{snr_spoly.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from polynomial method and the signal-to-noise ratio of stars with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{1}
+\caption{Scatter plots showing the relation between error in centroid measurement from the modified polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{2}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{sdss_without_knowing_true_pixel.png}
+  \includegraphics[width=\linewidth]{snr_sdss.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from SDSS method, when the center of the smoothing kernel is the center of the brightest pixel of star, and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{2}
+\caption{Scatter plots showing the relation between error in centroid measurement from the SDSS method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{3}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{sdss_fwhm_true_pixel.png}
+  \includegraphics[width=\linewidth]{snr_fitting.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from SDSS method, when the center of the smoothing kernel is the true centroid of star, and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{22}
+\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model to the stars and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{4}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{psf_snr.png}
+  \includegraphics[width=\linewidth]{fwhm_poly.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from PSF fitting method and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{3}
+\caption{Scatter plots showing the relation between error in centroid measurement from the polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{5}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{epoly_fwhm.png}
+  \includegraphics[width=\linewidth]{fwhm_spoly.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement of elliptical PSF profiles from polynomial method and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{111}
+\caption{Scatter plots showing the relation between error in centroid measurement from the modified polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{6}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{esdss_fwhm_notruth.png}
+  \includegraphics[width=\linewidth]{fwhm_sdss.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement of elliptical PSF profiles from SDSS method and the signal-to-noise ratio of stars with FWHM of: 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents $\rho$.}\label{222}
+\caption{Scatter plots showing the relation between error in centroid measurement from the SDSS method and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{7}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{poly_fwhm.png}
+  \includegraphics[width=\linewidth]{fwhm_fitting.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from polynomial method and the FWHM of stars with signal-to-noise-ratio of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
-In each scatter plot, the blue line represents the median of data points, and the green line represents $\rho$.}\label{4}
+\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{8}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{sdss_fwhm.png}
+  \includegraphics[width=\linewidth]{snr_wrongpsf.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from SDSS method and the FWHM of stars with signal-to-noise-ratio of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
-In each scatter plot, the blue line represents the median of data points, and the green line represents $\rho$.}\label{5}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{psf_fwhm.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from PSF fitting method and the FWHM of stars with signal-to-noise-ratio of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
-In each scatter plot, the blue line represents the median of data points, and the green line represents $\rho$.}\label{6}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{poly_ellipticity.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the polynomial method and the ellipticity of stars with ($S/N$, $\gamma$) of : (100, 2) (upper left), (20, 2) (upper right), (100, 4) (lower left), and (20, 4) (lower right).
-In each scatter plot, the blue line represents the median of data points.}\label{7}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{sdss_ellipticity.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the sdss method and the ellipticity of stars with ($S/N$, $\gamma$) of : (100, 2) (upper left), (20, 2) (upper right), (100, 4) (lower left), and (20, 4) (lower right).
-In each scatter plot, the blue line represents the median of data points.}\label{8}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{psf_ellipticity.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the PSF fitting method and the ellipticity of stars with ($S/N$, $\gamma$) of : (100, 2) (upper left), (20, 2) (upper right), (100, 4) (lower left), and (20, 4) (lower right).
-In each scatter plot, the blue line represents the median of data points.}\label{9}
+\caption{Scatter plots showing the relation between error in centroid measurement from: the SDSS method (upper left), the modified polynomial method (upper right), fitting circular PSF model (lower left), and  fitting the exact PSF model (lower right) and SNR of stars with major axis of 2.8 pixels and ellipticity of 0.2.
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{9}
 \end{figure}

### 2014-12-01 script/test_fwhm.py
given snr, same simulated data for all methods

@@ -19,7 +19,7 @@ Author: Mohammadjavad Vakili (July and August 2014)
 import centererr
 import numpy as np
 import sys
-
+import h5py
 
 
 if __name__ == '__main__':
@@ -43,6 +43,7 @@ if __name__ == '__main__':
         help='size of the postage_stamp')
     o.add_option('--sample', dest='sample', default=20000, type='int',
         help='number of stars in experiment')
+
     opts, args = o.parse_args(sys.argv[1:])
 
 
@@ -70,16 +71,24 @@ if __name__ == '__main__':
     xmin , xmax = size/2 , size/2 + 1
     ymin , ymax = size/2 , size/2 + 1
     
-    f = np.random.uniform( fmin , fmax , sample)
+    #f = np.random.uniform(fmin, fmax, sample)
+    f = np.loadtxt("f_snr5.txt")
     sigma = 0.478/(f*snr)
     
-    xx = np.random.uniform(xmin, xmax, sample)
-    yy = np.random.uniform(ymin, ymax, sample)
+    #xx = np.random.uniform(xmin, xmax, sample)
+    #yy = np.random.uniform(ymin, ymax, sample)
 
-    
+    #np.savetxt("xc_snr5.txt"  , np.array(xx)  ,fmt='%.12f')
+    xx = np.loadtxt("xc_snr5.txt")
+    #np.savetxt("yc_snr5.txt"  , np.array(yy)  ,fmt='%.12f')
+    yy = np.loadtxt("yc_snr5.txt")   
+    #np.savetxt("f_snr5.txt"   ,  np.array(f)  ,fmt='%.12f')
+    """F = h5py.File('data_snr5.h5' , 'r')
+    DATA = F["MyDataset"][:]"""
     if opts.method.startswith('poly'):
-
-       er = []
+       cent = []
+       erx  = []
+       ery  = []
        flag = []
        fwhm = []
        A = centererr.poly.design(2)
@@ -87,50 +96,96 @@ if __name__ == '__main__':
        for i in range(sample):
           
           xc =  np.array([xx[i],yy[i]])          
-          data = centererr.profile.makeMoffat(size , f[i] , beta , 0.2 , xc)
+          data = centererr.profile.makeMoffat(size , f[i] , beta , 0.0 , xc)
           data += np.random.normal(0, sigma[i] , data.shape)
           
           xs = centererr.poly.poly_centroid(data , A)
[…]

### 2014-12-01 ms/mainscatterf.py
make error-fwhm scatter plots

@@ -1,0 +1,155 @@
+import numpy as np
+import matplotlib.pyplot as plt
+plt.rcParams['text.latex.preamble'] = [r"\usepackage{lmodern}"]
+params = {'text.usetex' : True, 'font.size' : 17 , 'font.family' : 'lmodern' , 'text.latex.unicode' : True, }
+plt.rcParams.update(params)
+
+
+
+s1 = np.loadtxt("fwhm5_s5_00tb.txt")
+s2 = np.loadtxt("fwhm5_s10_00.txt")
+s3 = np.loadtxt("fwhm5_s20_00.txt")
+s4 = np.loadtxt("fwhm5_s40_00.txt")
+a1 = np.loadtxt("erx5_s5_00tb.txt")
+a2 = np.loadtxt("erx5_s10_00.txt")
+a3 = np.loadtxt("erx5_s20_00.txt")
+a4 = np.loadtxt("erx5_s40_00.txt")
+
+
+crap1 = np.array([1]) #np.loadtxt("flag5_s10_0.txt").astype(int)
+crap2 = np.array([1]) #np.loadtxt("flag5_s50_0.txt").astype(int)
+crap3 = np.array([1]) #np.loadtxt("flag5_s100_0.txt").astype(int)
+crap4 = np.array([1]) #np.loadtxt("flag5_s150_0.txt").astype(int)
+
+
+
+labels = [ 'S/N=5' ,  'S/N=10' ,  'S/N=20' ,  'S/N=40']
+
+fig , axarr = plt.subplots(2,2 , sharex = True , sharey = True) 
+
+total_bins = 40
+###################################################################### axarr[0,0] ################
+
+a = np.delete(s1, crap1,  axis=0)
+b = np.delete(a1, crap1,  axis=0)
+#a = a[b<10.]
+#b = b[b<10.]
+
+bins = np.linspace(a.min(), a.max(), total_bins)
+delta = bins[1]-bins[0]
+idx  = np.digitize(a,bins)
+
+textstr = 'S/N=5'
+
+axarr[0,0].text(0.6, 0.15, textstr, transform=axarr[0,0].transAxes, fontsize=18,
+        verticalalignment='top')
+
+axarr[0,0].semilogy(np.sort(a) , (np.sort(a)*.68466)/5. , 'g-', lw = 1 , alpha = 1. )
+axarr[0,0].scatter(a , b**.5 , s=1 , c = 'y' , marker='+' , alpha = 1.)
[…]

### 2014-12-01 ms/mainscatter.py
error-snr plots
Need to modify labels, use the same format as mainscatterf.py

@@ -1,0 +1,148 @@
+import numpy as np
+import matplotlib.pyplot as plt
+plt.rcParams['text.latex.preamble'] = [r"\usepackage{lmodern}"]
+params = {'text.usetex' : True, 'font.size' : 17 , 'font.family' : 'lmodern' , 'text.latex.unicode' : True, }
+plt.rcParams.update(params)
+
+################################################################# DATA #####################################
+
+s1 = (np.loadtxt("noise1_20_00.txt"))
+s2 = (np.loadtxt("noise1_40_00.txt"))
+s3 = (np.loadtxt("noise1_60_00.txt"))
+s4 = (np.loadtxt("noise1_80_00.txt"))
+a1 = np.loadtxt("erx1_20_00.txt")
+a2 = np.loadtxt("erx1_40_00.txt")
+a3 = np.loadtxt("erx1_60_00.txt")
+a4 = np.loadtxt("erx1_80_00.txt")
+
+################################################################# FLAGGED OBJECTS ##########################
+
+crap1 = np.array([1])#np.loadtxt("flag2_20_0.txt").astype(int)
+crap2 = np.array([1])#np.loadtxt("flag2_28_0.txt").astype(int)
+crap3 = np.array([1])#np.loadtxt("flag2_40_0.txt").astype(int)
+crap4 = np.array([1])#np.loadtxt("flag2_56_0.txt").astype(int)
+
+fig , axarr = plt.subplots(2 , 2 , sharex= True, sharey= True) 
+
+total_bins = 400
+###################################################################### axarr[0,0] ################
+a = s1
+b = a1
+
+a_clean = np.delete(s1, crap1,  axis=0)
+a_flag = a[crap1]
+
+b_clean = np.delete(a1, crap1,  axis=0)
+b_flag = b[crap1]
+
+bins = 10.**np.linspace(np.log10(a.min()), np.log10(a.max()), total_bins)
+delta = bins[1]-bins[0]
+idx  = np.digitize(a,bins)
+
+axarr[0,0].loglog(np.sort(a) , (2.*.68466)/(np.sort(a)) , 'g-', lw = 1 , alpha = 1.)
[…]

### 2014-12-02 src/spoly.py
covariance matrix inversion

@@ -33,9 +33,9 @@ def design(degree = 2):
 
 def regression( A , C , obs):
 
-  co = np.linalg.inv(np.dot(A.T , np.dot(C , A)))
+  co = np.linalg.inv(np.dot(A.T , np.linalg.solve(C , A)))
   
-  X = np.dot(co , np.dot(A.T , np.dot(C , obs)))
+  X = np.dot(co , np.dot(A.T , np.linalg.solve(C , obs)))
 
   return X
 
@@ -65,7 +65,7 @@ def cov(f , sigma):
   xv , yv =  np.meshgrid(np.array(nx) , np.array(ny))
   xc , yc =  xv.flatten() , yv.flatten()
 
-  C = np.zeros((npix , npix))
+  C = np.ones((npix , npix))
   
   for i in range(npix):
     for j in range(npix):
@@ -73,8 +73,8 @@ def cov(f , sigma):
       r2 = (xc[i] - xc[j])**2. + (yc[i] - yc[j])**2.   
 
       C[i,j] = np.exp(-1.*r2/(4.*f**2.))
+   
  
-  C = C*(sigma**2.)/(4.*np.pi*f**2.)
   return C
    
 
@@ -82,31 +82,32 @@ def spoly_centroid(data , A , f , sigma):
 
   size = data.shape[0]
   zero = size/2 + .5
-  kernel = profile.makeGaussian(7 , f , 0 , np.array([3.5,3.5]))
+  kernel = profile.makeGaussian(17, f , 0 , np.array([8.5,8.5]))
   
-  smoothed_image = signal.convolve2d(data , kernel , mode = "same")
+  image = signal.convolve2d(data , kernel , mode = "same")
   
-  image = smoothed_image#/np.sum(smoothed_image)
+  
   
   bp = np.where(image==image.max()) #brightest pixel in the smoothed image
   cen = [bp[1][0] , bp[0][0]]
-
+  
   k = image[cen[1]-1:cen[1]+2,cen[0]-1:cen[0]+2]
      
   if (k.shape!= (3,3)):
      center = np.array([0.,0.])
+     X = np.arange(6)*0.
   else:
      C = cov(f , sigma)
      X = regression(A , C , k.flatten())
   
      a , b , c, d , e , f = X
      matrix = np.array([[2.*d , e],[e , 2.*f]])
-     #matrix = matrix + (np.max(np.abs(matrix))/1000.)*np.array([[1,0],[0,1]])
[…]

### 2014-12-02 src/spoly.py
regularization term

@@ -33,9 +33,9 @@ def design(degree = 2):
 
 def regression( A , C , obs):
 
-  co = np.linalg.inv(np.dot(A.T , np.linalg.solve(C , A)))
+  co = np.linalg.inv(np.dot(A.T , np.dot(np.linalg.inv(C) , A)))
   
-  X = np.dot(co , np.dot(A.T , np.linalg.solve(C , obs)))
+  X = np.dot(co , np.dot(A.T , np.dot(np.linalg.inv(C) , obs)))
 
   return X
 
@@ -75,14 +75,14 @@ def cov(f , sigma):
       C[i,j] = np.exp(-1.*r2/(4.*f**2.))
    
  
-  return C
+  return (C*sigma**2.)/(4.*np.pi*f**2.)
    
 
 def spoly_centroid(data , A , f , sigma):
 
   size = data.shape[0]
   zero = size/2 + .5
-  kernel = profile.makeGaussian(17, f , 0 , np.array([8.5,8.5]))
+  kernel = profile.makeGaussian(7, f , 0 , np.array([3.5,3.5]))
   
   image = signal.convolve2d(data , kernel , mode = "same")
   
@@ -102,12 +102,12 @@ def spoly_centroid(data , A , f , sigma):
   
      a , b , c, d , e , f = X
      matrix = np.array([[2.*d , e],[e , 2.*f]])
-     #matrix = matrix + (np.max(np.abs(matrix))/10000.)*np.array([[1,0],[0,1]])
-     #matrix = matrix + (sigma/1000.)*np.array([[1,0],[0,1]])
+     #matrix = matrix + (np.max(np.abs(matrix))/9.)*np.array([[1,0],[0,1]])
+     matrix = matrix + (sigma/np.sqrt(4.*np.pi*f**2.))*np.array([[1,0],[0,1]])
      vector = np.array([-1.*b , -1.*c])
      center = np.dot(np.linalg.inv(matrix) , vector)
      #center = (c*e - b*f)/(2.*d*f - 2.*e**2.) , (b*e - c*d)/(2.*d*f - 2.*e**2.)   
-  return np.array(cen) + np.array([.5,.5]) + center , X        #also returning the curvature matrix
+  return np.array(cen) + np.array([.5,.5]) + center , X
 
 if __name__ == "__main__":
     print 'spoly main'

### 2014-12-02 src/spoly.py
no need to output curvature now

@@ -107,7 +107,7 @@ def spoly_centroid(data , A , f , sigma):
      vector = np.array([-1.*b , -1.*c])
      center = np.dot(np.linalg.inv(matrix) , vector)
      #center = (c*e - b*f)/(2.*d*f - 2.*e**2.) , (b*e - c*d)/(2.*d*f - 2.*e**2.)   
-  return np.array(cen) + np.array([.5,.5]) + center , X
+  return np.array(cen) + np.array([.5,.5]) + center
 
 if __name__ == "__main__":
     print 'spoly main'

### 2014-12-02 src/spoly.py
important comment on the regularization term
sigma/(4*pi*w**2)**.5, 
where w is the fwhm of the smoothing kernel.
adding sigma alone made results slightly worse, dividing the above term by 9 didn't make much difference.

@@ -103,7 +103,10 @@ def spoly_centroid(data , A , f , sigma):
      a , b , c, d , e , f = X
      matrix = np.array([[2.*d , e],[e , 2.*f]])
      #matrix = matrix + (np.max(np.abs(matrix))/9.)*np.array([[1,0],[0,1]])
-     matrix = matrix + (sigma/np.sqrt(4.*np.pi*f**2.))*np.array([[1,0],[0,1]])
+     matrix = matrix + (sigma/np.sqrt(4.*np.pi*f**2.))*np.array([[1,0],[0,1]]) #add maximum per pixel variance
+                                                                               #of the smoothed image to the
+                                                                               # diagonal elements of the curvature
+                                                                               #matrix
      vector = np.array([-1.*b , -1.*c])
      center = np.dot(np.linalg.inv(matrix) , vector)
      #center = (c*e - b*f)/(2.*d*f - 2.*e**2.) , (b*e - c*d)/(2.*d*f - 2.*e**2.)   

### 2014-12-02 src/spoly.py
speed up version with no reg!

@@ -1,64 +1,19 @@
+from __future__ import division
 import numpy as np
 import profile
 from scipy import signal , linalg
+from scipy.linalg import cho_factor, cho_solve
 
-def design(degree = 2):
-  
-  """This function evaluates the
-     entries of the 9by6 design
-     matrix used in 2nd order
-     polynomial centroiding"""
+x, y = np.meshgrid(range(-1, 2), range(-1, 2), indexing="ij")
+x, y = x.flatten(), y.flatten()
+AT = np.vstack((x*x, y*y, x*y, x, y, np.ones_like(x)))
+
+def cov(f=1.2):
 
   nx = np.array([-1. , 0. , 1.])
   ny = nx[:,np.newaxis]
   npix = 9
-  
-  #brightness = image.flatten()
-  
-  xv , yv =  np.meshgrid(np.array(nx) , np.array(ny))
-  xc , yc =  xv.flatten() , yv.flatten()
-  
-  A = np.zeros((npix , 6))
-  
-  A[:,0] = (xc**0.)*(yc**0.)
-  A[:,1] = (xc**1.)*(yc**0.)
-  A[:,2] = (xc**0.)*(yc**1.)
-  A[:,3] = (xc**2.)*(yc**0.)
-  A[:,4] = (xc**1.)*(yc**1.)    
-  A[:,5] = (xc**0.)*(yc**2.)
- 
-
-  return A
-
-
-def regression( A , C , obs):
-
-  co = np.linalg.inv(np.dot(A.T , np.dot(np.linalg.inv(C) , A)))
-  
-  X = np.dot(co , np.dot(A.T , np.dot(np.linalg.inv(C) , obs)))
-
-  return X
-
-def BP(data , f):
-
-  size = data.shape[0]
-  zero = size/2 + .5
-  kernel = profile.makeGaussian(size , f , 0 , np.array([zero,zero]))
-  smoothed_image = signal.convolve2d(data , kernel , mode = "same")
-  data = smoothed_image#/np.sum(smoothed_image)
-  
-  bp = np.where((data==data.max())) #brightest pixel in the smoothed image
-  cen = [bp[0][0] , bp[1][0]]
-
-  #kk = data[cen[0]-1:cen[0]+2,cen[1]-1:cen[1]+2]
-
-  return cen
-
-def cov(f , sigma):
-  """covariance matrix """
-  nx = np.array([-1. , 0. , 1.])
-  ny = nx[:,np.newaxis]
[…]

### 2014-12-02 src/poly.py
faster version with reg! in denominator

@@ -1,77 +1,33 @@
+from __future__ import division
 import numpy as np
+from scipy.linalg import cho_factor, cho_solve
 
-def design(degree = 2):
+
+x, y = np.meshgrid(range(-1, 2), range(-1, 2), indexing="ij")
+x, y = x.flatten(), y.flatten()
+AT = np.vstack((x*x, y*y, x*y, x, y, np.ones_like(x)))
+ATA = np.dot(AT, AT.T)
+factor = cho_factor(ATA, overwrite_a=True)
+
+
+def fit_3x3(img , sigma):
+    a, b, c, d, e, f = cho_solve(factor, np.dot(AT, img.flatten()))
   
-  """This function evaluates the
-     entries of the 9by6 design
-     matrix used in 2nd order
-     polynomial centroiding"""
-
-  nx = np.array([-1. , 0. , 1.])
-  ny = nx[:,np.newaxis]
-  npix = 9
-  
-  #brightness = image.flatten()
-  
-  xv , yv =  np.meshgrid(np.array(nx) , np.array(ny))
-  xc , yc =  xv.flatten() , yv.flatten()
-  
-  A = np.zeros((npix , 6))
-  
-  A[:,0] = (xc**0.)*(yc**0.)
-  A[:,1] = (xc**1.)*(yc**0.)
-  A[:,2] = (xc**0.)*(yc**1.)
-  A[:,3] = (xc**2.)*(yc**0.)
-  A[:,4] = (xc**1.)*(yc**1.)    
-  A[:,5] = (xc**0.)*(yc**2.)
- 
-
-  return A
+    m = 1. / (4 * a * b - c*c + sigma /9.)
+    x = (c * e - 2 * b * d) * m
+    y = (c * d - 2 * a * e) * m
+    return x, y
 
 
-def regression( A , obs):
+def find_centroid(img , sigma):
+    xi, yi = np.unravel_index(np.argmax(img), img.shape)
+    
+    if (xi >= 1 and xi < img.shape[0] - 1 and yi >= 1 and yi < img.shape[1] - 1):
+      ox, oy = fit_3x3(img[xi-1:xi+2, yi-1:yi+2] , sigma)
+    else:
+      ox , oy = 0. , 0.
+    return xi + ox + .5 , yi + ox + .5
 
-  X1 = np.dot(np.transpose(A) , A) 
-  X2 = np.linalg.inv(X1)
[…]

### 2014-12-03 src/poly.py
Update poly.py

@@ -13,7 +13,7 @@ factor = cho_factor(ATA, overwrite_a=True)
 def fit_3x3(img , sigma):
     a, b, c, d, e, f = cho_solve(factor, np.dot(AT, img.flatten()))
   
-    m = 1. / (4 * a * b - c*c + sigma /9.)
+    m = 1. / (4 * a * b - c*c + sigma**2. /9.)
     x = (c * e - 2 * b * d) * m
     y = (c * d - 2 * a * e) * m
     return x, y

### 2014-12-03 src/poly.py
Update poly.py

@@ -12,8 +12,9 @@ factor = cho_factor(ATA, overwrite_a=True)
 
 def fit_3x3(img , sigma):
     a, b, c, d, e, f = cho_solve(factor, np.dot(AT, img.flatten()))
-  
-    m = 1. / (4 * a * b - c*c + sigma**2. /9.)
+    a = a - (sigma)/8       #equivalent to adding sigma/4 to the diagonal elements of the curvature matrix!
+    b = b - (sigma)/8
+    m = 1. / (4 * a * b - c*c)     
     x = (c * e - 2 * b * d) * m
     y = (c * d - 2 * a * e) * m
     return x, y

### 2014-12-03 src/spoly.py
update regularization

@@ -42,6 +42,8 @@ def fit_3x3(im , sigma):
     #print C.shape
     imgg = np.dot(AT , np.dot(np.linalg.inv(C) , im.flatten()))
     a, b, c, d, e, f = cho_solve(factor, imgg)
+    a = a - (sigma)/8       #equivalent to adding sigma/4 to the diagonal elements of the curvature matrix!
+    b = b - (sigma)/8
     #cho_solve(factor, np.dot(AT, img.flatten()))
     m = 1. / (4 * a * b - c*c)
     x = (c * e - 2 * b * d) * m

### 2014-12-08 src/sdss.py
Update sdss.py

@@ -77,18 +77,21 @@ def lupton_2d(I , f , s):
 
 
   A_x = np.vstack((np.ones_like(mx_x), mx_x)).T
+  #C_x = np.identity(3)
   C_x = np.diag(yerr_x * yerr_x)
   cov_x = np.linalg.inv(np.dot(A_x.T, np.linalg.solve(C_x, A_x)))
   b_x, m_x = np.dot(cov_x, np.dot(A_x.T, np.linalg.solve(C_x, mx_y)))
 
   A_y = np.vstack((np.ones_like(my_y), my_y)).T
+  #C_y = np.identity(3)
   C_y = np.diag(yerr_y * yerr_y)
   cov_y = np.linalg.inv(np.dot(A_y.T, np.linalg.solve(C_y, A_y)))
   invb_y, invm_y = np.dot(cov_y, np.dot(A_y.T, np.linalg.solve(C_y, my_x)))
 
-  b_y , m_y = -invb_y/invm_y , invm_y**-1.
+  #b_y , m_y = -invb_y/invm_y , invm_y**-1.
 
-  xs = (b_x - b_y)/(m_y - m_x)
+  #xs = (b_x - b_y)/(m_y - m_x)
+  xs = (invm_y*b_x + invb_y)/(1-invm_y*m_x)
   ys = m_x*xs + b_x
   
 

### 2014-12-09 src/poly.py
Update poly.py

@@ -12,9 +12,8 @@ factor = cho_factor(ATA, overwrite_a=True)
 
 def fit_3x3(img , sigma):
     a, b, c, d, e, f = cho_solve(factor, np.dot(AT, img.flatten()))
-    a = a - (sigma)/8       #equivalent to adding sigma/4 to the diagonal elements of the curvature matrix!
-    b = b - (sigma)/8
-    m = 1. / (4 * a * b - c*c)     
+  
+    m = 1. / (4 * a * b - c*c + sigma /9.)
     x = (c * e - 2 * b * d) * m
     y = (c * d - 2 * a * e) * m
     return x, y
@@ -27,7 +26,7 @@ def find_centroid(img , sigma):
       ox, oy = fit_3x3(img[xi-1:xi+2, yi-1:yi+2] , sigma)
     else:
       ox , oy = 0. , 0.
-    return xi + ox + .5 , yi + ox + .5
+    return xi + ox + .5 , yi + oy + .5
 
 
 if __name__ == "__main__":

### 2014-12-09 src/spoly.py
Update spoly.py

@@ -8,12 +8,12 @@ x, y = np.meshgrid(range(-1, 2), range(-1, 2), indexing="ij")
 x, y = x.flatten(), y.flatten()
 AT = np.vstack((x*x, y*y, x*y, x, y, np.ones_like(x)))
 
-def cov(f=1.2):
+def cov(f):
 
   nx = np.array([-1. , 0. , 1.])
   ny = nx[:,np.newaxis]
   npix = 9
-  f = 1.2
+  
   
   #brightness = image.flatten()
   
@@ -31,6 +31,7 @@ def cov(f=1.2):
   return C
 
 C = cov(1.2)
+#C = np.identity(9)
 ATA = np.dot(AT, np.dot(np.linalg.inv(C) , AT.T))
 factor = cho_factor(ATA, overwrite_a=True)
 #ATA = np.dot(AT, AT.T)
@@ -42,10 +43,9 @@ def fit_3x3(im , sigma):
     #print C.shape
     imgg = np.dot(AT , np.dot(np.linalg.inv(C) , im.flatten()))
     a, b, c, d, e, f = cho_solve(factor, imgg)
-    a = a - (sigma)/8       #equivalent to adding sigma/4 to the diagonal elements of the curvature matrix!
-    b = b - (sigma)/8
-    #cho_solve(factor, np.dot(AT, img.flatten()))
-    m = 1. / (4 * a * b - c*c)
+    #a = a - (sigma)/11
+    #b = b - (sigma)/11
+    m = 1. / (4 * a * b - c*c + sigma**2./16)
     x = (c * e - 2 * b * d) * m
     y = (c * d - 2 * a * e) * m
     return x, y
@@ -63,7 +63,7 @@ def find_centroid(data , f , sigma):
       ox, oy = fit_3x3(img[xi-1:xi+2, yi-1:yi+2] , sigma)
   else:
       ox , oy = 0. , 0.
-  return xi + ox + .5 , yi + ox + .5
+  return xi + ox + .5 , yi + oy + .5
 
  
 

### 2014-12-09 src/poly.py
Update poly.py

@@ -12,8 +12,9 @@ factor = cho_factor(ATA, overwrite_a=True)
 
 def fit_3x3(img , sigma):
     a, b, c, d, e, f = cho_solve(factor, np.dot(AT, img.flatten()))
-  
-    m = 1. / (4 * a * b - c*c + sigma /9.)
+    a = a - sigma/18.
+    b = b - sigma/18.
+    m = 1. / (4 * a * b - c*c)
     x = (c * e - 2 * b * d) * m
     y = (c * d - 2 * a * e) * m
     return x, y

### 2014-12-10 src/poly.py
Update poly.py

@@ -12,8 +12,8 @@ factor = cho_factor(ATA, overwrite_a=True)
 
 def fit_3x3(img , sigma):
     a, b, c, d, e, f = cho_solve(factor, np.dot(AT, img.flatten()))
-    a = a - sigma/18.
-    b = b - sigma/18.
+    a = a - sigma
+    b = b - sigma
     m = 1. / (4 * a * b - c*c)
     x = (c * e - 2 * b * d) * m
     y = (c * d - 2 * a * e) * m

### 2014-12-10 ms/figure.tex
abstract

@@
 
-We present a 3$\times$3 method for estimating the centroid of stars in astronomical images.
-After simulating a large number of stars in a wide range of scales, in signal-to-noise-ratio, and full width at half maxima, we compare the results of our method to those obtained from the fourth order approximation method implemented in SDSS photometric pipeline, as well as finding the centroid by fitting the exact PSF model used to generate the simulated data.
-Comparison of the median squared error in centroid measurement, resulting from the proposed techniques to the Cramer-Rao lower bound of centroid estimates, suggests that, the 3$\times$3 polynomial trick, once modified by smoothing the image with a Gaussian kernel, is able to deliver sufficiently accurate estimates of centroid over a wide range of values in the parameter space.
+We present a modification of the 3$\times$3 polynomial method for estimating the centroid 
+of stars in astronomical images. After simulating a large number of stars with relatively low 
+signal-to-noise-ratio, and in a wide range of full width at half maxima, we compare the results of our method
+to those obtained from the quartic approximation method used in SDSS photometric pipeline, 
+as well as finding the centroid by fitting the exact PSF model which was used to generate the 
+simulated data. Comparison of the root-mean-squared error in centroid measurement, resulting 
+from the these techniques to the Cramer-Rao lower bound of centroid estimates, 
+suggests that, the modified 3$\times$3 polynomial trick, though not as accurate as PSF fitting method
+, is able to deliver sufficiently accurate estimates comparable to those obtained from the quartic approximation.
 

### 2014-12-10 ms/figure.tex
intro

@@
 simulated data. Comparison of the root-mean-squared error in centroid measurement, resulting 
-from the these techniques to the Cramer-Rao lower bound of centroid estimates, 
+from these techniques to the Cramer-Rao lower bound of centroid estimates, 
 suggests that, the modified 3$\times$3 polynomial trick, though not as accurate as PSF fitting method
@@
 
-A common practice in astronomy is taking imaging data, and then finding the coordinates of various light sources across the sky.
-Finding unbiased estimate of the center of point sources, convolved with telescope point spread function (and atmospheric PSF in case of ground based telescopes) and pixel response function, is crucial to further steps of astronomical image processing.
-For instance, proper measurement of the shape of galaxies requires interpolating the PSF from the position of sparsely located stars across the image to the position of galaxies.
-The accuracy of the PSF estimation therefore, depends on how accurately we know the centroid of stars.
+A common practice in astronomy is taking imaging data, and then finding the coordinates
+of various light sources across the sky. Finding unbiased estimate of the center of point
+sources, convolved with telescope point spread function (and atmospheric PSF in case of
+ground based telescopes), and pixel response function, is crucial to further steps of
+astronomical image processing. For instance, proper measurement of the shapes of galaxies
+requires interpolating the PSF from the position of sparsely located stars across the
+image to the positions of galaxies. The accuracy of the PSF estimation therefore,
+relies on how accurately we know the centroid of stars.
 
-Ideally, we want a centroiding procedure that provides measurements as accurate as possible, without putting a huge computational burden on the photometric pipeline.
-Reducing the computational cost becomes even more important in large surveys, where we want to estimate the centroid of thousands of point sources detected on the focal plane.
+Ideally, we want a centroiding procedure that provides measurements as accurate as possible,
+without putting a huge computational burden on the photometric pipeline.
+Reducing the computational cost becomes even more important in large surveys,
+where we want to estimate the centroid of thousands of point sources detected
+on the telescope's focal plane.
 
-Reaching the optimal measurement of the centroid of stars however, is limited by the lack of knowledge about the exact shape of PSF, and also presence of noise; both sky noise and CCD readout noise.
-Variance of the centroid estimate, will always have a theoretically set lower bound, known as the Cramer-Rao lower bound (hereafter denoted by CRLB) which has an inverse relation with the signal-to-noise-ratio.
-Thus, of particular interest is devising a fast method that returns less biased estimate of centroids in a realistic range of signal-to-noise ratios.
-
-To date, a number of softwares have been designed for the purpose of extracting astronomical sources and making catalogs.
-One of these softwares is SExtractor \citep{sex}, whose centroiding method involves first, finding the zeroth moment of the object as a first order estimate, and then iteratively correcting the centroid by computing the zeroth order moment of the object weighted by a Gaussian window function, until the correction falls below a particular threshold value.
+Reaching the optimal measurement of the centroid of stars however, is limited
+by the lack of knowledge about the exact shape of the PSF, and also presence of noise;
+both sky noise and CCD readout noise. Thus, of particular interest is devising a fast method that returns
+more accurate estimate of centroids in a realistic range of signal-to-noise ratios.       
+To date, a number of softwares have been designed for the purpose of extracting astronomical
+sources and making catalogs. One of these softwares is SExtractor \citep{sex},
+whose centroiding method involves first, finding the zeroth moment of the object
+as a first order estimate, and then iteratively correcting the centroid by computing
+the zeroth order moment of the object weighted by a Gaussian window function,
+until the correction falls below a particular threshold value.
 The width of the Gaussian window function is set by the object's half light radius.
 
-Another examples are DAOPHOT \citep{daophot} and DOPHOT \citep{dophot} which both assume analytic models for the stellar PSF profiles with centroid coordinates being free parameters of these models.
-DAOPHOT (DoPHOT) finds the centroid by fitting a Gaussian (power law) PSF to the light profile of stars.
+Another examples are DAOPHOT \citep{daophot}, and DOPHOT \citep{dophot}
+which both assume analytic models for the stellar PSF profiles with centroid
+coordinates being free parameters of these models.
+DAOPHOT (DoPHOT) finds the centroid by fitting a Gaussian (power law) PSF to
+the light profile of stars.
 
-In this paper, we propose to find the centroid of stars by smoothing the image of stars by a Gaussian kernel, and fitting a second order polynomial to the $3\times3$ pixels around the brightest pixel of smoothed image.
-We focus on studying the accuracy of this model by comparing the centroid measurement errors with the ones obtained from the approximate method used in SDSS.
-In order to do so, we apply these methods to a large number of simulated stars with different noise and size realizations.
+In this paper, we propose to find the centroid of stars by smoothing the image
+of stars by a Gaussian kernel, and fitting a second order polynomial to
+the $3\times3$ pixels around the brightest pixel of smoothed image.
+We focus on studying the accuracy of this model by comparing the centroid
+measurement errors with the ones obtained from the quartic approximate method used in SDSS.
+In order to do so, we apply these methods to a large number of simulated
+stars with different signal-to-noise ratio and size realizations. 
+Error from star centroiding methods, will always have 
+a theoretically set lower bound, known as the Cramer-Rao lower bound
+(hereafter denoted by CRLB) which has an inverse relation with the
+signal-to-noise-ratio of stars. Assuming the exact model of the PSF,
+one can compute the CRLB on ther centroiding error as a function of the
+parameters of the model (\eg FWHM).
 

### 2014-12-10 src/profile.py
remove e

@@ -1,7 +1,7 @@
 import numpy as np
 
 
-def makeMoffat(size , FWHM =3 , b = 2.5 , e = 0 , center = None ):
+def makeMoffat(size , fwhm =3 , b = 2.5  , center = None):
 
     #x = np.arange(0, size, 1, float)
     #y = x[:,np.newaxis]
@@ -14,10 +14,10 @@ def makeMoffat(size , FWHM =3 , b = 2.5 , e = 0 , center = None ):
         x0 = center[0]
         y0 = center[1]
     
-    a = FWHM/(2.*np.sqrt(2**(1./b) - 1.))
-    r = ((x-x0)**2. + ((y-y0)**2.)*(1. + np.abs(e))**2./(1. - np.abs(e))**2.)**.5
+    a = fwhm/(2.*(2**(1./b)-1)**.5)
+    r = ((x-x0)**2./a**2. + (y-y0)**2./a**2.)**.5
     
-    return ((b - 1.)*(1. + (r/a)**2.)**(-1.*b))/(np.pi*(a**2.))
+    return ((b - 1.)*(1. + r**2.)**(-1.*b))/(np.pi*(a**2.))
 
 def makeGaussian(size , FWHM =3 , e = 0 , center = None):
 

### 2014-12-11 script/test_fwhm.py
Update test_fwhm.py

@@ -4,15 +4,14 @@
 
 """
 Goal: This code tests centroiding of a set of 
-normalized moffat profiles with a given SNR and beta
-in a given range of full width at half maxima,
-using four different models:
+normalized moffat profiles with a given FWHM and beta
+in a given range of signal-to-noise-ratios,
+using three different models:
 SDSS method, Polynomial method, 
-and round PSF fitting method, 
-and elliptical PSF fitting.
+and PSF fitting method.
 
-Dependencies: numpy
-              
+Dependencies: numpy, profile.py,
+              poly.py, sdss.py
 Author: Mohammadjavad Vakili (July and August 2014)
 """
 
@@ -30,20 +29,19 @@ if __name__ == '__main__':
 
     o.add_option('-m', '--method', dest='method', default='poly',
         help='Set the centroiding method, polynomial or sdss or fitting, or efitting, default: polynomial')
-    o.add_option('-s', '--snr', dest='snr', default= 150, type='float',
-        help='SNR, default: 150')
+    o.add_option('-f', '--fwhm', dest='fwhm', default= 2., type='float',
+        help='FWHM of the moffat profile, default: 2')
     o.add_option('-b', '--beta', dest='beta', default= 2.5, type='float',
         help='Dimensionless parameter of Moffat profile, default: 2.5')
     
-    o.add_option('--fmin', dest='fmin', default=2., type='float',
-        help='Minimum fwhm in experiment, default: 2.')
-    o.add_option('--fmax', dest='fmax', default=5.6, type='float',
-        help='Maximum fwhm in experiment, default: 5.6')
+    o.add_option('--smin', dest='smin', default=5., type='float',
+        help='Minimum S/N in experiment, default: 10.0')
+    o.add_option('--smax', dest='smax', default=150, type='float',
+        help='Maximum S/N in experiment, default: 150.0')
     o.add_option('--size', dest='size', default=17, type='int',
         help='size of the postage_stamp')
     o.add_option('--sample', dest='sample', default=20000, type='int',
         help='number of stars in experiment')
-
[…]

### 2014-12-11 script/test_fwhm.py
Update test_fwhm.py

@@ -4,14 +4,15 @@
 
 """
 Goal: This code tests centroiding of a set of 
-normalized moffat profiles with a given FWHM and beta
-in a given range of signal-to-noise-ratios,
-using three different models:
+normalized moffat profiles with a given SNR and beta
+in a given range of full width at half maxima,
+using four different models:
 SDSS method, Polynomial method, 
-and PSF fitting method.
+and round PSF fitting method, 
+and elliptical PSF fitting.
 
-Dependencies: numpy, profile.py,
-              poly.py, sdss.py
+Dependencies: numpy
+              
 Author: Mohammadjavad Vakili (July and August 2014)
 """
 
@@ -29,19 +30,20 @@ if __name__ == '__main__':
 
     o.add_option('-m', '--method', dest='method', default='poly',
         help='Set the centroiding method, polynomial or sdss or fitting, or efitting, default: polynomial')
-    o.add_option('-f', '--fwhm', dest='fwhm', default= 2., type='float',
-        help='FWHM of the moffat profile, default: 2')
+    o.add_option('-s', '--snr', dest='snr', default= 150, type='float',
+        help='SNR, default: 150')
     o.add_option('-b', '--beta', dest='beta', default= 2.5, type='float',
         help='Dimensionless parameter of Moffat profile, default: 2.5')
     
-    o.add_option('--smin', dest='smin', default=5., type='float',
-        help='Minimum S/N in experiment, default: 10.0')
-    o.add_option('--smax', dest='smax', default=150, type='float',
-        help='Maximum S/N in experiment, default: 150.0')
+    o.add_option('--fmin', dest='fmin', default=2., type='float',
+        help='Minimum fwhm in experiment, default: 2.')
+    o.add_option('--fmax', dest='fmax', default=5.6, type='float',
+        help='Maximum fwhm in experiment, default: 5.6')
     o.add_option('--size', dest='size', default=17, type='int',
         help='size of the postage_stamp')
     o.add_option('--sample', dest='sample', default=20000, type='int',
         help='number of stars in experiment')
+
     opts, args = o.parse_args(sys.argv[1:])
 
 
[…]

### 2014-12-11 ms/figure.tex
update intro

@@
 citecolor=darkblue }
+
 \newcommand{\beq}{\begin{equation}}
@@
 \begin{document}
+
 \author{
@@
 
-\title{Towards fast and optimal centroiding of stars}
+\title{Towards fast and optimal centroiding of faint stars}
 
@@
 of stars in astronomical images. After simulating a large number of stars with relatively low 
-signal-to-noise-ratio, and in a wide range of full width at half maxima, we compare the results of our method
-to those obtained from the quartic approximation method used in SDSS photometric pipeline, 
+signal-to-noise-ratio, and in a wide range of full width at half maxima, we compare the results
+of our method to those obtained from the quartic approximation method used in SDSS photometric pipeline, 
 as well as finding the centroid by fitting the exact PSF model which was used to generate the 
@@
 suggests that, the modified 3$\times$3 polynomial trick, though not as accurate as PSF fitting method
-, is able to deliver sufficiently accurate estimates comparable to those obtained from the quartic approximation.
+, is able to deliver results sufficiently close to the Cramer-Rao lower bound.
 
@@
 A common practice in astronomy is taking imaging data, and then finding the coordinates
-of various light sources across the sky. Finding unbiased estimate of the center of point
+of various light sources across the sky. Finding accuarate estimate of the center of point
 sources, convolved with telescope point spread function (and atmospheric PSF in case of
-ground based telescopes), and pixel response function, is crucial to further steps of
+ground based telescopes), and also pixel response function, is crucial to further steps of
 astronomical image processing. For instance, proper measurement of the shapes of galaxies
@@
 both sky noise and CCD readout noise. Thus, of particular interest is devising a fast method that returns
-more accurate estimate of centroids in a realistic range of signal-to-noise ratios.       
+optimal estimates of centroids in a realistic range of signal-to-noise ratios.
+
 To date, a number of softwares have been designed for the purpose of extracting astronomical
@@
 whose centroiding method involves first, finding the zeroth moment of the object
-as a first order estimate, and then iteratively correcting the centroid by computing
+as a first-order estimate, and then iteratively correcting the centroid by computing
 the zeroth order moment of the object weighted by a Gaussian window function,
@@
 of stars by a Gaussian kernel, and fitting a second order polynomial to
-the $3\times3$ pixels around the brightest pixel of smoothed image.
-We focus on studying the accuracy of this model by comparing the centroid
-measurement errors with the ones obtained from the quartic approximate method used in SDSS.
+the $3\times$3 pixels around the brightest pixel of smoothed image.
+We compare the accuracy of this method with, the naive 3\times$3 second-order 
+polynomial method, the 3$\times$3 quartic approximation
+method used in SDSS photometric pipeline, and fitting a PSF model to the 
+star.
+
 In order to do so, we apply these methods to a large number of simulated
@@
 Error from star centroiding methods, will always have 
-a theoretically set lower bound, known as the Cramer-Rao lower bound
+a theoretically-set lower bound, known as the Cramer-Rao lower bound
 (hereafter denoted by CRLB) which has an inverse relation with the
-signal-to-noise-ratio of stars. Assuming the exact model of the PSF,
-one can compute the CRLB on ther centroiding error as a function of the
-parameters of the model (\eg FWHM).
+signal-to-noise-ratio of stars.
 
-This paper is structured as follows.
-In section \ref{sec:model}, we give a brief overview of the methods used in our investigation.
-In section \ref{sec:data}, we discuss the simulated data.
-In section \ref{sec:results}, we compare the results of our centroid measurement with those of SDSS method, once for a fixed set of full width at half maxima, and once for a set of fixed signal-to-noise-ratios.
-Finally, we discuss and conclude in \ref{sec:discussion}.
+Given the analytic model for the PSF,
+we derive an expression for CRLB on the centroiding error as
+a function of the parameters of the PSF model (\eg FWHM),
+and signal-to-noise-ratio of stars. We create two sets of simulations for which we 
+know the CRLB, one with variable (constant) signal-to-noise ratio (FWHM), and one 
+with variable (constant) FWHM (signal-to-noise ratio). After applying
+different centroiding methods to the simulations,
+we investigate how close these methods can get to saturating the CRLB for
+various ranges of background noise and FWHM.
+
+This paper is structured as follows. In section \ref{sec:method},
+we give a brief overview of the centroiding methods used in our investigation.
+In section \ref{sec:data}, we discuss the simulated data, and the CRLB on centroiding error.
+In section \ref{sec:results}, we compare the results of our proposed method with 
+those obtained from centroiding methods discussed in \ref{sec:method}, and 
+with the CRLB derived in \ref{sec:data}. Finally, we discuss and conclude
+in \ref{sec:discussion}.
 

### 2014-12-11 ms/figure.tex
update method

@@
 
-\title{Towards fast and optimal centroiding of faint stars}
+\title{Fast and optimal centroiding of faint stars}
 
@@
 
-\section{Model}\label{sec:model}
+\section{Methods}\label{sec:method}
 
-In order to find the centroid of a star, we fit a simple 2d polynomial $P(x,y)=a+bx+cy+dx^2+exy+fy^2$ to the $3\times3$ patch centered on the brightest pixel of the
-image.
-We apply this method to star images in the sky-dominated regime.
-In this regime, the covariance matrix of pixel uncertianties is simply given by $\sigma^{2}\mathbf{I}$, where $\sigma^{2}$ is variance of the uncorrelated Gaussian noise, and $\mathbf{I}$ is a 9$\times$9 identity matrix.
+\subsection{3$\times$3 polynomial method}
+
+In order to find the centroid of a star, 
+we fit a simple 2d polynomial $P(x,y)=a+bx+cy+dx^2+exy+fy^2$ to the
+$3\times3$ patch centered on the brightest pixel of the
+image. We apply this method to star images in the sky-dominated regime.
+In this regime, the covariance matrix of pixel uncertianties is simply
+given by $\sigma^{2}\mathbf{I}$, where $\sigma^{2}$ is variance of the
+uncorrelated Gaussian noise, and $\mathbf{I}$ is a 9$\times$9 identity matrix.
 Upon constructing a universal 9$\times$6 design matrix
-
 \begin{equation}
@@
 \end{equation}
-the free parameters of the model $\{a,b,c,d,e,f\}$ (hereafter compactly denoted by $\mathbf{X}$) can be determined by 
+the free parameters of the model $\{a,b,c,d,e,f\}$
+(hereafter compactly denoted by $\mathbf{X}$) can be determined by 
 \beq
@@
 \eeq
-where $\mathbf{Z}$ is given by $(I_{1},...,I_{9})^{T}$, with $I_{i}$, being the brightness of the $i-$th pixel of the 3$\times$3 patch.
+where $\mathbf{Z}$ is given by $(z_{1},...,z_{9})^{T}$,
+with $z_{i}$, being the brightness of the $i-$th pixel of the 3$\times$3 patch.
 Afterwards, the best fit parameters can be used to compute the centroid coordinate
@@
 
-Now, we modify the simple polynomial method explained above, by smoothing the image of the star with a Gaussian kernel with a given width (2 pixels in this study).
-Then we apply the same polynomial method to the 3$\times$3 patch around the brightest pixel of the smoothed image.
-The important difference between the previous approach and the modified method is that, there are non-zero covariances among the uncertainties of the brightness of different pixels of the smoothed image.
-That is, the covariance matrix $\mathbf{C}$ is non-diagonal.
+It is important to note that the algebraic operation in (\ref{center}) involves 
+inverting a 2$\times$2 curvature matrix
+\beq
+  D = 
+  \begin{bmatrix}
+      2d & e\\
+      e & 2f\\
+  \end{bmatrix}.
+\eeq
+When D has a zero (or very close to zero) deteminant,
+centroid estimated by (\ref{center}) gets arbitrarily 
+large in which case the centroiding method leads to a catastrophic 
+outlier. In order to tackle this issue, we add a small regularization term
+proportional to $\sigma$ to the diagonal elements of the curvature matrix.
+This soft regularization term prevents the determinant of the curvature matrix from
+getting zero, and removes the catastrophic outliers.
+
+\subsection{3$\times$3 modified polynomial method}
+Now, we modify the simple polynomial method explained above,
+by smoothing the image of the star with a Gaussian kernel
+\beq
+k(x) = \frac{1}{2\pi w^2}\exp(-\mathbf{x}^{2}/2w^{2}).
+\eeq
+Throughout this study, we keep the width of the Gaussian kernel $w$ constant.
+Then we apply the same polynomial method to the 3$\times$3 patch around the brightest
+pixel of the smoothed image. The important difference between the previous
+approach and the modified method is that, there are non-zero covariances
+among the uncertainties of the brightness of different pixels of the
+smoothed image. That is, the covariance matrix $\mathbf{C}$ is non-diagonal.
 It can be shown that after smoothing, elements of the covariance matrix are given by
@@
 \end{eqnarray}
-where $w$ is width of the kernel, and $x_{i}$ , $y_{i}$ are the $x$, and $y$ coordinates of the $i$-th pixel respectively.
-In the presence of the non-diagonal covariance matrix $\mathbf{C}$, equation (\ref{linearfit}) needs to be modified in the following way
+where $w$ is width of the kernel, $\sigma$ is the per-pixel uncertainty, and $x_{i}$
+, $y_{i}$ are the $x$, and $y$ coordinates of the $i$-th pixel
+respectively. In the presence of the non-diagonal covariance matrix
+$\mathbf{C}$, equation (\ref{linearfit}) needs to be modified in the following way
 \beq
@@
 \eeq
-
-Therefore, for a given star and a smoothing kernel, the outcome of equation (\ref{linearfit2}) can be plugged into equation (\ref{center}) to find the centroid estimate of the star.
-Hereafter, we call this method the modified polynomial method.
-
-Now, let us give a brief overview of centroiding method implemented in SDSS photometric pipeline \citep{sdss}: Consider any row or column of the 3$\times$3 patch around the brightest pixel of the smooth image and let us denote the brightness of these three pixels by $\{I_{-},I_{0},I_{+}\}$.
-The fundamental assumption behind the technique is that these brightness values can be approximated by the function $P(x) = Q\exp((x-x_{c})^{2}/2\beta^{2})$ evaluated at $x=-1,0,+1$; with $x_{c}$ being the position of centroid.
-Knowing the value of $P$ at $\{-1,0,1\}$, expanding $P(x)$ up to fourth order in $x$ leads to
+Therefore, for a given star and a smoothing kernel,
+the outcome of equation (\ref{linearfit2}) can be
+plugged into equation (\ref{center}) to find the centroid estimate
+of the star.
+\subsection{3$\times$3 quartic approximation method}
+Consider any row or column of the 3$\times$3 patch around
+the brightest pixel of the smooth image and let us denote
+the brightness of these three pixels by $\{I_{-},I_{0},I_{+}\}$.
+The fundamental assumption behind the technique is that these
+brightness values can be approximated
+by the function $P(x) = Q\exp((x-x_{c})^{2}/2\beta^{2})$
+evaluated at $x=-1,0,+1$; with $x_{c}$ being the position of centroid
+of the three pixels. Knowing the value of $P$ at $\{-1,0,1\}$,
+expanding $P(x)$ up to fourth order in $x$ leads to
 \beq

### 2014-12-12 ms/figure.tex
Update figure.tex

@@
 
-If we apply this method to every column and row of the 3$\times$3 patch around the brightest pixel of the smoothed image, we will find three local maxima for three rows $\{(x_{-},-1)$, $(x_{0},0)$, $(x_{+},1)\}$, and three local maxima for three columns $\{(-1,y_{-})$, $(0,y_{0})$, $(1,y_{+})\}$.
-It is important to note that, since the image has been smoothed, the covariance matrix between different pixels is not zero.
-Therefore, there is an uncertianty associated with any of these local maxima.
-The centroid is then estimated by finding the intersection of two curves, one fitted to three maxima corresponding to rows, and the other fitted to three maxima corresponding to columns.
+If we apply this procedure to every column and row of the 3$\times$3 patch
+around the brightest pixel of the smoothed image, we will find three local
+maxima for three rows $\{(x_{-},-1)$, $(x_{0},0)$, $(x_{+},1)\}$, and three
+local maxima for three columns $\{(-1,y_{-})$, $(0,y_{0})$, $(1,y_{+})\}$.
+The centroid is then estimated by finding the intersection of two curves,
+one fitted to three maxima corresponding to rows, and the other fitted
+to three maxima corresponding to columns.
+
 \section{Simulations and Tests}\label{sec:data}
 
-In order to test the accuracy of the two models and compare them against each other, we need to simulate a large set of stars for which we know the exact position of centroids.
+In order to test the accuracy of the method mentioned so far, and to ompare them against each other,
+and we need to simulate a large set of stars for which we know the exact position of centroids.
 Furthermore, we uniformly draw the centroids within sub-pixel regions. 
-
-We use the Moffat profile \citep{moffat} for our simulations.
-Moffat profile is an analytic model for stellar PSFs.
-It has broader wings than a simple Gaussian model.
-The surface brightness of the Moffat profile is given by
+We use the Moffat profile \citep{moffat} for our PSF simulations. 
+Moffat profile is an analytic model for stellar PSFs. It has broader wings than
+a simple Gaussian model. The surface brightness of the Moffat profile is given by
 \beq
@@
 \eeq
-where $F$ is the total flux, $\beta$ is a dimensionless paramter, and $\alpha$ is the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$) being $2\alpha\sqrt{2^{1/\beta}-1}$.
-We want to investigate the performance of the two models introduced in section \ref{sec:model} for different background noise levels, and also different values of $\gamma$.
-For further simplicity, we set the flux of all stars in our simulations to unity.
-Per pixel uncertainties are assumed to be uncorrelated Gaussian, and we only study the sky dominated regime.
+where $F$ is the total flux, $\beta$ is a dimensionless paramter, and $\alpha$ is
+the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$)
+being $2\alpha\sqrt{2^{1/\beta}-1}$. 
+We want to investigate the performance of centroiding methods introduced
+in section \ref{sec:model} for different background noise levels, and also different
+values of $\gamma$. For further simplicity, we set the flux of all stars in our
+simulations to unity. Per pixel uncertainties are assumed to be uncorrelated Gaussian,
+and we only study the sky-dominated regime.
 
-Moreover, it is more convenient to work with the signal-to-noise ratio (hereafter denoted by SNR) instead of the variance of the Gaussian noise.
-This is due to the fact that at the same noise level, simulated stars with different values of $\gamma$ have different SNRs.
+Moreover, it is more convenient to work with the signal-to-noise ratio
+(hereafter denoted by SNR) instead of the variance of the Gaussian noise.
+We define SNR as the ratio of the mean and variance of the distribution
+which the flux estimator is drawn from. Assume that the total flux from
+the point source is $f$, and that the PSF at the $i$-th pixel is given
+by $P_{i}$. Therefore the brightness of the $i$-th pixel is drawn from
+a Gaussian distribution $p(I_{i}) = \mathcal{N}(fP_{i},\sigma^{2})$.
 
-First, let us find an analytic expression for SNR.
-We define SNR as the ratio of the mean and variance of the distribution which the flux estimator is drawn from.
-Assume that the total flux from the point source is $f$, and that the PSF at the $i$-th pixel is given by $P_{i}$.
-Therefore the brightness of the $i$-th pixel is drawn from a Gaussian distribution $p(I_{i}) = \mathcal{N}(fP_{i},\sigma^{2})$.
-
-The optimal estimator of flux (an estimator which saturates Cramer-Rao bound), is the weighted average $\tilde{f}=\sum_{i}I_{i}P_{i}$. Knowing the distribution of $I_{i}$, it can be shown that 
+The optimal estimator of flux (one which saturates Cramer-Rao bound),
+is the weighted average $\tilde{f}=\sum_{i}I_{i}P_{i}$. Knowing the
+distribution of $I_{i}$, it can be shown that 
 \beq
@@
 
-Note that (\ref{snr}) is valid in the limit of sky-dominated images, and that is the limit we are interested in.
-In the case of our simulations, the expression (\ref{snr}) can be analytically expressed in terms of $\sigma$, $\gamma$, and also $\beta$.
-We fix $\beta$ at the fiducial value of 2.5.
+Note that (\ref{snr}) is valid in the limit of sky-dominated regimes,
+and that is the limit we are interested in. In the case of our simulations,
+SNR given in (\ref{snr}) can be analytically expressed in terms of the per pixel uncertainty
+$\sigma$, FWHM $\gamma$, and also $\beta$. We fix $\beta$ at the fiducial value of 2.5.
 In this case we have
@@
 
-Equation (\ref{snr2}) implies that for stars with the same flux $f$ and background noise level $\sigma$, those with bigger effective size have lower SNR.
-In this work, we study the relation between error in centroid measurement and $\gamma$ at fixed SNR, and vice versa.
+Equation (\ref{snr2}) implies that for stars with the same flux $f$ and background
+noise level $\sigma$, those with radius have lower SNR.
+
+We aim to study how centroiding errors from different methods behave with
+changing SNR and size, and how close they get to saturating the CRLB. 
+Given the PSF model that we have adopted for our simulations, We need 
+to derive an expression for the CRLB as a function of the size of of
+the stars, and SNR. We know that the CRLB is given by the inverse of 
+the Fisher information matrix \mathcal{F}. The closer an estimator is
+to saturating the CRLB, the more information about the quantity that we 
+need to estimate is preserved. A measure for closeness of an estimator to 
+saturating the CRLB is comparison of the root-mean-squared-error of that estimator 
+with the CRLB.
+
+In order to find the CRLB, it is sufficient to find the Fisher matrix.
+Let us assume that we have $M$ observables $\{f_{1}, ... , f_{M}\}$, each
+related to $B$ model parameters $\theta_{1} , ... , \theta_{B}$. Assuming
+un-correlated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
+of the Fisher matrix $\mathcal{F}_{ij}$ are given by
+\beq
+\mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
+\ref{fisher}
+\eeq
+
+In our case, the observables are Moffat PSF profile evaluated at different pixels, and  
+the model paramters are the centroid coordinates. Thus, \mathcal{F}
+is a 2$\times$2 matrix whose elements are given by
+
+\beq
+  \mathcal{F} = \sum_{\mathbf{p}}\frac{1}{\sigma_{p}^{2}}
+                \frac{\partial f_{\mathbf{p}}}{\partial \theta_{i}}\frac{\partial f_{\mathbf{p}}}{\partial \theta_{j}},
+\eeq
+where the summation is over pixels, $\theta={x_{c},y_{c}}$, $\sigma_{p}^{2}$ is variance
+of the uncorrelated Gaussian noise
+\begin{eqnarray}
+\langle n(\mathbf{x}) \rangle &=& 0, \\
+\langle n(\mathbf{x_{p}})n(\mathbf{x_{p^{\prime}}}) \rangle &=& \sigma^{2}\delta_{\mathbf{p}\mathbf{p}^{\prime}}. 
+\end{eqnarray}
+
 In the first experiment, we generate 100000 Moffat profiles centered randomly in the sub-pixel region inside the central pixel of a 17$\times$17 image, at four different full width at half maxima of 2, 2.8, 4, and 5.6 pixels with SNR ranging from 5 to 150.
 In the second experiment, we generate the same number of Moffat profiles with $\gamma$ ranging from 2 pixels to 6 pixels, with four different SNR values of 5, 50, 100, 150.
-
 In addition to the centroiding methods discussed in the previous sections, we compute the error from fitting the PSF model with the exact $\gamma$.
@@
 
-In order to test the accuracy of each model, we need to compare the mean squared error to the Cramer-Rao lower bound (hereafter CRLB).
-That is, after finding the centroid error for each model, we compute the mean in bins of $S/N$ (bins of $\gamma$ in the second experiment).
+In order to test the accuracy of each model, we need to compare
+the mean squared error to the Cramer-Rao lower bound (hereafter CRLB).
+That is, after finding the centroid error for each model, we
+compute the mean in bins of $S/N$ (bins of $\gamma$ in the second experiment).
 The closer the mean bias is to the CRLB, the more accurate the centroid estimate is.
@@
 In practice however, instead of mean squared error, we work with the median squared error.
-The reason is that, at the faint end of our simulations (SNR $\leq$ 10), the unmodified polynomial method leads to some catastrophic failures which could skew the mean squared centroid error of the sample.
-Thus, we use median squared error as a less biased representative of the performance of different centroiding techniques.
+The reason is that, at the faint end of our simulations (SNR $\leq$ 10),
+the unmodified polynomial method leads to some catastrophic failures which
+could skew the mean squared centroid error of the sample.
+Thus, we use median squared error as a less biased representative
+of the performance of different centroiding techniques.
 

### 2014-12-12 ms/figure.tex
Update figure.tex

@@
 the stars, and SNR. We know that the CRLB is given by the inverse of 
-the Fisher information matrix \mathcal{F}. The closer an estimator is
+the Fisher information matrix $\mathcal{F}$. The closer an estimator is
 to saturating the CRLB, the more information about the quantity that we 
@@
 Let us assume that we have $M$ observables $\{f_{1}, ... , f_{M}\}$, each
-related to $B$ model parameters $\theta_{1} , ... , \theta_{B}$. Assuming
-un-correlated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
+related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$. Assuming
+uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
 of the Fisher matrix $\mathcal{F}_{ij}$ are given by
@@
 \mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
-\ref{fisher}
+\label{fisher}
 \eeq
@@
 In our case, the observables are Moffat PSF profile evaluated at different pixels, and  
-the model paramters are the centroid coordinates. Thus, \mathcal{F}
+the model paramters are the centroid coordinates. Thus, $\mathcal{F}$
 is a 2$\times$2 matrix whose elements are given by
@@
 \beq
-  \mathcal{F} = \sum_{\mathbf{p}}\frac{1}{\sigma_{p}^{2}}
+  \mathcal{F}_{ij} = \sum_{\mathbf{p}}\frac{1}{\sigma_{p}^{2}}
                 \frac{\partial f_{\mathbf{p}}}{\partial \theta_{i}}\frac{\partial f_{\mathbf{p}}}{\partial \theta_{j}},
+\ref{fish}
 \eeq
-where the summation is over pixels, $\theta={x_{c},y_{c}}$, $\sigma_{p}^{2}$ is variance
+where the summation is over pixels, $f_{\mathbf{p}}$ is the value of the Moffat profile at pixel $\mathbf{p}$,
+$\theta=\{x_{c},y_{c}\}$, $\sigma_{p}^{2}$ is variance
 of the uncorrelated Gaussian noise
 \begin{eqnarray}
-\langle n(\mathbf{x}) \rangle &=& 0, \\
+\langle n(\mathbf{x_{p}}) \rangle &=& 0, \\
 \langle n(\mathbf{x_{p}})n(\mathbf{x_{p^{\prime}}}) \rangle &=& \sigma^{2}\delta_{\mathbf{p}\mathbf{p}^{\prime}}. 
@@
 
-In the first experiment, we generate 100000 Moffat profiles centered randomly in the sub-pixel region inside the central pixel of a 17$\times$17 image, at four different full width at half maxima of 2, 2.8, 4, and 5.6 pixels with SNR ranging from 5 to 150.
-In the second experiment, we generate the same number of Moffat profiles with $\gamma$ ranging from 2 pixels to 6 pixels, with four different SNR values of 5, 50, 100, 150.
-In addition to the centroiding methods discussed in the previous sections, we compute the error from fitting the PSF model with the exact $\gamma$.
-That is, we find the best estimates of flux and centroid by optimizing the $\chi^{2}$.
+Given the analytic expression for the Moffat PSF model (\ref{mof}), and choice of $\beta=2.5$, 
+the inverse of the Fisher matrix is given by
+\beq
+  \mathcal{F}^{-1} \simeq 0.6846 \frac{\gamma}{\text{SNR}} 
+  \begin{pmatrix}
+      1 & 0\\
+      0 & 1\\
+  \end{pmatrix}.
+\label{crlbmoffat}
+\eeq
+
+Equation (\ref{crlbmoffat}) implies that at given SNR and $\gamma$
+CRLB for each component of centroid is given by $.6846\gamma/\text{SNR}$,
+and that a good centroiding technique delivers centroids with
+root-mean-squared-error (hereafter RMSE) of each component close to
+this number.
+
+We perform two sets of simulations. In the first set, we choose four values of
+2, 2.8, 4, and 5.6 pixels for $\gamma$. For each $\gamma$, we generate 100,000 
+17 $\times$ 17 postage-stamps of Moffat profiles with centroids randomly drawn
+within the central pixel of the 17 $\times$ 17 postage-stamps. Moreover, Gaussian
+is noise added to each postage-stamp such that the stars are uniformly distributed
+in log-SNR between SNR = 5 to SNR = 150.
+
+In the second set, we generate 100,000 17$\times$17 postage-stamps
+of Moffat profile, with values of $\gamma$ randomly distributed 
+between 2 pixels and 6 pixels, and with centroids drawn randomly within 
+the central pixel. we choose four values for SNR: 5, 10, 20, and 40. 
+For each SNR, and for each postage-stamp with a given $\gamma$, 
+Gaussian noise, with variance corresponding to SNR and $\gamma$ through equation 
+(\ref{snr2}), is added to the each postage-stamp.
+
+In the first experiment, we study how centroiding error behaves with changing
+SNR, while $\gamma$ is being held constant. In the second experiment, we study 
+how centroiding error behaves with changing $\gamma$ while SNR is being held constant.
+
+In addition to the centroiding methods discussed in the previous sections,
+we compute the error from fitting the Moffat PSF model with the exact $\gamma$ to
+the data. That is, we find the best estimates of flux and centroid by
+optimizing the $\chi^{2}$. Furthermore, we computeth error from fitting a
+wrong PSF model (Gaussian profile) with the exact $\gamma$ to the data.
+In all cases in both experiments, we expect the PSF fitting method to saturate 
+the CRLB.
+
+\section{Results}\label{sec:results}
 
@@
 compute the mean in bins of $S/N$ (bins of $\gamma$ in the second experiment).
-The closer the mean bias is to the CRLB, the more accurate the centroid estimate is.
 
@@
 of the performance of different centroiding techniques.
-
-In statistics, CRLB sets a lower bound for the variance of the point estimator of a variable.
-Let us assume that the data is generated from the analytic model $f(\mathbf{x}, \{\theta\})$, where the vector $\mathbf{x}$ denotes coordinate, and $\{\theta\}$ represents parameters of the model.
-CRLB of the  estimator of the parameter $\theta_{i}$ can be computed from the inverse of the Fisher information information matrix
-\beq
-\text{CRLB}[\hat{\theta}_{i}] = (F^{-1})_{ii}, 
-\label{crlb}
-\eeq
-where the elements of the Fisher matrix can be computed according to
-\beq
-F_{ij} = \left \langle -\frac{\partial^{2} \ln \mathcal{L}}{\partial \theta_{i}\partial \theta_{j}} \right \rangle,   
-\label{fisher}
-\eeq
-where $\ln \mathcal{L}$ is the log-likelihood function (or Log probability density function of the observations) and is given by $-\chi^{2}/2$: 
-\beq
-\chi^{2} = \sigma^{-2}\sum_{\mathbf{p}}\big [ f(\mathbf{x}_{\mathbf{p}},\{\theta_{t}\})+ n(\mathbf{x}_\mathbf{p}) - f(\mathbf{x}_{\mathbf{p}},\{\theta\}) \big ]^{2},
-\label{lik}
-\eeq
-in which summation is over all pixels, ${\theta_{t}}$ represents the set of parameters used to generate the data, and $n(\mathbf{x}_{\mathbf{p}})$ is uncorrelated Gaussian noise map
-\begin{eqnarray}
-\langle n(\mathbf{x}) \rangle &=& 0, \\
-\langle n(\mathbf{x_{p}})n(\mathbf{x_{p^{\prime}}}) \rangle &=& \sigma^{2}\delta_{\mathbf{p}\mathbf{p}^{\prime}}. 
-\end{eqnarray}
-
-Combining (\ref{fisher}) and (\ref{lik}) yields
-\beq
-F_{ij} = \sigma^{-2}\sum_{\mathbf{p}}\frac{\partial f(\mathbf_{x}_{\mathbf{p}} , \{\theta_{t}\})}{\partial \theta_{i}}\frac{\partial f(\mathbf_{x}_{\mathbf{p}} , \{\theta_{t}\})}{\partial \theta_{j}}.
-\eeq
-
-Assuming the model (\ref{mof}) with $\beta = 2.5$, it can be shown that the inverse of the Fisher matrix is given by
-\beq
-  F^{-1} \simeq 0.6846 \frac{\gamma}{\text{SNR}} 
-  \begin{pmatrix}
-      1 & 0\\
-      0 & 1\\
-  \end{pmatrix}.
-\label{crlbmoffat}
-\eeq
-
-Equation (\ref{crlbmoffat}) implies that for different noise realizations of a moffat PSF at a given SNR and $\gamma$, an optimal centroiding technique delivers estimates whose mean (in this study, median) squared error along each axis is less than or equal to $0.6846 \gamma/\text{SNR}$.
-
-Moreover, it is worth investigating cases where we do not know the exact PSF model, or the model we use to find the centroid is slightly wrong.
-For instance, let us consider a set of images of stars generated from elliptical Moffat profile
-\beq
-P(r) = \frac{F(\beta - 1)}{\pi a_{1}a_{2}}\Big[1+\Big(\frac{x}{a_{1}}\Big)^{2}+\Big(\frac{y}{a_{2}}\Big)^{2}\Big]^{-\beta},
-\eeq    
-where $a_{1}$ is the major axis, $a_{2}$ is the minor axis, and for simplicity we have assumed that the major axis is along the $x$ axis.
-In this case, the CRLB associated with  the $x$ component of centroid is given by $0.6846 a_{1}/\text{SNR}$, and the CRLB associated with the $y$ component is given by $0.6846 a_{2}/\text{SNR}$.
-
-We also generate a set of elliptical Moffat profiles with $e=0.2$, and $a_{1} = 2.8$ pixels, with signal-to-noise ratios ranging from 5 to 150.
-In addition to the exact (elliptical) PSF model, we use circular PSF model with $\gamma = \sqrt{a_{1}a_{2}}$ to find the centroid of these stars.
-
-\section{Results}\label{sec:results}
 

### 2014-12-12 ms/figure.tex
Update figure.tex

@@
 We want to investigate the performance of centroiding methods introduced
-in section \ref{sec:model} for different background noise levels, and also different
+in section \ref{sec:method} for different background noise levels, and also different
 values of $\gamma$. For further simplicity, we set the flux of all stars in our
@@
 \beq
-  \mathcal{F}_{ij} = \sum_{\mathbf{p}}\frac{1}{\sigma_{p}^{2}}
+  \mathcal{F}_{ij} = \sum_{\mathbf{p}}\frac{1}{\sigma_{\mathbf{p}}^{2}}
                 \frac{\partial f_{\mathbf{p}}}{\partial \theta_{i}}\frac{\partial f_{\mathbf{p}}}{\partial \theta_{j}},
-\ref{fish}
+\label{fish}
 \eeq
 where the summation is over pixels, $f_{\mathbf{p}}$ is the value of the Moffat profile at pixel $\mathbf{p}$,
-$\theta=\{x_{c},y_{c}\}$, $\sigma_{p}^{2}$ is variance
-of the uncorrelated Gaussian noise
+$\theta=\{x_{c},y_{c}\}$, $\sigma_{\mathbf{p}}^{2}$ is variance
+of the uncorrelated Gaussian noise map $n(\mathbf{x_{p}})$
 \begin{eqnarray}
@@
 Equation (\ref{crlbmoffat}) implies that at given SNR and $\gamma$
-CRLB for each component of centroid is given by $.6846\gamma/\text{SNR}$,
+CRLB for each component of centroid is given by $0.6846\gamma/\text{SNR}$,
 and that a good centroiding technique delivers centroids with
@@
 
-In order to test the accuracy of each model, we need to compare
-the mean squared error to the Cramer-Rao lower bound (hereafter CRLB).
-That is, after finding the centroid error for each model, we
-compute the mean in bins of $S/N$ (bins of $\gamma$ in the second experiment).
-
-In practice however, instead of mean squared error, we work with the median squared error.
-The reason is that, at the faint end of our simulations (SNR $\leq$ 10),
-the unmodified polynomial method leads to some catastrophic failures which
-could skew the mean squared centroid error of the sample.
-Thus, we use median squared error as a less biased representative
-of the performance of different centroiding techniques.
-
 \subsection{Experiment 1}
 
+After finding the centroiding error for each method, we
+compute the RMSE in bins of SNR.
 Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}].
-As we expected, for all methods, median squared error becomes larger for fainter stars, and for stars with larger $\gamma$.
-As it can be seen in figure [\ref{1}], centroid estimate obtained from the polynomial method does not saturate the CRLB unless at smaller values of SNR.
+As we expected, for all methods, median squared error becomes larger for fainter stars,
+and for stars with larger $\gamma$. As it can be seen in figure [\ref{1}],
+centroid estimate obtained from the polynomial method does not saturate
+the CRLB unless at smaller values of SNR.
 
-The modified polynomial centroiding however, is able to deliver median squared error arbitrarily close to the CRLB in all ranges of SNR.
-At $\gamma = 2$ the modified centroiding estimate does not saturates the CRLB, but as $\gamma$ gets larger, centroid estimates of this techniques saturate and eventually, get lower than the CRLB.
-The median error from the SDSS method shows similar behaviour to that of modified polynomial method.
+The modified polynomial centroiding however, is able to deliver
+median squared error arbitrarily close to the CRLB in all ranges
+of SNR. At $\gamma = 2$ the modified centroiding estimate does not
+saturates the CRLB, but as $\gamma$ gets larger,
+centroid estimates of this techniques saturate and eventually,
+get lower than the CRLB. The median error from the SDSS method
+shows similar behaviour to that of modified polynomial method.
 See figures [\ref{2}], [\ref{3}].
-And finally, the centroid estimates from the exact fitting the exact PSF model give rise to a median error that is always below the CRLB [\ref{4}].
+And finally, the centroid estimates from the exact fitting the exact PSF
+model give rise to a median error that is always below the CRLB [\ref{4}].
 

### 2014-12-12 ms/figure.tex
Update figure.tex

@@
 the $3\times$3 pixels around the brightest pixel of smoothed image.
-We compare the accuracy of this method with, the naive 3\times$3 second-order 
+We compare the accuracy of this method with, the naive 3$\times$3 second-order 
 polynomial method, the 3$\times$3 quartic approximation
@@
 \beq
-k(x) = \frac{1}{2\pi w^2}\exp(-\mathbf{x}^{2}/2w^{2}).
+k(\mathbf{x}) = \frac{1}{2\pi w^2}\exp(-\mathbf{x}^{2}/2w^{2}).
 \eeq
@@
 is noise added to each postage-stamp such that the stars are uniformly distributed
-in log-SNR between SNR = 5 to SNR = 150.
+in log-SNR between SNR = 5 to SNR = 100.
 
@@
 
-After finding the centroiding error for each method, we
-compute the RMSE in bins of SNR.
-Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}].
-As we expected, for all methods, median squared error becomes larger for fainter stars,
-and for stars with larger $\gamma$. As it can be seen in figure [\ref{1}],
-centroid estimate obtained from the polynomial method does not saturate
-the CRLB unless at smaller values of SNR.
+In this experiment, after finding the centroiding error for each method, we compute the RMSE in bins of SNR in order to compare it to the CRLB. 
+Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}], [\ref{5}]. All methods deliver results with RMSE larger for fainter stars.
+In case of 3$\times$3 polynomial centroiding [\ref{1}], RMSE becomes very large as we move towards the fainter stars in our simulation.
+Moreover, we observe a kink in the plot of RMSE against SNR.
+For stars with larger $\gamma$, this kink moves toward higher values of SNR.
+As it can be seen in figure [\ref{1}], centroid estimate from the polynomial method do not even get close to saturating the CRLB.
+By increasing $\gamma$, RMSE moves further away from the CRLB.
 
-The modified polynomial centroiding however, is able to deliver
-median squared error arbitrarily close to the CRLB in all ranges
-of SNR. At $\gamma = 2$ the modified centroiding estimate does not
-saturates the CRLB, but as $\gamma$ gets larger,
-centroid estimates of this techniques saturate and eventually,
-get lower than the CRLB. The median error from the SDSS method
-shows similar behaviour to that of modified polynomial method.
-See figures [\ref{2}], [\ref{3}].
-And finally, the centroid estimates from the exact fitting the exact PSF
-model give rise to a median error that is always below the CRLB [\ref{4}].
+However, RMSE from the modified centroiding method [\ref{2}], and RMSE from the quartic approximation [\ref{3}] method are very close to the CRLB.
+As we increase $\gamma$ from 2 pixels to 2.8 pixels, RMSE gets closer to the CRLB.
+This implies that as stars get undersampled, the performance of these two models get slightly worse.
+But if we increase $\gamma$ to 4 and 5.6 pixels, RMSE gets farther from the CRLB.
+This is quite predictable since these two models only use the information contained in a 3$\times$ 3 patch.
+It is also important to note that the rate at which the RMSE from these two method drops eventually becomes smaller than the constant rate at which the CRLB decreases with increaing SNR.
+
+As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{4}] lies on the CRLB.
+Thus, centroid estimates from fitting the exact PSF model always saturate the CRLB.
+As it can be seen in figure [\ref{5}], even the centroid estimates found by fitting a wrong PSF model (Gaussian PSF) to the simulated stars saturate the CRLB.
 
 \subsection{Experiment 2}
+In this experiment, after finding the centroiding error for each method, we compute the RMSE in bins of $\gamma$ in order to compare it to the CRLB. 
+Behavior of error as a function of $\gamma$ for different values of SNR, is shown in figures [\ref{6}], [\ref{7}], and [\ref{8}], [\ref{9}], and [\ref{10}].
 
-Behavior of error as a function of $\gamma$ for different values of SNR, is shown in figures [\ref{5}], [\ref{6}], [\ref{7}], and [\ref{8}]. 
-By decreasing noise level of the background sky, $\Delta x$ becomes smaller at all ranges of $\gamma$.
+The centroid estimates obtained from the 3$\times$3 polynomial method [\ref{6}] result in RMSE much larger than the CRLB in all ranges of FWHM and for all four values of SNR in this experiment.
+In the case of extremely faint stars (SNR = 5), the polynomial method is not able to deliver any reliable estimate, and completely fails.
 
-The polynomial method fails to saturate the CRLB except in simulations with SNR of 5.
-The modified polynomial method, and the SDSS method result in  median squared error always lower than CRLB, except in simulated stars with small $\gamma$.
-As we expect, the median error from fitting the exact PSF model always saturates the CRLB.
+The 3$\times$3 modified polynomial method [\ref{7}], and the 3$\times$3 quartic approximation [\ref{8}] result in RMSE very close to the CRLB.
+For al four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels, RMSE gets slightly closer to the CRLB since these two models start to work slightly worse as we decrease $\gamma$ and move towards undersampled stars.
+After approximately 3 pixels, increasing $\gamma$ deviate RMSE of these methods from the CRLB.
+This is inherent characteristic of all
+3$\times$3 methos. Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) closer to the CRLB.
 
-\subsection{Elliptical PSF}
-
-In the last experiment, we compare the performances of the modified polynomial method, and SDSS method, with fitting the exact PSF model to the elliptical Moffat profiles, and also with fitting a circular PSF model.
-
-The median error from the modified polynomial and SDSS methods are very close to the CRLB.
-But only by fitting an approximate (circular) PSF profile, or eventually by fitting an exact PSF model, one can saturate the CRLB.
-However, it is important to note that centroiding errors of all four methods are extremely close to each other.
+Again The RMSE from centroiding by fitting the exact PSF model as a function of FWHM perfectly lies on the CRLB [\ref{9}].
+Thus, centroid estimates from fitting the exact PSF model always saturate the CRLB.
+Once again, we observe that the centroid estimates found by fitting a Gaussian PSF to the simulated stars also saturate the CRLB in all ranges of $\gamma$ [\ref{10}].
 
@@
 In this work, we proposed a method for centroiding stars based on fitting a low order polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel. 
-Employing this technique into large scale astronomical surveys can considerably reduce the computational cost of initial astrometry of these surveys.
+Furthermore, we compared the performance of this method with the naive 3$\times$3 polynomial centroiding, 3$\times$3 quartic approximation, and PSF fitting.
+In order to make this comparison, we performed some tests on a large number of simulated data, and investigated to see if these estimators can saturate the Cramer-Rao lower bound, or how close to they get to saturating the bound.
+
+Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns centroid estimates that saturate the CRLB.
+We found that the estimates found by 3$\times$3 polynomial method are far away from saturating the CRLB.
+On the other hand, the RMSE of centroid estimates of our proposed 3$\times$3 modified polynomial method, and that of the 3$\times$3 quartic approximation, are much closer to the CRLB.
+The performance of these two methods however, is limited by two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} size of the stars.
+
+These two techniques only take advantage of the information contained in a 3$\times$3 patch around the brighest pixel of the smoothed image. Thus, when we apply 
+these methods to find the centroid of stars with larger FWHM, a certain amount of information (encoded in the Cramer-Rao lower bound) is lost, and therefore, the RMSE of these methods deviates from the CRLB.
+This deviation gets even larger at lower signal-to-noise ratios.
+Besides, the performance of these methods slightly degrades in the case of undersampled stars.
+Presence of noise is another limitting factor.
+Although these methods are able to get close to saturating the CRLB in a wide range of signal-to-noise ratios, they are not as reliable in the extremely faint stars (SNR less than 10).
+This is mostly due to the fact that presence of noise could move the true brightest pixel of image.
+
+In this investigation we showed that PSF fitting is always better at centroiding stars.
+In practice however, we do no know the the exact PSF.
+Besides finding the centroid by PSF fitting is computationally expensive whereas by employing tht 3$\times$3 modified polynomial technique into large scale astronomical surveys can considerably reduce the computational cost of initial astrometry of these surveys.
 The advantage of this method becomes more pronounced in PSF estimation in which we need to know the centroid of stars accurately, but at the same time, with fewer number of algebraic operations.
+This method can roughly be thousand times faster than centroiding by model fitting, and requires fewer operations than the 3$\times$3 quartic approximation mehod.
 
-This method can roughly be thousand times faster than centroiding through model fitting, and requires fewer operations than the method implemented in SDSS photo pipeline.
-More importantly, it requires no prior knowledge about the shape of the PSF.
-
-Comparison of this technique with the centroiding method based on a fourth-order approximation implemented in SDSS photo pipeline suggests that in wide ranges of size and noise level of the background sky, the error arising from this method is close to the theoretically set CRLB, and comparable to the error obtained from SDSS method.
-
-Although having a reasonable PSF model should always deliver better centroid estimates, one can achieve sensibly accurate results by employing this simple 3$\times$3 method without making any assumption about the PSF model.
+Having a reasonable PSF model should always deliver better centroid estimates, but over a certain range of low signal-to-noise ratios, one can achieve sensibly accurate results by employing this simple 3$\times$3 method without making any assumption about the PSF model.
 
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
 In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{1}
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the modified polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 modified polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
 In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{2}
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the SDSS method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 quartic aproximation method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
 In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{3}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_fitting.png}
+  \includegraphics[width=\linewidth]{snr_psf.png}
 \endminipage
@@
 \minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{snr_wrongpsf.png}
+\endminipage
+\caption{Scatter plots showing the relation between error in centroid measurement from fitting a Gaussian PSF model to the stars and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{5}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
   \includegraphics[width=\linewidth]{fwhm_poly.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{5}
+\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{6}
 \end{figure}
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the modified polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{6}
+\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 modified polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{7}
 \end{figure}
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the SDSS method and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{7}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_fitting.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right).
+\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 quartic approximation method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
 In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{8}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_wrongpsf.png}
+  \includegraphics[width=\linewidth]{fwhm_psf.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from: the SDSS method (upper left), the modified polynomial method (upper right), fitting circular PSF model (lower left), and  fitting the exact PSF model (lower right) and SNR of stars with major axis of 2.8 pixels and ellipticity of 0.2.
+\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
 In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{9}
@@
 
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{fwhm_wrongpsf.png}
+\endminipage
+\captionScatter plots showing the relation between error in centroid measurement from fitting a Gaussian PSF model and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
+In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{10}
+\end{figure}
+
 \end{document}

### 2014-12-12 ms/mainscatter.py
Delete mainscatter.py

@@ -1,148 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-plt.rcParams['text.latex.preamble'] = [r"\usepackage{lmodern}"]
-params = {'text.usetex' : True, 'font.size' : 17 , 'font.family' : 'lmodern' , 'text.latex.unicode' : True, }
-plt.rcParams.update(params)
-
-################################################################# DATA #####################################
-
-s1 = (np.loadtxt("noise1_20_00.txt"))
-s2 = (np.loadtxt("noise1_40_00.txt"))
-s3 = (np.loadtxt("noise1_60_00.txt"))
-s4 = (np.loadtxt("noise1_80_00.txt"))
-a1 = np.loadtxt("erx1_20_00.txt")
-a2 = np.loadtxt("erx1_40_00.txt")
-a3 = np.loadtxt("erx1_60_00.txt")
-a4 = np.loadtxt("erx1_80_00.txt")
-
-################################################################# FLAGGED OBJECTS ##########################
-
-crap1 = np.array([1])#np.loadtxt("flag2_20_0.txt").astype(int)
-crap2 = np.array([1])#np.loadtxt("flag2_28_0.txt").astype(int)
-crap3 = np.array([1])#np.loadtxt("flag2_40_0.txt").astype(int)
-crap4 = np.array([1])#np.loadtxt("flag2_56_0.txt").astype(int)
-
-fig , axarr = plt.subplots(2 , 2 , sharex= True, sharey= True) 
-
-total_bins = 400
-###################################################################### axarr[0,0] ################
-a = s1
-b = a1
-
-a_clean = np.delete(s1, crap1,  axis=0)
-a_flag = a[crap1]
-
-b_clean = np.delete(a1, crap1,  axis=0)
-b_flag = b[crap1]
-
-bins = 10.**np.linspace(np.log10(a.min()), np.log10(a.max()), total_bins)
-delta = bins[1]-bins[0]
-idx  = np.digitize(a,bins)
-
-axarr[0,0].loglog(np.sort(a) , (2.*.68466)/(np.sort(a)) , 'g-', lw = 1 , alpha = 1.)
[…]

### 2014-12-12 ms/mainscatterf.py
Delete mainscatterf.py

@@ -1,155 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-plt.rcParams['text.latex.preamble'] = [r"\usepackage{lmodern}"]
-params = {'text.usetex' : True, 'font.size' : 17 , 'font.family' : 'lmodern' , 'text.latex.unicode' : True, }
-plt.rcParams.update(params)
-
-
-
-s1 = np.loadtxt("fwhm5_s5_00tb.txt")
-s2 = np.loadtxt("fwhm5_s10_00.txt")
-s3 = np.loadtxt("fwhm5_s20_00.txt")
-s4 = np.loadtxt("fwhm5_s40_00.txt")
-a1 = np.loadtxt("erx5_s5_00tb.txt")
-a2 = np.loadtxt("erx5_s10_00.txt")
-a3 = np.loadtxt("erx5_s20_00.txt")
-a4 = np.loadtxt("erx5_s40_00.txt")
-
-
-crap1 = np.array([1]) #np.loadtxt("flag5_s10_0.txt").astype(int)
-crap2 = np.array([1]) #np.loadtxt("flag5_s50_0.txt").astype(int)
-crap3 = np.array([1]) #np.loadtxt("flag5_s100_0.txt").astype(int)
-crap4 = np.array([1]) #np.loadtxt("flag5_s150_0.txt").astype(int)
-
-
-
-labels = [ 'S/N=5' ,  'S/N=10' ,  'S/N=20' ,  'S/N=40']
-
-fig , axarr = plt.subplots(2,2 , sharex = True , sharey = True) 
-
-total_bins = 40
-###################################################################### axarr[0,0] ################
-
-a = np.delete(s1, crap1,  axis=0)
-b = np.delete(a1, crap1,  axis=0)
-#a = a[b<10.]
-#b = b[b<10.]
-
-bins = np.linspace(a.min(), a.max(), total_bins)
-delta = bins[1]-bins[0]
-idx  = np.digitize(a,bins)
-
-textstr = 'S/N=5'
-
-axarr[0,0].text(0.6, 0.15, textstr, transform=axarr[0,0].transAxes, fontsize=18,
-        verticalalignment='top')
-
-axarr[0,0].semilogy(np.sort(a) , (np.sort(a)*.68466)/5. , 'g-', lw = 1 , alpha = 1. )
-axarr[0,0].scatter(a , b**.5 , s=1 , c = 'y' , marker='+' , alpha = 1.)
[…]

### 2014-12-14 src/fitting.py
change opt method

@@ -1,40 +1,38 @@
 import numpy as np
 import scipy.optimize as op
 
-def Moffat(data , FWHM , b , x0 , y0 , x , y ):
-   
+def Moffat(FWHM , b , flux , x0 , y0 , x , y ):
     
-    a = FWHM/(2.*np.sqrt(2**(1./b) - 1.))
+    a = FWHM/(2.*np.sqrt(2.**(1./b) - 1.))
     r = ((x-x0)**2. +(y-y0)**2.)**.5
-    return ((b - 1.)*(1. + (r/a)**2.)**(-1.*b))/(a*np.pi)
+    return (flux*(b - 1.)*(1. + (r/a)**2.)**(-1.*b))/(np.pi*a**2.)
+
+def lnlike(theta , I , sigma , FWHM , b , x , y):
+
+    flux , x0 , y0 = theta
+    model = Moffat(FWHM , b , flux , x0 , y0 , x , y )
+    inv_sigma2 = sigma**-2.
+    return -0.5 * (np.sum((I - model)**2.*inv_sigma2 - np.log(inv_sigma2)))
 
 
 
-def lnlike(theta , I , x , y):
 
-    FWHM , b , x0 , y0 = theta
-    model = Moffat(I , FWHM , b, x0 , y0 , x ,y)
-    inv_sigma2 = 1.
-    return -0.5*(np.sum((I-model)**2*inv_sigma2 - np.log(inv_sigma2)))
-
-
-
-def fitting_centroid(I):
+def fitting_centroid(I , sigma , FWHM , b):
     size = I.shape[0]
     x = np.linspace(0.5, size - .5, size)
     y = x[:,np.newaxis]
-    FWHM_true = I.shape[0]/4.
-    b_true = 2.5
     x0_true = I.shape[0]/2.
     y0_true = I.shape[0]/2.
+    flux0_true = 1.
     size = I.shape[0]
     x = np.linspace(0.5, size - .5, size)
     y = x[:,np.newaxis]
     nll = lambda *args: -lnlike(*args)
-    results = op.minimize(nll , [FWHM_true , b_true , x0_true , y0_true] , args = (I , x , y))
-    FWHM_ml , b_ml , x0_ml , y0_ml = results["x"]
+    results = op.fmin(nll , [flux0_true , x0_true , y0_true] , args = (I , sigma , FWHM , b , x , y) , disp = False)
+ 
+    #flux0_ml , x0_ml , y0_ml = results["x"]
 
[…]

### 2014-12-16 ms/figure.tex
Update figure.tex

@@
 
-We present a modification of the 3$\times$3 polynomial method for estimating the centroid 
-of stars in astronomical images. After simulating a large number of stars with relatively low 
-signal-to-noise-ratio, and in a wide range of full width at half maxima, we compare the results
-of our method to those obtained from the quartic approximation method used in SDSS photometric pipeline, 
-as well as finding the centroid by fitting the exact PSF model which was used to generate the 
-simulated data. Comparison of the root-mean-squared error in centroid measurement, resulting 
-from these techniques to the Cramer-Rao lower bound of centroid estimates, 
-suggests that, the modified 3$\times$3 polynomial trick, though not as accurate as PSF fitting method
-, is able to deliver results sufficiently close to the Cramer-Rao lower bound.
+One of the most demanding tasks in astronomical image processing is centroiding of stars. 
+The upcoming large scale astronomical surveys are going to take images of billions of point sources, 
+including many faint stars, in short exposure times. Thus, real-time accurate estimation of the
+centroid of stars is crucial for further analysis of the photometric data such as PSF estimation,
+and infering the proper motion of stars. In this work, we aim to compare the performances of
+fast and profile-fitting centroiding methods when applied to relatively low signal-to-noise ratio
+stars in a wide range of full width at half maxima.
+Besides, in order to see how information preserving these techniques are, we compare
+the root-mean-squared-error arising from these centroiding techniques with the Cramer-Rao
+lower bound. The methods we discuss in this paper are: the naive 3$\times$3 polynomial centroiding,
+a modification of this method, 3$\times$3 quartic approximation, and PSF profile fitting.
+We find that 3$\times$3 modified polynomial cetroiding leads to
+significant improvement in comparison with the naive polynomial centroiding, and gives rise
+to centroiding errors comparable to those of 3$\times$3 quartic approximation method.
+Moreover, our findings suggest that the 3$\times$3 modified polynomial, and the 3$\times$3
+quartic approximation techniques, though not as accurate as PSF profile fitting methods,
+are able to deliver results sufficiently close to saturating the Cramer-Rao lower bound in a range 
+of relatively faint stars.
 

### 2014-12-16 ms/figure.tex
Update figure.tex

@@
 and infering the proper motion of stars. In this work, we aim to compare the performances of
-fast and profile-fitting centroiding methods when applied to relatively low signal-to-noise ratio
-stars in a wide range of full width at half maxima.
-Besides, in order to see how information preserving these techniques are, we compare
-the root-mean-squared-error arising from these centroiding techniques with the Cramer-Rao
+fast and slow profile-fitting centroiding methods against each other, when they are applied
+to relatively low signal-to-noise ratio stars in a wide range of full width at half maxima.
+Furthermore, in order to investigate how information-preserving these techniques are, we compare
+the root-mean-squared-error arising from these centroiding methods with the Cramer-Rao
 lower bound. The methods we discuss in this paper are: the naive 3$\times$3 polynomial centroiding,
 a modification of this method, 3$\times$3 quartic approximation, and PSF profile fitting.
-We find that 3$\times$3 modified polynomial cetroiding leads to
-significant improvement in comparison with the naive polynomial centroiding, and gives rise
-to centroiding errors comparable to those of 3$\times$3 quartic approximation method.
+We find that in comparison with the naive polynomial centroiding, the modified polynomial
+cetroiding leads to significant improvements, and gives rise to centroiding errors comparable
+to those of the 3$\times$3 quartic approximation method.
 Moreover, our findings suggest that the 3$\times$3 modified polynomial, and the 3$\times$3

### 2014-12-16 ms/figure.tex
abstract updates

--- 2014-12-12 ms/figure.tex
@@
 \begin{abstract}
-
-We present a modification of the 3$\times$3 polynomial method for estimating the centroid 
-of stars in astronomical images. After simulating a large number of stars with relatively low 
-signal-to-noise-ratio, and in a wide range of full width at half maxima, we compare the results
-of our method to those obtained from the quartic approximation method used in SDSS photometric pipeline, 
-as well as finding the centroid by fitting the exact PSF model which was used to generate the 
-simulated data. Comparison of the root-mean-squared error in centroid measurement, resulting 
-from these techniques to the Cramer-Rao lower bound of centroid estimates, 
-suggests that, the modified 3$\times$3 polynomial trick, though not as accurate as PSF fitting method
-, is able to deliver results sufficiently close to the Cramer-Rao lower bound.
-
+One of the most demanding tasks in astronomical image processing---in terms of precision---is the centroiding of stars. 
+Upcoming large surveys are going to take images of billions of point sources, 
+including many faint stars, with short exposure times. Real-time estimation of the
+centroid of stars is crucial for real-time PSF estimation, and precision is required
+for measurements of proper motion. In this work, we aim to compare the performance of
+fast and slow centroiding methods, when they are applied
+to relatively low signal-to-noise ratio stars in a wide range of psf sizes.
+In order to investigate how information-preserving these techniques are, we compare
+the root-mean-squared-error arising from these centroiding methods with the fundamental Cramer-Rao
+lower bound. The methods we discuss in this paper include weighted moments, naive 3$\times$3 polynomial centroiding,
+the 3$\times$3 quartic approximation used in the \textsl{Sloan Digital Sky Surveys}, and PSF profile fitting
+(with both the correct and the incorrect PSF).
+We recommend a particular form of polynomial cetroiding; it is very fast.
+Although it is not as accurate as PSF profile fitting with a good PSF estimate,
+it comes close to saturating the Cramer-Rao lower bound in a wide range of conditions.
 \end{abstract}

### 2014-12-31 ms/figure.tex
Update figure.tex

@@
 
+\subsection{7$\times$7 weighted moments}
+
+In addition to the methods mentioned above, we examine weighted moment method which
+requires taking a 7$\times$7 patch of image around the brightest pixel,
+weighting the pixels by the intensity, and computing the first moments (or center
+of mass) of the weighted 7$\times$7 patch thereafter.
+
 \section{Simulations and Tests}\label{sec:data}
@@
 
-In this experiment, after finding the centroiding error for each method, we compute the RMSE in bins of SNR in order to compare it to the CRLB. 
+In this experiment, after finding the centroiding error for each method,
+we compute the RMSE in bins of SNR in order to compare it to the CRLB. 
 Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}], [\ref{5}]. All methods deliver results with RMSE larger for fainter stars.
@@
 \minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{snr_moment.png}
+\endminipage
+\caption{Scatter plots showing the relation between error in centroid measurement
+from the 7$\times$7 weighted moment method and the signal-to-noise ratio of stars,
+with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right)
+pixels. In each scatter plot, the blue line represents the running median of data points,
+and the green line represents CRLB.}\label{4}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
   \includegraphics[width=\linewidth]{snr_psf.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model to the stars and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{4}
+\caption{Scatter plots showing the relation between error in centroid measurement
+from fitting the exact PSF model to the stars and the signal-to-noise ratio of stars,
+with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right)
+pixels. In each scatter plot, the blue line represents the running median of data points,
+and the green line represents CRLB.}\label{5}
 \end{figure}
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from fitting a Gaussian PSF model to the stars and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{5}
+\caption{Scatter plots showing the relation between error in centroid
+measurement from fitting a Gaussian PSF model to the stars and the signal-to-noise
+ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left),
+and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the
+running median of data points, and the green line represents CRLB.}\label{6}
 \end{figure}
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{6}
+\caption{Scatter plots showing the relation between error in centroid measurement
+from the 3$\times$3 polynomial method and FWHM of stars, with SNR  of : 5 (upper left),
+10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue
+line represents the running median of data points, and the green line represents CRLB.}\label{7}
 \end{figure}
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 modified polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{7}
+\caption{Scatter plots showing the relation between error in centroid measurement
+from the 3$\times$3 modified polynomial method and FWHM of stars, with SNR  of 
+: 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each
+scatter plot, the blue line represents the running median of data points, and the
+green line represents CRLB.}\label{8}
 \end{figure}
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 quartic approximation method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{8}
+\caption{Scatter plots showing the relation between error in centroid measurement from
+the 3$\times$3 quartic approximation method and FWHM of stars, with SNR  of : 5 (upper left),
+10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line
+represents the running median of data points, and the green line represents CRLB.}\label{9}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{fwhm_moment.png}
+\endminipage
+\caption{Scatter plots showing the relation between error in centroid
+measurement from the 7$\times$7 weighted moment method and FWHM of stars,
+with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
+In each scatter plot, the blue line represents the running median of data points,
+and the green line represents CRLB.}\label{10}
 \end{figure}
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{9}
+\caption{Scatter plots showing the relation between error in centroid measurement
+from fitting the exact PSF model and FWHM of stars, with SNR  of : 5 (upper left),
+10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot,
+the blue line represents the running median of data points, and the
+green line represents CRLB.}\label{11}
 \end{figure}
@@
 \endminipage
-\captionScatter plots showing the relation between error in centroid measurement from fitting a Gaussian PSF model and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{10}
+\captionScatter plots showing the relation between error in centroid measurement
+from fitting a Gaussian PSF model and FWHM of stars, with SNR  of : 5 (upper left),
+10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the
+blue line represents the running median of data points, and the green line represents CRLB.}\label{12}
 \end{figure}

### 2014-12-31 ms/figure.tex
Update figure.tex

@@
 we compute the RMSE in bins of SNR in order to compare it to the CRLB. 
-Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}], [\ref{5}]. All methods deliver results with RMSE larger for fainter stars.
-In case of 3$\times$3 polynomial centroiding [\ref{1}], RMSE becomes very large as we move towards the fainter stars in our simulation.
+Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}],
+[\ref{3}], [\ref{4}], [\ref{5}], [\ref{6}]. All methods deliver results
+with RMSE larger for fainter stars.
+In case of 3$\times$3 polynomial centroiding [\ref{1}], RMSE becomes
+very large as we move towards the fainter stars in our simulation.
 Moreover, we observe a kink in the plot of RMSE against SNR.
 For stars with larger $\gamma$, this kink moves toward higher values of SNR.
-As it can be seen in figure [\ref{1}], centroid estimate from the polynomial method do not even get close to saturating the CRLB.
-By increasing $\gamma$, RMSE moves further away from the CRLB.
+As it can be seen in figure [\ref{1}], centroid estimate from the polynomial
+method do not even get close to saturating the CRLB. By increasing $\gamma$,
+RMSE moves further away from the CRLB.
 
-However, RMSE from the modified centroiding method [\ref{2}], and RMSE from the quartic approximation [\ref{3}] method are very close to the CRLB.
-As we increase $\gamma$ from 2 pixels to 2.8 pixels, RMSE gets closer to the CRLB.
-This implies that as stars get undersampled, the performance of these two models get slightly worse.
-But if we increase $\gamma$ to 4 and 5.6 pixels, RMSE gets farther from the CRLB.
-This is quite predictable since these two models only use the information contained in a 3$\times$ 3 patch.
-It is also important to note that the rate at which the RMSE from these two method drops eventually becomes smaller than the constant rate at which the CRLB decreases with increaing SNR.
+However, RMSE from the modified centroiding method [\ref{2}],
+and RMSE from the quartic approximation [\ref{3}] method are very
+close to the CRLB except at the very small values of SNR (SNR $<$ 10).
+As we increase $\gamma$ from 2 pixels to 2.8 pixels, RMSE gets closer
+to the CRLB. This implies that as stars get undersampled, the performance
+of these two models get slightly worse. But if we increase $\gamma$ to
+4 and 5.6 pixels, RMSE gets farther from the CRLB.
+This effect is quite predictable since these two models only use the
+information contained in a 3$\times$ 3 patch. It is also important to
+note that the rate at which the RMSE from these two method drops
+eventually becomes smaller than the constant rate at which the CRLB
+decreases with increaing SNR. Also the results from 7$\times$7 weighted moment
+method [\ref{4}] suggest that this method does worse than the qurtic approximation, and
+the modified polynomial method, and at low values of SNR the centroiding RMSE from
+this method moves significantly away from the CRLB.
 
-As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{4}] lies on the CRLB.
-Thus, centroid estimates from fitting the exact PSF model always saturate the CRLB.
-As it can be seen in figure [\ref{5}], even the centroid estimates found by fitting a wrong PSF model (Gaussian PSF) to the simulated stars saturate the CRLB.
+As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{5}]
+lies on the CRLB except at values of SNR below 10 where the RMSE gets slightly pulled away
+from the CRLB because of the presence of a few outliers.
+Thus, centroid estimates from fitting the exact PSF model always
+saturate the CRLB. As it can be seen in figure [\ref{6}],
+even the centroid estimates found by fitting a wrong PSF model (Gaussian PSF)
+to the simulated stars saturate the CRLB.
 
 \subsection{Experiment 2}
-In this experiment, after finding the centroiding error for each method, we compute the RMSE in bins of $\gamma$ in order to compare it to the CRLB. 
-Behavior of error as a function of $\gamma$ for different values of SNR, is shown in figures [\ref{6}], [\ref{7}], and [\ref{8}], [\ref{9}], and [\ref{10}].
+In this experiment, after finding the centroiding error for each method, we
+compute the RMSE in bins of $\gamma$ in order to compare it to the CRLB. 
+Behavior of error as a function of $\gamma$ for different values of SNR,
+is shown in figures [\ref{7}], [\ref{8}], and [\ref{9}], [\ref{10}], [\ref{11}], and [\ref{12}].
 
-The centroid estimates obtained from the 3$\times$3 polynomial method [\ref{6}] result in RMSE much larger than the CRLB in all ranges of FWHM and for all four values of SNR in this experiment.
-In the case of extremely faint stars (SNR = 5), the polynomial method is not able to deliver any reliable estimate, and completely fails.
+The centroid estimates obtained from the 3$\times$3 polynomial method [\ref{7}]
+result in RMSE much larger than the CRLB in all ranges of FWHM and for all four
+values of SNR in this experiment. In the case of extremely faint stars (SNR = 5),
+the polynomial method is not able to deliver any reliable estimate, and completely fails.
 
-The 3$\times$3 modified polynomial method [\ref{7}], and the 3$\times$3 quartic approximation [\ref{8}] result in RMSE very close to the CRLB.
-For al four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels, RMSE gets slightly closer to the CRLB since these two models start to work slightly worse as we decrease $\gamma$ and move towards undersampled stars.
+The 3$\times$3 modified polynomial method [\ref{8}], and the 3$\times$3
+quartic approximation [\ref{9}] result in RMSE very close to the CRLB.
+For al four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels,
+RMSE gets slightly closer to the CRLB since these two models start to work
+slightly worse as we decrease $\gamma$ and move towards undersampled stars.
 After approximately 3 pixels, increasing $\gamma$ deviate RMSE of these methods from the CRLB.
-This is inherent characteristic of all
-3$\times$3 methos. Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) closer to the CRLB.
+This is inherent characteristic of all 3$\times$3 methos. 
+Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) get
+closer to the CRLB. Also we observe that in the case of 7$\times$7 weighted moment 
+centroiding, deviation of the centroiding RMSE from the CRLB is significantly higher
+than those of 3$\times$3 quartic approximation, and 3$\times$3 modified polynomial.
 
-Again The RMSE from centroiding by fitting the exact PSF model as a function of FWHM perfectly lies on the CRLB [\ref{9}].
-Thus, centroid estimates from fitting the exact PSF model always saturate the CRLB.
-Once again, we observe that the centroid estimates found by fitting a Gaussian PSF to the simulated stars also saturate the CRLB in all ranges of $\gamma$ [\ref{10}].
+Again The RMSE from centroiding by fitting the exact PSF model as a function of FWHM
+perfectly lies on the CRLB [\ref{11}] except at SNR = 5 where the RMSE slightly deviates
+from the CRLB due tp the presence of outliers. Thus, centroid estimates from fitting
+the exact PSF model always saturate the CRLB. Once again, we observe that the centroid
+estimates found by fitting a Gaussian PSF to the simulated stars also saturate
+-- except in the case of SNR = 5-- the CRLB in all ranges of $\gamma$ [\ref{12}].
 
@@
 
-In this work, we proposed a method for centroiding stars based on fitting a low order polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel. 
-Furthermore, we compared the performance of this method with the naive 3$\times$3 polynomial centroiding, 3$\times$3 quartic approximation, and PSF fitting.
-In order to make this comparison, we performed some tests on a large number of simulated data, and investigated to see if these estimators can saturate the Cramer-Rao lower bound, or how close to they get to saturating the bound.
+In this work, we proposed a method for centroiding stars based on fitting a low order
+polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel. 
+Furthermore, we compared the performance of this method with the naive 3$\times$3 polynomial
+centroiding, 3$\times$3 quartic approximation, and PSF fitting.
+In order to make this comparison, we performed some tests on a large number of
+simulated data, and investigated to see if these estimators can saturate the Cramer-Rao
+lower bound, or how close to they get to saturating the bound.
 
-Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns centroid estimates that saturate the CRLB.
-We found that the estimates found by 3$\times$3 polynomial method are far away from saturating the CRLB.
-On the other hand, the RMSE of centroid estimates of our proposed 3$\times$3 modified polynomial method, and that of the 3$\times$3 quartic approximation, are much closer to the CRLB.
-The performance of these two methods however, is limited by two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} size of the stars.
+Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
+centroid estimates that saturate the CRLB. We found that the estimates found by 3$\times$3
+polynomial method are far away from saturating the CRLB. On the other hand, the RMSE of
+centroid estimates of our proposed 3$\times$3 modified polynomial method, and that of the
+3$\times$3 quartic approximation, are much closer to the CRLB. The performance of these two
+methods however, is limited by two important factors: \emph{(i)} signal-to-noise ratio,
+and \emph{(ii)} size of the stars.
 
-These two techniques only take advantage of the information contained in a 3$\times$3 patch around the brighest pixel of the smoothed image. Thus, when we apply 
-these methods to find the centroid of stars with larger FWHM, a certain amount of information (encoded in the Cramer-Rao lower bound) is lost, and therefore, the RMSE of these methods deviates from the CRLB.
-This deviation gets even larger at lower signal-to-noise ratios.
-Besides, the performance of these methods slightly degrades in the case of undersampled stars.
-Presence of noise is another limitting factor.
-Although these methods are able to get close to saturating the CRLB in a wide range of signal-to-noise ratios, they are not as reliable in the extremely faint stars (SNR less than 10).
-This is mostly due to the fact that presence of noise could move the true brightest pixel of image.
+These two techniques only take advantage of the information contained in a 3$\times$3
+patch around the brighest pixel of the smoothed image. Thus, when we apply 
+these methods to find the centroid of stars with larger FWHM, a certain amount of
+information (encoded in the Cramer-Rao lower bound) is lost, and therefore, the RMSE
+of these methods deviates from the CRLB. This deviation gets even larger at lower
+signal-to-noise ratios. Besides, the performance of these methods slightly degrades
+in the case of undersampled stars. Presence of noise is another limitting factor.
+Although these methods are able to get close to saturating the CRLB in a wide range of
+signal-to-noise ratios, they are not as reliable in the extremely faint stars
+(SNR less than 10). This is mostly due to the fact that presence of noise could
+move the true brightest pixel of image.
 
 In this investigation we showed that PSF fitting is always better at centroiding stars.
-In practice however, we do no know the the exact PSF.
-Besides finding the centroid by PSF fitting is computationally expensive whereas by employing tht 3$\times$3 modified polynomial technique into large scale astronomical surveys can considerably reduce the computational cost of initial astrometry of these surveys.
-The advantage of this method becomes more pronounced in PSF estimation in which we need to know the centroid of stars accurately, but at the same time, with fewer number of algebraic operations.
-This method can roughly be thousand times faster than centroiding by model fitting, and requires fewer operations than the 3$\times$3 quartic approximation mehod.
+In practice however, we do no know the the exact PSF. Besides finding the centroid by PSF
+fitting is computationally expensive whereas by employing tht 3$\times$3 modified polynomial
+technique into large scale astronomical surveys can considerably reduce the computational cost
+of initial astrometry of these surveys. The advantage of this method becomes more pronounced
+in PSF estimation in which we need to know the centroid of stars accurately, but at the
+same time, with fewer number of algebraic operations. This method can roughly be thousand
+times faster than centroiding by model fitting, and requires fewer operations than the
+3$\times$3 quartic approximation mehod.
 
-Having a reasonable PSF model should always deliver better centroid estimates, but over a certain range of low signal-to-noise ratios, one can achieve sensibly accurate results by employing this simple 3$\times$3 method without making any assumption about the PSF model.
+Having a reasonable PSF model should always deliver better centroid estimates, but
+over a certain range of low signal-to-noise ratios, one can achieve sensibly accurate
+results by employing this simple 3$\times$3 method without making any assumption about
+the PSF model.
 
-In this investigation we narrowed our focus on a set of data simulated from a very specific model.
-Although there are various cases where Moffat profiles provide reasonable representation of point spread function, these models are not generic enough to let us reach a more general conclusion.
-Another important, and untapped, area of study would be devising a model that infers the centroid of stars and point spread function (in its full extent, not at the catalog level) across an astronomical image simultaneously.
+In this investigation we narrowed our focus on a set of data simulated from a very specific
+model. Although there are various cases where Moffat profiles provide reasonable
+representation of point spread function, these models are not generic enough to let us
+reach a more general conclusion. Another important, and untapped, area of study
+would be devising a model that infers the centroid of stars and point spread function
+(in its full extent, not at the catalog level) across an astronomical image simultaneously.
 This is beyond the scope of this study.

### 2015-01-30 ms/figure.tex
Update figure.tex

@@
 
-In this work, we proposed a method for centroiding stars based on fitting a low order
+An optimal stellar centroiding algorithm must always saturate the Cramer-Rao lower 
+bound. That is, in all ranges of background noise level, size, radial light profile,
+and shape, it must preserve information about the centroid of stars. In practice however,
+that is only achievable when we know the exact PSF. Since, we do not know the exact PSF
+profile, we make use of various approximate centroiding algorithms. In this work, we
+studied how different methods get close to saturating the CRLB for relatively low SNR
+stars.
+
+We also proposed a method for centroiding stars based on fitting a low order
 polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel. 
 Furthermore, we compared the performance of this method with the naive 3$\times$3 polynomial
-centroiding, 3$\times$3 quartic approximation, and PSF fitting.
+centroiding, 3$\times$3 quartic approximation, moment-based method, and PSF fitting.
 In order to make this comparison, we performed some tests on a large number of
@@
 Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
-centroid estimates that saturate the CRLB. We found that the estimates found by 3$\times$3
-polynomial method are far away from saturating the CRLB. On the other hand, the RMSE of
-centroid estimates of our proposed 3$\times$3 modified polynomial method, and that of the
-3$\times$3 quartic approximation, are much closer to the CRLB. The performance of these two
-methods however, is limited by two important factors: \emph{(i)} signal-to-noise ratio,
-and \emph{(ii)} size of the stars.
+centroid estimates that saturate the CRLB; with the exception of SNR being less than 10, 
+in which a few centroiding ouliers caused the RMSE to slightly, but not significantly, deviate
+from the CRLB.
+
+We found that the estimates found by 3$\times$3 polynomial method are far away from
+saturating the CRLB. On the other hand, the RMSE of centroid estimates of our proposed
+3$\times$3 modified polynomial method, and that of the 3$\times$3 quartic approximation,
+are much closer to the CRLB. The performance of these two methods however, is limited by
+two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} size of the stars.
 

### 2015-01-30 ms/figure.tex
Update figure.tex

@@
 in which a few centroiding ouliers caused the RMSE to slightly, but not significantly, deviate
-from the CRLB.
-
-We found that the estimates found by 3$\times$3 polynomial method are far away from
+from the CRLB. We found that the estimates found by 3$\times$3 polynomial method are far away from
 saturating the CRLB. On the other hand, the RMSE of centroid estimates of our proposed
@@
 signal-to-noise ratios, they are not as reliable in the extremely faint stars
-(SNR less than 10). This is mostly due to the fact that presence of noise could
-move the true brightest pixel of image.
+(SNR less than 10). This is mostly due to the fact that in the presence of noise, 
+the brightest pixel of image, does not necessarily contain the centroid of stars.
 
@@
 technique into large scale astronomical surveys can considerably reduce the computational cost
-of initial astrometry of these surveys. The advantage of this method becomes more pronounced
+of initial astrometry of these surveys.
+
+It is important to note that the PSF fitting method can be made faster by only keeping the 
+term proportional to the product of the PSF model and the image in $\chi^2$. This is because 
+the other terms are not sensitive to the position of centroid. However, this only allows
+us to vary the poition of centroid, and not the flux, while fitting the PSF model
+to the star.
+
+Modifying the $\chi^2$ such that it contains the product of the PSF and image, 
+provides a nice interpretation for the PSF fitting method. It corresponds to oversampling
+of the image with the correct PSF, and finding the centroid in the oversampled image afterwards.
+On the other hand, one can think of the initial smoothing step in 3$\times$3 methods
+such as modified polynomial and quartic approximation methods, as oversampling of the 
+image with an approximate Gaussian PSF. The fitting and approximate methods are different 
+in that after upsamlping, in the approximate methods, our knowledge is limited to the 3$\times$3 
+patch around the brightest pixel and as a result, we loose some information.
+
+The advantage of this method becomes more pronounced
 in PSF estimation in which we need to know the centroid of stars accurately, but at the

### 2015-02-13 ms/figure.tex
Update figure.tex

@@
 \begin{abstract}
-One of the most demanding tasks in astronomical image processing---in terms of precision---is the centroiding of stars. 
-Upcoming large surveys are going to take images of billions of point sources, 
+One of the most demanding tasks in astronomical image processing---in terms of precision---is
+the centroiding of stars. Upcoming large surveys are going to take images of billions of point sources, 
 including many faint stars, with short exposure times. Real-time estimation of the
@@
 the root-mean-squared-error arising from these centroiding methods with the fundamental Cramer-Rao
-lower bound. The methods we discuss in this paper include weighted moments, naive 3$\times$3 polynomial centroiding,
-the 3$\times$3 quartic approximation used in the \textsl{Sloan Digital Sky Surveys}, and PSF profile fitting
-(with both the correct and the incorrect PSF).
-We recommend a particular form of polynomial cetroiding; it is very fast.
-Although it is not as accurate as PSF profile fitting with a good PSF estimate,
-it comes close to saturating the Cramer-Rao lower bound in a wide range of conditions.
+lower bound.
+
+%include weighted moments, naive 3$\times$3 polynomial centroiding,
+%the 3$\times$3 quartic approximation used in the \textsl{Sloan Digital Sky Surveys}, and PSF profile fitting
+%(with both the correct and the incorrect PSF).
+%We recommend a particular form of polynomial cetroiding; it is very fast.
+%Although it is not as accurate as PSF profile fitting with a good PSF estimate,
+%it comes close to saturating the Cramer-Rao lower bound in a wide range of conditions.
 \end{abstract}

### 2015-02-15 ms/figure.tex
Update figure.tex

@@
 \begin{abstract}
-One of the most demanding tasks in astronomical image processing---in terms of precision---is
-the centroiding of stars. Upcoming large surveys are going to take images of billions of point sources, 
+One of the most demanding tasks in astronomical image processing---in terms of precision---is the centroiding of stars. 
+Upcoming large surveys are going to take images of billions of point sources, 
 including many faint stars, with short exposure times. Real-time estimation of the
@@
 the root-mean-squared-error arising from these centroiding methods with the fundamental Cramer-Rao
-lower bound.
+lower bound. We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
+of the PSF, (ii) when we do not know the PSF. In the case that we know the PSF, we show that a fast
+ polynomial centroiding after smoothing the image by the PSF can be 
+as accurate as PSF profile fitting with a good PSF estimate. In the case that we do not
+know the PSF, we demonstrate that although a particular form of polynomial centroiding method is not as
+accurate as PSF profile fitting, it comes close to saturating the Cramer-Rao lower bound
+in a wide range of conditions.
 

### 2015-02-16 ms/figure.tex
Update figure.tex

@@
 
-In this paper, we propose to find the centroid of stars by smoothing the image
-of stars by a Gaussian kernel, and fitting a second order polynomial to
-the $3\times$3 pixels around the brightest pixel of smoothed image.
-We compare the accuracy of this method with, the naive 3$\times$3 second-order 
-polynomial method, the 3$\times$3 quartic approximation
-method used in SDSS photometric pipeline, and fitting a PSF model to the 
-star.
-
-In order to do so, we apply these methods to a large number of simulated
-stars with different signal-to-noise ratio and size realizations. 
-Error from star centroiding methods, will always have 
+In this paper, we study how optimal various techniques are at centroiding 
+faint stars. That is, we apply a number of centroiding methods 
+to a large number of simulated stars with different signal-to-noise ratio and
+ size realizations. Error from star centroiding methods, will always have 
 a theoretically-set lower bound, known as the Cramer-Rao lower bound
@@
 Given the analytic model for the PSF,
-we derive an expression for CRLB on the centroiding error as
-a function of the parameters of the PSF model (\eg FWHM),
+we derive an expression for the fundamental lower bound on the centroiding error as
+a function of the parameters of the PSF model (\eg size),
 and signal-to-noise-ratio of stars. We create two sets of simulations for which we 
@@
 various ranges of background noise and FWHM.
+
+In this work, we focus on three centroiding methods. The first method finds
+ the centroid of stars by smoothing the image of
+ stars by a Gaussian kernel of a fixed size, and fitting a second order
+ polynomial to the $3\times$3 patch around the brightest pixel of smoothed
+ image. This method is fast and does not require any knowledge of the 
+PSF. In the second method, we apply the same polynomial centroiding to the
+ $3\times$3 patch around the brightest pixel of the image of star convolved 
+with the full PSF postage stamp. The last method that we consider, is fitting 
+a PSF profile, assuming that we have a good PSF estimate, to the star.
+%We compare the accuracy of this method with, the naive 3$\times$3 second-order 
+%polynomial method, the 3$\times$3 quartic approximation
+%method used in SDSS photometric pipeline, and fitting a PSF model to the 
+%star.
 
@@
 
-\subsection{3$\times$3 polynomial method}
+\subsection{Non PSF-based methods}
+
+\item {\bf 3$\times$3 polynomial centroiding}\quad
 
@@
 image. We apply this method to star images in the sky-dominated regime.
-In this regime, the covariance matrix of pixel uncertianties is simply
-given by $\sigma^{2}\mathbf{I}$, where $\sigma^{2}$ is variance of the
-uncorrelated Gaussian noise, and $\mathbf{I}$ is a 9$\times$9 identity matrix.
 Upon constructing a universal 9$\times$6 design matrix
@@
 \eeq
-When D has a zero (or very close to zero) deteminant,
+When $D$ has a zero (or very close to zero) deteminant,
 centroid estimated by (\ref{center}) gets arbitrarily 
 large in which case the centroiding method leads to a catastrophic 
-outlier. In order to tackle this issue, we add a small regularization term
-proportional to $\sigma$ to the diagonal elements of the curvature matrix.
-This soft regularization term prevents the determinant of the curvature matrix from
-getting zero, and removes the catastrophic outliers.
+outlier. In order to tackle this issue, we add a soft regularization term
+proportional to $\sigma^{2}$ to the determinant of $D$.
 
-\subsection{3$\times$3 modified polynomial method}
+\item {\bf 3$\times$3 modified polynomial method I}\quad
+
 Now, we modify the simple polynomial method explained above,
@@
 \eeq
-Throughout this study, we keep the width of the Gaussian kernel $w$ constant.
+Throughout this study, we keep the width of the Gaussian kernel $w$ constant and equal to
+1.2 pixels (corresponding to FWHM = 2.8 pixels).
 Then we apply the same polynomial method to the 3$\times$3 patch around the brightest
-pixel of the smoothed image. The important difference between the previous
-approach and the modified method is that, there are non-zero covariances
-among the uncertainties of the brightness of different pixels of the
-smoothed image. That is, the covariance matrix $\mathbf{C}$ is non-diagonal.
-It can be shown that after smoothing, elements of the covariance matrix are given by
-\begin{eqnarray}
-\mathbf{C}_{ij} &=& \frac{\sigma^{2}}{4\pi w^{2}} \exp(-\frac{r_{ij}^{2}}{4\pi w^{2}}),\\
-r_{ij}^{2} &=& (x_{i} - x_{j})^{2} + (y_{i} - y_{j})^{2},
-\label{nondiagonal}
-\end{eqnarray}
-where $w$ is width of the kernel, $\sigma$ is the per-pixel uncertainty, and $x_{i}$
-, $y_{i}$ are the $x$, and $y$ coordinates of the $i$-th pixel
-respectively. In the presence of the non-diagonal covariance matrix
-$\mathbf{C}$, equation (\ref{linearfit}) needs to be modified in the following way
-\beq
-\mathbf{X} = [\mathbf{A}^{T}\mathbf{C}^{-1}\mathbf{A}]^{-1}[\mathbf{A}^{T}\mathbf{C}^{-1}\mathbf{Z}].
-\label{linearfit2}
-\eeq
-Therefore, for a given star and a smoothing kernel,
-the outcome of equation (\ref{linearfit2}) can be
+pixel of the smoothed image. Therefore, for a given star and a smoothing kernel,
+the outcome of equation (\ref{linearfit}) can be
 plugged into equation (\ref{center}) to find the centroid estimate
 of the star.
-\subsection{3$\times$3 quartic approximation method}
-Consider any row or column of the 3$\times$3 patch around
-the brightest pixel of the smooth image and let us denote
-the brightness of these three pixels by $\{I_{-},I_{0},I_{+}\}$.
-The fundamental assumption behind the technique is that these
-brightness values can be approximated
-by the function $P(x) = Q\exp((x-x_{c})^{2}/2\beta^{2})$
-evaluated at $x=-1,0,+1$; with $x_{c}$ being the position of centroid
-of the three pixels. Knowing the value of $P$ at $\{-1,0,1\}$,
-expanding $P(x)$ up to fourth order in $x$ leads to
-\beq
-x = \frac{s}{t}(1+k\frac{t}{4Q}(1-(s/t)^{2})),
-\eeq
-where k = 1.33, and
 
-\begin{eqnarray}
-s&=&(I_{+}-I_{-})/2, \\
-t &=&2I_{0} - (I_{+}+I_{-}), \\
-Q &=& I_{0} +s^{2}/2t.
-\label{def}
-\end{eqnarray}
+\subsection{PSF-based methods}
 
-If we apply this procedure to every column and row of the 3$\times$3 patch
-around the brightest pixel of the smoothed image, we will find three local
-maxima for three rows $\{(x_{-},-1)$, $(x_{0},0)$, $(x_{+},1)\}$, and three
-local maxima for three columns $\{(-1,y_{-})$, $(0,y_{0})$, $(1,y_{+})\}$.
-The centroid is then estimated by finding the intersection of two curves,
-one fitted to three maxima corresponding to rows, and the other fitted
-to three maxima corresponding to columns.
+\item {\bf 3$\times$3 modified polynomial method II}\quad
 
-\subsection{7$\times$7 weighted moments}
+Consider the case that we have a good estimate of the PSF at
+the position of the faint star under consideration. Therefore, we 
+can modify the smoothing step in the following way. Instead of smoothing
+with a Gaussian kernel with a fixed size, we convolve the image of star
+with the full postage stamp of the PSF. Then, we apply the same polynomial
+fitting to the 3$\times$3 patch around the brightest pixel of the convolved image.
 
-In addition to the methods mentioned above, we examine weighted moment method which
-requires taking a 7$\times$7 patch of image around the brightest pixel,
-weighting the pixels by the intensity, and computing the first moments (or center
-of mass) of the weighted 7$\times$7 patch thereafter.
+The procedure of convolving the image of star with the PSF results in a
+more well-sampled, which eventually, leads to having more
+information regarding the centroid of stars in the 3$\times$3 patch around the
+brightest pixel. In addition, a simple 2d polynomial will provides a better fit 
+since convolution with the PSF makes the variation of the image across the 3 pixels
+very smooth.
 
-\section{Simulations and Tests}\label{sec:data}
+\item {\bf psf profile fitting}\quad
 
-In order to test the accuracy of the method mentioned so far, and to ompare them against each other,
-and we need to simulate a large set of stars for which we know the exact position of centroids.
-Furthermore, we uniformly draw the centroids within sub-pixel regions. 
+In addition to the methods mentioned so far, we examine fitting stars with the exact
+ PSF profile. That is, in our Cramer-Rao bound saturation tests, That is, we find the best
+ estimates of flux and centroid by
+optimizing the $\chi^{2}$. We expect this method to perform better in determing the centroid
+ of stars. In theory, it always saturates the CRLB.
+
+\section{Simulations and Cramer-Rao saturation tests}\label{sec:data}
+
+In order to test the accuracy of the method mentioned in section \ref{sec:method},
+ and to compare their performance at saturating the Cramer-Rao bound against each other, 
+we need to simulate a large set of stars for which we know the exact position of centroids.
+Furthermore, we uniformly draw the centroids of these simulated stars within sub-pixel regions. 
 We use the Moffat profile \citep{moffat} for our PSF simulations. 
 Moffat profile is an analytic model for stellar PSFs. It has broader wings than
-a simple Gaussian model. The surface brightness of the Moffat profile is given by
+a simple Gaussian profile. The surface brightness of the Moffat profile is given by
 \beq
@@
 being $2\alpha\sqrt{2^{1/\beta}-1}$. 
-We want to investigate the performance of centroiding methods introduced
+We aim to investigate the performance of centroiding methods introduced
 in section \ref{sec:method} for different background noise levels, and also different
@@
 which the flux estimator is drawn from. Assume that the total flux from
-the point source is $f$, and that the PSF at the $i$-th pixel is given
+the point source is $F$, and that the PSF at the $i$-th pixel is given
 by $P_{i}$. Therefore the brightness of the $i$-th pixel is drawn from
-a Gaussian distribution $p(I_{i}) = \mathcal{N}(fP_{i},\sigma^{2})$.
+a Gaussian distribution $p(I_{i}) = \mathcal{N}(FP_{i},\sigma^{2})$.
 
 The optimal estimator of flux (one which saturates Cramer-Rao bound),
-is the weighted average $\tilde{f}=\sum_{i}I_{i}P_{i}$. Knowing the
+is the weighted average $\tilde{F}=\sum_{i}I_{i}P_{i}$. Knowing the
 distribution of $I_{i}$, it can be shown that 
 \beq
-p(\tilde{f}) = \mathcal{N}(f , \frac{\sigma^{2}}{\sum_{i}P_{i}^{2}}),
+p(\tilde{F}) = \mathcal{N}(F , \frac{\sigma^{2}}{\sum_{i}P_{i}^{2}}),
 \eeq  
@@
 Note that (\ref{snr}) is valid in the limit of sky-dominated regimes,
-and that is the limit we are interested in. In the case of our simulations,
-SNR given in (\ref{snr}) can be analytically expressed in terms of the per pixel uncertainty
+and that is the limit we are interested in throughout our investigation.
+ In the case of our simulations, SNR given in (\ref{snr}) can be analytically
+ expressed in terms of the per pixel uncertainty
 $\sigma$, FWHM $\gamma$, and also $\beta$. We fix $\beta$ at the fiducial value of 2.5.
@@
 
-Equation (\ref{snr2}) implies that for stars with the same flux $f$ and background
-noise level $\sigma$, those with radius have lower SNR.
+Equation (\ref{snr2}) implies that for stars with the same flux $F$,
+ and background
+noise level $\sigma$, those with higher size have lower SNR.
 
@@
 changing SNR and size, and how close they get to saturating the CRLB. 
-Given the PSF model that we have adopted for our simulations, We need 
-to derive an expression for the CRLB as a function of the size of of
-the stars, and SNR. We know that the CRLB is given by the inverse of 
-the Fisher information matrix $\mathcal{F}$. The closer an estimator is
-to saturating the CRLB, the more information about the quantity that we 
+The closer an estimator is to saturating the CRLB, the more information
+ about the quantity that we 
 need to estimate is preserved. A measure for closeness of an estimator to 
@@
 
-In order to find the CRLB, it is sufficient to find the Fisher matrix.
+Given the PSF model that we have adopted for our simulations, we need 
+to derive an expression for the CRLB as a function of the size, and SNR of stars.
+ We know that the CRLB is given by the inverse of 
+the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
+ it is sufficient to compute the Fisher matrix.
 Let us assume that we have $M$ observables $\{f_{1}, ... , f_{M}\}$, each
@@
 
-Equation (\ref{crlbmoffat}) implies that at given SNR and $\gamma$
+Equation (\ref{crlbmoffat}) implies that at given SNR and $\gamma$,
 CRLB for each component of centroid is given by $0.6846\gamma/\text{SNR}$,
@@
 within the central pixel of the 17 $\times$ 17 postage-stamps. Moreover, Gaussian
-is noise added to each postage-stamp such that the stars are uniformly distributed
-in log-SNR between SNR = 5 to SNR = 100.
+noise is added to each postage-stamp such that the simulated stars are uniformly
+ distributed in log-SNR between SNR = 5 to SNR = 100.
 
@@
 between 2 pixels and 6 pixels, and with centroids drawn randomly within 
-the central pixel. we choose four values for SNR: 5, 10, 20, and 40. 
+the central pixel. We choose four values for SNR: 5, 10, 20, and 40. 
 For each SNR, and for each postage-stamp with a given $\gamma$, 
@@
 In the first experiment, we study how centroiding error behaves with changing
-SNR, while $\gamma$ is being held constant. In the second experiment, we study 
-how centroiding error behaves with changing $\gamma$ while SNR is being held constant.
-
-In addition to the centroiding methods discussed in the previous sections,
-we compute the error from fitting the Moffat PSF model with the exact $\gamma$ to
-the data. That is, we find the best estimates of flux and centroid by
-optimizing the $\chi^{2}$. Furthermore, we computeth error from fitting a
-wrong PSF model (Gaussian profile) with the exact $\gamma$ to the data.
-In all cases in both experiments, we expect the PSF fitting method to saturate 
-the CRLB.
+SNR, while $\gamma$ is held constant. In the second experiment, we study 
+how centroiding error behaves with changing $\gamma$ while SNR is held constant.
 
@@
 Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}],
-[\ref{3}], [\ref{4}], [\ref{5}], [\ref{6}]. All methods deliver results
+[\ref{3}], [\ref{4}]. All methods deliver results
 with RMSE larger for fainter stars.
 In case of 3$\times$3 polynomial centroiding [\ref{1}], RMSE becomes
-very large as we move towards the fainter stars in our simulation.
-Moreover, we observe a kink in the plot of RMSE against SNR.
-For stars with larger $\gamma$, this kink moves toward higher values of SNR.
-As it can be seen in figure [\ref{1}], centroid estimate from the polynomial
-method do not even get close to saturating the CRLB. By increasing $\gamma$,
-RMSE moves further away from the CRLB.
+quite large as we move towards fainter stars in our simulation.
+For stars with larger $\gamma$, centroid estimate from the naive polynomial
+method show large deviation from the CRLB. By increasing $\gamma$,
+RMSE deviates further away from the CRLB.
 
-However, RMSE from the modified centroiding method [\ref{2}],
-and RMSE from the quartic approximation [\ref{3}] method are very
-close to the CRLB except at the very small values of SNR (SNR $<$ 10).
+However, RMSE from the modified centroiding method I [\ref{2}],
+is very close to the CRLB except at the very small values of SNR (SNR $<$ 10).
 As we increase $\gamma$ from 2 pixels to 2.8 pixels, RMSE gets closer
-to the CRLB. This implies that as stars get undersampled, the performance
-of these two models get slightly worse. But if we increase $\gamma$ to
-4 and 5.6 pixels, RMSE gets farther from the CRLB.
-This effect is quite predictable since these two models only use the
-information contained in a 3$\times$ 3 patch. It is also important to
-note that the rate at which the RMSE from these two method drops
+to the CRLB. Besides, Also, when we increase $\gamma$ to
+4 and 5.6 pixels, RMSE gets farther from the CRLB. For stars with $\gamma$ = 2 pixels, 
+the rate at which the RMSE from this method drops
 eventually becomes smaller than the constant rate at which the CRLB
-decreases with increaing SNR. Also the results from 7$\times$7 weighted moment
-method [\ref{4}] suggest that this method does worse than the qurtic approximation, and
-the modified polynomial method, and at low values of SNR the centroiding RMSE from
-this method moves significantly away from the CRLB.
+decreases with increaing SNR. The reason for this is that even after smoothing
+the with a Gaussian kernel, the image is still not well-sampled, and smooth enough
+for a 2d polynomial fitting to provide highly accurate centroiding estimates.
+For stars with $\gamma=2.8$ pixels, since the FWHM of the Gaussian kernel matches that 
+of the underlying simulations, the smooth images are well-sampled and therefore, 
+the method is able to deliver estimates very close to saturating the CRLB. As $\gamma$
+gets higher for the simulations, the convolved images are not as well-sampled as those 
+whose $\gamma$ matches the FWHM of the smoothing kernel and as a result, we loose
+some information by fitting a polynomial to only a 3$\times$3 patch. That is the 
+reason for why we observe slight deviation from the CRLB for stas with $\gamma$ = 4 pixels, and 
+slightly more deviations as we increase $\gamma$ to 5.6 pixels.
 
-As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{5}]
-lies on the CRLB except at values of SNR below 10 where the RMSE gets slightly pulled away
-from the CRLB because of the presence of a few outliers.
-Thus, centroid estimates from fitting the exact PSF model always
-saturate the CRLB. As it can be seen in figure [\ref{6}],
-even the centroid estimates found by fitting a wrong PSF model (Gaussian PSF)
-to the simulated stars saturate the CRLB.
+As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{4}]
+lies on the CRLB except for simulations with SNR = 5 where the RMSE gets slightly pulled away
+from the CRLB due to presence of a few outliers. Figure [\ref{3}] demonstrates that even the modified centroiding
+ method II is able deliver centroiding estimates as accurate as PSF profile fitting, with the exception
+of simulated stars with $\gamma$ = 2 pixels. For stars with $\gamma$ = 2 pixels, the 3$\times$3 polynomial
+fitting fails to saturate the CRLB since the PSF is undersampled. For simulated images higher $\gamma$, convolving the
+data with the PSF result in images that are well-sampled around the brightest pixel. This allows the 
+polynomial centroiding to deliver highly accurate results that can saturate the CRLB for simulated
+data with SNR $\ga$ 10.
 
 \subsection{Experiment 2}
+
 In this experiment, after finding the centroiding error for each method, we
@@
 Behavior of error as a function of $\gamma$ for different values of SNR,
-is shown in figures [\ref{7}], [\ref{8}], and [\ref{9}], [\ref{10}], [\ref{11}], and [\ref{12}].
+is shown in figures [\ref{5}], [\ref{6}], and [\ref{7}], and [\ref{8}].
 
-The centroid estimates obtained from the 3$\times$3 polynomial method [\ref{7}]
+The centroid estimates obtained from the naive 3$\times$3 polynomial method [\ref{5}]
 result in RMSE much larger than the CRLB in all ranges of FWHM and for all four
@@
 
-The 3$\times$3 modified polynomial method [\ref{8}], and the 3$\times$3
-quartic approximation [\ref{9}] result in RMSE very close to the CRLB.
-For al four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels,
-RMSE gets slightly closer to the CRLB since these two models start to work
-slightly worse as we decrease $\gamma$ and move towards undersampled stars.
-After approximately 3 pixels, increasing $\gamma$ deviate RMSE of these methods from the CRLB.
-This is inherent characteristic of all 3$\times$3 methos. 
-Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) get
-closer to the CRLB. Also we observe that in the case of 7$\times$7 weighted moment 
-centroiding, deviation of the centroiding RMSE from the CRLB is significantly higher
-than those of 3$\times$3 quartic approximation, and 3$\times$3 modified polynomial.
+The 3$\times$3 modified polynomial method I [\ref{6}], results in RMSE very close to the CRLB.
+For all four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels,
+RMSE gets slightly closer to the CRLB since the method starts to perform
+slightly better as we move away from undersampled stars, and as the FWHM of the smoothing kernel
+gets closer to that of simulated images.
+After approximately 3 pixels, increasing $\gamma$ result in deviation of RMSE of the method from the CRLB.
+This is a characteristic of 3$\times$3 method as we apply it to a smoothed image which is still not sufficiently
+well sampled.  Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) get
+closer to the CRLB.
 
 Again The RMSE from centroiding by fitting the exact PSF model as a function of FWHM
-perfectly lies on the CRLB [\ref{11}] except at SNR = 5 where the RMSE slightly deviates
-from the CRLB due tp the presence of outliers. Thus, centroid estimates from fitting
+perfectly lies on the CRLB [\ref{8}] except at SNR = 5 where the RMSE slightly deviates
+from the CRLB due to presence of a few outliers. Thus, centroid estimates from fitting
 the exact PSF model always saturate the CRLB. Once again, we observe that the centroid
-estimates found by fitting a Gaussian PSF to the simulated stars also saturate
--- except in the case of SNR = 5-- the CRLB in all ranges of $\gamma$ [\ref{12}].
+estimates found by the 3$\times$3 modified polynomial method II saturate the CRLB with the
+exception of simulated stars with SNR = 5, or $\gamma$ very close to 2 pixels. [\ref{7}].
 
@@
 
-An optimal stellar centroiding algorithm must always saturate the Cramer-Rao lower 
+A perfectly optimal stellar centroiding algorithm must saturate the fundamental Cramer-Rao lower 
 bound. That is, in all ranges of background noise level, size, radial light profile,
 and shape, it must preserve information about the centroid of stars. In practice however,
-that is only achievable when we know the exact PSF. Since, we do not know the exact PSF
-profile, we make use of various approximate centroiding algorithms. In this work, we
-studied how different methods get close to saturating the CRLB for relatively low SNR
+that is only achievable when we have a very good estimate of the PSF. Since, we do not always 
+know the exact PSF profile, we make use of various approximate centroiding algorithms. In this work, we
+studied how different methods get close to saturating the CRLB for relatively low signal-to-noise ratio
 stars.
 
-We also proposed a method for centroiding stars based on fitting a low order
-polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel. 
-Furthermore, we compared the performance of this method with the naive 3$\times$3 polynomial
-centroiding, 3$\times$3 quartic approximation, moment-based method, and PSF fitting.
-In order to make this comparison, we performed some tests on a large number of
-simulated data, and investigated to see if these estimators can saturate the Cramer-Rao
-lower bound, or how close to they get to saturating the bound.
+We focused on examples from two classes of centroiding algorithms. The first class contains fast and approximate
+methods that do not require any knowledge of the PSF at the poistion of stars. Of methods that belong to this class
+we consider a simple method for centroiding stars based on fitting a low order
+polynomial to a 3$\times$3 patch of star images, once smoothed by a Gaussian kernel of fixed width, and once without any smoothing step. 
+The second class of centroiding algorithms contains methods which require knowledge of the PSF (or having a good estimate
+of the PSF) at the position of stars. We considered two examples from this class. The first example
+was the 3\times3 polynomial centroiding applied to the image of the star convolved with the PSF, and the
+second example is the PSF profile fitting. In terms of saturating the Cramer-Rao bound we compared 
+the performances of these mthods against each other. We call the 3$\times$3 polynomial method applied 
+to the image convolved with a fixed Gaussian kernel (the PSF), 3$\times$3 polynomial method I (II).
 
+%Furthermore, we compared the performance of these methods with the naive 3$\times$3 polynomial
+%centroiding, 3$\times$3 quartic approximation, moment-based method, and PSF fitting.
+%In order to make this comparison, we performed some tests on a large number of
+%simulated data, and investigated to see if these estimators can saturate the Cramer-Rao
+%lower bound, or how close to they get to saturating the bound. 
 Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
@@
 from the CRLB. We found that the estimates found by 3$\times$3 polynomial method are far away from
-saturating the CRLB. On the other hand, the RMSE of centroid estimates of our proposed
-3$\times$3 modified polynomial method, and that of the 3$\times$3 quartic approximation,
-are much closer to the CRLB. The performance of these two methods however, is limited by
+saturating the CRLB. On the other hand, the RMSE of centroid estimates of 
+3$\times$3 modified polynomial method I are much closer to saturating the CRLB.
+The performance of this two method however, is limited by
 two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} size of the stars.
 
-These two techniques only take advantage of the information contained in a 3$\times$3
-patch around the brighest pixel of the smoothed image. Thus, when we apply 
+The 3$\times$3 modified polynomial method I technique only takes advantage of the information contained in a 3$\times$3
+patch around the brighest pixel of the smoothed image which is only well-sampled when the FWHM of the simulated star
+ matches that of the smoothing kernel. Thus, when we apply 
 these methods to find the centroid of stars with larger FWHM, a certain amount of
@@
 of these methods deviates from the CRLB. This deviation gets even larger at lower
-signal-to-noise ratios. Besides, the performance of these methods slightly degrades
-in the case of undersampled stars. Presence of noise is another limitting factor.
-Although these methods are able to get close to saturating the CRLB in a wide range of
-signal-to-noise ratios, they are not as reliable in the extremely faint stars
+signal-to-noise ratios. Besides, the performance of this method slightly degrades
+in the case of undersampled stars (with FWHM close two 2 pixels). 
+Presence of noise is another limitting factor.
+Although this method is able to get close to saturating the CRLB in a wide range of
+signal-to-noise ratios, It is not reliable in the case of extremely faint stars
 (SNR less than 10). This is mostly due to the fact that in the presence of noise, 
-the brightest pixel of image, does not necessarily contain the centroid of stars.
+the brightest pixel of image, does not necessarily contain the centroid of stars even after smoothing 
+the image.
+
+Once we modify the polynomial method even further by smoothing the image with the full postage stamp
+of the PSF, we obtain results that saturate the CRLB in a wide range of PSF sizes and noise levels.  
+This is due to the fact that once the images are convolved with the right PSF, they become so well-sampled and smooth
+that fitting a 2d polynomial to the 3$\times$3 patch around the brightest pixel of the smooth image can deliver
+results as accurate as results obtained from fitting a PSF profile. The only exception where we observed deviaiotn from
+saturating the CRLB occured in the case of extremely faint star (SNR $\la$ 10), and undersampled PSF (FWHM \sim 2 pixels).
+One advantage of this method over PSF fitting method is that it is fast, and that it is able to saturate the CRLB in 
+a wide range of conditions. Although this method is more accurate than 3$\times$3 modified polynomial I, but it is
+slightly slower because it requires convolution of the image with the full potage stamp of the PSF.
 
 In this investigation we showed that PSF fitting is always better at centroiding stars.
-In practice however, we do no know the the exact PSF. Besides finding the centroid by PSF
-fitting is computationally expensive whereas by employing tht 3$\times$3 modified polynomial
+However, this method has its own disadvantegouses since we do not always know the the exact PSF, and 
+finding the centroid by PSF fitting is computationally expensive whereas by employing the 3$\times$3 modified polynomial I
 technique into large scale astronomical surveys can considerably reduce the computational cost
-of initial astrometry of these surveys.
+of initial astrometry of these surveys. This method can roughly be thousand
+times faster than centroiding by model fitting. Even in the case that we have a good estimate of the PSF, the 
+3$\times$3 modified polynomial II is a much faster algorithm.
 
-It is important to note that the PSF fitting method can be made faster by only keeping the 
+Moreover, it is important to note that the PSF fitting method can be made faster by only keeping the 
 term proportional to the product of the PSF model and the image in $\chi^2$. This is because 
@@
 image with an approximate Gaussian PSF. The fitting and approximate methods are different 
-in that after upsamlping, in the approximate methods, our knowledge is limited to the 3$\times$3 
+in that after upsamlping, in approximate methods, our knowledge is limited to the 3$\times$3 
 patch around the brightest pixel and as a result, we loose some information.
-
-The advantage of this method becomes more pronounced
-in PSF estimation in which we need to know the centroid of stars accurately, but at the
-same time, with fewer number of algebraic operations. This method can roughly be thousand
-times faster than centroiding by model fitting, and requires fewer operations than the
-3$\times$3 quartic approximation mehod.
 
@@
 \caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{1}
+In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{1}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_spoly.png}
+  \includegraphics[width=\linewidth]{snr_psfpix28poly.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 modified polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{2}
+\caption{Scatter plots showing the relation between error in centroid measurement from the  and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{2}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_sdss.png}
+  \includegraphics[width=\linewidth]{snr_psfpoly.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 quartic aproximation method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
-In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{3}
+\caption{Scatter plots showing the relation between error in centroid
+measurement from 3$\times$3 modified polynomial method II and the signal-to-noise
+ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left),
+and 5.6 (lower right) pixels. In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{3}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_moment.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement
-from the 7$\times$7 weighted moment method and the signal-to-noise ratio of stars,
-with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right)
-pixels. In each scatter plot, the blue line represents the running median of data points,
-and the green line represents CRLB.}\label{4}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_psf.png}
+  \includegraphics[width=\linewidth]{snr_psffitting.png}
 \endminipage
@@
 with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right)
-pixels. In each scatter plot, the blue line represents the running median of data points,
-and the green line represents CRLB.}\label{5}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_wrongpsf.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid
-measurement from fitting a Gaussian PSF model to the stars and the signal-to-noise
-ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left),
-and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the
-running median of data points, and the green line represents CRLB.}\label{6}
+pixels. In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{4}
 \end{figure}
@@
 from the 3$\times$3 polynomial method and FWHM of stars, with SNR  of : 5 (upper left),
-10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue
-line represents the running median of data points, and the green line represents CRLB.}\label{7}
+10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, 
+the blue solid
+ line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{5}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_spoly.png}
+  \includegraphics[width=\linewidth]{fwhm_psfpix28poly.png}
 \endminipage
 \caption{Scatter plots showing the relation between error in centroid measurement
-from the 3$\times$3 modified polynomial method and FWHM of stars, with SNR  of 
+from the 3$\times$3 modified polynomial method I and FWHM of stars, with SNR  of 
 : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each
-scatter plot, the blue line represents the running median of data points, and the
-green line represents CRLB.}\label{8}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_sdss.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from
-the 3$\times$3 quartic approximation method and FWHM of stars, with SNR  of : 5 (upper left),
-10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line
-represents the running median of data points, and the green line represents CRLB.}\label{9}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_moment.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid
-measurement from the 7$\times$7 weighted moment method and FWHM of stars,
-with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right).
-In each scatter plot, the blue line represents the running median of data points,
-and the green line represents CRLB.}\label{10}
+scatter plot, the blue solid
+ line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{6}
 \end{figure}
@@
 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot,
-the blue line represents the running median of data points, and the
-green line represents CRLB.}\label{11}
+the blue solid
+ line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{7}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_wrongpsf.png}
+  \includegraphics[width=\linewidth]{fwhm_psfpoly.png}
 \endminipage
-\captionScatter plots showing the relation between error in centroid measurement
-from fitting a Gaussian PSF model and FWHM of stars, with SNR  of : 5 (upper left),
-10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the
-blue line represents the running median of data points, and the green line represents CRLB.}\label{12}
+\caption{Scatter plots showing the relation between error in centroid measurement
+from the 3$\times$3 modified polynomial method II and FWHM of stars, with SNR  of : 5 (upper left),
+10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue solid
+ line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{8}
 \end{figure}

### 2015-02-17 ms/figure.tex
Update figure.tex

@@
 faint stars. That is, we apply a number of centroiding methods 
-to a large number of simulated stars with different signal-to-noise ratio and
+to a large number of simulated faint stars with different signal-to-noise ratio and
  size realizations. Error from star centroiding methods, will always have 
@@
 
-Given the analytic model for the PSF,
+Given the analytic expression for the PSF model,
 we derive an expression for the fundamental lower bound on the centroiding error as
@@
 we investigate how close these methods can get to saturating the CRLB for
-various ranges of background noise and FWHM.
+various ranges of background noise level and PSF FWHM.
 
-In this work, we focus on three centroiding methods. The first method finds
- the centroid of stars by smoothing the image of
- stars by a Gaussian kernel of a fixed size, and fitting a second order
- polynomial to the $3\times$3 patch around the brightest pixel of smoothed
+In this work, we focus on four centroiding methods. The first method
+estimates the centroid of a star by a fitting a 2d polynomial to the 3$\times$3 patch around 
+the brightest pixel of the image. The second method centroids stars by
+ smoothing the image of stars by a Gaussian kernel of a fixed size,
+ and then applying the same 3$\times$3 polynomial trick to the smooth
  image. This method is fast and does not require any knowledge of the 
-PSF. In the second method, we apply the same polynomial centroiding to the
- $3\times$3 patch around the brightest pixel of the image of star convolved 
-with the full PSF postage stamp. The last method that we consider, is fitting 
-a PSF profile, assuming that we have a good PSF estimate, to the star.
+PSF. In the third method, the 3$\times$3 polynomial centroiding is applied to the
+ image of star convolved with the full PSF postage stamp. The last method we consider,
+ is fitting a PSF profile, assuming that we have a good PSF estimate, to the star.
 %We compare the accuracy of this method with, the naive 3$\times$3 second-order 
@@
 we give a brief overview of the centroiding methods used in our investigation.
-In section \ref{sec:data}, we discuss the simulated data, and the CRLB on centroiding error.
-In section \ref{sec:results}, we compare the results of our proposed method with 
-those obtained from centroiding methods discussed in \ref{sec:method}, and 
-with the CRLB derived in \ref{sec:data}. Finally, we discuss and conclude
-in \ref{sec:discussion}.
+In section \ref{sec:data}, we discuss the simulated data, and the Cramer-Rao bound
+ on centroiding error. In section \ref{sec:results}, we compare the performances of the methods
+discussed in \ref{sec:method}, with the CRLB derived in \ref{sec:data}. Finally,
+ we discuss and conclude in \ref{sec:discussion}.
 
-\section{Methods}\label{sec:method}
+\section{Methods}\label{sec:Centroiding methods}
 
@@
 \eeq
-Throughout this study, we keep the width of the Gaussian kernel $w$ constant and equal to
-1.2 pixels (corresponding to FWHM = 2.8 pixels).
+Throughout this study, the full-width at half-maximum of the Gaussian kernel is held at
+a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels).
+
 Then we apply the same polynomial method to the 3$\times$3 patch around the brightest
@@
 
-Consider the case that we have a good estimate of the PSF at
+Now let us consider the case in which we have a good estimate of the PSF at
 the position of the faint star under consideration. Therefore, we 
 can modify the smoothing step in the following way. Instead of smoothing
-with a Gaussian kernel with a fixed size, we convolve the image of star
+with a Gaussian kernel of a fixed size, we convolve the image of star
 with the full postage stamp of the PSF. Then, we apply the same polynomial
@@
 The procedure of convolving the image of star with the PSF results in a
-more well-sampled, which eventually, leads to having more
+more well-sampled image, which eventually, leads to having more
 information regarding the centroid of stars in the 3$\times$3 patch around the
-brightest pixel. In addition, a simple 2d polynomial will provides a better fit 
-since convolution with the PSF makes the variation of the image across the 3 pixels
-very smooth.
+brightest pixel. In addition, a simple 2d polynomial will provide a better fit 
+since convolution with the PSF makes the variation of the brightness of the image
+ across the 3$\times$3 patch very smooth.
 
-\item {\bf psf profile fitting}\quad
+\item {\bf PSF profile fitting}\quad
 
-In addition to the methods mentioned so far, we examine fitting stars with the exact
- PSF profile. That is, in our Cramer-Rao bound saturation tests, That is, we find the best
- estimates of flux and centroid by
-optimizing the $\chi^{2}$. We expect this method to perform better in determing the centroid
- of stars. In theory, it always saturates the CRLB.
+In addition to the methods mentioned so far, we examine fitting an exact
+ PSF profile to the stars. That is, in our Cramer-Rao bound saturation tests, we find the best
+ estimates of flux and centroid by optimizing the $\chi^{2}$.
+ We expect this method to perform better in determing the centroid
+ of stars. In theory, this method should always saturate the CRLB.
 
@@
 (hereafter denoted by SNR) instead of the variance of the Gaussian noise.
-We define SNR as the ratio of the mean and variance of the distribution
+We use the definition of SNR according to which, SNR is given by the ratio
+ of the mean and variance of the distribution
 which the flux estimator is drawn from. Assume that the total flux from
@@
 
-The optimal estimator of flux (one which saturates Cramer-Rao bound),
+The optimal estimator of flux (one that saturates Cramer-Rao bound),
 is the weighted average $\tilde{F}=\sum_{i}I_{i}P_{i}$. Knowing the
@@
  expressed in terms of the per pixel uncertainty
-$\sigma$, FWHM $\gamma$, and also $\beta$. We fix $\beta$ at the fiducial value of 2.5.
+$\sigma$, FWHM $\gamma$, and also $\beta$. We hold $\beta$ fixed at the fiducial value of 2.5.
 In this case we have
@@
 
-Given the PSF model that we have adopted for our simulations, we need 
-to derive an expression for the CRLB as a function of the size, and SNR of stars.
+Given the PSF model that we have adopted for our simulations, we can derive
+ an expression for the CRLB as a function of the size, and SNR of stars.
  We know that the CRLB is given by the inverse of 
@@
 In the second set, we generate 100,000 17$\times$17 postage-stamps
-of Moffat profile, with values of $\gamma$ randomly distributed 
-between 2 pixels and 6 pixels, and with centroids drawn randomly within 
+of Moffat profile, with values of $\gamma$ uniformly distributed 
+between 2 and 6 pixels, and with centroids drawn randomly within 
 the central pixel. We choose four values for SNR: 5, 10, 20, and 40. 
@@
 Gaussian noise, with variance corresponding to SNR and $\gamma$ through equation 
-(\ref{snr2}), is added to the each postage-stamp.
+(\ref{snr2}), is added to each postage-stamp.
 
@@
 Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}],
-[\ref{3}], [\ref{4}]. All methods deliver results
+[\ref{3}], and [\ref{4}]. All methods deliver results
 with RMSE larger for fainter stars.
@@
 quite large as we move towards fainter stars in our simulation.
-For stars with larger $\gamma$, centroid estimate from the naive polynomial
-method show large deviation from the CRLB. By increasing $\gamma$,
+For stars with larger $\gamma$, centroid estimates from the naive 3$\times$3
+ polynomial method show large deviation from the CRLB. By increasing $\gamma$,
 RMSE deviates further away from the CRLB.
@@
 As we increase $\gamma$ from 2 pixels to 2.8 pixels, RMSE gets closer
-to the CRLB. Besides, Also, when we increase $\gamma$ to
+to the CRLB. When we increase $\gamma$ to
 4 and 5.6 pixels, RMSE gets farther from the CRLB. For stars with $\gamma$ = 2 pixels, 
@@
 decreases with increaing SNR. The reason for this is that even after smoothing
-the with a Gaussian kernel, the image is still not well-sampled, and smooth enough
+the with a Gaussian kernel, the image is still relatively undersampled, and not smooth enough
 for a 2d polynomial fitting to provide highly accurate centroiding estimates.
 For stars with $\gamma=2.8$ pixels, since the FWHM of the Gaussian kernel matches that 
-of the underlying simulations, the smooth images are well-sampled and therefore, 
-the method is able to deliver estimates very close to saturating the CRLB. As $\gamma$
+of the PSF of underlying simulations, the smooth images are well-sampled and therefore, 
+the method is able to deliver estimates extremely close to saturating the CRLB. As $\gamma$
 gets higher for the simulations, the convolved images are not as well-sampled as those 
 whose $\gamma$ matches the FWHM of the smoothing kernel and as a result, we loose
-some information by fitting a polynomial to only a 3$\times$3 patch. That is the 
-reason for why we observe slight deviation from the CRLB for stas with $\gamma$ = 4 pixels, and 
-slightly more deviations as we increase $\gamma$ to 5.6 pixels.
+some information by fitting a polynomial to a 3$\times$3 patch. Therefore,
+ we observe slight deviation from the CRLB for stars with $\gamma$ = 4 pixels, and 
+slightly more deviation as we increase $\gamma$ to 5.6 pixels.
 
@@
  method II is able deliver centroiding estimates as accurate as PSF profile fitting, with the exception
-of simulated stars with $\gamma$ = 2 pixels. For stars with $\gamma$ = 2 pixels, the 3$\times$3 polynomial
-fitting fails to saturate the CRLB since the PSF is undersampled. For simulated images higher $\gamma$, convolving the
+of simulated stars with $\gamma$ = 2 pixels. For stars with $\gamma$ = 2 pixels, although the 3$\times$3 polynomial
+fitting gets close to saturating the CRLB, it fails to saturate the CRLB since the PSF is undersampled. For simulated images with higher $\gamma$, convolving the
 data with the PSF result in images that are well-sampled around the brightest pixel. This allows the 
@@
 Behavior of error as a function of $\gamma$ for different values of SNR,
-is shown in figures [\ref{5}], [\ref{6}], and [\ref{7}], and [\ref{8}].
+is shown in figures [\ref{5}], [\ref{6}], [\ref{7}], and [\ref{8}].
 
@@
 slightly better as we move away from undersampled stars, and as the FWHM of the smoothing kernel
-gets closer to that of simulated images.
+gets closer to that of the simulated images.
 After approximately 3 pixels, increasing $\gamma$ result in deviation of RMSE of the method from the CRLB.
 This is a characteristic of 3$\times$3 method as we apply it to a smoothed image which is still not sufficiently
-well sampled.  Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) get
+well-sampled.  Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) become
 closer to the CRLB.
 
-Again The RMSE from centroiding by fitting the exact PSF model as a function of FWHM
-perfectly lies on the CRLB [\ref{8}] except at SNR = 5 where the RMSE slightly deviates
-from the CRLB due to presence of a few outliers. Thus, centroid estimates from fitting
+Once again, the RMSE from centroiding by fitting the exact PSF model as a function of FWHM
+perfectly lies on the CRLB except at SNR = 5 where the RMSE slightly deviates
+from the CRLB due to presence of a few outliers [\ref{8}].
+. Thus, centroid estimates from fitting
 the exact PSF model always saturate the CRLB. Once again, we observe that the centroid
 estimates found by the 3$\times$3 modified polynomial method II saturate the CRLB with the
-exception of simulated stars with SNR = 5, or $\gamma$ very close to 2 pixels. [\ref{7}].
+exception of simulated stars with SNR = 5, or $\gamma$ very close to 2 pixels [\ref{7}].
 
@@
 
-A perfectly optimal stellar centroiding algorithm must saturate the fundamental Cramer-Rao lower 
+An optimal stellar centroiding algorithm must saturate the fundamental Cramer-Rao lower 
 bound. That is, in all ranges of background noise level, size, radial light profile,
 and shape, it must preserve information about the centroid of stars. In practice however,
-that is only achievable when we have a very good estimate of the PSF. Since, we do not always 
+this is only achievable when we have a reasonably good estimate of the PSF. Since, we do not always 
 know the exact PSF profile, we make use of various approximate centroiding algorithms. In this work, we
@@
 We focused on examples from two classes of centroiding algorithms. The first class contains fast and approximate
-methods that do not require any knowledge of the PSF at the poistion of stars. Of methods that belong to this class
+methods that do not require any knowledge of the PSF at the position of stars. Of methods that belong to this class,
 we consider a simple method for centroiding stars based on fitting a low order
 polynomial to a 3$\times$3 patch of star images, once smoothed by a Gaussian kernel of fixed width, and once without any smoothing step. 
-The second class of centroiding algorithms contains methods which require knowledge of the PSF (or having a good estimate
+The second class of centroiding algorithms contains methods that require knowledge of the PSF (or having a good estimate
 of the PSF) at the position of stars. We considered two examples from this class. The first example
-was the 3\times3 polynomial centroiding applied to the image of the star convolved with the PSF, and the
-second example is the PSF profile fitting. In terms of saturating the Cramer-Rao bound we compared 
-the performances of these mthods against each other. We call the 3$\times$3 polynomial method applied 
-to the image convolved with a fixed Gaussian kernel (the PSF), 3$\times$3 polynomial method I (II).
+was the 3$\times$3 polynomial centroiding applied to the image of the star convolved with the PSF, and the
+second example is the PSF profile fitting. In terms of saturating the Cramer-Rao bound, we compared 
+the performances of these methods against each other. Throughout this work, we called the 3$\times$3 polynomial method applied 
+to the image convolved with a fixed Gaussian kernel ( convolved with the PSF), 3$\times$3 modified polynomial method I (II).
 
@@
 3$\times$3 modified polynomial method I are much closer to saturating the CRLB.
-The performance of this two method however, is limited by
-two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} size of the stars.
+The performance of this method however, is limited by
+two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} PSF size.
 
-The 3$\times$3 modified polynomial method I technique only takes advantage of the information contained in a 3$\times$3
-patch around the brighest pixel of the smoothed image which is only well-sampled when the FWHM of the simulated star
+The 3$\times$3 modified polynomial method I technique only takes advantage of the information
+ contained in a 3$\times$3 patch around the brighest pixel of the smoothed image which is only
+ well-sampled when the FWHM of the simulated image of star
  matches that of the smoothing kernel. Thus, when we apply 
-these methods to find the centroid of stars with larger FWHM, a certain amount of
+this method to find the centroid of stars with larger FWHM, certain amount of
 information (encoded in the Cramer-Rao lower bound) is lost, and therefore, the RMSE
-of these methods deviates from the CRLB. This deviation gets even larger at lower
+of these methods deviates from the CRLB. This deviation becomes even larger at lower
 signal-to-noise ratios. Besides, the performance of this method slightly degrades
@@
 Although this method is able to get close to saturating the CRLB in a wide range of
-signal-to-noise ratios, It is not reliable in the case of extremely faint stars
-(SNR less than 10). This is mostly due to the fact that in the presence of noise, 
-the brightest pixel of image, does not necessarily contain the centroid of stars even after smoothing 
+signal-to-noise ratios, It is not reliable in the case of extremely faint stars.
+ This is partly due to the fact that in the presence of noise, 
+the brightest pixel of image does not necessarily contain the centroid of stars even after smoothing 
 the image.
@@
 This is due to the fact that once the images are convolved with the right PSF, they become so well-sampled and smooth
-that fitting a 2d polynomial to the 3$\times$3 patch around the brightest pixel of the smooth image can deliver
-results as accurate as results obtained from fitting a PSF profile. The only exception where we observed deviaiotn from
-saturating the CRLB occured in the case of extremely faint star (SNR $\la$ 10), and undersampled PSF (FWHM \sim 2 pixels).
+that fitting a 2d polynomial to the 3$\times$3 patch around the brightest pixel of the smooth image is sufficient for us to obtain
+results as accurate as those from fitting a PSF profile. The only conditions in which deviation from
+saturating the CRLB occures are very low signal-to-noise ratios (SNR $\la$ 10), and undersampled PSF (FWHM $\sim$ 2 pixels).
 One advantage of this method over PSF fitting method is that it is fast, and that it is able to saturate the CRLB in 
-a wide range of conditions. Although this method is more accurate than 3$\times$3 modified polynomial I, but it is
+a wide range of conditions. In the case that we have a good estimate of the PSF, the 
+3$\times$3 modified polynomial II is a much faster algorithm. 
+Although this method is more accurate than 3$\times$3 modified polynomial I, it is
 slightly slower because it requires convolution of the image with the full potage stamp of the PSF.
@@
 In this investigation we showed that PSF fitting is always better at centroiding stars.
-However, this method has its own disadvantegouses since we do not always know the the exact PSF, and 
-finding the centroid by PSF fitting is computationally expensive whereas by employing the 3$\times$3 modified polynomial I
-technique into large scale astronomical surveys can considerably reduce the computational cost
-of initial astrometry of these surveys. This method can roughly be thousand
-times faster than centroiding by model fitting. Even in the case that we have a good estimate of the PSF, the 
-3$\times$3 modified polynomial II is a much faster algorithm.
+However, this method has its own disadvantages. First, we do not always know the the exact PSF. Second, finding
+ the centroid by profile fitting is computationally expensive, whereas by employing any of the 3$\times$3 modified polynomial 
+techniques into large scale astronomical surveys can considerably reduce the computational cost
+of initial astrometry of the point sources detected by these surveys.
 
 Moreover, it is important to note that the PSF fitting method can be made faster by only keeping the 
-term proportional to the product of the PSF model and the image in $\chi^2$. This is because 
-the other terms are not sensitive to the position of centroid. However, this only allows
+term proportional to the dot product of the PSF model and the image in $\chi^2$. This is because 
+the other terms are not sensitive to the position of the centroid. However, this only allows
 us to vary the poition of centroid, and not the flux, while fitting the PSF model
@@
 
-Modifying the $\chi^2$ such that it contains the product of the PSF and image, 
-provides a nice interpretation for the PSF fitting method. It corresponds to oversampling
-of the image with the correct PSF, and finding the centroid in the oversampled image afterwards.
-On the other hand, one can think of the initial smoothing step in 3$\times$3 methods
-such as modified polynomial and quartic approximation methods, as oversampling of the 
-image with an approximate Gaussian PSF. The fitting and approximate methods are different 
-in that after upsamlping, in approximate methods, our knowledge is limited to the 3$\times$3 
-patch around the brightest pixel and as a result, we loose some information.
+Modifying the $\chi^2$ such that it contains the dot product of the PSF and image, 
+provides a nice interpretation for the PSF fitting method. It corresponds to searching for the 
+centroid in a very high resolution grid which the dot product of the image and the PSF model is
+sensitive to. On the other hand, one can think of the initial smoothing step in the first modified 3$\times$3 method 
+as upsampling of the image around the center through convolving it with an approximate Gaussian PSF. 
+The PSF profile fitting and the first modified method are different in that when there is mismatch between the
+widths of the smoothing kernel and the PSF, we loose some information by employing a 3$\times$3 polynomial trick.
+When we have the advantage of knowing the PSF, this isuue can be resolved by employing the second modified polynomial method.
 
 Having a reasonable PSF model should always deliver better centroid estimates, but
-over a certain range of low signal-to-noise ratios, one can achieve sensibly accurate
-results by employing this simple 3$\times$3 method without making any assumption about
-the PSF model.
+over a certain range of low signal-to-noise ratios and PSF sizes, one can achieve sensibly
+ accurate results by employing a simple 3$\times$3 method after smooting the image with
+ a Gaussian kernel of fixed width, and without making any assumption about the PSF model.
 
-In this investigation we narrowed our focus on a set of data simulated from a very specific
-model. Although there are various cases where Moffat profiles provide reasonable
-representation of point spread function, these models are not generic enough to let us
+In this investigation we narrowed our focus on a set of data simulated from a particular
+PSF profile. Although there are various cases where Moffat profiles provide reasonable
+representation of point spread function, these profiles are not generic enough to let us
 reach a more general conclusion. Another important, and untapped, area of study
@@
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the  and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 modified polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
 In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{2}
@@
 \caption{Scatter plots showing the relation between error in centroid
-measurement from 3$\times$3 modified polynomial method II and the signal-to-noise
+measurement from the 3$\times$3 modified polynomial method II and the signal-to-noise
 ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left),
@@
 \minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{fwhm_psfpoly.png}
+\endminipage
+\caption{Scatter plots showing the relation between error in centroid measurement
+from the 3$\times$3 modified polynomial method II and FWHM of stars, with SNR  of : 5 (upper left),
+10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue solid
+ line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{7}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
   \includegraphics[width=\linewidth]{fwhm_psf.png}
@@
 the blue solid
- line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{7}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_psfpoly.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement
-from the 3$\times$3 modified polynomial method II and FWHM of stars, with SNR  of : 5 (upper left),
-10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue solid
  line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{8}

### 2015-03-04 ms/figure.tex
Update figure.tex

@@
 including many faint stars, with short exposure times. Real-time estimation of the
-centroid of stars is crucial for real-time PSF estimation, and precision is required
+centroids of stars is crucial for real-time PSF estimation, and maximal precision is required
 for measurements of proper motion. In this work, we aim to compare the performance of
-fast and slow centroiding methods, when they are applied
-to relatively low signal-to-noise ratio stars in a wide range of psf sizes.
+various centroiding methods, when they are applied
+to relatively low signal-to-noise ratio unsaturated stars.
 In order to investigate how information-preserving these techniques are, we compare
-the root-mean-squared-error arising from these centroiding methods with the fundamental Cramer-Rao
+the root-mean-squared-error with the fundamental Cramer-Rao
 lower bound. We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
@@
  polynomial centroiding after smoothing the image by the PSF can be 
-as accurate as PSF profile fitting with a good PSF estimate. In the case that we do not
-know the PSF, we demonstrate that although a particular form of polynomial centroiding method is not as
+as accurate as full PSF profile fitting. In the case that we do not
+know the PSF, we demonstrate that although polynomial centroiding is not as
 accurate as PSF profile fitting, it comes close to saturating the Cramer-Rao lower bound
-in a wide range of conditions.
+in a wide range of conditions. We also show that the center-of-light never comes close to 
+saturating the bound, and thus it does not deliver reliable estimates of centroids.
 

### 2015-03-09 ms/figure.tex
after word rearrangement and adding moments!

@@
 A common practice in astronomy is taking imaging data, and then finding the coordinates
-of various light sources across the sky. Finding accuarate estimate of the center of point
+of various light sources across the sky. Finding accuarate estimates of the centers of point
 sources, convolved with telescope point spread function (and atmospheric PSF in case of
@@
 astronomical image processing. For instance, proper measurement of the shapes of galaxies
-requires interpolating the PSF from the position of sparsely located stars across the
+requires interpolating the PSF from the positions of sparsely located stars across the
 image to the positions of galaxies. The accuracy of the PSF estimation therefore,
-relies on how accurately we know the centroid of stars.
+relies on how accurately we know the centroids of stars.
 
@@
 Reducing the computational cost becomes even more important in large surveys,
-where we want to estimate the centroid of thousands of point sources detected
+where we want to estimate the centroids of thousands of point sources detected
 on the telescope's focal plane.
 
-Reaching the optimal measurement of the centroid of stars however, is limited
+Reaching the optimal measurement of the centroids of stars however, is limited
 by the lack of knowledge about the exact shape of the PSF, and also presence of noise;
@@
 coordinates being free parameters of these models.
-DAOPHOT (DoPHOT) finds the centroid by fitting a Gaussian (power law) PSF to
+DAOPHOT (DoPHOT) finds the centroids by fitting a Gaussian (a truncated power series for a Gaussian) PSF to
 the light profile of stars.
@@
 In this paper, we study how optimal various techniques are at centroiding 
-faint stars. That is, we apply a number of centroiding methods 
+faint unsaturated stars. That is, we apply a number of centroiding methods 
 to a large number of simulated faint stars with different signal-to-noise ratio and
@@
 In this work, we focus on four centroiding methods. The first method
-estimates the centroid of a star by a fitting a 2d polynomial to the 3$\times$3 patch around 
-the brightest pixel of the image. The second method centroids stars by
+involves fitting a PSF profile, assuming that we have a good PSF estimate, to the star. 
+The second method estimates the centroid of a star by fitting a 2d polynomial to
+ the 3$\times$3 patch around the brightest pixel of the image convolved with the PSF. 
+The third method centroids stars by
  smoothing the image of stars by a Gaussian kernel of a fixed size,
@@
  image. This method is fast and does not require any knowledge of the 
-PSF. In the third method, the 3$\times$3 polynomial centroiding is applied to the
- image of star convolved with the full PSF postage stamp. The last method we consider,
- is fitting a PSF profile, assuming that we have a good PSF estimate, to the star.
-%We compare the accuracy of this method with, the naive 3$\times$3 second-order 
-%polynomial method, the 3$\times$3 quartic approximation
-%method used in SDSS photometric pipeline, and fitting a PSF model to the 
-%star.
+PSF. The last method we consider, is the center of light centroiding applied to the
+ 7$\times$7 patch around the brightest pixel of the image.
 
-This paper is structured as follows. In section \ref{sec:method},
-we give a brief overview of the centroiding methods used in our investigation.
-In section \ref{sec:data}, we discuss the simulated data, and the Cramer-Rao bound
- on centroiding error. In section \ref{sec:results}, we compare the performances of the methods
+This paper is structured as follows. In section \ref{sec:CRLB},
+we discuss the Cramer-Rao lower bound, and we derive
+an analytic expression for the lower bound on centroiding error
+of the simulated data, and also PSF profile fitting. 
+In section \ref{sec:method} we give a brief overview of approximate 
+centroiding methods used in our investigation.
+In section \ref{sec:data} we discuss the Cramer-Rao lower bound satuaration
+tests and their corresponding simulated data.
+In section \ref{sec:result}, we compare the performances of the methods
 discussed in \ref{sec:method}, with the CRLB derived in \ref{sec:data}. Finally,
  we discuss and conclude in \ref{sec:discussion}.               
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Cramer-Rao lower Bound %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Methods}\label{sec:Centroiding methods}
+\section{Cramer-Rao lower bound on centroiding error}\label{sec:CRLB}
 
-\subsection{Non PSF-based methods}
+In order to test the accuracy of various centroiding methods, we need to to compare their 
+performances against each other at saturating the Cramer-Rao lower bound. The closer an estimator is to saturating 
+the CRLB, the more information about the quantity that we 
+need to estimate is preserved. A measure for closeness of an estimator to 
+saturating the CRLB is comparison of the root-mean-squared-error of that estimator 
+with the CRLB.
 
-\item {\bf 3$\times$3 polynomial centroiding}\quad
+This requires simulation of a large set of stars for which we know the exact position of centroids
+and the corresponding lower bound for each star, and comparing the centroiding error with the lower bound.
 
-In order to find the centroid of a star, 
-we fit a simple 2d polynomial $P(x,y)=a+bx+cy+dx^2+exy+fy^2$ to the
-$3\times3$ patch centered on the brightest pixel of the
-image. We apply this method to star images in the sky-dominated regime.
-Upon constructing a universal 9$\times$6 design matrix
-\begin{equation}
-    \mathbf{A} = 
-    \begin{bmatrix}
-        1 & x_{1} & y_{1} & x_{1}^{2} & x_{1}y_{1} & y_{1}^{2} \\
-        . & . & . & . & . & .  \\
-        . & . & . & . & . & .  \\
-        . & . & . & . & . & .  \\
-        1 & x_{9} & y_{9} & x_{9}^{2} & x_{9}y_{9} & y_{9}^{2}
-    \end{bmatrix},
-\end{equation}
-the free parameters of the model $\{a,b,c,d,e,f\}$
-(hereafter compactly denoted by $\mathbf{X}$) can be determined by 
-\beq
-\mathbf{X} = (\mathbf{A}^{T}\mathbf{A})^{-1}\mathbf{A}^{T}\mathbf{Z},
-\label{linearfit}
-\eeq
-where $\mathbf{Z}$ is given by $(z_{1},...,z_{9})^{T}$,
-with $z_{i}$, being the brightness of the $i-$th pixel of the 3$\times$3 patch.
-Afterwards, the best fit parameters can be used to compute the centroid coordinate
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% THIS GOES TO TESTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Furthermore, we uniformly draw the centroids of these simulated stars within sub-pixel regions. 
+%We aim to study how centroiding errors from different methods behave with
+%changing SNR and size, and how close they get to saturating the CRLB. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\beq
-  \begin{bmatrix}
-      x_{c}\\
-      y_{c}\\
-  \end{bmatrix} = 
-  \begin{bmatrix}
-      2d & e\\
-      e & 2f\\
-  \end{bmatrix}^{-1}
-  \begin{bmatrix}
-      -b\\
-      -c\\
-  \end{bmatrix}.
-\label{center}
-\eeq
-
-It is important to note that the algebraic operation in (\ref{center}) involves 
-inverting a 2$\times$2 curvature matrix
-\beq
-  D = 
-  \begin{bmatrix}
-      2d & e\\
-      e & 2f\\
-  \end{bmatrix}.
-\eeq
-When $D$ has a zero (or very close to zero) deteminant,
-centroid estimated by (\ref{center}) gets arbitrarily 
-large in which case the centroiding method leads to a catastrophic 
-outlier. In order to tackle this issue, we add a soft regularization term
-proportional to $\sigma^{2}$ to the determinant of $D$.
-
-\item {\bf 3$\times$3 modified polynomial method I}\quad
-
-Now, we modify the simple polynomial method explained above,
-by smoothing the image of the star with a Gaussian kernel
-\beq
-k(\mathbf{x}) = \frac{1}{2\pi w^2}\exp(-\mathbf{x}^{2}/2w^{2}).
-\eeq
-Throughout this study, the full-width at half-maximum of the Gaussian kernel is held at
-a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels).
-
-Then we apply the same polynomial method to the 3$\times$3 patch around the brightest
-pixel of the smoothed image. Therefore, for a given star and a smoothing kernel,
-the outcome of equation (\ref{linearfit}) can be
-plugged into equation (\ref{center}) to find the centroid estimate
-of the star.
-
-\subsection{PSF-based methods}
-
-\item {\bf 3$\times$3 modified polynomial method II}\quad
-
-Now let us consider the case in which we have a good estimate of the PSF at
-the position of the faint star under consideration. Therefore, we 
-can modify the smoothing step in the following way. Instead of smoothing
-with a Gaussian kernel of a fixed size, we convolve the image of star
-with the full postage stamp of the PSF. Then, we apply the same polynomial
-fitting to the 3$\times$3 patch around the brightest pixel of the convolved image.
-
-The procedure of convolving the image of star with the PSF results in a
-more well-sampled image, which eventually, leads to having more
-information regarding the centroid of stars in the 3$\times$3 patch around the
-brightest pixel. In addition, a simple 2d polynomial will provide a better fit 
-since convolution with the PSF makes the variation of the brightness of the image
- across the 3$\times$3 patch very smooth.
-
-\item {\bf PSF profile fitting}\quad
-
-In addition to the methods mentioned so far, we examine fitting an exact
- PSF profile to the stars. That is, in our Cramer-Rao bound saturation tests, we find the best
- estimates of flux and centroid by optimizing the $\chi^{2}$.
- We expect this method to perform better in determing the centroid
- of stars. In theory, this method should always saturate the CRLB.
-
-\section{Simulations and Cramer-Rao saturation tests}\label{sec:data}
-
-In order to test the accuracy of the method mentioned in section \ref{sec:method},
- and to compare their performance at saturating the Cramer-Rao bound against each other, 
-we need to simulate a large set of stars for which we know the exact position of centroids.
-Furthermore, we uniformly draw the centroids of these simulated stars within sub-pixel regions. 
 We use the Moffat profile \citep{moffat} for our PSF simulations. 
@@
 being $2\alpha\sqrt{2^{1/\beta}-1}$. 
-We aim to investigate the performance of centroiding methods introduced
-in section \ref{sec:method} for different background noise levels, and also different
+We aim to investigate the performance of centroiding methods for
+ different background noise levels, and also different
 values of $\gamma$. For further simplicity, we set the flux of all stars in our
@@
 and that is the limit we are interested in throughout our investigation.
- In the case of our simulations, SNR given in (\ref{snr}) can be analytically
+ In the case of Moffat profiles, SNR given in (\ref{snr}) can be analytically 
 expressed in terms of the per pixel uncertainty
@@
 noise level $\sigma$, those with higher size have lower SNR.
-
-We aim to study how centroiding errors from different methods behave with
-changing SNR and size, and how close they get to saturating the CRLB. 
-The closer an estimator is to saturating the CRLB, the more information
- about the quantity that we 
-need to estimate is preserved. A measure for closeness of an estimator to 
-saturating the CRLB is comparison of the root-mean-squared-error of that estimator 
-with the CRLB.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%SAY SOMETHING MAARRRR%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We examine fitting an exact
+ PSF profile to the stars. That is, in our Cramer-Rao bound saturation tests, we find the best
+ estimates of flux and centroid by optimizing the $\chi^{2}$.
+ We expect this method to perform better in determing the centroids
+ of stars. In theory, this method should always saturate the CRLB.
+
+\section{Approximate methods}\label{sec:method}
+
+\item{\bf  PSF-based 3$\times$3 polynomial centroiding}\quad Let us consider the case 
+in which we have a good estimate of the PSF at
+the position of the faint star under consideration. 
+We can smooth the image of the star, by convolving it with the 
+full postage stamp of the PSF. Then, we fit a simple 2d polynomial 
+$P(x,y)=a+bx+cy+dx^2+exy+fy^2$ 
+to the 3$\times$3 patch around the brightest pixel of the convolved image.
+Upon constructing a universal 9$\times$6 design matrix
+\begin{equation}
+    \mathbf{A} = 
+    \begin{bmatrix}
+        1 & x_{1} & y_{1} & x_{1}^{2} & x_{1}y_{1} & y_{1}^{2} \\
+        . & . & . & . & . & .  \\
+        . & . & . & . & . & .  \\
+        . & . & . & . & . & .  \\
+        1 & x_{9} & y_{9} & x_{9}^{2} & x_{9}y_{9} & y_{9}^{2}
+    \end{bmatrix},
+\end{equation}
+the free parameters $\{a,b,c,d,e,f\}$
+(hereafter compactly denoted by $\mathbf{X}$) can be determined by 
+\beq
+\mathbf{X} = (\mathbf{A}^{T}\mathbf{A})^{-1}\mathbf{A}^{T}\mathbf{Z},
+\label{linearfit}
+\eeq
+where $\mathbf{Z}$ is given by $(z_{1},...,z_{9})^{T}$,
+with $z_{i}$, being the brightness of the $i-$th pixel of the 3$\times$3 patch.
+Afterwards, the best fit parameters can be used to compute the centroid coordinate
+
+\beq
+  \begin{bmatrix}
+      x_{c}\\
+      y_{c}\\
+  \end{bmatrix} = 
+  \begin{bmatrix}
+      2d & e\\
+      e & 2f\\
+  \end{bmatrix}^{-1}
+  \begin{bmatrix}
+      -b\\
+      -c\\
+  \end{bmatrix}.
+\label{center}
+\eeq
+
+It is important to note that the algebraic operation in (\ref{center}) involves 
+inverting a 2$\times$2 curvature matrix
+\beq
+  D = 
+  \begin{bmatrix}
+      2d & e\\
+      e & 2f\\
+  \end{bmatrix}.
+\eeq
+
+When $D$ has a zero (or very close to zero) deteminant,
+centroid estimated by (\ref{center}) gets arbitrarily 
+large in which case the centroiding method leads to a catastrophic 
+outlier. In order to tackle this issue, we add a soft regularization term
+proportional to $\sigma^{2}$ to the determinant of $D$.
+
+The procedure of convolving the image of star with the PSF results in a
+more well-sampled image, which eventually, leads to having more
+information regarding the centroids of stars in the 3$\times$3 patch around the
+brightest pixel. In addition, a simple 2d polynomial will provide a better fit 
+since convolution with the PSF makes the variation of the brightness of the image
+ across the 3$\times$3 patch very smooth.
+
+\item{\bf 3$\times$3 polynomial centroiding}\quad In the case that 
+we do not have know the PSF at the position of star, we change 
+the smoothing step in the following way. Instead of smoothing the image 
+with the PSF, we smooth it with a Gaussian kernel of a fixed size. 
+\beq
+k(\mathbf{x}) = \frac{1}{2\pi w^2}\exp(-\mathbf{x}^{2}/2w^{2}).
+\eeq
+Throughout this study, the full-width at half-maximum of the Gaussian kernel is held at
+a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels).
+
+Then we apply the same 2d polynomial method to the 3$\times$3 patch around the brightest
+pixel of the smoothed image. Therefore, for a given star and a smoothing kernel,
+the outcome of equation (\ref{linearfit}) can be
+plugged into equation (\ref{center}) to find the centroid estimate
+of the star. This is inspired by the 3$\times$3 quartic approximation 
+used in the \textsl{Sloan Digital Sky Surveys} photometric pipeline \citep{sdss}.
+
+\item {\bf Center of light centroiding}\quad In addition to the methods 
+mentioned so far, we examine centroiding stars by computing their zeroth moments
+in a 7$\times$7 patch around the brightest pixel of the image.
+In terms of saturating the Cramer-Rao lower bound, we expect this simple 
+center of light centroiding to perform worse than all other methods mentioned in 
+this section. Hereafter, we call this method $7\times7$ moment centroiding.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%THIS METHOD SUCKS BALLS%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Tests}\label{sec:data}
+
 We perform two sets of simulations. In the first set, we choose four values of
@@
 
-\section{Results}\label{sec:results}
+\section{Results}\label{sec:result}
 
@@
 Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}],
-[\ref{3}], and [\ref{4}]. All methods deliver results
-with RMSE larger for fainter stars.
-In case of 3$\times$3 polynomial centroiding [\ref{1}], RMSE becomes
-quite large as we move towards fainter stars in our simulation.
-For stars with larger $\gamma$, centroid estimates from the naive 3$\times$3
- polynomial method show large deviation from the CRLB. By increasing $\gamma$,
-RMSE deviates further away from the CRLB.
+[\ref{3}], [\ref{4}]. All methods deliver results with RMSE larger 
+for fainter stars.
 
-However, RMSE from the modified centroiding method I [\ref{2}],
-is very close to the CRLB except at the very small values of SNR (SNR $<$ 10).
+As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{1}]
+lies on the CRLB except for simulations with SNR $\la$ 10 where the RMSE gets slightly pulled away
+from the CRLB due to presence of a few outliers. Figure [\ref{2}] demonstrates that even the PSF-based 3$\times$3 polynomial 
+centroiding is able deliver centroiding estimates as accurate as PSF profile fitting, with the exception
+of simulated stars with $\gamma$ = 2 pixels. For stars with $\gamma$ = 2 pixels, although the 3$\times$3 polynomial
+fitting gets close to saturating the CRLB, it fails to saturate the CRLB since the PSF is undersampled. For simulated images with higher $\gamma$, convolving the
+data with the PSF result in images that are well-sampled around the brightest pixel. This allows the 
+polynomial centroiding to deliver highly accurate results that can saturate the CRLB for simulated
+data with SNR $\ga$ 10.
+
+RMSE from the 3$\times$3 polynomial centroiding [\ref{3}],
+is very close to the CRLB except at the very small values of SNR (SNR $\la$ 10).
 As we increase $\gamma$ from 2 pixels to 2.8 pixels, RMSE gets closer
@@
 
-As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{4}]
-lies on the CRLB except for simulations with SNR = 5 where the RMSE gets slightly pulled away
-from the CRLB due to presence of a few outliers. Figure [\ref{3}] demonstrates that even the modified centroiding
- method II is able deliver centroiding estimates as accurate as PSF profile fitting, with the exception
-of simulated stars with $\gamma$ = 2 pixels. For stars with $\gamma$ = 2 pixels, although the 3$\times$3 polynomial
-fitting gets close to saturating the CRLB, it fails to saturate the CRLB since the PSF is undersampled. For simulated images with higher $\gamma$, convolving the
-data with the PSF result in images that are well-sampled around the brightest pixel. This allows the 
-polynomial centroiding to deliver highly accurate results that can saturate the CRLB for simulated
-data with SNR $\ga$ 10.
+However, in case of 7$\times$7 moment method [\ref{4}], RMSE becomes
+quite large as we move towards fainter stars in our simulation.
+For stars with larger $\gamma$, centroid estimates from the naive center of light 
+centroiding show large deviation from saturating the CRLB. By increasing $\gamma$,
+RMSE deviates further away from the CRLB.
 
@@
 
-The centroid estimates obtained from the naive 3$\times$3 polynomial method [\ref{5}]
-result in RMSE much larger than the CRLB in all ranges of FWHM and for all four
-values of SNR in this experiment. In the case of extremely faint stars (SNR = 5),
-the polynomial method is not able to deliver any reliable estimate, and completely fails.
+Once again, the RMSE from centroiding by fitting the exact PSF model as a function of FWHM
+perfectly lies on the CRLB except at SNR = 5 where the RMSE slightly deviates
+from the CRLB due to presence of a few outliers [\ref{5}]. 
+Thus, centroid estimates from fitting
+the exact PSF model always saturate the CRLB. Once again, we observe that the centroid
+estimates found by the PSF-based 3$\times$3 polynomial centroiding saturate the CRLB with the
+exception of simulated stars with SNR = 5, or $\gamma$ very close to 2 pixels [\ref{6}].
 
-The 3$\times$3 modified polynomial method I [\ref{6}], results in RMSE very close to the CRLB.
+The 3$\times$3 polynomial method [\ref{7}], results in RMSE very close to the CRLB.
 For all four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels,
@@
 
-Once again, the RMSE from centroiding by fitting the exact PSF model as a function of FWHM
-perfectly lies on the CRLB except at SNR = 5 where the RMSE slightly deviates
-from the CRLB due to presence of a few outliers [\ref{8}].
-. Thus, centroid estimates from fitting
-the exact PSF model always saturate the CRLB. Once again, we observe that the centroid
-estimates found by the 3$\times$3 modified polynomial method II saturate the CRLB with the
-exception of simulated stars with SNR = 5, or $\gamma$ very close to 2 pixels [\ref{7}].
+The centroid estimates obtained from the naive 7$\times$7 moment method [\ref{8}]
+result in RMSE much larger than the CRLB in all ranges of FWHM and for all four
+values of SNR in this experiment. In the case of extremely faint stars (SNR = 5),
+the polynomial method is not able to deliver any reliable estimate, and completely fails.
 
@@
 bound. That is, in all ranges of background noise level, size, radial light profile,
-and shape, it must preserve information about the centroid of stars. In practice however,
+and shape, it must preserve information about the centroids of stars. In practice however,
 this is only achievable when we have a reasonably good estimate of the PSF. Since, we do not always 
 know the exact PSF profile, we make use of various approximate centroiding algorithms. In this work, we
-studied how different methods get close to saturating the CRLB for relatively low signal-to-noise ratio
-stars.
+studied how different methods come close to saturating the CRLB for relatively low signal-to-noise ratio
+unsaturated stars.
 
 We focused on examples from two classes of centroiding algorithms. The first class contains fast and approximate
-methods that do not require any knowledge of the PSF at the position of stars. Of methods that belong to this class,
-we consider a simple method for centroiding stars based on fitting a low order
-polynomial to a 3$\times$3 patch of star images, once smoothed by a Gaussian kernel of fixed width, and once without any smoothing step. 
+methods that do not require any knowledge of the PSF at the positions of stars. Of methods that belong to this class,
+we consider centroiding stars based on fitting a low order
+polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel of fixed width, and finding the center of light 
+of a 7$\times$7 patch around the brightest pixel of the star.
 The second class of centroiding algorithms contains methods that require knowledge of the PSF (or having a good estimate
-of the PSF) at the position of stars. We considered two examples from this class. The first example
-was the 3$\times$3 polynomial centroiding applied to the image of the star convolved with the PSF, and the
-second example is the PSF profile fitting. In terms of saturating the Cramer-Rao bound, we compared 
-the performances of these methods against each other. Throughout this work, we called the 3$\times$3 polynomial method applied 
-to the image convolved with a fixed Gaussian kernel ( convolved with the PSF), 3$\times$3 modified polynomial method I (II).
+of the PSF) at the positions of stars. We considered two examples from this class. The first example
+is the 3$\times$3 polynomial centroiding applied to the image of the star convolved with the PSF, and the
+second example is the full PSF profile fitting. In terms of saturating the Cramer-Rao bound, we compared 
+the performances of these methods against each other.
 
@@
 %lower bound, or how close to they get to saturating the bound.
+
 Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
 centroid estimates that saturate the CRLB; with the exception of SNR being less than 10, 
-in which a few centroiding ouliers caused the RMSE to slightly, but not significantly, deviate
-from the CRLB. We found that the estimates found by 3$\times$3 polynomial method are far away from
-saturating the CRLB. On the other hand, the RMSE of centroid estimates of 
-3$\times$3 modified polynomial method I are much closer to saturating the CRLB.
+in which case a few centroiding ouliers caused the RMSE to slightly, but not significantly, deviate
+from the CRLB. We found that the estimates found by 7$\times$7 moment method, except in the case of
+very high SNR values and very small ranges of $\gamma$, do not come close to
+saturating the CRLB. In a considerable range of PSF sizes and background noise levels, 
+this method completely fails to deliver any reliable centroiding estimates.
+
+On the other hand, the RMSE of centroid estimates of 
+3$\times$3 polynomial centroiding are much closer to saturating the CRLB in all ranges of signal-to-noise ratio.
 The performance of this method however, is limited by
 two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} PSF size.
-
-The 3$\times$3 modified polynomial method I technique only takes advantage of the information
+The 3$\times$3 polynomial centroiding technique only takes advantage of the information
  contained in a 3$\times$3 patch around the brighest pixel of the smoothed image which is only
@@
 Presence of noise is another limitting factor.
-Although this method is able to get close to saturating the CRLB in a wide range of
-signal-to-noise ratios, It is not reliable in the case of extremely faint stars.
+Although this method is able to get very close to saturating the CRLB in a wide range of
+signal-to-noise ratios, it is not reliable in the case of extremely faint stars.
  This is partly due to the fact that in the presence of noise, 
@@
 
-Once we modify the polynomial method even further by smoothing the image with the full postage stamp
+Once we modify the polynomial method further by smoothing the image with the full postage stamp
 of the PSF, we obtain results that saturate the CRLB in a wide range of PSF sizes and noise levels.  
-This is due to the fact that once the images are convolved with the right PSF, they become so well-sampled and smooth
+This is due to the fact that once the images are convolved with the correct PSF, they become so well-sampled and smooth
 that fitting a 2d polynomial to the 3$\times$3 patch around the brightest pixel of the smooth image is sufficient for us to obtain
-results as accurate as those from fitting a PSF profile. The only conditions in which deviation from
+results as accurate as those from fitting a PSF profile. The only conditions in which slight deviation from
 saturating the CRLB occures are very low signal-to-noise ratios (SNR $\la$ 10), and undersampled PSF (FWHM $\sim$ 2 pixels).
@@
 a wide range of conditions. In the case that we have a good estimate of the PSF, the 
-3$\times$3 modified polynomial II is a much faster algorithm. 
-Although this method is more accurate than 3$\times$3 modified polynomial I, it is
+PSF-based 3$\times$3 polynomial centroiding is a significantly much faster algorithm. 
+Although this method is more accurate than 3$\times$3 polynomial centroiding, it is
 slightly slower because it requires convolution of the image with the full potage stamp of the PSF.
@@
 However, this method has its own disadvantages. First, we do not always know the the exact PSF. Second, finding
- the centroid by profile fitting is computationally expensive, whereas by employing any of the 3$\times$3 modified polynomial 
-techniques into large scale astronomical surveys can considerably reduce the computational cost
+ the centroid by profile fitting is computationally expensive, whereas by employing any of the 3$\times$3 polynomial techniques 
+considered in this study into large scale astronomical surveys can considerably reduce the computational cost
 of initial astrometry of the point sources detected by these surveys.
@@
 term proportional to the dot product of the PSF model and the image in $\chi^2$. This is because 
-the other terms are not sensitive to the position of the centroid. However, this only allows
+the other terms in $\chi^{2}$ are not sensitive to the position of the centroid. However, this only allows
 us to vary the poition of centroid, and not the flux, while fitting the PSF model
@@
 centroid in a very high resolution grid which the dot product of the image and the PSF model is
-sensitive to. On the other hand, one can think of the initial smoothing step in the first modified 3$\times$3 method 
+sensitive to. On the other hand, one can think of the initial smoothing step in the 3$\times$3 polynomial method 
 as upsampling of the image around the center through convolving it with an approximate Gaussian PSF. 
-The PSF profile fitting and the first modified method are different in that when there is mismatch between the
-widths of the smoothing kernel and the PSF, we loose some information by employing a 3$\times$3 polynomial trick.
-When we have the advantage of knowing the PSF, this isuue can be resolved by employing the second modified polynomial method.
+The PSF profile fitting and the 3$\times$3 polynomial centroiding are different in that when there is mismatch between the
+widths of the smoothing kernel and the that of the PSF, we loose some information by employing a 3$\times$3 polynomial trick.
+When we have the advantage of knowing the PSF, this issue can be resolved by employing the PSF-based polynomial method.
 
-Having a reasonable PSF model should always deliver better centroid estimates, but
+Having a reasonable PSF model always helps us obtain more reliable centroid estimates, but
 over a certain range of low signal-to-noise ratios and PSF sizes, one can achieve sensibly
@@
 PSF profile. Although there are various cases where Moffat profiles provide reasonable
-representation of point spread function, these profiles are not generic enough to let us
+representations of point spread function, these profiles are not generic enough to let us
 reach a more general conclusion. Another important, and untapped, area of study
-would be devising a model that infers the centroid of stars and point spread function
+would be devising a model that infers the centroids of stars and point spread function
 (in its full extent, not at the catalog level) across an astronomical image simultaneously.
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_poly.png}
+  \includegraphics[width=\linewidth]{snr_psffitting.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
-In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{1}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_psfpix28poly.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 modified polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
-In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{2}
+\caption{Scatter plots showing the relation between error in centroid measurement
+from fitting the exact PSF model to the stars and the signal-to-noise ratio of stars,
+with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right)
+pixels. In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{1}
 \end{figure}
@@
 \caption{Scatter plots showing the relation between error in centroid
-measurement from the 3$\times$3 modified polynomial method II and the signal-to-noise
+measurement from the PSF-based 3$\times$3 polynomial method and the signal-to-noise
 ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left),
-and 5.6 (lower right) pixels. In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{3}
+and 5.6 (lower right) pixels. In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{2}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_psffitting.png}
+  \includegraphics[width=\linewidth]{snr_psfpix28poly.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement
-from fitting the exact PSF model to the stars and the signal-to-noise ratio of stars,
-with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right)
-pixels. In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{4}
+\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 polynomial centroiding and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{3}
 \end{figure}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_poly.png}
+  \includegraphics[width=\linewidth]{snr_moment.png}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement
-from the 3$\times$3 polynomial method and FWHM of stars, with SNR  of : 5 (upper left),
-10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, 
-the blue solid
- line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{5}
+\caption{Scatter plots showing the relation between error in centroid measurement from the 7$\times$7 moment method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{4}
 \end{figure}
 
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_psfpix28poly.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement
-from the 3$\times$3 modified polynomial method I and FWHM of stars, with SNR  of 
-: 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each
-scatter plot, the blue solid
- line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{6}
-\end{figure}
-
-\begin{figure}[!htb]
-\minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_psfpoly.png}
-\endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement
-from the 3$\times$3 modified polynomial method II and FWHM of stars, with SNR  of : 5 (upper left),
-10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue solid
- line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{7}
-\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FWHM PLOTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 the blue solid
+ line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{5}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{fwhm_psfpoly.png}
+\endminipage
+\caption{Scatter plots showing the relation between error in centroid measurement
+from the PSF-based 3$\times$3 polynomial method and FWHM of stars, with SNR  of : 5 (upper left),
+10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue solid
+ line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{6}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{fwhm_psfpix28poly.png}
+\endminipage
+\caption{Scatter plots showing the relation between error in centroid measurement
+from the 3$\times$3 polynomial centroiding and FWHM of stars, with SNR  of 
+: 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each
+scatter plot, the blue solid
+ line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{7}
+\end{figure}
+
+\begin{figure}[!htb]
+\minipage{.8\textwidth}
+  \includegraphics[width=\linewidth]{fwhm_moment.png}
+\endminipage
+\caption{Scatter plots showing the relation between error in centroid measurement
+from the 7$\times$7 moment method and FWHM of stars, with SNR of : 5 (upper left),
+10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, 
+the blue solid
  line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{8}

### 2015-03-10 ms/figure.tex
update intro

@@
 \begin{document}
+\title{Fast and optimal centroiding of faint stars}
 
@@
   Mohammadjavad~Vakili\altaffilmark{1},
-  David~W.~Hogg\altaffilmark{1,2,3}
-\altaffiltext{1}{Center for Cosmology and Particle Physics, New York University}
-\altaffiltext{2}{Center for Data Science, New York University}
-\altaffiltext{3}{Max-Planck-Institut f\"ur Astronomie}
-}
-
-\title{Fast and optimal centroiding of faint stars}
+  David~W.~Hogg\altaffilmark{1,2,3}}
+\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Phyics,
+             New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA}
+\altaffiltext{2}{Center for Data Science, New York University, 726 Broadway, 7th Floor, New York, NY 10003, USA}
+\altaffiltext{3}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
+\email{mjvakili@nyu.edu}
 
 \begin{abstract}
-One of the most demanding tasks in astronomical image processing---in terms of precision---is the centroiding of stars. 
-Upcoming large surveys are going to take images of billions of point sources, 
+One of the most demanding tasks in astronomical image processing---in terms of precision---is measurement
+of the positions of stars. 
+Upcoming ground-based surveys are going to take images of billions of point sources, 
 including many faint stars, with short exposure times. Real-time estimation of the
@@
 the root-mean-squared-error with the fundamental Cramer-Rao
-lower bound. We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
-of the PSF, (ii) when we do not know the PSF. In the case that we know the PSF, we show that a fast
+bound on precision. We discuss the case in which we have a good estimate
+of the PSF, and the case in which we don't. In the first case, we show that a fast
  polynomial centroiding after smoothing the image by the PSF can be 
-as accurate as full PSF profile fitting. In the case that we do not
-know the PSF, we demonstrate that although polynomial centroiding is not as
-accurate as PSF profile fitting, it comes close to saturating the Cramer-Rao lower bound
-in a wide range of conditions. We also show that the center-of-light never comes close to 
-saturating the bound, and thus it does not deliver reliable estimates of centroids.
-
-%include weighted moments, naive 3$\times$3 polynomial centroiding,
-%the 3$\times$3 quartic approximation used in the \textsl{Sloan Digital Sky Surveys}, and PSF profile fitting
-%(with both the correct and the incorrect PSF).
-%We recommend a particular form of polynomial cetroiding; it is very fast.
-%Although it is not as accurate as PSF profile fitting with a good PSF estimate,
-%it comes close to saturating the Cramer-Rao lower bound in a wide range of conditions.
+as accurate as full PSF profile fitting. In the second case, we demonstrate 
+that although polynomial centroiding is not as
+accurate as PSF profile fitting, it comes close to saturating the Cramer-Rao bound
+in a wide range of conditions. We also show that the center-of-light (or the taking of moments) 
+never comes close to saturating the bound.
 \end{abstract}
@@
 
-A common practice in astronomy is taking imaging data, and then finding the coordinates
-of various light sources across the sky. Finding accuarate estimates of the centers of point
-sources, convolved with telescope point spread function (and atmospheric PSF in case of
-ground based telescopes), and also pixel response function, is crucial to further steps of
-astronomical image processing. For instance, proper measurement of the shapes of galaxies
+When we take imaging---and we take prodigious amounts of imaging---we ususally have to find the coordinates
+of the stars in that imaging. Finding accuarate estimates of the centers of point
+sources, convolved with telescope point spread function (and atmospheric PSF in the case of
+ground-based telescopes), and also pixel response function, is usually crucial to all further steps in the 
+image processing pipeline. For instance, proper measurement of the shapes of galaxies
 requires interpolating the PSF from the positions of sparsely located stars across the
@@
 Reducing the computational cost becomes even more important in large surveys,
-where we want to estimate the centroids of thousands of point sources detected
-on the telescope's focal plane.
+where we want to estimate the centroids of many thousands of point sources detected
+on the telescope's focal plane in real time.
 
-Reaching the optimal measurement of the centroids of stars however, is limited
-by the lack of knowledge about the exact shape of the PSF, and also presence of noise;
-both sky noise and CCD readout noise. Thus, of particular interest is devising a fast method that returns
+Measurement of the centroids of stars however, is limited
+by lack of knowledge about the exact shape of the PSF, and also the presence of noise;
+both sky noise and CCD readout noise. Thus, it is of particular interest to devise a fast method that returns
 optimal estimates of centroids in a realistic range of signal-to-noise ratios.
 
-To date, a number of softwares have been designed for the purpose of extracting astronomical
-sources and making catalogs. One of these softwares is SExtractor \citep{sex},
+To date, a number of software packages have been designed for the purpose of extracting astronomical
+sources and making catalogs. One of these softwares is \textsl{SExtractor} \citep{sex},
 whose centroiding method involves first, finding the zeroth moment of the object
@@
 until the correction falls below a particular threshold value.
-The width of the Gaussian window function is set by the object's half light radius.
+The width of the Gaussian window function is set by the object's half-light radius.
 
-Another examples are DAOPHOT \citep{daophot}, and DOPHOT \citep{dophot}
+Other examples are DAOPHOT \citep{daophot}, and DOPHOT \citep{dophot}
 which both assume analytic models for the stellar PSF profiles with centroid
 coordinates being free parameters of these models.
-DAOPHOT (DoPHOT) finds the centroids by fitting a Gaussian (a truncated power series for a Gaussian) PSF to
+DAOPHOT (DoPHOT) finds the centroids by fitting a Gaussian (truncated power series for a Gaussian) PSF to
 the light profile of stars.
 
-In this paper, we study how optimal various techniques are at centroiding 
+In this paper, we compare various techniques for centroiding 
 faint unsaturated stars. That is, we apply a number of centroiding methods 
 to a large number of simulated faint stars with different signal-to-noise ratio and
- size realizations. Error from star centroiding methods, will always have 
+ size realizations. Uncertainties from star centroiding methods will always have 
 a theoretically-set lower bound, known as the Cramer-Rao lower bound
-(hereafter denoted by CRLB) which has an inverse relation with the
-signal-to-noise-ratio of stars.
+(hereafter denoted by CRLB), which has an inverse relation with the
+signal-to-noise-ratio of stars (see section \ref{sec:CRLB}).
 
@@
 various ranges of background noise level and PSF FWHM.
-
+%%%%%%%%%%%%%%%%%%%% FIXED%%%%%%%%%%%%%%%%%%%
 In this work, we focus on four centroiding methods. The first method
 involves fitting a PSF profile, assuming that we have a good PSF estimate, to the star. 
-The second method estimates the centroid of a star by fitting a 2d polynomial to
- the 3$\times$3 patch around the brightest pixel of the image convolved with the PSF. 
-The third method centroids stars by
- smoothing the image of stars by a Gaussian kernel of a fixed size,
- and then applying the same 3$\times$3 polynomial trick to the smooth
+The second method estimates the centroid of a star by convolving the image with the PSF 
+and then fitting a 2d second-order polynomial to
+ the 3$\times$3 patch around the brightest pixel. The third method centroids stars by
+ smoothing the image of stars with a Gaussian kernel of a fixed size,
+ and then applying the same 3$\times$3 polynomial fit to the smooth
  image. This method is fast and does not require any knowledge of the 
-PSF. The last method we consider, is the center of light centroiding applied to the
- 7$\times$7 patch around the brightest pixel of the image.
-
+PSF. The last method we consider, the center of light centroiding, involves computing moments in the
+ 7$\times$7 patch centered at the brightest pixel of the image.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 This paper is structured as follows. In section \ref{sec:CRLB},

### 2015-03-22 ms/figure.tex
Update figure.tex

@@
 In order to test the accuracy of various centroiding methods, we need to to compare their 
-performances against each other at saturating the Cramer-Rao lower bound. The closer an estimator is to saturating 
+performances against each other at saturating the Cramer-Rao lower bound on centroiding error. 
+The closer an estimator is to saturating 
 the CRLB, the more information about the quantity that we 
@@
 with the CRLB.
+
+The CRLB is given by the inverse of 
+the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
+ it is sufficient to compute the Fisher matrix.
+Let us assume that we have $M$ observables $\{f_{1}, ... , f_{M}\}$, each
+related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$. Assuming
+uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
+of the Fisher matrix $\mathcal{F}_{ij}$ are given by
+\beq
+\mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
+\label{fisher}
+\eeq
 
@@
  an expression for the CRLB as a function of the size, and SNR of stars.
- We know that the CRLB is given by the inverse of 
-the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
- it is sufficient to compute the Fisher matrix.
-Let us assume that we have $M$ observables $\{f_{1}, ... , f_{M}\}$, each
-related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$. Assuming
-uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
-of the Fisher matrix $\mathcal{F}_{ij}$ are given by
-\beq
-\mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
-\label{fisher}
-\eeq
 

### 2015-03-23 ms/figure.tex
Update figure.tex

@@
  it is sufficient to compute the Fisher matrix.
-Let us assume that we have $M$ observables $\{f_{1}, ... , f_{M}\}$, each
-related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$. Assuming
+
+Let us assume that there are $M$ observables $\{f_{1}, ... , f_{M}\}$, each
+related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$
+\beq
+f_{m} = f_{m}(\theta_{1} , ... , \theta_{B}) \,\, m=1,...,M
+\eeq
+Assuming
 uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
@@
 The optimal estimator of flux (one that saturates Cramer-Rao bound),
-is the weighted average $\tilde{F}=\sum_{i}I_{i}P_{i}$. Knowing the
+is the weighted average $\tilde{F}=\sum_{i}y_{i}P_{i}$. Knowing the
 distribution of $I_{i}$, it can be shown that 

### 2015-03-24 ms/figure.tex
Update figure.tex

--- 2015-03-22 ms/figure.tex
@@
 \begin{document}
-\title{Fast and optimal centroiding of faint stars}
 
@@
   Mohammadjavad~Vakili\altaffilmark{1},
-  David~W.~Hogg\altaffilmark{1,2,3}}
-\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Phyics,
-             New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA}
-\altaffiltext{2}{Center for Data Science, New York University, 726 Broadway, 7th Floor, New York, NY 10003, USA}
-\altaffiltext{3}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
-\email{mjvakili@nyu.edu}
+  David~W.~Hogg\altaffilmark{1,2,3}
+\altaffiltext{1}{Center for Cosmology and Particle Physics, New York University}
+\altaffiltext{2}{Center for Data Science, New York University}
+\altaffiltext{3}{Max-Planck-Institut f\"ur Astronomie}
+}
+
+\title{Fast and optimal centroiding of faint stars}
 
 \begin{abstract}
-One of the most demanding tasks in astronomical image processing---in terms of precision---is measurement
-of the positions of stars. 
-Upcoming ground-based surveys are going to take images of billions of point sources, 
+One of the most demanding tasks in astronomical image processing---in terms of precision---is the centroiding of stars. 
+Upcoming large surveys are going to take images of billions of point sources, 
 including many faint stars, with short exposure times. Real-time estimation of the
@@
 the root-mean-squared-error with the fundamental Cramer-Rao
-bound on precision. We discuss the case in which we have a good estimate
-of the PSF, and the case in which we don't. In the first case, we show that a fast
+lower bound. We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
+of the PSF, (ii) when we do not know the PSF. In the case that we know the PSF, we show that a fast
  polynomial centroiding after smoothing the image by the PSF can be 
-as accurate as full PSF profile fitting. In the second case, we demonstrate 
-that although polynomial centroiding is not as
-accurate as PSF profile fitting, it comes close to saturating the Cramer-Rao bound
-in a wide range of conditions. We also show that the center-of-light (or the taking of moments) 
-never comes close to saturating the bound.
+as accurate as full PSF profile fitting. In the case that we do not
+know the PSF, we demonstrate that although polynomial centroiding is not as
+accurate as PSF profile fitting, it comes close to saturating the Cramer-Rao lower bound
+in a wide range of conditions. We also show that the center-of-light never comes close to 
+saturating the bound, and thus it does not deliver reliable estimates of centroids.
+
+%include weighted moments, naive 3$\times$3 polynomial centroiding,
+%the 3$\times$3 quartic approximation used in the \textsl{Sloan Digital Sky Surveys}, and PSF profile fitting
+%(with both the correct and the incorrect PSF).
+%We recommend a particular form of polynomial cetroiding; it is very fast.
+%Although it is not as accurate as PSF profile fitting with a good PSF estimate,
+%it comes close to saturating the Cramer-Rao lower bound in a wide range of conditions.
 \end{abstract}
@@
 
-When we take imaging---and we take prodigious amounts of imaging---we ususally have to find the coordinates
-of the stars in that imaging. Finding accuarate estimates of the centers of point
-sources, convolved with telescope point spread function (and atmospheric PSF in the case of
-ground-based telescopes), and also pixel response function, is usually crucial to all further steps in the 
-image processing pipeline. For instance, proper measurement of the shapes of galaxies
-requires interpolating the PSF from the positions of sparsely located stars across the
-image to the positions of galaxies. The accuracy of the PSF estimation therefore,
-relies on how accurately we know the centroids of stars.
+A common practice in astronomy is taking imaging data, and then finding the coordinates
+of various light sources across the sky. Finding accuarate estimates of the centers of point
+sources, convolved with telescope point spread function (and atmospheric PSF in case of
+ground based telescopes), and also pixel response function, is crucial to further steps of
+astronomical image processing. For instance, proper measurement of the shapes of galaxies
+requires interpolating the PSF estimates from the positions of stars across the
+image to the positions of galaxies. At the position of each star, PSF is estimated by sub-pixel 
+shifting of the star so that it is centered on its centroid. If the sub-pixel shifts are wrong, then 
+the PSF estimates will be biased. Moreover, measurement of the proper motions of stars
+depends on how well we can measure their centroids.
 
@@
 Reducing the computational cost becomes even more important in large surveys,
-where we want to estimate the centroids of many thousands of point sources detected
-on the telescope's focal plane in real time.
+where we want to estimate the centroids of thousands of point sources detected
+on the telescope's focal plane.
 
-Measurement of the centroids of stars however, is limited
-by lack of knowledge about the exact shape of the PSF, and also the presence of noise;
-both sky noise and CCD readout noise. Thus, it is of particular interest to devise a fast method that returns
+Reaching the optimal measurement of the centroids of stars however, is limited
+by the lack of knowledge about the exact shape of the PSF, and also presence of noise;
+both sky noise and CCD readout noise. Thus, of particular interest is devising a fast method that returns
 optimal estimates of centroids in a realistic range of signal-to-noise ratios.
 
-To date, a number of software packages have been designed for the purpose of extracting astronomical
-sources and making catalogs. One of these softwares is \textsl{SExtractor} \citep{sex},
+To date, a number of softwares have been designed for the purpose of extracting astronomical
+sources and making catalogs. One of these softwares is SExtractor \citep{sex},
 whose centroiding method involves first, finding the zeroth moment of the object
@@
 until the correction falls below a particular threshold value.
-The width of the Gaussian window function is set by the object's half-light radius.
+The width of the Gaussian window function is set by the object's half light radius.
 
-Other examples are DAOPHOT \citep{daophot}, and DOPHOT \citep{dophot}
+Another examples are DAOPHOT \citep{daophot}, and DOPHOT \citep{dophot}
 which both assume analytic models for the stellar PSF profiles with centroid
 coordinates being free parameters of these models.
-DAOPHOT (DoPHOT) finds the centroids by fitting a Gaussian (truncated power series for a Gaussian) PSF to
+DAOPHOT (DoPHOT) finds the centroids by fitting a Gaussian (a truncated power series for a Gaussian) PSF to
 the light profile of stars.
 
-In this paper, we compare various techniques for centroiding 
+In this paper, we study how optimal various techniques are at centroiding 
 faint unsaturated stars. That is, we apply a number of centroiding methods 
 to a large number of simulated faint stars with different signal-to-noise ratio and
- size realizations. Uncertainties from star centroiding methods will always have 
+ size realizations. Error from star centroiding methods, will always have 
 a theoretically-set lower bound, known as the Cramer-Rao lower bound
-(hereafter denoted by CRLB), which has an inverse relation with the
-signal-to-noise-ratio of stars (see section \ref{sec:CRLB}).
+(hereafter denoted by CRLB) which has an inverse relation with the
+signal-to-noise-ratio of stars.
 
@@
 various ranges of background noise level and PSF FWHM.
-%%%%%%%%%%%%%%%%%%%% FIXED%%%%%%%%%%%%%%%%%%%
+
 In this work, we focus on four centroiding methods. The first method
 involves fitting a PSF profile, assuming that we have a good PSF estimate, to the star. 
-The second method estimates the centroid of a star by convolving the image with the PSF 
-and then fitting a 2d second-order polynomial to
- the 3$\times$3 patch around the brightest pixel. The third method centroids stars by
- smoothing the image of stars with a Gaussian kernel of a fixed size,
- and then applying the same 3$\times$3 polynomial fit to the smooth
+The second method estimates the centroid of a star by fitting a 2d polynomial to
+ the 3$\times$3 patch around the brightest pixel of the image convolved with the PSF. 
+The third method centroids stars by
+ smoothing the image of stars by a Gaussian kernel of a fixed size,
+ and then applying the same 3$\times$3 polynomial trick to the smooth
  image. This method is fast and does not require any knowledge of the 
-PSF. The last method we consider, the center of light centroiding, involves computing moments in the
- 7$\times$7 patch centered at the brightest pixel of the image.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+PSF. The last method we consider, is the center of light centroiding applied to the
+ 7$\times$7 patch around the brightest pixel of the image.
+
 This paper is structured as follows. In section \ref{sec:CRLB},
@@
 
-The CRLB is given by the inverse of 
+The CRLB is given by square-root of the inverse of 
 the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
- it is sufficient to compute the Fisher matrix.
-Let us assume that we have $M$ observables $\{f_{1}, ... , f_{M}\}$, each
-related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$. Assuming
+ it is sufficient to compute the Fisher matrix. Consider the following log-likelihood 
+function. Let us assume that there are $M$ observables $\{f_{1}, ... , f_{M}\}$, each
+related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$
+\beq
+f_{m} = f_{m}(\theta_{1} , ... , \theta_{B}).
+\eeq
+
+Assuming
 uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
@@
 
-This requires simulation of a large set of stars for which we know the exact position of centroids
-and the corresponding lower bound for each star, and comparing the centroiding error with the lower bound.
+In this investigation, the observables are the PSF profile evaluated at different pixel locations, and  
+the model paramters are the centroid coordinates. Therfore, $\mathcal{F}$
+is a 2$\times$2 matrix whose elements are given by
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% THIS GOES TO TESTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Furthermore, we uniformly draw the centroids of these simulated stars within sub-pixel regions. 
-%We aim to study how centroiding errors from different methods behave with
-%changing SNR and size, and how close they get to saturating the CRLB. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\beq
+  \mathcal{F}_{ij} = \sum_{\mathbf{p}}\frac{1}{\sigma^{2}}
+                \frac{\partial f_{\mathbf{p}}}{\partial \theta_{i}}\frac{\partial f_{\mathbf{p}}}{\partial \theta_{j}},
+\label{fish}
+\eeq
+where the summation is over pixels, $f_{\mathbf{p}}$ is the value of the PSF profile at pixel location $\mathbf{p}$,
+$\theta=\{x_{c},y_{c}\}$, $\sigma^{2}$ is variance of the uncorrelated Gaussian noise map $n(\mathbf{x_{p}})$
+\begin{eqnarray}
+\langle n(\mathbf{x_{p}}) \rangle &=& 0, \\
+\langle n(\mathbf{x_{p}})n(\mathbf{x_{p^{\prime}}}) \rangle &=& \sigma^{2}\delta_{\mathbf{p}\mathbf{p}^{\prime}}. 
+\end{eqnarray}
 
+Derivation of an explicit expression for the Fisher matrix $\mathcal{F}$ requires specifying a PSF model.
 We use the Moffat profile \citep{moffat} for our PSF simulations. 
@@
 \eeq
-where $F$ is the total flux, $\beta$ is a dimensionless paramter, and $\alpha$ is
+where $F$ is the total flux, $\beta$ is a dimensionless parameter, and $\alpha$ is
 the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$)
-being $2\alpha\sqrt{2^{1/\beta}-1}$. 
-We aim to investigate the performance of centroiding methods for
- different background noise levels, and also different
-values of $\gamma$. For further simplicity, we set the flux of all stars in our
-simulations to unity. Per pixel uncertainties are assumed to be uncorrelated Gaussian,
-and we only study the sky-dominated regime.
+being $2\alpha\sqrt{2^{1/\beta}-1}$. At a fixed $\gamma$, Moffat profiles with lower values
+of $\beta$ have broader tails. It is also important to note that for a sufficiently large $\beta$, 
+the Moffat PSF becomes arbitrarily close to a simple Gaussian PSF.
+
+In order to investigate the performance of centroiding methods for
+ different background noise levels and different
+values of $\gamma$, simulation of a large number of stars---for which the exact positions of centroids
+and their corresponding lower bounds are known---is required.
+
+Given the PSF model (\ref{mof}), an expression for the CRLB as a function of the size, and SNR of stars can be 
+derived. For further simplicity, the flux of all stars in our simulations are set to unity and per-pixel 
+uncertainties are assumed to be uncorrelated Gaussian.
 
@@
 which the flux estimator is drawn from. Assume that the total flux from
-the point source is $F$, and that the PSF at the $i$-th pixel is given
-by $P_{i}$. Therefore the brightness of the $i$-th pixel is drawn from
-a Gaussian distribution $p(I_{i}) = \mathcal{N}(FP_{i},\sigma^{2})$.
+the point source is $F$, and that the sub-pixel shifted PSF at the $i$-th pixel is given
+by $P_{i}$. Therefore the brightness of the $i$-th pixel $y_{i}$ is drawn from
+a Gaussian distribution 
+\beq
+p(y_{i}) = \mathcal{N}(FP_{i},\sigma^{2}). 
+\eeq
 
-The optimal estimator of flux (one that saturates Cramer-Rao bound),
-is the weighted average $\tilde{F}=\sum_{i}I_{i}P_{i}$. Knowing the
-distribution of $I_{i}$, it can be shown that 
+The optimal estimator of flux---one that saturates Cramer-Rao bound---is 
+the matched filter $\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
 \beq
@@
 \begin{array}{l}
-\text{SNR} $=$ \frac{\sqrt{\sum_{i} P_{i}^{2}}}{\sigma}.
+\text{SNR} = \frac{F\sqrt{\sum_{i} P_{i}^{2}}}{\sigma}.
 \end{array}
@@
 
-Note that (\ref{snr}) is valid in the limit of sky-dominated regimes,
-and that is the limit we are interested in throughout our investigation.
- In the case of Moffat profiles, SNR given in (\ref{snr}) can be analytically 
+ In the case of Moffat profiles (\ref{mof}) with total flux of stars set to unity, 
+SNR given in (\ref{snr}) can be analytically 
 expressed in terms of the per pixel uncertainty
-$\sigma$, FWHM $\gamma$, and also $\beta$. We hold $\beta$ fixed at the fiducial value of 2.5.
-In this case we have
+$\sigma$, FWHM $\gamma$, and also $\beta$
 \beq
-\text{SNR} = \frac{0.478}{\sigma \gamma}.
+\text{SNR} = \frac{2(\beta-1)(2^{1/\beta}-1)^{1/2}}{\pi^{1/2}(2\beta-1)^{1/2}}\frac{1}{\sigma \gamma}.
 \label{snr2}
@@
 
-Equation (\ref{snr2}) implies that for stars with the same flux $F$,
- and background
-noise level $\sigma$, those with higher size have lower SNR.
+Equation (\ref{snr2}) implies that at a fixed $\gamma$ and background noise level $\sigma$, 
+stars with broader tails (lower $\beta$) have lower SNR. On the other hand, stars
+with higher value of $\beta$ have higher SNR. For sufficiently large $\beta$---where the PSF can be
+approximated by Gaussian profile---SNR is approximately given by $0.664}/(\sigma\gamma)$.
+Furthermore, at a fixed $\beta$ and background noise level $\sigma$, those with higher $\gamma$ 
+have lower SNR.
 
-Given the PSF model that we have adopted for our simulations, we can derive
- an expression for the CRLB as a function of the size, and SNR of stars.
-
-In our case, the observables are Moffat PSF profile evaluated at different pixels, and  
-the model paramters are the centroid coordinates. Thus, $\mathcal{F}$
-is a 2$\times$2 matrix whose elements are given by
-
+Throughout this investigation, $\beta$ is held fixed at the fiducial value of 2.5, where SNR
+is given by the following expression
 \beq
-  \mathcal{F}_{ij} = \sum_{\mathbf{p}}\frac{1}{\sigma_{\mathbf{p}}^{2}}
-                \frac{\partial f_{\mathbf{p}}}{\partial \theta_{i}}\frac{\partial f_{\mathbf{p}}}{\partial \theta_{j}},
-\label{fish}
+\text{SNR} \simeq \frac{0.478}{\sigma \gamma}.
 \eeq
-where the summation is over pixels, $f_{\mathbf{p}}$ is the value of the Moffat profile at pixel $\mathbf{p}$,
-$\theta=\{x_{c},y_{c}\}$, $\sigma_{\mathbf{p}}^{2}$ is variance
-of the uncorrelated Gaussian noise map $n(\mathbf{x_{p}})$
-\begin{eqnarray}
-\langle n(\mathbf{x_{p}}) \rangle &=& 0, \\
-\langle n(\mathbf{x_{p}})n(\mathbf{x_{p^{\prime}}}) \rangle &=& \sigma^{2}\delta_{\mathbf{p}\mathbf{p}^{\prime}}. 
-\end{eqnarray}
 
@@
 \beq
-  \mathcal{F}^{-1} \simeq 0.6846 \frac{\gamma}{\text{SNR}} 
+  \mathcal{F}^{-1} \simeq \Big(0.685 \frac{\gamma}{\text{SNR}}\Big)^{2} 
   \begin{pmatrix}
@@
 Equation (\ref{crlbmoffat}) implies that at given SNR and $\gamma$,
-CRLB for each component of centroid is given by $0.6846\gamma/\text{SNR}$,
+CRLB for each component of centroid is approximately given by $0.685\gamma/\text{SNR}$,
 and that a good centroiding technique delivers centroids with
-root-mean-squared-error (hereafter RMSE) of each component close to
-this number.
+root-mean-squared-error (hereafter RMSE) close to this.
+
+It is worth noting that for any PSF model whose radial light profile is some function of 
+$r/\gamma$, CRLB remains proportional to the ratio between $\gamma$ and SNR. For PSF profiles with 
+shorter tails, the prefactor of 0.685 in (\ref{crlbmoffat}) becomes smaller. 
+In particular case of Gaussian PSF, the prefactor is approximately 0.6.
 
@@
  of stars. In theory, this method should always saturate the CRLB.
-
 \section{Approximate methods}\label{sec:method}
 
-\item{\bf  PSF-based 3$\times$3 polynomial centroiding}\quad Let us consider the case 
+\item{\bf  Matched-filter polynomial centroiding}\quad Let us consider the case 
 in which we have a good estimate of the PSF at
@@
 We can smooth the image of the star, by convolving it with the 
-full postage stamp of the PSF. Then, we fit a simple 2d polynomial 
+full postage stamp of the PSF
+\begin{eqnarray}
+Y^{(s)} &=& Y \star \mathcal{P}, \\
+Y^{(s)}_{[i,j]} &=& \sum_{k,l}Y_{[i-k,j-l]}\mathcal{P}_{[k,l]},
+\end{eqnarray}
+where $\mathcal{P}$ is the PSF postage stamp, $Y$ is the image of the star, and $Y^{(s)}$ is the smooth image.
+
+Then, we fit a simple 2d polynomial 
 $P(x,y)=a+bx+cy+dx^2+exy+fy^2$ 
-to the 3$\times$3 patch around the brightest pixel of the convolved image.
+to the 3$\times$3 patch around the brightest pixel of the convolved image $Y^{s}$.
 Upon constructing a universal 9$\times$6 design matrix
@@
 where $\mathbf{Z}$ is given by $(z_{1},...,z_{9})^{T}$,
-with $z_{i}$, being the brightness of the $i-$th pixel of the 3$\times$3 patch.
+with $z_{i}$, being the brightness of the $i-$th pixel of the 3$\times$3 patch centered on the brightest pixel of $Y^{(s)}$.
 Afterwards, the best fit parameters can be used to compute the centroid coordinate
@@
 the smoothing step in the following way. Instead of smoothing the image 
-with the PSF, we smooth it with a Gaussian kernel of a fixed size. 
+by convolving it with the PSF, smoothing is done by convolving the image 
+with a Gaussian kernel of a fixed size 
 \beq
-k(\mathbf{x}) = \frac{1}{2\pi w^2}\exp(-\mathbf{x}^{2}/2w^{2}).
+k(\mathbf{x}) = \frac{1}{2\pi w^2}\exp(-\mathbf{x}^{2}/2w^{2}),
 \eeq
-Throughout this study, the full-width at half-maximum of the Gaussian kernel is held at
-a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels).
-
-Then we apply the same 2d polynomial method to the 3$\times$3 patch around the brightest
-pixel of the smoothed image. Therefore, for a given star and a smoothing kernel,
+where throughout this study, the full-width at half-maximum of the Gaussian kernel is held at
+a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels). Convolution is done as follows
+\begin{eqnarray}
+Y^{(s)} &=& Y \star \mathcal{K}, \\
+Y^{(s)}_{[i,j]} &=& \sum_{k,l}Y_{[i-k,j-l]}\mathcal{K}_{[k,l]},
+\end{eqnarray}
+where $Y$ is the image of the star, $Y^{(s)}$ is the smooth image, and $\mathcal{K}$ is a 7$\times$7 
+array whose elements are given by the Gaussian kernel
+\beq
+\mathcal{K}_{[k,l]} = k(x_{k},y_{l}).
+\eeq 
+Then we apply the same 2d polynomial method to the 3$\times$3 patch centered on the brightest
+pixel of the smooth image $Y^{(s)}$. Therefore, for a given star and a smoothing kernel,
 the outcome of equation (\ref{linearfit}) can be
@@
 \item {\bf Center of light centroiding}\quad In addition to the methods 
-mentioned so far, we examine centroiding stars by computing their zeroth moments
+mentioned so far, we examine centroiding stars by computing their first moments
 in a 7$\times$7 patch around the brightest pixel of the image.
+
+\begin{eqnarray}
+x_{c} &=& \frac{\sum_\mathbf{p}x_{\mathbf{p}}Y_{\mathbf{p}}}{\sum_\mathbf{p}Y_{\mathbf{p}}}, \\
+y_{c} &=& \frac{\sum_\mathbf{p}y_{\mathbf{p}}Y_{\mathbf{p}}}{\sum_\mathbf{p}Y_{\mathbf{p}}},
+\end{eqnarray}
+where the summation is done over all the pixels of the 7$\times$7 patch, and $x_{\mathbf{p}}$, 
+$y_{\mathbf{p}}$, and $Y_{\mathbf{p}}$, are the $x$ coordinate, $y$ coordinate, and the brightness
+of pixel $\mathbf{p}$ respectively.
+
 In terms of saturating the Cramer-Rao lower bound, we expect this simple 
@@
 \section{Tests}\label{sec:data}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% THIS GOES TO TESTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Furthermore, we uniformly draw the centroids of these simulated stars within sub-pixel regions. 
+%We aim to study how centroiding errors from different methods behave with
+%changing SNR and size, and how close they get to saturating the CRLB. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 We perform two sets of simulations. In the first set, we choose four values of

### 2015-03-24 ms/figure.tex
Update figure.tex

@@
 the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
- it is sufficient to compute the Fisher matrix. Consider the following log-likelihood 
-function. Let us assume that there are $M$ observables $\{f_{1}, ... , f_{M}\}$, each
+ it is sufficient to compute the Fisher matrix. Let us assume that there are $M$ observables $\{f_{1}, ... , f_{M}\}$, each
 related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$
@@
 uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
-of the Fisher matrix $\mathcal{F}_{ij}$ are given by
+of the $B\times B$Fisher matrix $\mathcal{F}_{ij}$ are given by
 \beq
@@
 
-The optimal estimator of flux---one that saturates Cramer-Rao bound---is 
+The optimal estimator of flux is 
 the matched filter $\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
@@
 It is worth noting that for any PSF model whose radial light profile is some function of 
-$r/\gamma$, CRLB remains proportional to the ratio between $\gamma$ and SNR. For PSF profiles with 
-shorter tails, the prefactor of 0.685 in (\ref{crlbmoffat}) becomes smaller. 
+$r/\gamma$, CRLB has the same functional form, in that it is proportional to the ratio between $\gamma$ and SNR. 
+For PSF profiles with shorter tails, the prefactor of 0.685 in (\ref{crlbmoffat}) becomes smaller. 
 In particular case of Gaussian PSF, the prefactor is approximately 0.6.
@@
 
-\item{\bf 3$\times$3 polynomial centroiding}\quad In the case that 
+\item{\bf Default polynomial centroiding}\quad In the case that 
 we do not have know the PSF at the position of star, we change 
@@
 lies on the CRLB except for simulations with SNR $\la$ 10 where the RMSE gets slightly pulled away
-from the CRLB due to presence of a few outliers. Figure [\ref{2}] demonstrates that even the PSF-based 3$\times$3 polynomial 
+from the CRLB due to presence of a few outliers. Figure [\ref{2}] demonstrates that even the matched-filter polynomial 
 centroiding is able deliver centroiding estimates as accurate as PSF profile fitting, with the exception
-of simulated stars with $\gamma$ = 2 pixels. For stars with $\gamma$ = 2 pixels, although the 3$\times$3 polynomial
+of simulated stars with $\gamma$ = 2 pixels. For stars with $\gamma$ = 2 pixels, although second-order polynomial
 fitting gets close to saturating the CRLB, it fails to saturate the CRLB since the PSF is undersampled. For simulated images with higher $\gamma$, convolving the
@@
 
-RMSE from the 3$\times$3 polynomial centroiding [\ref{3}],
+RMSE from the default polynomial centroiding [\ref{3}],
 is very close to the CRLB except at the very small values of SNR (SNR $\la$ 10).
@@
 the with a Gaussian kernel, the image is still relatively undersampled, and not smooth enough
-for a 2d polynomial fitting to provide highly accurate centroiding estimates.
+for a second-order polynomial fitting to provide highly accurate centroiding estimates.
 For stars with $\gamma=2.8$ pixels, since the FWHM of the Gaussian kernel matches that 
@@
 whose $\gamma$ matches the FWHM of the smoothing kernel and as a result, we loose
-some information by fitting a polynomial to a 3$\times$3 patch. Therefore,
+some information by fitting a second-order polynomial to a 3$\times$3 patch. Therefore,
  we observe slight deviation from the CRLB for stars with $\gamma$ = 4 pixels, and 
@@
 the exact PSF model always saturate the CRLB. Once again, we observe that the centroid
-estimates found by the PSF-based 3$\times$3 polynomial centroiding saturate the CRLB with the
+estimates found by matched-filter polynomial centroiding saturate the CRLB with the
 exception of simulated stars with SNR = 5, or $\gamma$ very close to 2 pixels [\ref{6}].
 
-The 3$\times$3 polynomial method [\ref{7}], results in RMSE very close to the CRLB.
+The default polynomial method [\ref{7}], results in RMSE very close to the CRLB.
 For all four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels,
@@
 gets closer to that of the simulated images.
-After approximately 3 pixels, increasing $\gamma$ result in deviation of RMSE of the method from the CRLB.
-This is a characteristic of 3$\times$3 method as we apply it to a smoothed image which is still not sufficiently
+After approximately 3 pixels, increasing $\gamma$ results in deviation of RMSE of the method from the CRLB.
+This is a characteristic of polynomial method as we apply it to a smooth image which is still not sufficiently
 well-sampled.  Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) become
-closer to the CRLB.
+closer to the CRLB. In the case of extremely faint stars (SNR = 5),
+default polynomial centroiding is not able to deliver any reliable estimate, and it fails.
 
@@
 result in RMSE much larger than the CRLB in all ranges of FWHM and for all four
-values of SNR in this experiment. In the case of extremely faint stars (SNR = 5),
-the polynomial method is not able to deliver any reliable estimate, and completely fails.
+values of SNR in this experiment.
 

### 2015-03-24 ms/figure.tex
Update figure.tex

@@
 methods that do not require any knowledge of the PSF at the positions of stars. Of methods that belong to this class,
-we consider centroiding stars based on fitting a low order
+we consider centroiding stars based on fitting a second-order
 polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel of fixed width, and finding the center of light 
@@
 of the PSF) at the positions of stars. We considered two examples from this class. The first example
-is the 3$\times$3 polynomial centroiding applied to the image of the star convolved with the PSF, and the
+is the matched-filter polynomial centroiding, and the
 second example is the full PSF profile fitting. In terms of saturating the Cramer-Rao bound, we compared 
 the performances of these methods against each other.
-
-%Furthermore, we compared the performance of these methods with the naive 3$\times$3 polynomial
-%centroiding, 3$\times$3 quartic approximation, moment-based method, and PSF fitting.
-%In order to make this comparison, we performed some tests on a large number of
-%simulated data, and investigated to see if these estimators can saturate the Cramer-Rao
-%lower bound, or how close to they get to saturating the bound.
 
@@
 saturating the CRLB. In a considerable range of PSF sizes and background noise levels, 
-this method completely fails to deliver any reliable centroiding estimates.
+this method fails to deliver any reliable centroiding estimates.
 
 On the other hand, the RMSE of centroid estimates of 
-3$\times$3 polynomial centroiding are much closer to saturating the CRLB in all ranges of signal-to-noise ratio.
+default polynomial centroiding are much closer to saturating the CRLB in all ranges of signal-to-noise ratio.
 The performance of this method however, is limited by
 two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} PSF size.
-The 3$\times$3 polynomial centroiding technique only takes advantage of the information
- contained in a 3$\times$3 patch around the brighest pixel of the smoothed image which is only
+The default polynomial centroiding technique only takes advantage of the information
+ contained in a 3$\times$3 patch centered on the brighest pixel of the smoothed image which is only
  well-sampled when the FWHM of the simulated image of star
  matches that of the smoothing kernel. Thus, when we apply 
-this method to find the centroid of stars with larger FWHM, certain amount of
+this method to find the centroids of stars with larger FWHM, certain amount of
 information (encoded in the Cramer-Rao lower bound) is lost, and therefore, the RMSE
@@
 Although this method is able to get very close to saturating the CRLB in a wide range of
-signal-to-noise ratios, it is not reliable in the case of extremely faint stars.
+signal-to-noise ratios, it is not reliable in the case of centroiding extremely faint stars.
  This is partly due to the fact that in the presence of noise, 
@@
 
-Once we modify the polynomial method further by smoothing the image with the full postage stamp
+Once we modify the polynomial method further by convolving the image with the full postage stamp
 of the PSF, we obtain results that saturate the CRLB in a wide range of PSF sizes and noise levels.  
-This is due to the fact that once the images are convolved with the correct PSF, they become so well-sampled and smooth
-that fitting a 2d polynomial to the 3$\times$3 patch around the brightest pixel of the smooth image is sufficient for us to obtain
+This is due to the fact that once the images of stars are convolved with the correct PSF, they become so well-sampled and smooth
+that fitting a second-order polynomial to the 3$\times$3 patch centered on the brightest pixel of the smooth image is sufficient for us to obtain
 results as accurate as those from fitting a PSF profile. The only conditions in which slight deviation from
-saturating the CRLB occures are very low signal-to-noise ratios (SNR $\la$ 10), and undersampled PSF (FWHM $\sim$ 2 pixels).
+saturating the CRLB occurs are very low signal-to-noise ratios (SNR $\la$ 10), and undersampled PSF (FWHM $\sim$ 2 pixels).
 One advantage of this method over PSF fitting method is that it is fast, and that it is able to saturate the CRLB in 
 a wide range of conditions. In the case that we have a good estimate of the PSF, the 
-PSF-based 3$\times$3 polynomial centroiding is a significantly much faster algorithm. 
-Although this method is more accurate than 3$\times$3 polynomial centroiding, it is
+matched-filter polynomial centroiding is a significantly much faster algorithm. 
+Although this method is more accurate than default polynomial centroiding, it is
 slightly slower because it requires convolution of the image with the full potage stamp of the PSF.
 
-In this investigation we showed that PSF fitting is always better at centroiding stars.
+In this investigation we showed that PSF fitting always performs better---in terms of saturating the CRLB---at centroiding stars.
 However, this method has its own disadvantages. First, we do not always know the the exact PSF. Second, finding
- the centroid by profile fitting is computationally expensive, whereas by employing any of the 3$\times$3 polynomial techniques 
-considered in this study into large scale astronomical surveys can considerably reduce the computational cost
-of initial astrometry of the point sources detected by these surveys.
+ the centroid by profile fitting is computationally expensive, whereas employing any of the 3$\times$3 polynomial techniques 
+considered in this study in large scale astronomical surveys reduces the computational cost
+of initial astrometry of the point sources considerably.
 
@@
 centroid in a very high resolution grid which the dot product of the image and the PSF model is
-sensitive to. On the other hand, one can think of the initial smoothing step in the 3$\times$3 polynomial method 
-as upsampling of the image around the center through convolving it with an approximate Gaussian PSF. 
-The PSF profile fitting and the 3$\times$3 polynomial centroiding are different in that when there is mismatch between the
-widths of the smoothing kernel and the that of the PSF, we loose some information by employing a 3$\times$3 polynomial trick.
-When we have the advantage of knowing the PSF, this issue can be resolved by employing the PSF-based polynomial method.
+sensitive to. On the other hand, one can think of the initial smoothing step in the default polynomial method 
+as upsampling of the image around the center by convolving it with an approximate Gaussian PSF. 
+The default polynomial centroiding is different from PSF-fitting method in that, when there is mismatch between the
+widths of the smoothing kernel and the that of the PSF, we loose some information by employing a 3$\times$3 polynomial fitting.
+When we have the advantage of knowing the PSF, this issue can be resolved by employing the matched-filter polynomial method.
 
@@
  accurate results by employing a simple 3$\times$3 method after smooting the image with
- a Gaussian kernel of fixed width, and without making any assumption about the PSF model.
+ a Gaussian kernel of a fixed width, and without making any assumption about the PSF model at the positions of stars.
 
@@
 PSF profile. Although there are various cases where Moffat profiles provide reasonable
-representations of point spread function, these profiles are not generic enough to let us
+representations of the point spread function, these profiles are not generic enough to let us
 reach a more general conclusion. Another important, and untapped, area of study
 would be devising a model that infers the centroids of stars and point spread function
-(in its full extent, not at the catalog level) across an astronomical image simultaneously.
+---in its full extent, not at the catalog level---across an astronomical image simultaneously.
 This is beyond the scope of this study.

### 2015-03-24 ms/figure.tex
Update figure.tex

@@
 involves fitting a PSF profile, assuming that we have a good PSF estimate, to the star. 
-The second method estimates the centroid of a star by fitting a 2d polynomial to
+The second method estimates the centroid of a star by fitting a 2d second-order polynomial to
  the 3$\times$3 patch around the brightest pixel of the image convolved with the PSF. 
@@
 
-Then, we fit a simple 2d polynomial 
+Then, we fit a simple 2d second-order polynomial 
 $P(x,y)=a+bx+cy+dx^2+exy+fy^2$ 
@@
 information regarding the centroids of stars in the 3$\times$3 patch around the
-brightest pixel. In addition, a simple 2d polynomial will provide a better fit 
+brightest pixel. In addition, a simple second-order polynomial will provide a better fit 
 since convolution with the PSF makes the variation of the brightness of the image
@@
 \eeq 
-Then we apply the same 2d polynomial method to the 3$\times$3 patch centered on the brightest
+Then we apply the same 2d second-order polynomial method to the 3$\times$3 patch centered on the brightest
 pixel of the smooth image $Y^{(s)}$. Therefore, for a given star and a smoothing kernel,

### 2015-03-24 ms/figure.tex
Update figure.tex

@@
 uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
-of the $B\times B$Fisher matrix $\mathcal{F}_{ij}$ are given by
+of the $B\times B$ Fisher matrix $\mathcal{F}_{ij}$ are given by
 \beq

### 2015-03-24 ms/figure.tex
Update figure.tex

@@
 
-Assuming
-uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
+Assuming uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
 of the $B\times B$ Fisher matrix $\mathcal{F}_{ij}$ are given by
@@
 In this investigation, the observables are the PSF profile evaluated at different pixel locations, and  
-the model paramters are the centroid coordinates. Therfore, $\mathcal{F}$
+the model paramters are the centroid coordinates. Therefore, $\mathcal{F}$
 is a 2$\times$2 matrix whose elements are given by
@@
 $r/\gamma$, CRLB has the same functional form, in that it is proportional to the ratio between $\gamma$ and SNR. 
-For PSF profiles with shorter tails, the prefactor of 0.685 in (\ref{crlbmoffat}) becomes smaller. 
+For PSF profiles with shorter tails (\eg Gaussian), the prefactor of 0.685 in (\ref{crlbmoffat}) becomes smaller. 
 In particular case of Gaussian PSF, the prefactor is approximately 0.6.
@@
 $P(x,y)=a+bx+cy+dx^2+exy+fy^2$ 
-to the 3$\times$3 patch around the brightest pixel of the convolved image $Y^{s}$.
+to the 3$\times$3 patch centered on the brightest pixel of the convolved image $Y^{s}$.
 Upon constructing a universal 9$\times$6 design matrix
@@
 \item{\bf Default polynomial centroiding}\quad In the case that 
-we do not have know the PSF at the position of star, we change 
+we do not know the PSF at the position of star, we change 
 the smoothing step in the following way. Instead of smoothing the image 
@@
 where throughout this study, the full-width at half-maximum of the Gaussian kernel is held at
-a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels). Convolution is done as follows
+a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels). Smoothing step is done as follows
 \begin{eqnarray}

### 2015-04-05 ms/figure.tex
Update figure.tex

@@
   Mohammadjavad~Vakili\altaffilmark{1},
-  David~W.~Hogg\altaffilmark{1,2,3}
-\altaffiltext{1}{Center for Cosmology and Particle Physics, New York University}
-\altaffiltext{2}{Center for Data Science, New York University}
-\altaffiltext{3}{Max-Planck-Institut f\"ur Astronomie}
-}
+  David~W.~Hogg\altaffilmark{1,2,3}}
+\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Phyics,
+             New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA}
+\altaffiltext{2}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
+\altaffiltext{3}{Center for Data Science, New York University, 726 Broadway, 7th Floor, New York, NY 10003, USA}
+\email{mjvakili@nyu.edu}
 
@@
 
-%include weighted moments, naive 3$\times$3 polynomial centroiding,
-%the 3$\times$3 quartic approximation used in the \textsl{Sloan Digital Sky Surveys}, and PSF profile fitting
-%(with both the correct and the incorrect PSF).
-%We recommend a particular form of polynomial cetroiding; it is very fast.
-%Although it is not as accurate as PSF profile fitting with a good PSF estimate,
-%it comes close to saturating the Cramer-Rao lower bound in a wide range of conditions.
 \end{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%SAY SOMETHING MAARRRR%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 We examine fitting an exact
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%THIS METHOD SUCKS BALLS%%%%%%%%%%%%%%%%%%%%%%%
+\section{Tests}\label{sec:data}
 
-\section{Tests}\label{sec:data}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% THIS GOES TO TESTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Furthermore, we uniformly draw the centroids of these simulated stars within sub-pixel regions. 
-%We aim to study how centroiding errors from different methods behave with
-%changing SNR and size, and how close they get to saturating the CRLB. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 We perform two sets of simulations. In the first set, we choose four values of

### 2015-05-31 ms/figure.tex
Update figure.tex

@@
 
-Assuming uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
+Assuming uncorrelated Gaussian error with variance $\sigma^{2}_{m}$ for each observable $f_{m}$, elements
 of the $B\times B$ Fisher matrix $\mathcal{F}_{ij}$ are given by
@@
 
-In this investigation, the observables are the PSF profile evaluated at different pixel locations, and  
-the model paramters are the centroid coordinates. Therefore, $\mathcal{F}$
+In this investigation, the observables are the pixel-convolved PSF (PSF profile evaluated at different pixel locations), and  
+the model paramters under consideration are the centroid coordinates. Therefore, $\mathcal{F}$
 is a 2$\times$2 matrix whose elements are given by
@@
 \eeq
-where the summation is over pixels, $f_{\mathbf{p}}$ is the value of the PSF profile at pixel location $\mathbf{p}$,
+where the summation is over pixels, $f_{\mathbf{p}}$ is the value of the PSF at pixel location $\mathbf{p}$,
 $\theta=\{x_{c},y_{c}\}$, $\sigma^{2}$ is variance of the uncorrelated Gaussian noise map $n(\mathbf{x_{p}})$
@@
 being $2\alpha\sqrt{2^{1/\beta}-1}$. At a fixed $\gamma$, Moffat profiles with lower values
-of $\beta$ have broader tails. It is also important to note that for a sufficiently large $\beta$, 
-the Moffat PSF becomes arbitrarily close to a simple Gaussian PSF.
+of $\beta$ have broader tails. It is also important to note that for sufficiently large values of the 
+parameter $\beta$, the Moffat PSF becomes arbitrarily close to a simple Gaussian PSF.
 
@@
  different background noise levels and different
-values of $\gamma$, simulation of a large number of stars---for which the exact positions of centroids
+values of the parameter $\gamma$, simulation of a large number of images of stars---for which the exact positions of centroids
 and their corresponding lower bounds are known---is required.
@@
 The optimal estimator of flux is 
-the matched filter $\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
+the matched filter flux estimator $\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
 \beq
@@
 
-Equation (\ref{snr2}) implies that at a fixed $\gamma$ and background noise level $\sigma$, 
-stars with broader tails (lower $\beta$) have lower SNR. On the other hand, stars
-with higher value of $\beta$ have higher SNR. For sufficiently large $\beta$---where the PSF can be
+Equation (\ref{snr2}) implies that at a fixed $\gamma$ and background Gaussian noise 
+with variance $\sigma^{2}$, stars with broader tails (lower $\beta$) have lower SNR.
+On the other hand, stars with higher value of $\beta$ have higher SNR. 
+For sufficiently large $\beta$---where the PSF can be
 approximated by Gaussian profile---SNR is approximately given by $0.664}/(\sigma\gamma)$.
-Furthermore, at a fixed $\beta$ and background noise level $\sigma$, those with higher $\gamma$ 
-have lower SNR.
+Furthermore, at a fixed $\beta$ and variance of the background noise $\sigma^{2}$,
+observed stars with higher $\gamma$ have lower SNR.
 
@@
 It is worth noting that for any PSF model whose radial light profile is some function of 
-$r/\gamma$, CRLB has the same functional form, in that it is proportional to the ratio between $\gamma$ and SNR. 
-For PSF profiles with shorter tails (\eg Gaussian), the prefactor of 0.685 in (\ref{crlbmoffat}) becomes smaller. 
-In particular case of Gaussian PSF, the prefactor is approximately 0.6.
+$r/\gamma$, CRLB has the same functional form, in that it is proportional to the ratio
+between $\gamma$ and SNR. 
+For PSF profiles with shorter tails (\eg Gaussian), the prefactor of 0.685 in (\ref{crlbmoffat})
+becomes smaller. In particular case of Gaussian PSF, the prefactor is approximately 0.6.
 
@@
  We expect this method to perform better in determing the centroids
- of stars. In theory, this method should always saturate the CRLB.
+ of stars, and deliver RMSE very close to Cramer-Rao bound. In the next section,
+ we briefly discuss the centroiding methods used in our Cramer-Rao bound saturating tests.
+
 \section{Approximate methods}\label{sec:method}
@@
 \item{\bf  Matched-filter polynomial centroiding}\quad Let us consider the case 
-in which we have a good estimate of the PSF at
+in which we have a good estimate of the pixel-convolved PSF at
 the position of the faint star under consideration. 
 We can smooth the image of the star, by convolving it with the 
-full postage stamp of the PSF
+full PSF $\mathcal{P}$
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $\mathcal{P}$ is the PSF postage stamp, $Y$ is the image of the star, and $Y^{(s)}$ is the smooth image.
+where $Y$ is the image of the star, and $Y^{(s)}$ is the smooth image.
 

### 2015-05-31 ms/figure.tex
matched filtering

@@
 the position of the faint star under consideration. 
-We can smooth the image of the star, by convolving it with the 
-full PSF $\mathcal{P}$
+We can smooth the image of the star, by correlating it with the 
+full PSF $\mathcal{P}$ at the position of the star.
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $Y$ is the image of the star, and $Y^{(s)}$ is the smooth image.
+where $Y$ is the image of the star, and $Y^{(s)}$ is the smooth image which 
+is called matched-filter image.
 
@@
 $P(x,y)=a+bx+cy+dx^2+exy+fy^2$ 
-to the 3$\times$3 patch centered on the brightest pixel of the convolved image $Y^{s}$.
+to the 3$\times$3 patch centered on the brightest pixel of the
+mathched-filter image $Y^{s}$.
 Upon constructing a universal 9$\times$6 design matrix
@@
 
-When $D$ has a zero (or very close to zero) deteminant,
-centroid estimated by (\ref{center}) gets arbitrarily 
-large in which case the centroiding method leads to a catastrophic 
-outlier. In order to tackle this issue, we add a soft regularization term
+When the curvature matrix $D$ has a zero (or very close to zero) deteminant,
+centroid estimates obtained from equation (\ref{center}) can become arbitrarily 
+large which leads to catastrophic outliers. 
+In order to tackle this issue, we add a soft regularization term
 proportional to $\sigma^{2}$ to the determinant of $D$.

### 2015-05-31 ms/figure.tex
rearranged some words in matched-filtering method

@@
 
-\section{Approximate methods}\label{sec:method}
+\section{Centroiding methods}\label{sec:method}
 
-\item{\bf  Matched-filter polynomial centroiding}\quad Let us consider the case 
+\item{\bf  Matched filter polynomial centroiding}\quad Let us consider the case 
 in which we have a good estimate of the pixel-convolved PSF at
@@
 \end{eqnarray}
-where $Y$ is the image of the star, and $Y^{(s)}$ is the smooth image which 
-is called matched-filter image.
+where $Y$ is the image of the star, and $Y^{(s)}$ is called matched filter. 
+Matched filter is a model where the data $Y$ is correlated (convolved in the 
+case of symmetrical PSF) with the PSF $\mathcal{P}$. It provides an optimal an 
+optimal detection map where the peak of the map is the likely position of the 
+point source (Lang \emph{et al.}, in preparation).
 
@@
 
-\item {\bf Center of light centroiding}\quad In addition to the methods 
+\item {\bf Center-of-light centroiding}\quad In addition to the methods 
 mentioned so far, we examine centroiding stars by computing their first moments

### 2015-07-15 ms/figure.tex
Update figure.tex

@@
 the root-mean-squared-error with the fundamental Cramer-Rao
-lower bound. We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
-of the PSF, (ii) when we do not know the PSF. In the case that we know the PSF, we show that a fast
- polynomial centroiding after smoothing the image by the PSF can be 
+lower bound assuming zero-mean constant Gaussian noise. We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
+of the PSF, (ii) when we do not know the PSF. In the case that we know the PSF, 
+we show that a fast polynomial centroiding after smoothing the image by the PSF can be 
 as accurate as full PSF profile fitting. In the case that we do not

### 2015-07-15 ms/figure.tex
Update figure.tex

@@
  of the mean and variance of the distribution
-which the flux estimator is drawn from. Assume that the total flux from
+which the flux estimator is drawn from. Assuming that the total flux from
 the point source is $F$, and that the sub-pixel shifted PSF at the $i$-th pixel is given
@@
 
-The optimal estimator of flux is 
-the matched filter flux estimator $\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
+The optimal estimator of flux is the matched-filter flux estimator 
+$\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
 \beq
@@
 17 $\times$ 17 postage-stamps of Moffat profiles with centroids randomly drawn
-within the central pixel of the 17 $\times$ 17 postage-stamps. Moreover, Gaussian
-noise is added to each postage-stamp such that the simulated stars are uniformly
- distributed in log-SNR between SNR = 5 to SNR = 100.
+within the central pixel of the 17 $\times$ 17 postage-stamps. Moreover, zero-mean 
+uncorrelated Gaussian noise is added to each postage-stamp such that the simulated 
+stars are uniformly distributed in log-SNR between SNR = 5 to SNR = 100.
 
@@
 For each SNR, and for each postage-stamp with a given $\gamma$, 
-Gaussian noise, with variance corresponding to SNR and $\gamma$ through equation 
-(\ref{snr2}), is added to each postage-stamp.
+zero-mean uncorrelated Gaussian noise, with standard deviation corresponding 
+to SNR and $\gamma$ through equation (\ref{snr2}), is added to each postage-stamp.
 

### 2015-07-16 ms/figure.tex
Update figure.tex

@@
 In order to investigate how information-preserving these techniques are, we compare
-the root-mean-squared-error with the fundamental Cramer-Rao
+the root-mean-squared-error with the fundamental Cram\'{e}r-Rao
 lower bound assuming zero-mean constant Gaussian noise. We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
@@
 know the PSF, we demonstrate that although polynomial centroiding is not as
-accurate as PSF profile fitting, it comes close to saturating the Cramer-Rao lower bound
+accurate as PSF profile fitting, it comes close to saturating the Cram\'{e}r-Rao lower bound
 in a wide range of conditions. We also show that the center-of-light never comes close to 
@@
 faint unsaturated stars. That is, we apply a number of centroiding methods 
-to a large number of simulated faint stars with different signal-to-noise ratio and
- size realizations. Error from star centroiding methods, will always have 
-a theoretically-set lower bound, known as the Cramer-Rao lower bound
-(hereafter denoted by CRLB) which has an inverse relation with the
-signal-to-noise-ratio of stars.
+to a large number of simulated faint stars, assuming uncorrelated Gaussian noise, 
+with different signal-to-noise ratio and size realizations. Error from star 
+centroiding methods, will always have a theoretically-set lower bound, 
+known as the Cram\'{e}r-Rao lower bound (hereafter denoted by CRLB) which 
+has an inverse relation with the signal-to-noise-ratio of stars.
 
@@
 This paper is structured as follows. In section \ref{sec:CRLB},
-we discuss the Cramer-Rao lower bound, and we derive
+we discuss the Cram\'{e}r-Rao lower bound, and we derive
 an analytic expression for the lower bound on centroiding error
@@
 centroiding methods used in our investigation.
-In section \ref{sec:data} we discuss the Cramer-Rao lower bound satuaration
+In section \ref{sec:data} we discuss the Cram\'{e}r-Rao lower bound satuaration
 tests and their corresponding simulated data.
@@
  we discuss and conclude in \ref{sec:discussion}.               
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Cramer-Rao lower Bound %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%Cram\'{e}r-Rao lower Bound %%%%%%%%%%%%%%
 
-\section{Cramer-Rao lower bound on centroiding error}\label{sec:CRLB}
+\section{Cram\'{e}r-Rao lower bound on centroiding error}\label{sec:CRLB}
 
 In order to test the accuracy of various centroiding methods, we need to to compare their 
-performances against each other at saturating the Cramer-Rao lower bound on centroiding error. 
-The closer an estimator is to saturating 
-the CRLB, the more information about the quantity that we 
+performances against each other at saturating the Cram\'{e}r-Rao lower bound on centroiding error. 
+The closer an estimator is to saturating the CRLB, the more information about the quantity that we 
 need to estimate is preserved. A measure for closeness of an estimator to 
-saturating the CRLB is comparison of the root-mean-squared-error of that estimator 
+saturating the CRLB is comparison of the root-mean-squared error of that estimator 
 with the CRLB.
 
-The CRLB is given by square-root of the inverse of 
+The Cram\'{e}r-Rao inequality \citep{cramer} sets a lower bound on the 
+root-mean-squared error of unbiased estimators. The CRLB is given by square-root of the inverse of 
 the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
@@
 We examine fitting an exact
- PSF profile to the stars. That is, in our Cramer-Rao bound saturation tests, we find the best
+ PSF profile to the stars. That is, in our Cram\'{e}r-Rao bound saturation tests, we find the best
  estimates of flux and centroid by optimizing the $\chi^{2}$.
  We expect this method to perform better in determing the centroids
- of stars, and deliver RMSE very close to Cramer-Rao bound. In the next section,
- we briefly discuss the centroiding methods used in our Cramer-Rao bound saturating tests.
+ of stars, and deliver RMSE very close to Cram\'{e}r-Rao bound. In the next section,
+ we briefly discuss the centroiding methods used in our Cram\'{e}r-Rao bound saturating tests.
 
@@
 
-In terms of saturating the Cramer-Rao lower bound, we expect this simple 
+In terms of saturating the Cram\'{e}r-Rao lower bound, we expect this simple 
 center of light centroiding to perform worse than all other methods mentioned in 
@@
 
-An optimal stellar centroiding algorithm must saturate the fundamental Cramer-Rao lower 
+An optimal stellar centroiding algorithm must saturate the fundamental Cram\'{e}r-Rao lower 
 bound. That is, in all ranges of background noise level, size, radial light profile,
@@
 is the matched-filter polynomial centroiding, and the
-second example is the full PSF profile fitting. In terms of saturating the Cramer-Rao bound, we compared 
+second example is the full PSF profile fitting. In terms of saturating the Cram\'{e}r-Rao bound, we compared 
 the performances of these methods against each other.
@@
 this method to find the centroids of stars with larger FWHM, certain amount of
-information (encoded in the Cramer-Rao lower bound) is lost, and therefore, the RMSE
+information (encoded in the Cram\'{e}r-Rao lower bound) is lost, and therefore, the RMSE
 of these methods deviates from the CRLB. This deviation becomes even larger at lower
@@
 
-\bibitem[Bertin \& Arnouts (1996)]{sex} Bertin, E., Arnouts, S. \ 1996  Astronomy and Astrophysics Supplement Series, 117, 393-404
+\bibitem[Bertin \& Arnouts (1996)]{sex} Bertin, E., Arnouts, S. \ 1996  Astronomy and Astrophysics Supplement Series, 117, 393-40
+\bibitem[Cram\'{e}r (1946)]{cramer} Cram\'{e}r, H. \ 1946 Mathematical methods of statistics, Princeton university press
 \bibitem[Lupton etal. (2001)]{sdss} Lupton, R. etal. \ 2001  arXiv: astro-ph/0101420

### 2015-07-20 ms/figure.tex
Update figure.tex

@@
 citecolor=darkblue }
+
+\DeclareMathOperator*{\argmax}{arg\,max}
 
@@
 saturating the CRLB is comparison of the root-mean-squared error of that estimator 
-with the CRLB.
+with the CRLB. The closer the root-mean-squared-error of a given estimator is to the bound, 
+the more optimal the estimator is.
 
@@
 the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
- it is sufficient to compute the Fisher matrix. Let us assume that there are $M$ observables $\{f_{1}, ... , f_{M}\}$, each
-related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$
+ it is sufficient to compute the Fisher matrix.
+
+Let us assume that there are $M$ observables $\mathbf{f} = (f_{1}, ... , f_{M})$, each
+related to $B$ model parameters $\Boldsymbol{\mathbf{\theta}} = (\theta_{1} , ... , \theta_{B})$ 
 \beq
 f_{m} = f_{m}(\theta_{1} , ... , \theta_{B}).
+\label{genmodel}
 \eeq
@@
 \beq
-\mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
+\mathcal{F}_{ij} = \sum_{m=1}^{M}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
 \label{fisher}
 \eeq
+
+Let us assume that, for each parameter $\theta_{i}$, there exists a set of 
+unbiased estimators $\{\hat{\theta}_{i}\}$. The Cram\'{e}r-Rao inequality 
+states that the root-mean-squared error of this set is greater than or equal to 
+the $i$-th diagonal element of the inverse of the Fisher information matrix:
+\beq
+\text{RMSE}[\{\hat{\theta_{i}}\}] \geq \sqrt{[\mathcal{F}^{-1}]_{ii}},
+\label{inequality}
+\eeq
+where the left hand side of the inequality is called the Cram\'{e}r-Rao bound on 
+the root-mean-squared error of estimating the parameter $\theta_{i}$. Note that 
+the bound is computed assuming that the model (\ref{genmodel}) generating the data 
+is known, and that uncertainties are given by additive uncorrelated Gaussian noise.
+
+Based on inequality (\ref{inequality}), \citet{cramer} defines efficiency of unbiased 
+estimators as the ratio of the CRLB and the root-mean-squared-error such that the maximum efficiency 
+achievable by an estimator is unity. The closer the root mean-squared 
+to the CRLB, the more information about the parameter of interest is preserved, and thus the more efficient 
+the estimator is.
+
+Let us consider the case of maximum likelihood estimate $\boldsymbol{\mathbf{\theta}}_{\text{ML}}$
+
+\begin{eqnarray}
+\boldsymbol{\mathbf{\theta}}_{\text{ML}} &=& \argmax \mathcal{L}, \\
+-2\ln \mathcal{L} &=& \sum_{m}\frac{1}{\sigma_{m}^{2}}( y_{m} - f_{m}(\boldsymbol{\mathbf{\theta}}))^{2}, \\
+\end{eqnarray}
+where $y_{m}$ is the $m$th component of the observed data $\mathbf{y}$
+\beq
+\mathbf{y} = \mathbf{f}(\boldsymbol{\mathbf{\theta}}_{\text{true}}) + \mathbf{n},
+\eeq
+under the assumption that $\mathbf{n} = (n_{1}, ... , n_{M})$ is uncorrelated Gaussian noise
+\begin{eqnarray}
+\langle n_{m} \rangle &=& 0, \\
+\langle n_{m}n_{m^{\prime}} \rangle &=& \sigma_{m}^{2}\delta_{m,m^{\prime}}. 
+\end{eqnarray}
+
+Maximum efficiency can be achived by maximum likelihood estimates under the condition. That is, 
+the root-mean-squared error, computed for a large ensemble of maximum liklihood estimators can become 
+arbitrarily close to the CRLB.
+
+However, the relation (\ref{inequality}) does not necessarily hold for biased estimators. That is, 
+the root-mean-squared-error can be smaller than the CRLB (see \citet{lecam}; \citet{hodge}).
+
+Furthermore, an unbiased estimator is called efficient when the root-mean-squared-error 
+and the CRLB are equal. Maximum likelihood estimators are asymptotically efficient and maximum 
+efficiency can be achieved.
 
@@
 \bibitem[Cram\'{e}r (1946)]{cramer} Cram\'{e}r, H. \ 1946 Mathematical methods of statistics, Princeton university press
+\bibitem[Le Cam (1953)]{lecam} Le Cam, L. M. \ 1953 On some asymptotic properties of maximum likelihood estimates and related Bayes' estimates (Vol. 1, No. 11), University of California press
 \bibitem[Lupton etal. (2001)]{sdss} Lupton, R. etal. \ 2001  arXiv: astro-ph/0101420

### 2015-07-20 ms/figure.tex
Update figure.tex

@@
 estimators as the ratio of the CRLB and the root-mean-squared-error such that the maximum efficiency 
-achievable by an estimator is unity. The closer the root mean-squared 
+achievable by an estimator is unity. The closer the root-mean-squared 
 to the CRLB, the more information about the parameter of interest is preserved, and thus the more efficient 
@@
 
-Maximum efficiency can be achived by maximum likelihood estimates under the condition. That is, 
-the root-mean-squared error, computed for a large ensemble of maximum liklihood estimators can become 
-arbitrarily close to the CRLB.
+Asymptotically, maximum likelihood estimators can achieve maximum efficiency. That is, for sufficiently large 
+number of estimates in a set of maximum likelihood estimates $\{\theta_{\text{ML}}\}$, the root-mean-squared 
+error becomes arbitrarily close to the CRLB (see \citet{cramer}; \citet{lecam} for proof).
 
 However, the relation (\ref{inequality}) does not necessarily hold for biased estimators. That is, 
-the root-mean-squared-error can be smaller than the CRLB (see \citet{lecam}; \citet{hodge}).
-
-Furthermore, an unbiased estimator is called efficient when the root-mean-squared-error 
-and the CRLB are equal. Maximum likelihood estimators are asymptotically efficient and maximum 
-efficiency can be achieved.
+the root-mean-squared-error can be smaller than the CRLB (see \citet{lecam} for examples).
+Therefore, we want to investigate the conditions under which, RMSE arising from a given centroiding method 
+becomes close to the CRLB, or whether it can become equal to the CRLB in which case the method is \emph{saturating} 
+the bound, or whether it can drop below the CRLB in which case the method is \emph{beating} the bound.
 

### 2015-09-25 ms/figure.tex
script is debugged

@@
 
+%----- typeset certain kinds of words
+\newcommand{\latin}[1]{\textit{#1}}
 \DeclareMathOperator*{\argmax}{arg\,max}
-
 \newcommand{\beq}{\begin{equation}}
 \newcommand{\eeq}{\end{equation}}
+\newcommand{\eg}{\latin{e.g.}}
+\newcommand{\etal}{\latin{et~al.}}
+\newcommand{\etc}{\latin{etc.}}
+\newcommand{\ie}{\latin{i.e.}}
+
+%----- math shih
+\newcommand{\given}{\,|\,}
+
+% these are already defined in aastex package
+%----- typeset journals  
+%\newcommand{\aj}{Astron.\,J.}
+%\newcommand{\apj}{Astrophys.\,J.}
+%\newcommand{\apjl}{Astrophys.\,J.\,Lett.}
+%\newcommand{\apjs}{Astrophys.\,J.\,Supp.\,Ser.}
+%\newcommand{\mnras}{Mon.\,Not.\,Roy.\,Ast.\,Soc.}
+%\newcommand{\pasp}{Pubs.\,Astron.\,Soc.\,Pac.}
+%\newcommand{\aap}{Astron.\,\&~Astrophys.}
 
@@
 Let us assume that there are $M$ observables $\mathbf{f} = (f_{1}, ... , f_{M})$, each
-related to $B$ model parameters $\Boldsymbol{\mathbf{\theta}} = (\theta_{1} , ... , \theta_{B})$ 
+related to $B$ model parameters $\boldsymbol{\mathbf{\theta}} = (\theta_{1} , ... , \theta_{B})$ 
 \beq
@@
 For sufficiently large $\beta$---where the PSF can be
-approximated by Gaussian profile---SNR is approximately given by $0.664}/(\sigma\gamma)$.
+approximated by Gaussian profile---SNR is approximately given by $0.664/(\sigma\gamma)$.
 Furthermore, at a fixed $\beta$ and variance of the background noise $\sigma^{2}$,
@@
 \section{Centroiding methods}\label{sec:method}
-
-\item{\bf  Matched filter polynomial centroiding}\quad Let us consider the case 
+\begin{description}
+%\item{{\bf :N}} \quad \\ 
+\item{{\bf Matched filter polynomial centroiding}} \quad Let us consider the case 
 in which we have a good estimate of the pixel-convolved PSF at
@@
 
-\item{\bf Default polynomial centroiding}\quad In the case that 
+\item{{\bf Default polynomial centroiding}} \quad In the case that 
 we do not know the PSF at the position of star, we change 
@@
 
-\item {\bf Center-of-light centroiding}\quad In addition to the methods 
+\item{{\bf Center-of-light centroiding}} \quad In addition to the methods 
 mentioned so far, we examine centroiding stars by computing their first moments
@@
 this section. Hereafter, we call this method $7\times7$ moment centroiding.
+
+\end{description}
 

### 2015-11-04 ms/figure.tex
slight correction in the references
edited the first 3 pages

@@
 accurate as PSF profile fitting, it comes close to saturating the Cram\'{e}r-Rao lower bound
-in a wide range of conditions. We also show that the center-of-light never comes close to 
+in a wide range of conditions. We also show that the moment-based methods of center-of-light never comes close to 
 saturating the bound, and thus it does not deliver reliable estimates of centroids.
@@
 
-A common practice in astronomy is taking imaging data, and then finding the coordinates
-of various light sources across the sky. Finding accuarate estimates of the centers of point
-sources, convolved with telescope point spread function (and atmospheric PSF in case of
-ground based telescopes), and also pixel response function, is crucial to further steps of
+Accuarate estimates of the centers of point
+sources, which are convolved with telescope point spread function (and atmospheric PSF in case of
+ground based telescopes), and also the pixel response function, are crucial to further steps of
 astronomical image processing. For instance, proper measurement of the shapes of galaxies
-requires interpolating the PSF estimates from the positions of stars across the
-image to the positions of galaxies. At the position of each star, PSF is estimated by sub-pixel 
+requires interpolation of the PSF estimates from the positions of stars across the
+image to the positions of galaxies. At the position of each star, the PSF is wrongly estimated by sub-pixel 
 shifting of the star so that it is centered on its centroid. If the sub-pixel shifts are wrong, then 
-the PSF estimates will be biased. Moreover, measurement of the proper motions of stars
+the PSF estimates will be biased. Moreover, measurements of the parallaxes and the proper motions of stars
 depends on how well we can measure their centroids.
 
-Ideally, we want a centroiding procedure that provides measurements as accurate as possible,
+Ideally, we want a centroiding procedure that provides measurements as precise as possible,
 without putting a huge computational burden on the photometric pipeline.
@@
 where we want to estimate the centroids of thousands of point sources detected
-on the telescope's focal plane.
+on the telescope's focal plane, for various real-time applications.
+
+In this paper, we study the optimality of various techniques for centroiding 
+faint, unsaturated stars. That is, we apply a number of centroiding methods 
+to a large number of simulated faint stars, assuming uncorrelated Gaussian noise, 
+with different signal-to-noise ratio and size realizations. Error from star 
+centroiding methods, will always have a theoretically-set lower bound, 
+known as the Cram\'{e}r-Rao lower bound (hereafter denoted by CRLB) which 
+has an inverse relation with the signal-to-noise-ratio of stars.
 
@@
 
-To date, a number of softwares have been designed for the purpose of extracting astronomical
+To date, a number of softwares packages have been designed for the purpose of extracting astronomical
 sources and making catalogs. One of these softwares is SExtractor \citep{sex},
-whose centroiding method involves first, finding the zeroth moment of the object
+whose centroiding method involves first finding the zeroth moment of the object
 as a first-order estimate, and then iteratively correcting the centroid by computing
@@
 until the correction falls below a particular threshold value.
-The width of the Gaussian window function is set by the object's half light radius.
-
-Another examples are DAOPHOT \citep{daophot}, and DOPHOT \citep{dophot}
+The width of the Gaussian window function is set by the object's half-light radius.
+Other examples are DAOPHOT \citep{daophot}, and DOPHOT \citep{dophot}
 which both assume analytic models for the stellar PSF profiles with centroid
@@
 
-In this paper, we study how optimal various techniques are at centroiding 
-faint unsaturated stars. That is, we apply a number of centroiding methods 
-to a large number of simulated faint stars, assuming uncorrelated Gaussian noise, 
-with different signal-to-noise ratio and size realizations. Error from star 
-centroiding methods, will always have a theoretically-set lower bound, 
-known as the Cram\'{e}r-Rao lower bound (hereafter denoted by CRLB) which 
-has an inverse relation with the signal-to-noise-ratio of stars.
-
-Given the analytic expression for the PSF model,
+Given an analytic expression for the PSF model,
 we derive an expression for the fundamental lower bound on the centroiding error as
-a function of the parameters of the PSF model (\eg size),
+a function of the parameters of the PSF model (\eg PSF size),
 and signal-to-noise-ratio of stars. We create two sets of simulations for which we 
@@
 The second method estimates the centroid of a star by fitting a 2d second-order polynomial to
- the 3$\times$3 patch around the brightest pixel of the image convolved with the PSF. 
+ the 3$\times$3 patch around the brightest pixel of the image after convolution with the PSF. 
 The third method centroids stars by
@@
  image. This method is fast and does not require any knowledge of the 
-PSF. The last method we consider, is the center of light centroiding applied to the
+PSF. The last method we consider, is a center of light centroiding 
+(measurement of a first moment), applied to the 
 7$\times$7 patch around the brightest pixel of the image.
 
-This paper is structured as follows. In section \ref{sec:CRLB},
+This paper is structured as follows. In Section \ref{sec:CRLB},
 we discuss the Cram\'{e}r-Rao lower bound, and we derive
@@
 of the simulated data, and also PSF profile fitting. 
-In section \ref{sec:method} we give a brief overview of approximate 
+In Section \ref{sec:method} we give a brief overview of approximate 
 centroiding methods used in our investigation.
-In section \ref{sec:data} we discuss the Cram\'{e}r-Rao lower bound satuaration
+In Section \ref{sec:data} we discuss the Cram\'{e}r-Rao lower bound satuaration
 tests and their corresponding simulated data.
-In section \ref{sec:result}, we compare the performances of the methods
+In Section \ref{sec:result}, we compare the performances of the methods
 discussed in \ref{sec:method}, with the CRLB derived in \ref{sec:data}. Finally,
- we discuss and conclude in \ref{sec:discussion}.               
+ we discuss and conclude in Section \ref{sec:discussion}.               
 %%%%%%%%%%%%%%%%%%%%Cram\'{e}r-Rao lower Bound %%%%%%%%%%%%%%
 
-\section{Cram\'{e}r-Rao lower bound on centroiding error}\label{sec:CRLB}
+\section{Cram\'{e}r-Rao lower bound}\label{sec:CRLB}
 
-In order to test the accuracy of various centroiding methods, we need to to compare their 
+Cram\'{e}r-Rao lower bound sets a limit, in some sense, on how well a measurement 
+can be made in noisy data.  The bound can only be computed in the context of a 
+generative model, or a probabilistic forward model of the data.  That is, we can 
+only compute the CRLB in the context of assumptions about the properties of the data. 
+However, it makes sense for us to use centroiding methods that saturate the CRLB under 
+some reasonable assumptions, even if we find that those assumptions are slightly wrong 
+in detail in real situations.
+
+In order to test the accuracy of various centroiding methods, we need to comapre their 
 performances against each other at saturating the Cram\'{e}r-Rao lower bound on centroiding error. 
 The closer an estimator is to saturating the CRLB, the more information about the quantity that we 
-need to estimate is preserved. A measure for closeness of an estimator to 
-saturating the CRLB is comparison of the root-mean-squared error of that estimator 
-with the CRLB. The closer the root-mean-squared-error of a given estimator is to the bound, 
+need to estimate is preserved. The closer the root-mean-squared-error of a given estimator is to the bound, 
 the more optimal the estimator is.
@@
 
+This work was partially supported by the NSF (grants IIS-1124794 and AST-1517237), NASA (grant NNX12AI50G), 
+and the Moore-Sloan Data Science Environment at NYU. We thank Jo Bovy for useful discussions.
+
 \begin{thebibliography}{70}
@@
 \bibitem[Le Cam (1953)]{lecam} Le Cam, L. M. \ 1953 On some asymptotic properties of maximum likelihood estimates and related Bayes' estimates (Vol. 1, No. 11), University of California press
-\bibitem[Lupton etal. (2001)]{sdss} Lupton, R. etal. \ 2001  arXiv: astro-ph/0101420
-\bibitem[Schechter etal. (1993)]{dophot} Schechter, P. L., Mateo, M., Saha, A. \ 1993 \pasp, 1342-1353
+\bibitem[Lupton \etal (2001)]{sdss} Lupton, R. etal. \ 2001  arXiv: astro-ph/0101420
+\bibitem[Schechter \etal (1993)]{dophot} Schechter, P. L., Mateo, M., Saha, A. \ 1993 \pasp, 1342-1353
 \bibitem[Stetson (1987)]{daophot} Stetson, P. B. \ 1987, \pasp, 191-222

### 2015-11-04 ms/figure.tex
finished editing the first 3 pages

@@
 and signal-to-noise-ratio of stars. We create two sets of simulations for which we 
-know the CRLB, one with variable (constant) signal-to-noise ratio (FWHM), and one 
-with variable (constant) FWHM (signal-to-noise ratio). After applying
+know the CRLB, one with variable signal-to-noise ratio and constant FWHM, and one 
+with variable FWHM and constant signal-to-noise ratio. After applying
 different centroiding methods to the simulations,

### 2015-11-09 ms/figure.tex
updated text

@@
 \usepackage{hyperref}
+\usepackage{enumitem}
 \hypersetup{colorlinks}
@@
 The Cram\'{e}r-Rao inequality \citep{cramer} sets a lower bound on the 
-root-mean-squared error of unbiased estimators. The CRLB is given by square-root of the inverse of 
+root-mean-squared error of unbiased estimators. The CRLB is given by the square-root of the inverse of 
 the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
- it is sufficient to compute the Fisher matrix.
+ it is sufficient to compute the Fisher matrix. This computation relies on a set of assumptions:
+
+\begin{itemize}
+  \item Known, constant model observable with known dependence on the model parameters. 
+        In this work the model observables the Moffat PSF profiles, and the model parameters are 
+        the centroids. 
+  \item Known, stationary noise process. In the context of centroiding stars, this is equivalent to 
+        having background limited nosie due to sky background, and CCD readout noise.
+  \item Uncorrelated Gaussian noise with no outliers. 
+\end{itemize}
 

### 2015-11-10 ms/figure.tex
edited the text

@@
 Let us assume that, for each parameter $\theta_{i}$, there exists a set of 
-unbiased estimators $\{\hat{\theta}_{i}\}$. The Cram\'{e}r-Rao inequality 
+asymptotically unbiased estimators $\{\hat{\theta}_{i}\}$. The Cram\'{e}r-Rao inequality 
 states that the root-mean-squared error of this set is greater than or equal to 
@@
 
-Let us consider the case of maximum likelihood estimate $\boldsymbol{\mathbf{\theta}}_{\text{ML}}$
+Let us consider the case of a maximum likelihood estimate $\boldsymbol{\mathbf{\theta}}_{\text{ML}}$, where the lieklihood function corresponds to the same generative assumptions that we used to compute the CRLB.
 
@@
 \beq
-\mathbf{y} = \mathbf{f}(\boldsymbol{\mathbf{\theta}}_{\text{true}}) + \mathbf{n},
+\mathbf{y} = \mathbf{f}(\boldsymbol{\mathbf{\theta}}_{\text{true}}) + \mathbf{n}.
 \eeq
-under the assumption that $\mathbf{n} = (n_{1}, ... , n_{M})$ is uncorrelated Gaussian noise
-\begin{eqnarray}
-\langle n_{m} \rangle &=& 0, \\
-\langle n_{m}n_{m^{\prime}} \rangle &=& \sigma_{m}^{2}\delta_{m,m^{\prime}}. 
-\end{eqnarray}
 
@@
 However, the relation (\ref{inequality}) does not necessarily hold for biased estimators. That is, 
-the root-mean-squared-error can be smaller than the CRLB (see \citet{lecam} for examples).
+the root-mean-squared-error for a biased estimator can be smaller than the CRLB (see \citet{lecam} for examples).
 Therefore, we want to investigate the conditions under which, RMSE arising from a given centroiding method 
 becomes close to the CRLB, or whether it can become equal to the CRLB in which case the method is \emph{saturating} 
-the bound, or whether it can drop below the CRLB in which case the method is \emph{beating} the bound.
+the bound, or whether it can drop below the CRLB in which case the method is \emph{beating} the bound (in the case of bias).
 
-In this investigation, the observables are the pixel-convolved PSF (PSF profile evaluated at different pixel locations), and  
+In this investigation, the model observables for the noisy data are the pixel-convolved PSF (PSF profile evaluated at different pixel locations), and  
 the model paramters under consideration are the centroid coordinates. Therefore, $\mathcal{F}$

### 2015-11-18 ms/figure.tex
new edit

@@
   \item Known, constant model observable with known dependence on the model parameters. 
-        In this work the model observables the Moffat PSF profiles, and the model parameters are 
-        the centroids. 
+        In this work the model observables are the presumed known Moffat PSF profiles, 
+        and the model parameters are the centroids. 
   \item Known, stationary noise process. In the context of centroiding stars, this is equivalent to 
-        having background limited nosie due to sky background, and CCD readout noise.
+        having background limited nosie from sky background and CCD readout noise.
   \item Uncorrelated Gaussian noise with no outliers. 
@@
 
-Let us consider the case of a maximum likelihood estimate $\boldsymbol{\mathbf{\theta}}_{\text{ML}}$, where the lieklihood function corresponds to the same generative assumptions that we used to compute the CRLB.
+Let us consider the case of a maximum likelihood estimate $\boldsymbol{\mathbf{\theta}}_{\text{ML}}$, where the likelihood function corresponds to the same generative assumptions that we used to compute the CRLB.
 
@@
 the root-mean-squared-error for a biased estimator can be smaller than the CRLB (see \citet{lecam} for examples).
-Therefore, we want to investigate the conditions under which, RMSE arising from a given centroiding method 
+Therefore, we want to investigate the conditions under which the RMSE arising from a given centroiding method 
 becomes close to the CRLB, or whether it can become equal to the CRLB in which case the method is \emph{saturating} 
-the bound, or whether it can drop below the CRLB in which case the method is \emph{beating} the bound (in the case of bias).
+the bound, or whether it can drop below the CRLB in which case the method is \emph{beating} the bound (and threfore must be biased).
 
 In this investigation, the model observables for the noisy data are the pixel-convolved PSF (PSF profile evaluated at different pixel locations), and  
-the model paramters under consideration are the centroid coordinates. Therefore, $\mathcal{F}$
+the model parameters under consideration are the centroid coordinates. Therefore, $\mathcal{F}$
 is a 2$\times$2 matrix whose elements are given by
@@
 \beq
-  \mathcal{F}_{ij} = \sum_{\mathbf{p}}\frac{1}{\sigma^{2}}
-                \frac{\partial f_{\mathbf{p}}}{\partial \theta_{i}}\frac{\partial f_{\mathbf{p}}}{\partial \theta_{j}},
+  \mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma^{2}}
+                \frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}},
 \label{fish}
 \eeq
-where the summation is over pixels, $f_{\mathbf{p}}$ is the value of the PSF at pixel location $\mathbf{p}$,
-$\theta=\{x_{c},y_{c}\}$, $\sigma^{2}$ is variance of the uncorrelated Gaussian noise map $n(\mathbf{x_{p}})$
+where the summation is over pixels, $f_{m}$ is the value of the PSF at pixel location $m$,
+$\theta=\{x_{c},y_{c}\}$, $\sigma^{2}$ is variance of the uncorrelated Gaussian noise map $n(\mathbf{x}_{m})$
 \begin{eqnarray}
-\langle n(\mathbf{x_{p}}) \rangle &=& 0, \\
-\langle n(\mathbf{x_{p}})n(\mathbf{x_{p^{\prime}}}) \rangle &=& \sigma^{2}\delta_{\mathbf{p}\mathbf{p}^{\prime}}. 
+E[n(\mathbf{x}_{m})] &=& 0, \\
+E[n(\mathbf{x}_{m})n(\mathbf{x}_{m^{\prime}})] &=& \sigma^{2}\delta_{m,m^{\prime}}. 
 \end{eqnarray}

### 2015-11-19 ms/figure.tex
more modification

@@
 
-Asymptotically, maximum likelihood estimators can achieve maximum efficiency. That is, for sufficiently large 
-number of estimates in a set of maximum likelihood estimates $\{\theta_{\text{ML}}\}$, the root-mean-squared 
-error becomes arbitrarily close to the CRLB (see \citet{cramer}; \citet{lecam} for proof).
+Asymptotically, maximum likelihood estimators can achieve maximum efficiency. That is, the RMSE from a 
+large set of maximum likelihood estimates $\{\theta_{\text{ML}}\}$, 
+becomes greater than or equal to the CRLB (see \citet{cramer}; \citet{lecam} for proof).
 
 However, the relation (\ref{inequality}) does not necessarily hold for biased estimators. That is, 
-the root-mean-squared-error for a biased estimator can be smaller than the CRLB (see \citet{lecam} for examples).
+the root-mean-squared-error for a biased estimator can be smaller than the CRLB (see \citealt{lecam} for examples).
 Therefore, we want to investigate the conditions under which the RMSE arising from a given centroiding method 

### 2015-11-30 ms/figure.tex
updated the text

@@
 
-Derivation of an explicit expression for the Fisher matrix $\mathcal{F}$ requires specifying a PSF model.
+Derivation of an explicit expression for the Fisher matrix $\mathcal{F}$ requires specifying a presumed correct 
+PSF model.
 We use the Moffat profile \citep{moffat} for our PSF simulations. 
@@
 where $F$ is the total flux, $\beta$ is a dimensionless parameter, and $\alpha$ is
-the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$)
+the scale radius of the Moffat profile, with FWHM (hereafter denoted by $\gamma$)
 being $2\alpha\sqrt{2^{1/\beta}-1}$. At a fixed $\gamma$, Moffat profiles with lower values
@@
 
-Throughout this investigation, $\beta$ is held fixed at the fiducial value of 2.5, where SNR
+Throughout this investigation, $\beta$ is held fixed at the fiducial value of $\beta=$ 2.5, where SNR
 is given by the following expression
 \beq
-\text{SNR} \simeq \frac{0.478}{\sigma \gamma}.
+\text{SNR} \simeq \frac{0.478}{\sigma \gamma} & \text{   for } \beta = 2.5.
 \eeq
@@
 between $\gamma$ and SNR. 
-For PSF profiles with shorter tails (\eg Gaussian), the prefactor of 0.685 in (\ref{crlbmoffat})
+For PSF profiles with shorter tails (\eg, Gaussian), the prefactor of 0.685 in (\ref{crlbmoffat})
 becomes smaller. In particular case of Gaussian PSF, the prefactor is approximately 0.6.
@@
  PSF profile to the stars. That is, in our Cram\'{e}r-Rao bound saturation tests, we find the best
- estimates of flux and centroid by optimizing the $\chi^{2}$.
- We expect this method to perform better in determing the centroids
- of stars, and deliver RMSE very close to Cram\'{e}r-Rao bound. In the next section,
- we briefly discuss the centroiding methods used in our Cram\'{e}r-Rao bound saturating tests.
-
+ estimates of flux and centroid by optimizing the likelihood using the correct PSF.
+ We expect this method to perform best in determing the centroids
+ of stars, and deliver RMSE equal to Cram\'{e}r-Rao bound. 
 \section{Centroiding methods}\label{sec:method}
@@
 \end{eqnarray}
-where $Y$ is the image of the star, and $Y^{(s)}$ is called matched filter. 
-Matched filter is a model where the data $Y$ is correlated (convolved in the 
-case of symmetrical PSF) with the PSF $\mathcal{P}$. It provides an optimal an 
-optimal detection map where the peak of the map is the likely position of the 
+where $Y$ is the image of the star, and $Y^{(s)}$ is sometimes called a matched filter. 
+A matched filter is a method in which the data $Y$ is correlated (convolved in the 
+case of symmetrical PSF) with the PSF $\mathcal{P}$. It is equivalent to optimizing the 
+likelihood and therefore provides an optimal map 
+where the peak of the map is the likely position of the 
 point source (Lang \emph{et al.}, in preparation).
@@
 centroid estimates obtained from equation (\ref{center}) can become arbitrarily 
-large which leads to catastrophic outliers. 
+large, which leads to catastrophic outliers. 
 In order to tackle this issue, we add a soft regularization term
-proportional to $\sigma^{2}$ to the determinant of $D$.
+proportional to $\sigma^{2}$ to the diagonals of $D$ prior to inversion.
 

### 2015-12-04 ms/figure.tex
more corrections

@@
 The procedure of convolving the image of star with the PSF results in a
-more well-sampled image, which eventually, leads to having more
-information regarding the centroids of stars in the 3$\times$3 patch around the
-brightest pixel. In addition, a simple second-order polynomial will provide a better fit 
+smoother image. Therefore, a simple second-order polynomial will provide a better fit 
 since convolution with the PSF makes the variation of the brightness of the image
@@
 by convolving it with the PSF, smoothing is done by convolving the image 
-with a Gaussian kernel of a fixed size 
+with a default Gaussian kernel of a fixed size 
 \beq
@@
 where throughout this study, the full-width at half-maximum of the Gaussian kernel is held at
-a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels). Smoothing step is done as follows
+a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels).The smoothing step is done as follows
 \begin{eqnarray}
@@
 \eeq 
-Then we apply the same 2d second-order polynomial method to the 3$\times$3 patch centered on the brightest
+Then we apply the same 2d second-order polynomial method (\ref{linearfit},\ref{center}) to the 3$\times$3 patch centered on the brightest
 pixel of the smooth image $Y^{(s)}$. Therefore, for a given star and a smoothing kernel,
@@
 
-\item{{\bf Center-of-light centroiding}} \quad In addition to the methods 
+\item{{\bf Center-of-light centroiding}} \quad In addition to thetwo fitting methods 
 mentioned so far, we examine centroiding stars by computing their first moments
@@
 
-In the first experiment, we study how centroiding error behaves with changing
+In the first experiment, we study how the centroiding error behaves with changing
 SNR, while $\gamma$ is held constant. In the second experiment, we study 
-how centroiding error behaves with changing $\gamma$ while SNR is held constant.
+how the centroiding error behaves with changing $\gamma$ while SNR is held constant.
 
@@
 we compute the RMSE in bins of SNR in order to compare it to the CRLB. 
-Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}],
-[\ref{3}], [\ref{4}]. All methods deliver results with RMSE larger 
+Results of the first experiment are shown in Figures ~\ref{1}, ~\ref{2},
+~\ref{3}, ~\ref{4}. All methods deliver results with RMSE larger 
 for fainter stars.
@@
 lies on the CRLB except for simulations with SNR $\la$ 10 where the RMSE gets slightly pulled away
-from the CRLB due to presence of a few outliers. Figure [\ref{2}] demonstrates that even the matched-filter polynomial 
+from the CRLB due to presence of a few outliers. Figure ~\ref{2} demonstrates that even the matched-filter polynomial 
 centroiding is able deliver centroiding estimates as accurate as PSF profile fitting, with the exception
 of simulated stars with $\gamma$ = 2 pixels. For stars with $\gamma$ = 2 pixels, although second-order polynomial
-fitting gets close to saturating the CRLB, it fails to saturate the CRLB since the PSF is undersampled. For simulated images with higher $\gamma$, convolving the
-data with the PSF result in images that are well-sampled around the brightest pixel. This allows the 
+fitting gets close to saturating the CRLB, it fails to saturate the CRLB since the PSF is slightly undersampled. 
+For simulated images with higher $\gamma$, convolving the
+data with the PSF results in images that are wellsampled around the brightest pixel. This allows the 
 polynomial centroiding to deliver highly accurate results that can saturate the CRLB for simulated
@@
 
-RMSE from the default polynomial centroiding [\ref{3}],
+The RMSE from the default polynomial centroiding (Figure ~\ref{3}),
 is very close to the CRLB except at the very small values of SNR (SNR $\la$ 10).
@@
 decreases with increaing SNR. The reason for this is that even after smoothing
-the with a Gaussian kernel, the image is still relatively undersampled, and not smooth enough
+the data with a Gaussian kernel, the image is still relatively undersampled, and not smooth enough
 for a second-order polynomial fitting to provide highly accurate centroiding estimates.
@@
 For stars with larger $\gamma$, centroid estimates from the naive center of light 
-centroiding show large deviation from saturating the CRLB. By increasing $\gamma$,
-RMSE deviates further away from the CRLB.
+centroiding do not even come close to saturating the CRLB. As $\gamma$ increases, the 
+RMSE deviates further from the CRLB.
 
@@
 Behavior of error as a function of $\gamma$ for different values of SNR,
-is shown in figures [\ref{5}], [\ref{6}], [\ref{7}], and [\ref{8}].
+is shown in Figures ~\ref{5}, ~\ref{6}, ~\ref{7}, and ~\ref{8}.
 

### 2015-12-07 ms/figure.tex
more edits

@@
 
-An optimal stellar centroiding algorithm must saturate the fundamental Cram\'{e}r-Rao lower 
+An optimal stellar centroiding algorithm must saturate --or come close to saturating-- the fundamental Cram\'{e}r-Rao lower 
 bound. That is, in all ranges of background noise level, size, radial light profile,
 and shape, it must preserve information about the centroids of stars. In practice however,
-this is only achievable when we have a reasonably good estimate of the PSF. Since, we do not always 
-know the exact PSF profile, we make use of various approximate centroiding algorithms. In this work, we
-studied how different methods come close to saturating the CRLB for relatively low signal-to-noise ratio
+this is only achievable when we have a reasonably good estimate of the PSF. Since we do not always 
+know the exact PSF profile, we must make use of approximate centroiding algorithms. In this work, we
+studied how close we get to saturating the CRLB with an approximate method acting on relatively low signal-to-noise ratio,
 unsaturated stars.
@@
 Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
-centroid estimates that saturate the CRLB; with the exception of SNR being less than 10, 
-in which case a few centroiding ouliers caused the RMSE to slightly, but not significantly, deviate
+centroid estimates that saturate the CRLB; with the only exceptions at SNR being less than 10, 
+in which case a few centroiding ouliers cause the RMSE to slightly deviate
 from the CRLB. We found that the estimates found by 7$\times$7 moment method, except in the case of
@@
 
-On the other hand, the RMSE of centroid estimates of 
-default polynomial centroiding are much closer to saturating the CRLB in all ranges of signal-to-noise ratio.
+On the other hand, the RMSE of centroid estimates of the default polynomial centroiding are much 
+closer to saturating the CRLB in all ranges of signal-to-noise ratio even though this method does not require knowledge of 
+the PSF.
 The performance of this method however, is limited by
@@
  matches that of the smoothing kernel. Thus, when we apply 
-this method to find the centroids of stars with larger FWHM, certain amount of
-information (encoded in the Cram\'{e}r-Rao lower bound) is lost, and therefore, the RMSE
+this method to find the centroids of stars with larger FWHM, a certain amount of
+information (encoded in the Cram\'{e}r-Rao lower bound) is lost, and therefore the RMSE
 of these methods deviates from the CRLB. This deviation becomes even larger at lower

### 2015-12-08 ms/figure.tex
edited the discussions section

@@
 
-An optimal stellar centroiding algorithm must saturate --or come close to saturating-- the fundamental Cram\'{e}r-Rao lower 
+An optimal stellar centroiding algorithm must saturate---or come close to saturating---the fundamental Cram\'{e}r-Rao lower 
 bound. That is, in all ranges of background noise level, size, radial light profile,
@@
 us to vary the poition of centroid, and not the flux, while fitting the PSF model
-to the star.
+to the star. This is the advantage of a matched filter approach.
 
-Modifying the $\chi^2$ such that it contains the dot product of the PSF and image, 
-provides a nice interpretation for the PSF fitting method. It corresponds to searching for the 
-centroid in a very high resolution grid which the dot product of the image and the PSF model is
-sensitive to. On the other hand, one can think of the initial smoothing step in the default polynomial method 
-as upsampling of the image around the center by convolving it with an approximate Gaussian PSF. 
+Modifying the $\chi^2$ such that it only contains the dot product of the PSF and image, 
+provides a nice interpretation. Finding a centroid coordinate that maximizes the dot product 
+of the PSF and the star image is equivalent to finding the peak of the 
+correlation of the PSF and the image. Therefore optimizing the modified $\chi^2$ is equivalent to finding the 
+location of the peak of the matched filter.
+
+On the other hand, one can think of the initial smoothing step in the default polynomial method 
+as upsampling of the image around the center by correlating it with an approximate Gaussian PSF. 
 The default polynomial centroiding is different from PSF-fitting method in that, when there is mismatch between the
@@
 over a certain range of low signal-to-noise ratios and PSF sizes, one can achieve sensibly 
- accurate results by employing a simple 3$\times$3 method after smooting the image with
- a Gaussian kernel of a fixed width, and without making any assumption about the PSF model at the positions of stars.
+accurate results by employing a simple 3$\times$3 method after smoothing the image with 
+a Gaussian kernel of a fixed width, and without making any assumption about the PSF model 
+at the positions of stars.
 
@@
 This work was partially supported by the NSF (grants IIS-1124794 and AST-1517237), NASA (grant NNX12AI50G), 
-and the Moore-Sloan Data Science Environment at NYU. We thank Jo Bovy for useful discussions.
+and the Moore-Sloan Data Science Environment at NYU. We thank Jo Bovy and Dustin Lang for useful discussions.
 

### 2015-12-11 ms/ms.tex
got rid of some typos

--- 2015-12-08 ms/figure.tex
@@
 accurate as PSF profile fitting, it comes close to saturating the Cram\'{e}r-Rao lower bound
-in a wide range of conditions. We also show that the moment-based methods of center-of-light never comes close to 
+in a wide range of conditions. We also show that the moment-based method of center-of-light never comes close to 
 saturating the bound, and thus it does not deliver reliable estimates of centroids.    
+\end{abstract}
 
-\end{abstract}
+\keywords{methods: statistical --- methods: data analysis --- techniques: image processing}
 
@@
 by the lack of knowledge about the exact shape of the PSF, and also presence of noise;
-both sky noise and CCD readout noise. Thus, of particular interest is devising a fast method that returns
+both sky noise and CCD readout noise. Thus we need a fast method that returns
 optimal estimates of centroids in a realistic range of signal-to-noise ratios.
@@
 coordinates being free parameters of these models.
-DAOPHOT (DoPHOT) finds the centroids by fitting a Gaussian (a truncated power series for a Gaussian) PSF to
+DAOPHOT (DOPHOT) finds the centroids by fitting a Gaussian (a truncated power series for a Gaussian) PSF to
 the light profile of stars.
@@
  we discuss and conclude in Section \ref{sec:discussion}.
+
 %%%%%%%%%%%%%%%%%%%%Cram\'{e}r-Rao lower Bound %%%%%%%%%%%%%%
@@
 \beq
-\text{SNR} \simeq \frac{0.478}{\sigma \gamma} & \text{   for } \beta = 2.5.
+\text{SNR} \simeq \frac{0.478}{\sigma \gamma}\;\;\; \mathrm{for}\;\;\; \beta = 2.5.
 \eeq
@@
 
-Modifying the $\chi^2$ such that it only contains the dot product of the PSF and image, 
+Modifying the $\chi^2$ such that it only contains the dot product of the PSF and image 
 provides a nice interpretation. Finding a centroid coordinate that maximizes the dot product 
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_psffitting.png}
+  \includegraphics[width=\linewidth]{f1.png}
 \endminipage
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_psfpoly.png}
+  \includegraphics[width=\linewidth]{f2.png}
 \endminipage
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_psfpix28poly.png}
+  \includegraphics[width=\linewidth]{f3.png}
 \endminipage
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{snr_moment.png}
+  \includegraphics[width=\linewidth]{f4.png}
 \endminipage
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_psf.png}
+  \includegraphics[width=\linewidth]{f5.png}
 \endminipage
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_psfpoly.png}
+  \includegraphics[width=\linewidth]{f6.png}
 \endminipage
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_psfpix28poly.png}
+  \includegraphics[width=\linewidth]{f7.png}
 \endminipage
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{fwhm_moment.png}
+  \includegraphics[width=\linewidth]{f8.png}
 \endminipage

### 2015-12-13 ms/ms.tex
final edit

@@
 \newcommand{\eg}{\latin{e.g.}}
-\newcommand{\etal}{\latin{et~al.}}
+\newcommand{\etal}{et~al.}
 \newcommand{\etc}{\latin{etc.}}
@@
 known as the Cram\'{e}r-Rao lower bound (hereafter denoted by CRLB) which 
-has an inverse relation with the signal-to-noise-ratio of stars.
+has an inverse relation with the signal-to-noise-ratio of stars. In the context 
+of astrometry, the Cram\'{e}r-Rao lower bound saturation for least-squares 
+estimators has been tested in specific limits where the centroiding bias is 
+negligible (\citealt{lobos}).
 
@@
 To date, a number of softwares packages have been designed for the purpose of extracting astronomical
-sources and making catalogs. One of these softwares is SExtractor \citep{sex},
+sources and making catalogs. One of these softwares is SExtractor (\citealt{sextractor}),
 whose centroiding method involves first finding the zeroth moment of the object
@@
 The width of the Gaussian window function is set by the object's half-light radius.
-Other examples are DAOPHOT \citep{daophot}, and DOPHOT \citep{dophot}
+Other examples are DAOPHOT (\citealt{daophot}), and DOPHOT (\citealt{dophot})
 which both assume analytic models for the stellar PSF profiles with centroid
@@
 we derive an expression for the fundamental lower bound on the centroiding error as
-a function of the parameters of the PSF model (\eg PSF size),
+a function of the parameters of the PSF model (e.g. PSF size),
 and signal-to-noise-ratio of stars. We create two sets of simulations for which we 
@@
 large set of maximum likelihood estimates $\{\theta_{\text{ML}}\}$, 
-becomes greater than or equal to the CRLB (see \citet{cramer}; \citet{lecam} for proof).
+becomes greater than or equal to the CRLB (see \citealt{cramer}; \citealt{lecam} for proof).
 
@@
 \begin{eqnarray}
-E[n(\mathbf{x}_{m})] &=& 0, \\
-E[n(\mathbf{x}_{m})n(\mathbf{x}_{m^{\prime}})] &=& \sigma^{2}\delta_{m,m^{\prime}}. 
+\mathbb{E}[n(\mathbf{x}_{m})] &=& 0, \\
+\mathbb{E}[n(\mathbf{x}_{m})n(\mathbf{x}_{m^{\prime}})] &=& \sigma^{2}\delta_{m,m^{\prime}}. 
 \end{eqnarray}
@@
 
-We examine fitting an exact
- PSF profile to the stars. That is, in our Cram\'{e}r-Rao bound saturation tests, we find the best
- estimates of flux and centroid by optimizing the likelihood using the correct PSF.
- We expect this method to perform best in determing the centroids
- of stars, and deliver RMSE equal to Cram\'{e}r-Rao bound. 
 \section{Centroiding methods}\label{sec:method}
 \begin{description}
-%\item{{\bf :N}} \quad \\ 
+
+\item{{\bf Centroiding via fitting a correct PSF profile}} \quad
+
+We examine fitting an exact PSF profile to the stars. That is, 
+in our Cram\'{e}r-Rao bound saturation tests, we find the best
+estimates of flux and centroid by optimizing the likelihood using 
+the correct PSF. We expect this method to perform best in determing the centroids
+of stars, and deliver RMSE equal to Cram\'{e}r-Rao bound.
+
 \item{{\bf Matched filter polynomial centroiding}} \quad Let us consider the case 
@@
 
+We should nonlinearly optmize a psf to saturate the bound.
+But because this is done through a chi-squared fitting, 
+this is equivalent to optimizing a matched filter. 
+And if the image is well sampled (in the psf-convolved image) this
+is equivalent to interpolating a matched filter on a grid. 
+Therefore we expect the matched filter centroiding method to 
+saturate the bound in cases where the image is well sampled.
+
 \item{{\bf Default polynomial centroiding}} \quad In the case that 
@@
 we compute the RMSE in bins of SNR in order to compare it to the CRLB. 
-Results of the first experiment are shown in Figures ~\ref{1}, ~\ref{2},
-~\ref{3}, ~\ref{4}. All methods deliver results with RMSE larger 
+Results of the first experiment are shown in Figures~\ref{1},~\ref{2},
+~\ref{3},~\ref{4}. All methods deliver results with RMSE larger 
 for fainter stars.
 
-As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{1}]
+As we expected, the RMSE from centroiding by fitting the exact PSF model (Figure~\ref{1})
 lies on the CRLB except for simulations with SNR $\la$ 10 where the RMSE gets slightly pulled away
@@
 
-However, in case of 7$\times$7 moment method [\ref{4}], RMSE becomes
+However, Figure~\ref{4} shows that in case of 7$\times$7 moment method, RMSE becomes
 quite large as we move towards fainter stars in our simulation.
@@
 Behavior of error as a function of $\gamma$ for different values of SNR,
-is shown in Figures ~\ref{5}, ~\ref{6}, ~\ref{7}, and ~\ref{8}.
+is shown in Figures~\ref{5},~\ref{6},~\ref{7}, and~\ref{8}.
 
@@
 perfectly lies on the CRLB except at SNR = 5 where the RMSE slightly deviates
-from the CRLB due to presence of a few outliers [\ref{5}]. 
+from the CRLB due to presence of a few outliers (see Figure~\ref{5}). 
 Thus, centroid estimates from fitting
@@
 estimates found by matched-filter polynomial centroiding saturate the CRLB with the
-exception of simulated stars with SNR = 5, or $\gamma$ very close to 2 pixels [\ref{6}].
+exception of simulated stars with SNR = 5, or $\gamma$ very close to 2 pixels (see Figure~\ref{6}).
 
-The default polynomial method [\ref{7}], results in RMSE very close to the CRLB.
+Figure~\ref{7} illustrates that the default polynomial method results in RMSE very close to the CRLB.
 For all four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels,
@@
 
-The centroid estimates obtained from the naive 7$\times$7 moment method [\ref{8}]
+The centroid estimates obtained from the naive 7$\times$7 moment method (see Figure ~\ref{8})
 result in RMSE much larger than the CRLB in all ranges of FWHM and for all four
@@
 
-\bibitem[Bertin \& Arnouts (1996)]{sex} Bertin, E., Arnouts, S. \ 1996  Astronomy and Astrophysics Supplement Series, 117, 393-40
-\bibitem[Cram\'{e}r (1946)]{cramer} Cram\'{e}r, H. \ 1946 Mathematical methods of statistics, Princeton university press
-\bibitem[Le Cam (1953)]{lecam} Le Cam, L. M. \ 1953 On some asymptotic properties of maximum likelihood estimates and related Bayes' estimates (Vol. 1, No. 11), University of California press
-\bibitem[Lupton \etal (2001)]{sdss} Lupton, R. etal. \ 2001  arXiv: astro-ph/0101420
-\bibitem[Schechter \etal (1993)]{dophot} Schechter, P. L., Mateo, M., Saha, A. \ 1993 \pasp, 1342-1353
-\bibitem[Stetson (1987)]{daophot} Stetson, P. B. \ 1987, \pasp, 191-222
-\bibitem[Trujillo etal. (2001)]{moffat} Trujillo, I., et al. \ 2001 \mnras, 977-985
+\bibitem[Bertin \& Arnouts (1996)]{sextractor} Bertin, E., Arnouts, S., 1996,  A\&AS , 117, 393
+\bibitem[Cram\'{e}r (1946)]{cramer} Cram\'{e}r, H., 1946, Mathematical methods of statistics, Princeton university press
+\bibitem[Le Cam (1953)]{lecam} Le Cam, L. M., 1953, University of California publications in statistics, Vol. 1 (no. 11.), 277
+\bibitem[Lobos \etal (2015)]{lobos} Lobos, R.~A., Silva, J.~F., Mendez, R.~A., Orchard, M., 2015, \pasp , 127, 1166
+\bibitem[Lupton \etal (2001)]{sdss} Lupton, R. \etal, 2001,  arXiv:astro-ph/0101420
+\bibitem[Schechter \etal (1993)]{dophot} Schechter, P. L., Mateo, M., Saha, A., 1993, \pasp , 105, 1342
+\bibitem[Stetson (1987)]{daophot} Stetson, P. B., 1987, \pasp , 99, 191
+\bibitem[Trujillo etal. (2001)]{moffat} Trujillo, I., \etal, 2001, \mnras , 328, 977
 

### 2015-12-14 ms/ms.tex
changed the formats
final edit(2)

@@
 of astrometry, the Cram\'{e}r-Rao lower bound saturation for least-squares 
-estimators has been tested in specific limits where the centroiding bias is 
+estimators has been tested in specific limits in which the centroiding bias is 
 negligible (\citealt{lobos}).
@@
 coordinates being free parameters of these models.
-DAOPHOT (DOPHOT) finds the centroids by fitting a Gaussian (a truncated power series for a Gaussian) PSF to
+DAOPHOT (DOPHOT) finds the centroids by fitting a Gaussian (a truncated power series) to 
 the light profile of stars.
@@
 an analytic expression for the lower bound on centroiding error
-of the simulated data, and also PSF profile fitting. 
-In Section \ref{sec:method} we give a brief overview of approximate 
+of the simulated data. 
+In Section \ref{sec:method} we give a brief overview of 
 centroiding methods used in our investigation.
@@
 In Section \ref{sec:result}, we compare the performances of the methods
-discussed in \ref{sec:method}, with the CRLB derived in \ref{sec:data}. Finally,
+discussed in \ref{sec:method}, with the CRLB derived in \ref{sec:CRLB}. Finally,
  we discuss and conclude in Section \ref{sec:discussion}.
@@
 becomes close to the CRLB, or whether it can become equal to the CRLB in which case the method is \emph{saturating} 
-the bound, or whether it can drop below the CRLB in which case the method is \emph{beating} the bound (and threfore must be biased).
+the bound, or whether it can drop below the CRLB in which case the method is \emph{beating} the bound (and therefore the estimator must be biased).
 
@@
 where the summation is over pixels, $f_{m}$ is the value of the PSF at pixel location $m$,
-$\theta=\{x_{c},y_{c}\}$, $\sigma^{2}$ is variance of the uncorrelated Gaussian noise map $n(\mathbf{x}_{m})$
+$\theta=\{x_{c},y_{c}\}$, and $\sigma^{2}$ is variance of the uncorrelated Gaussian noise map $n(\mathbf{x}_{m})$
 \begin{eqnarray}
@@
 between $\gamma$ and SNR. 
-For PSF profiles with shorter tails (\eg, Gaussian), the prefactor of 0.685 in (\ref{crlbmoffat})
+For PSF profiles with shorter tails (e.g., Gaussian), the prefactor of 0.685 in (\ref{crlbmoffat})
 becomes smaller. In particular case of Gaussian PSF, the prefactor is approximately 0.6.
@@
 
-\item{{\bf Centroiding via fitting a correct PSF profile}} \quad
-
-We examine fitting an exact PSF profile to the stars. That is, 
+\item{{\bf Centroiding by fitting a correct PSF profile}} \quad We examine fitting an exact PSF 
+profile to the stars. That is, 
 in our Cram\'{e}r-Rao bound saturation tests, we find the best
@@
 In order to tackle this issue, we add a soft regularization term
-proportional to $\sigma^{2}$ to the diagonals of $D$ prior to inversion.
+proportional to $\sigma$ to the diagonals of $D$ prior to inversion.
 
@@
 We should nonlinearly optmize a psf to saturate the bound.
-But because this is done through a chi-squared fitting, 
+But because optimization is done through a chi-squared fitting, 
 this is equivalent to optimizing a matched filter. 
@@
 where throughout this study, the full-width at half-maximum of the Gaussian kernel is held at
-a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels).The smoothing step is done as follows
+a fixed value of 2.8 pixels (corresponding to w $\simeq$ 1.2 pixels). The smoothing step is done as follows
 \begin{eqnarray}
@@
 \eeq 
-Then we apply the same 2d second-order polynomial method (\ref{linearfit},\ref{center}) to the 3$\times$3 patch centered on the brightest
+Then we apply the same 2d second-order polynomial method (see equations \ref{linearfit}, \ref{center}) to the 3$\times$3 patch centered on the brightest
 pixel of the smooth image $Y^{(s)}$. Therefore, for a given star and a smoothing kernel,
@@
 
-\item{{\bf Center-of-light centroiding}} \quad In addition to thetwo fitting methods 
+\item{{\bf Center-of-light centroiding}} \quad In addition to the fitting methods 
 mentioned so far, we examine centroiding stars by computing their first moments
@@
 \begin{eqnarray}
-x_{c} &=& \frac{\sum_\mathbf{p}x_{\mathbf{p}}Y_{\mathbf{p}}}{\sum_\mathbf{p}Y_{\mathbf{p}}}, \\
-y_{c} &=& \frac{\sum_\mathbf{p}y_{\mathbf{p}}Y_{\mathbf{p}}}{\sum_\mathbf{p}Y_{\mathbf{p}}},
+x_{c} &=& \frac{\sum_{m}x_{m}Y_{m}}{\sum_{m}Y_{m}}, \\
+y_{c} &=& \frac{\sum_{m}y_{m}Y_{m}}{\sum_{m}Y_{m}},
 \end{eqnarray}
-where the summation is done over all the pixels of the 7$\times$7 patch, and $x_{\mathbf{p}}$, 
-$y_{\mathbf{p}}$, and $Y_{\mathbf{p}}$, are the $x$ coordinate, $y$ coordinate, and the brightness
-of pixel $\mathbf{p}$ respectively.
+where the summation is done over all the pixels of the 7$\times$7 patch, and $x_{m}$, 
+$y_{m}$, and $Y_{m}$, are the $x$ coordinate, $y$ coordinate, and the brightness
+of pixel $m$ respectively.
 
@@
 lies on the CRLB except for simulations with SNR $\la$ 10 where the RMSE gets slightly pulled away
-from the CRLB due to presence of a few outliers. Figure ~\ref{2} demonstrates that even the matched-filter polynomial 
+from the CRLB due to presence of a few outliers. Figure~\ref{2} demonstrates that even the matched filter polynomial 
 centroiding is able deliver centroiding estimates as accurate as PSF profile fitting, with the exception
@@
 
-The RMSE from the default polynomial centroiding (Figure ~\ref{3}),
+The RMSE from the default polynomial centroiding (Figure~\ref{3}),
 is very close to the CRLB except at the very small values of SNR (SNR $\la$ 10).
@@
 the exact PSF model always saturate the CRLB. Once again, we observe that the centroid
-estimates found by matched-filter polynomial centroiding saturate the CRLB with the
+estimates found by matched filter polynomial centroiding saturate the CRLB with the
 exception of simulated stars with SNR = 5, or $\gamma$ very close to 2 pixels (see Figure~\ref{6}).
@@
 Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
-centroid estimates that saturate the CRLB; with the only exceptions at SNR being less than 10, 
+centroid estimates that saturate the CRLB; with the only exceptions at SNR less than 10, 
 in which case a few centroiding ouliers cause the RMSE to slightly deviate
@@
 The performance of this method however, is limited by
-two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} PSF size.
+two important factors: (i) signal-to-noise ratio, and (ii) PSF size.
 The default polynomial centroiding technique only takes advantage of the information 
@@
 information (encoded in the Cram\'{e}r-Rao lower bound) is lost, and therefore the RMSE
-of these methods deviates from the CRLB. This deviation becomes even larger at lower
+of these methods deviates from the CRLB. This deviation becomes larger at lower
 signal-to-noise ratios. Besides, the performance of this method slightly degrades
@@
 widths of the smoothing kernel and the that of the PSF, we loose some information by employing a 3$\times$3 polynomial fitting.
-When we have the advantage of knowing the PSF, this issue can be resolved by employing the matched-filter polynomial method.
+When we have the advantage of knowing the PSF, this issue can be resolved by employing the matched filter polynomial method.
 
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{f1.png}
+  \includegraphics[width=\linewidth]{f1.eps}
 \endminipage
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{f2.png}
+  \includegraphics[width=\linewidth]{f2.eps}
 \endminipage
 \caption{Scatter plots showing the relation between error in centroid
-measurement from the PSF-based 3$\times$3 polynomial method and the signal-to-noise
+measurement from the matched filter polynomial method and the signal-to-noise
 ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left),
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{f3.png}
+  \includegraphics[width=\linewidth]{f3.eps}
 \endminipage
-\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 polynomial centroiding and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
+\caption{Scatter plots showing the relation between error in centroid measurement from the default polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels.
 In each scatter plot, the blue solid line represents the root-mean-squared-error, and the green dashed line represents CRLB.}\label{3}
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{f4.png}
+  \includegraphics[width=\linewidth]{f4.eps}
 \endminipage
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{f5.png}
+  \includegraphics[width=\linewidth]{f5.eps}
 \endminipage
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{f6.png}
+  \includegraphics[width=\linewidth]{f6.eps}
 \endminipage
 \caption{Scatter plots showing the relation between error in centroid measurement
-from the PSF-based 3$\times$3 polynomial method and FWHM of stars, with SNR  of : 5 (upper left),
+from the matched filter polynomial method and FWHM of stars, with SNR  of : 5 (upper left),
 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue solid
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{f7.png}
+  \includegraphics[width=\linewidth]{f7.eps}
 \endminipage
 \caption{Scatter plots showing the relation between error in centroid measurement
-from the 3$\times$3 polynomial centroiding and FWHM of stars, with SNR  of 
+from the default polynomial centroiding and FWHM of stars, with SNR  of 
 : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each
@@
 \minipage{.8\textwidth}
-  \includegraphics[width=\linewidth]{f8.png}
+  \includegraphics[width=\linewidth]{f8.eps}
 \endminipage

### 2016-09-23 ms/ms.tex
edited the title and abstract

@@
 
-\title{Fast and optimal centroiding of faint stars}
+\title{Do fast stellar centroiding methods saturate the Cramer-Rao lower bound?}
 
 \begin{abstract}
-One of the most demanding tasks in astronomical image processing---in terms of precision---is the centroiding of stars. 
-Upcoming large surveys are going to take images of billions of point sources, 
-including many faint stars, with short exposure times. Real-time estimation of the
-centroids of stars is crucial for real-time PSF estimation, and maximal precision is required
-for measurements of proper motion. In this work, we aim to compare the performance of
-various centroiding methods, when they are applied
-to relatively low signal-to-noise ratio unsaturated stars.
-In order to investigate how information-preserving these techniques are, we compare
-the root-mean-squared-error with the fundamental Cram\'{e}r-Rao
-lower bound assuming zero-mean constant Gaussian noise. We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
+One of the most demanding tasks in astronomical image processing---in terms of precision---is 
+the centroiding of stars. Upcoming large surveys are going to take images of 
+billions of point sources, including many faint stars, with short exposure times. 
+Real-time estimation of the centroids of stars is crucial for real-time PSF estimation, 
+and maximal precision is required for measurements of proper motion.
+
+The fundamental Crame\'{e}r-Rao lower bound sets a limit on the root-mean-squared-error 
+achievable by optimal estimators. Information-preserving estimators are able to deliver 
+root-mean-squared-errors lower than the Crame\'{e}r-Rao bound. In this work, we aim to compare 
+the performance of various centroiding methods, in terms of saturating the bound, when they 
+are applied to relatively low signal-to-noise ratio unsaturated stars assuming zero-mean 
+constant Gaussian noise. In order to make this comparison, we present the root-mean-squared-errors of 
+these estimators and their corrsponding Crame\'{e}r-Rao bound as a function of the signal-to-noise ratio 
+and the full-width at half-maximum of faint stars.
+
+We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
 of the PSF, (ii) when we do not know the PSF. In the case that we know the PSF, 
 we show that a fast polynomial centroiding after smoothing the image by the PSF can be 
-as accurate as full PSF profile fitting. In the case that we do not
-know the PSF, we demonstrate that although polynomial centroiding is not as
-accurate as PSF profile fitting, it comes close to saturating the Cram\'{e}r-Rao lower bound
-in a wide range of conditions. We also show that the moment-based method of center-of-light never comes close to 
-saturating the bound, and thus it does not deliver reliable estimates of centroids.    
+as information-reserving as the maximum-likelihood estimator with full PSF profile fitting. 
+In the case that we do not know the PSF, we demonstrate that although polynomial centroiding 
+is not as optimal as PSF profile fitting, it comes very close to saturating the Cram\'{e}r-Rao lower bound
+in a wide range of conditions. We also show that the moment-based method of center-of-light 
+never comes close to saturating the bound, and thus it does not deliver reliable estimates of centroids.    
 \end{abstract}

### 2016-09-23 ms/ms.tex
polshing up the intro

@@
 requires interpolation of the PSF estimates from the positions of stars across the
-image to the positions of galaxies. At the position of each star, the PSF is wrongly estimated by sub-pixel 
+image to the positions of galaxies. At the position of each star, the PSF is estimated by sub-pixel 
 shifting of the star so that it is centered on its centroid. If the sub-pixel shifts are wrong, then 
@@
 In this paper, we study the optimality of various techniques for centroiding 
-faint, unsaturated stars. That is, we apply a number of centroiding methods 
+faint, unsaturated stars. Our requirement for optimality is saturation of the Cram\'{e}r-Rao 
+lower bound by a centroiding method. We apply a number of centroiding methods 
 to a large number of simulated faint stars, assuming uncorrelated Gaussian noise, 
@@
 by the lack of knowledge about the exact shape of the PSF, and also presence of noise;
-both sky noise and CCD readout noise. Thus we need a fast method that returns
-optimal estimates of centroids in a realistic range of signal-to-noise ratios.
+both sky noise and CCD readout noise. Thus we want investigate whether fast centroiding 
+estimates can saturate the bound in a realistic range of signal-to-noise ratios.
 
-To date, a number of softwares packages have been designed for the purpose of extracting astronomical
-sources and making catalogs. One of these softwares is SExtractor (\citealt{sextractor}),
-whose centroiding method involves first finding the zeroth moment of the object
-as a first-order estimate, and then iteratively correcting the centroid by computing
-the zeroth order moment of the object weighted by a Gaussian window function,
-until the correction falls below a particular threshold value.
-The width of the Gaussian window function is set by the object's half-light radius.
-Other examples are DAOPHOT (\citealt{daophot}), and DOPHOT (\citealt{dophot})
-which both assume analytic models for the stellar PSF profiles with centroid
-coordinates being free parameters of these models.
-DAOPHOT (DOPHOT) finds the centroids by fitting a Gaussian (a truncated power series) to 
-the light profile of stars.
+%To date, a number of softwares packages have been designed for the purpose of extracting astronomical
+%sources and making catalogs. One of these softwares is SExtractor (\citealt{sextractor}),
+%whose centroiding method involves first finding the zeroth moment of the object
+%as a first-order estimate, and then iteratively correcting the centroid by computing
+%the zeroth order moment of the object weighted by a Gaussian window function,
+%until the correction falls below a particular threshold value.
+%The width of the Gaussian window function is set by the object's half-light radius.
+%Other examples are DAOPHOT (\citealt{daophot}), and DOPHOT (\citealt{dophot})
+%which both assume analytic models for the stellar PSF profiles with centroid
+%coordinates being free parameters of these models.
+%DAOPHOT (DOPHOT) finds the centroids by fitting a Gaussian (a truncated power series) to 
+%the light profile of stars.
 
-Given an analytic expression for the PSF model,
+Given an analytic expression for the PSF model adopted in this study,
 we derive an expression for the fundamental lower bound on the centroiding error as
 a function of the parameters of the PSF model (e.g. PSF size),
-and signal-to-noise-ratio of stars. We create two sets of simulations for which we 
-know the CRLB, one with variable signal-to-noise ratio and constant FWHM, and one 
+and signal-to-noise-ratio of stars. We create two sets of simulations for which we can 
+compute the CRLB, one with variable signal-to-noise ratio and constant FWHM, and one 
 with variable FWHM and constant signal-to-noise ratio. After applying
@@
 we investigate how close these methods can get to saturating the CRLB for
-various ranges of background noise level and PSF FWHM.
+various ranges of background Gaussian noise level and PSF FWHM.
 
-In this work, we focus on four centroiding methods. The first method
-involves fitting a PSF profile, assuming that we have a good PSF estimate, to the star. 
+In this work, we focus on four centroiding methods. The first method is the maximum-likelihood 
+estimator which involves fitting a PSF profile, assuming that we have a good PSF estimate, to the star. 
 The second method estimates the centroid of a star by fitting a 2d second-order polynomial to

### 2016-09-23 ms/ms.tex
changed a few things in the intro

@@
 
-\title{Do fast stellar centroiding methods saturate the Cramer-Rao lower bound?}
+\title{Do fast stellar centroiding methods saturate the Cram\'{e}r-Rao lower bound?}
 
@@
 
-The fundamental Crame\'{e}r-Rao lower bound sets a limit on the root-mean-squared-error 
+The fundamental Cram\'{e}r-Rao lower bound sets a limit on the root-mean-squared-error 
 achievable by optimal estimators. Information-preserving estimators are able to deliver 
@@
 
-Accuarate estimates of the centers of point
-sources, which are convolved with telescope point spread function (and atmospheric PSF in case of
-ground based telescopes), and also the pixel response function, are crucial to further steps of
+Accuarate estimates of the centers of point sources, which are convolved with telescope point spread function (and atmospheric PSF in case of ground based telescopes), and also the pixel response function, are crucial to further steps of
 astronomical image processing. For instance, proper measurement of the shapes of galaxies
@@
 
-Ideally, we want a centroiding procedure that provides measurements as precise as possible,
-without putting a huge computational burden on the photometric pipeline.
+Ideally, we want a centroiding procedure that provides measurements as precise 
+as possible, without putting a huge computational burden on the photometric pipeline.
 Reducing the computational cost becomes even more important in large surveys,
@@
 In this paper, we study the optimality of various techniques for centroiding 
-faint, unsaturated stars. Our requirement for optimality is saturation of the Cram\'{e}r-Rao 
-lower bound by a centroiding method. We apply a number of centroiding methods 
-to a large number of simulated faint stars, assuming uncorrelated Gaussian noise, 
-with different signal-to-noise ratio and size realizations. Error from star 
-centroiding methods, will always have a theoretically-set lower bound, 
-known as the Cram\'{e}r-Rao lower bound (hereafter denoted by CRLB) which 
-has an inverse relation with the signal-to-noise-ratio of stars. In the context 
-of astrometry, the Cram\'{e}r-Rao lower bound saturation for least-squares 
+faint, unsaturated stars. Our requirement for optimality is saturation of the 
+theoretically-set lower bound, known as the Cram\'{e}r-Rao lower bound by the 
+centroiding methods considered in this study. We apply a number of 
+centroiding methods to a large number of simulated faint stars, assuming uncorrelated 
+Gaussian noise, with different signal-to-noise ratio and size realizations. 
+The Cram\'{e}r-Rao lower bound has an inverse relation with the signal-to-noise-ratio 
+of stars. In the context of astrometry, the Cram\'{e}r-Rao lower bound saturation for least-squares 
 estimators has been tested in specific limits in which the centroiding bias is 
@@
 by the lack of knowledge about the exact shape of the PSF, and also presence of noise;
-both sky noise and CCD readout noise. Thus we want investigate whether fast centroiding 
+both sky noise and CCD readout noise. Thus we want to investigate whether fast centroiding 
 estimates can saturate the bound in a realistic range of signal-to-noise ratios.
@@
 with variable FWHM and constant signal-to-noise ratio. After applying
-different centroiding methods to the simulations,
-we investigate how close these methods can get to saturating the CRLB for
-various ranges of background Gaussian noise level and PSF FWHM.
+different centroiding methods to the simulations, we investigate how close 
+these methods can get to saturating the CRLB for various ranges of background 
+Gaussian noise level and PSF FWHM.
 
@@
 
-In order to test the accuracy of various centroiding methods, we need to comapre their 
+In order to test the accuracy of various centroiding methods, we need to compare their 
 performances against each other at saturating the Cram\'{e}r-Rao lower bound on centroiding error. 
@@
 to the 3$\times$3 patch centered on the brightest pixel of the
-mathched-filter image $Y^{s}$.
+matched-filter image $Y^{s}$.
 Upon constructing a universal 9$\times$6 design matrix
@@
 
-We should nonlinearly optmize a psf to saturate the bound.
+We should nonlinearly optimize a PSF to saturate the bound.
 But because optimization is done through a chi-squared fitting, 
 this is equivalent to optimizing a matched filter. 
-And if the image is well sampled (in the psf-convolved image) this
+And if the image is well sampled (in the PSF-convolved image) this
 is equivalent to interpolating a matched filter on a grid. 
@@
 For simulated images with higher $\gamma$, convolving the
-data with the PSF results in images that are wellsampled around the brightest pixel. This allows the 
+data with the PSF results in images that are well-sampled around the brightest pixel. This allows the 
 polynomial centroiding to deliver highly accurate results that can saturate the CRLB for simulated
@@
 The default polynomial centroiding technique only takes advantage of the information 
-contained in a 3$\times$3 patch centered on the brighest pixel of the smoothed image which is only 
+contained in a 3$\times$3 patch centered on the brightest pixel of the smoothed image which is only 
 well-sampled when the FWHM of the simulated image of star 

### 2016-09-23 ms/ms.tex
done with the intro for now

@@
  image. This method is fast and does not require any knowledge of the 
-PSF. The last method we consider, is a center of light centroiding 
-(measurement of a first moment), applied to the 
-7$\times$7 patch around the brightest pixel of the image.
+PSF. The last method we consider, is a center-of-light centroiding 
+(measurement of a first moment), applied to the 7$\times$7 patch around the brightest pixel of the image.
 
@@
 know the exact PSF profile, we must make use of approximate centroiding algorithms. In this work, we
-studied how close we get to saturating the CRLB with an approximate method acting on relatively low signal-to-noise ratio,
-unsaturated stars.
+studied how close we get to saturating the CRLB with an approximate method acting on relatively low 
+signal-to-noise ratio, unsaturated stars.
 

### 2016-09-26 ms/ms.tex
clarification of CRLB and the Gaussian noise assumption, dropping the word accuracy

@@
 
-In order to test the accuracy of various centroiding methods, we need to compare their 
-performances against each other at saturating the Cram\'{e}r-Rao lower bound on centroiding error. 
 The closer an estimator is to saturating the CRLB, the more information about the quantity that we 
 need to estimate is preserved. The closer the root-mean-squared-error of a given estimator is to the bound,  
-the more optimal the estimator is.
+the more optimal---in terms of preseving the information---the estimator is. In order to test how information-preserving 
+various centroiding methods are, we need to compare their 
+performances against each other at saturating the Cram\'{e}r-Rao lower bound 
+on centroiding error.
 
@@
 root-mean-squared error of unbiased estimators. The CRLB is given by the square-root of the inverse of 
-the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
- it is sufficient to compute the Fisher matrix. This computation relies on a set of assumptions:
+the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB, it is sufficient to compute the Fisher matrix. 
+This computation relies on a set of assumptions:
 
@@
   \item Known, stationary noise process. In the context of centroiding stars, this is equivalent to 
-        having background limited nosie from sky background and CCD readout noise.
+        having background limited noise from sky background and CCD readout noise.
   \item Uncorrelated Gaussian noise with no outliers. 
 \end{itemize}
+
+We note that the conditions of stationary noise process and uncorrelated Gaussian noise,  may not be representive of many realistic scenarios. 
+For instance, in a situation where there is substantial contribution from instruement gain---more effective for the 
+bright sources---to the noise, the last two conditions are not met. In this study however, we are only going to consider relatively faint stars, 
+for which the assumption of a Gaussian background noise is valid.
 

### 2016-09-26 ms/ms.tex
minor changes

@@
 estimators as the ratio of the CRLB and the root-mean-squared-error such that the maximum efficiency 
-achievable by an estimator is unity. The closer the root-mean-squared 
-to the CRLB, the more information about the parameter of interest is preserved, and thus the more efficient 
+achievable by an estimator is unity. The closer the RMSE to the CRLB, 
+the more information about the parameter of interest is preserved, and thus the more efficient 
 the estimator is.
 
-Let us consider the case of a maximum likelihood estimate $\boldsymbol{\mathbf{\theta}}_{\text{ML}}$, where the likelihood function corresponds to the same generative assumptions that we used to compute the CRLB.
+Let us consider the case of a maximum likelihood estimate $\boldsymbol{\mathbf{\theta}}_{\text{ML}}$, 
+where the likelihood function corresponds to the same generative assumptions that we used to compute the CRLB.
 
@@
 \section{Centroiding methods}\label{sec:method}
+
+In this section, we briefly discuss the approximate and the non-approximate centroiding methods considered in this 
+study.
+
 \begin{description}
@@
 
-An optimal stellar centroiding algorithm must saturate---or come close to saturating---the fundamental Cram\'{e}r-Rao lower 
-bound. That is, in all ranges of background noise level, size, radial light profile,
+An efficient stellar centroiding algorithm must saturate---or come close to saturating---the fundamental 
+Cram\'{e}r-Rao lower bound. That is, in all ranges of background noise level, size, radial light profile,
 and shape, it must preserve information about the centroids of stars. In practice however,

### 2016-09-27 ms/ms.tex
ms.tex

@@
 %\newcommand{\aap}{Astron.\,\&~Astrophys.}
+
+\newcommand{\todo}[1]{{\em \textcolor{red}{ #1}}}
 
@@
 
-Reaching the optimal measurement of the centroids of stars however, is limited
-by the lack of knowledge about the exact shape of the PSF, and also presence of noise;
-both sky noise and CCD readout noise. Thus we want to investigate whether fast centroiding 
-estimates can saturate the bound in a realistic range of signal-to-noise ratios.
+Saturating the Cram\'{e}r-Rao lower bound in estimating the centroids of stars however, is limited
+by the lack of knowledge about the exact shape of the PSF, also presence of noise. 
+There are many sources of noise such as the CCD readout noise, sky noise, errors resulting from 
+\todo{incorrect} flatfield corrections, and photon noise from the astronomical object itself. 
+In this study, we limit our investigation to the simulated images that contain non-overlapping faint sources 
+that are sky-limitted. We assume that the generated images are not affected by flatfield corrections.
+
+However, we focus the scope of this investigation to sky-limited images for which the sky level has been 
+subtracted. Furthermore, we assume that any instruement gain has been calibrated out, and that the 
+simulated images are free of any contamination by cosmic rays, stray light from neighboring fields, or 
+any other type of defect in real images. We expect these defects to move the centroiding errors further from the 
+fundamental bound.
+
+We intend to investigate whether fast centroiding 
+estimates can saturate the bound in a realistic range of low signal-to-noise ratio images that are sky-limited.
 
@@
 
-We note that the conditions of stationary noise process and uncorrelated Gaussian noise,  may not be representive of many realistic scenarios. 
-For instance, in a situation where there is substantial contribution from instruement gain---more effective for the 
-bright sources---to the noise, the last two conditions are not met. In this study however, we are only going to consider relatively faint stars, 
-for which the assumption of a Gaussian background noise is valid.
+\todo{HOGG HELP: can you read the following paragraph and see whether it makes sense or not?}
+
+Note that in this study, we explicitly focus on sky-limited images. In the sky-limited images, the contribution 
+to the Poisson pixel noise is largely domiated by the sky rather than the objects. The exceptions are the very bright 
+sources, but we only consider relatively low signal-to-noise ratio faint stellar sources. After subtraction of the 
+sky background level, distribution of the Poisson pixel noise can be approximated by a Gaussian distribution with 
+zero mean. \todo{Also mention in the discussion: The assumption of uncorrelated Gaussian noise is only an approximation 
+to a Poisson distribution which has broader tails than what we expect from a Gaussian!} 
+\todo{HOGG HELP: can you write a few words about uncorrelated noise?}
 
@@
 
+\todo{Given that the authors are using simulated data, a direct search for biases in the estimator outputs is far more powerful than using violations of the Cramer-Rao inequality to infer biased techniques.}
+
 In this investigation, the model observables for the noisy data are the pixel-convolved PSF (PSF profile evaluated at different pixel locations), and  
@@
 
-Derivation of an explicit expression for the Fisher matrix $\mathcal{F}$ requires specifying a presumed correct 
-PSF model.
+Derivation of an explicit expression for the Fisher matrix $\mathcal{F}$ requires 
+specifying a presumed correct PSF model.
 We use the Moffat profile \citep{moffat} for our PSF simulations. 
@@
 parameter $\beta$, the Moffat PSF becomes arbitrarily close to a simple Gaussian PSF.
+
+\todo{HOGG HELP: can you read the following paragraph and maybe add a few words to it?}
+
+Note that in our PSF simulations, we assume that the individual generated images are 
+Nyquist sampled. All pixels in the images are identical, and the stars are simulated 
+by sampling from the pixel-convolved PSF. In well-sampled images, the center of 
+the pixel-convolved PSF must be very close to the center of the optical PSF.
 
@@
 
+\todo{The use of a 7x7 kernel appears arbitrary. For the sake of a fair comparison with the matched filter, the size of the kernel should be equivalent to that used in the matched filter section.}
+
 \begin{eqnarray}
@@
 
+\todo{ The authors imply the PSF-fitting can only be used when the PSF is known. This is not true; one of the variables in PSF-fitting algorithms is often the PSF size (and sometimes shape) itself.}
+
 Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
@@
 this method fails to deliver any reliable centroiding estimates.
+
+\todo{The authors should quantify the difference in accuracy between the 7x7 moment method and an optimal estimator. Is it 10$\%$ worse? 10 times worse?}
 
@@
 
+\todo{The intent of the statement that the default polynomial centroiding uses only a 3x3 pixel region of the smoothed image is unclear.
+While this is a factually true statement, the smoothing algorithm requires far more than 3x3 pixels on the original image to operate.}
+
 Once we modify the polynomial method further by convolving the image with the full postage stamp
@@
 of initial astrometry of the point sources considerably.
+
+\todo{If PSF-fitting is to be argued against for speed reasons, the authors should compare the speed of PSF-fitting astrometry and flux estimates against matched filter astrometry plus PSF-fitting flux estimation.
+It is not clear that the PSF-fitting only approach would be slower, given that the matched filter requires a convolution as well as something with the accuracy of PSF-fitting to estimate flux.}
 
@@
 at the positions of stars.
+
+\todo{It should be noted that estimation of a PSF within a few tenths of a pixel is trivial from most images.
+Thus, when dealing with realistic images, there is little if any difference between a true matched filter and the default polynomial.}
 

### 2017-05-31 ms/response1/response.md
first revision and response

Dear Editor,

This was a very helpful and constructive referee report and we have revised the paper
accordingly. We think the referee comments have improved the paper
substantially.

Mohammadjavad Vakili (on behalf of the authors)

-----

We very much appreciate the thorough and constructive referee comments;
they have led to substantial improvements in the paper. 
In what follows, the referee comments are indented and our responses are not
indented.

  Referee comment:

  The authors propose the use of matched filtering to centroid bright stars as an alternative to more computationally expensive PSF-fitting algorithms. 
  The manuscript contains a handful of tests demonstrating that matched    filtering is as accurate as PSF-fitting in most regimes of SNR and PSF size.
  My primary concern is that matched filtering is an accepted technique that has been in the literature for decades (e.g., Ribak, Hege & Christou 1985) and
  predates the use of PSF-fitting. This study proposes using a quadratic interpolator to estimate the peak of a matched filter, 
  which I do not believe meets the Astronomical Journal's criteria for significant contribution to the  literature.

Our response:

We want to point out that the aim of our investigation is not introducing a new method for estimating the centroids of stars. As the referee has pointed out, the matched-filter polynomial centroiding method has been widely used in the astronomy literature. We do not wish to present a novel method for centroiding stars. Our goal for writing this manuscript is to show whether or not fast and approximate methods can saturate the fundamental Cram\'{e}r-Rao lower bound on the centroiding errors. We apologize to the referee if we failed to make it clear that the scope of our investigation is limited to testing the saturation of the Cram\'{e}r-Rao lower bound on centroiding errors. 
We have made major changes to the abstract and the introduction of our manuscript.  We have broken the first paragraph of the abstract to two paragraphs. we begin the second paragraph by explaining the CRLB. Afterwards, we aim to compare the performance of various centroiding methods, in terms of saturating the bound. We omit the paragraph in the intro that discussed software packages for astrometry and photometry of stars. We mostly focus on discussions related to CRLB.

  Referee comment:

  First, astronomical images do not have stationary noise. Additionally, for cameras with low background levels, 
  the Gaussian noise assumption is invalid as the photon noise distribution becomes asymmetric at low flux levels and 
  noise is quantized into counts during readout. While I understand that the limitations of the authors'  analysis 
  require stationary Gaussian noise, one suspects that the interdependence of brightness and noise (and thus  centroid) 
  may adversely impact the technique advocated in this paper.
  For example, equations 13-17 in section 2 are only valid for constant pixel noise, while an astronomical image containing 
  sources not only has variable noise but the noise itself is a function of the brightness of the sources.   The reader is thus left to suspect that use of a realistic noise model could alter the outcomes of the tests presented.

Our response:

We agree with the referee's comment that the the assumption of stationary noise is not in general true. However, we make it clear in the introduction that we limit the scope of our paper to the sky-limited images for which sky level has been subtracted and any instrument gain has been calibrated out. 
In the introduction section, we added two paragraphs that briefly explain the underlying assumptions of our data generation procedure. In the 5th paragraph of the introduction, we briefly overview the various sources of noise that could potentially cause deviation of centroiding errors from the CRLB. We also explicitly mention that we limit our investigation to the simulated images that are sky limited. 
In the 6th paragraph of introduction, we we discuss the general assumptions we make in our investigation. These assumptions include perfect flat-field calibration, lack of contamination by cosmic rays, etc.

Furthermore, in section 2 of the manuscript, we provide explanation for the assumption of stationary noise process listed in the assumptions in the bullet points. After the bullet points, we have added two paragraphs in order to explain these assumptions. We mention in the text that we explicitly focus on sky-limited images, for which the Poisson noise is mostly dominated by the sky.  We also mention 
that in the limit where the number of photons per pixel is large, the Poisson noise can be approximated by a Gaussian distribution. This is a very good approximation for many astronomical imaging datasets such as the Sloan Digital Sky Survey, DECAM Legacy Survey,  etc.

  Referee comment:

  A second major concern is that the authors have not discussed the potential impact of sampling PSFs in the center of each pixel vs. 
  integrating the PSF over a pixel.  While this has minimal impact on Nyquist-sampled images, undersampled images such as those from WFC3/IR suffer from 
  significant variation of the PSF within a pixel, which can create errors in  the inferred centroiding (e.g., Anderson & King 2000). 
  While the authors do not indicate whether they sample or integrate, this is a key concern for   any discussion of centroiding and must be included in this paper.

Our response:

The model of the PSF considered in our manuscript is a model of  the pixel-convolved PSF which is the instrumental PSF convolved with the pixel response function. 
It is the pixel-convolved PSF that can be directly estimated from observations without making any assumption about the sensitivity of detector pixels. Moreover, it is the pixel-convolved PSF that can be used to perform astrometry and photometry measurements as well as galaxy shape measurements in weak lensing.

In the third page of our manuscript we have added a paragraph explaining the assumptions about the PSF model used in  our data generation. First, we mention that the simulated images (in the pixel space) are close to Nyquist-sampled or close to 
Nyquist-sampled. Then, we mention that the pixels in the simulated images are identical and the stars are simulated by sampling from the pixel-convolved PSF. This concept is thoroughly explained in (Anderson & King 2000). Note that in that paper, the pixel-convolved PSF is referred to as the effective PSF.

We are aware of the challenges that one might in modeling astronomical images for which the PSF is under-sampled such as the images observed by the HST WFC3-IR channel. In such cases, the solution for the super-resolution (super-sampled) pixel-convolved PSF is degenerate with the centroid offsets of stars. Therefore, estimating the super-resolution PSF in those images requires imposing extra conditions for breaking those degeneracies. In a nearly-completed manuscript (Vakili, Hogg, and Fadely in prep) we are presenting a data-driven model for estimating the super-resolution PSF from under-sampled images of the HST WFC3-IR channel. In this manuscript, we specifically focus on the Nyquist-sampled or close to Nyquist-sampled images. We agree with the referee comment and we have clarified the assumptions we made for simulating the images in our manuscript.

We agree with the referee's comment that the RMSE approaches the CRLB and we replaced the expression "becomes greater than or equal to approaches

  Referee comment:

  A third concern about the analysis is that the impact of neighboring sources is never discussed. 
  A specific concern about the matched filter is that smoothing the image wipes out any fainter neighbors, while PSF-fitting 
  photometry approaches are able to accurately obtain astrometry and photometry of sources separated by  the image FWHM.

Our response:

The purpose of this manuscript is to investigate whether fast stellar centroiding methods can saturate the Cramer-Rao lower bound or not when they are applied to single isolated stars. 
The PSF-fitting method based that delivers a maximum-likelihood estimator of the centroid of a given star can saturate this fundamental theoretical bound as long as a correct model 
of the PSF is used.  In analysis of the data from the wide imaging surveys such as the Sloan Digital Sky Survey and the upcoming Large Synoptic Survey Telescope (LSST), fast approximate methods 
are used to estimate the centroids of stars. One of these methods is the well-known matched-filter polynomial centroiding estimator that we include in our study. We only wish to investigate whether these 
fast estimators are able to saturate the Cramer-lower bound on stellar centroiding errors or not.  For investigating the saturation of the Cramer-Rao lower bound, it is sufficient to see whether these methods 
are capable of saturate the bound when applied to images of isolated stars or not.

  Referee comment:

  - Section 1, paragraph 1: it is unclear why the PSF would be "wrongly estimated", unless the centroid is calculated incorrectly.

Our response:

We just wanted to point out that in a forward model of the image of a given star, it is the PSF model 
that should be shifted to the center of the star. The image of the star itself should not be shifted.
But we note that it is not necessary to include this and it is not related to the goal of this paper. 
So we dropped that sentence from the manuscript.

  Referee comment:

  - Section 1, paragraph 4: there are significantly more noise sources than sky and CCD readout noise: photon noise from the object, flatfield errors, bias/overscan subtraction errors, etc.

Our response:

We agree with the referee comment. In paragraph of 5 of section 1 we have included many more examples of possible noise sources such as the CCD readout noise, sky noise, errors resulting from 
incorrect flat-field calibration, and photon noise from the astronomical object itself. We end this paragraph by mentioning that we limit the focus of our investigation to 
the simulated images with non-overlapping faint sources that are sky limited. In paragraph 6 of section 1, we list other assumptions we have made for simulating images. 
Furthermore, we assume that the sky has been subtracted, instrument gain has been calibrated out, and that the simulated images are free of contamination by cosmic rays, 
stray light from neighboring fields, and any other defect.

  Referee comment:

  - Section 2, paragraph 3, bullet 2: "noise" is misspelled

Our response:

We corrected that.

  Referee comment:

  - Section 2, paragraph 10 (beginning with "Asymptotically"): since the RMS is always "greater than or equal to the CRLB", I believe the authors mean that the RMS "approaches the CRLB".

Our response:

We agree with the author. We changed this to "approaches the CRLB".

  Referee comment:

  Given that the authors are using simulated data, a direct search for biases in the estimator outputs is far more powerful than using violations of the Cramer-Rao inequality to infer biased techniques.

Our response:

we are sorry if this sentence implies that we are using the CRLB to estimate biases. 
We do not wish to use use CRLB as a proxy to determine the biases arising from centroiding methods. 
This is not the purpose of this investigation. We notice that the entire discussion of beating the CRLB may 
imply that we want to see whether we can find biases by looking at whether 
the CRLB is beaten or not. We realized that this does not serve any purpose in our investigation. 
We drop the paragraph starting with "However, the relation (3) does not necessarily hold for biased estimators..." 
and the entire discussion of "beating the CRLB". We apologize if that have caused any confusion.

  Referee comment:

  As a point of formatting, the manuscript could benefit from use of subsections. For example, section 3 is four pages long in the version provided, 
  with four major subsections highlighted by bold text. I suggest the authors make these sections 3.1, 3.2, 3.3, and 3.4.

Our response:

We agree with this comment. We have divided section 3 to four subsection: 3.1, 3.2, 3.3, and 3.4.

  Referee comment:

  the authors imply the PSF-fitting can only be used when the PSF is known. This is not true; one of the variables in PSF-fitting algorithms is often the PSF size (and sometimes shape) itself.

Our response:

We apologize the referee if has caused any confusion. We have this clarified this in subsection 3.4. 
We mention that the PSF-fitting method in our investigation is done by maximizing a likelihood functions which assumes a correct model 
of the PSF (Moffat profile) with  a correct size. Given that the correct PSF is assumed, we expect the RMSE arising from this method 
to saturate the CRLB. Therefore, this method serves as the most efficient estimator, in that it preserves the most amount of information (encoded in the 
Fisher information matrix) that can be achieved in the presence of noise.

  Referee comment:

  - Section 3, "Default polynomial centroiding" section. The use of a 7x7 kernel appears arbitrary. For the sake of a fair comparison with the matched filter, 
  the size of the kernel should be equivalent to that used in the   matched filter section.

Our response:

We completely agree with the referee that the use of a 7x7 kernel seems arbitrary. In order to present a fair comparison between this method 
and the matched filter method, we use the same kernel size that is used in the matched-filter method. Furthermore, we found that the title 
"Default polynomial centroiding" is ambiguous. Thus, we changed that to "Fixed-Gaussian polynomial centroiding". This names refers to 
the fact that a Gaussian kernel with a fixed size is applied in this method.

  Referee comment:

  - Section 6, paragraph 2: The authors imply the PSF-fitting can only be used when the PSF is known. This is not true; one of the variables in PSF-fitting algorithms is often the PSF size (and sometimes shape) itself.

Our response:

We apologize the referee if has caused any confusion. We have this clarified this in subsection 3.4. 
We mention that the PSF-fitting method in our investigation is done by maximizing a likelihood functions which assumes a correct model 
of the PSF (Moffat profile) with  a correct size. Given that the correct PSF is assumed, we expect the RMSE arising from this method 
to saturate the CRLB. Therefore, this method serves as the most efficient estimator, in that it preserves the most amount of information (encoded in the 
Fisher information matrix) that can be achieved in the presence of noise.

  Referee comment:

  - Section 6, paragraph 3: The authors should quantify the difference in accuracy between the 7x7 moment method and an optimal estimator. Is it 10% worse? 10x worse?

Our response:

We agree with this and we have included some numbers in order to quantify the difference. We mention the difference in 
terms of the ratio between the root-mean-squared error and the CRLB. For an optimal estimator, 
the ratio is one or very close to one. This discussion is now moved to paragraph 5 of section 6. In paragraph 5 of section 6, 
we quantify the percentage deviation of the 7x7 moment centroiding errors from the CRLB.

  Referee comment:

  - Section 6, paragraph 4: The intent of the statement that the default polynomial centroiding uses only a 3x3 pixel region of the smoothed image is unclear. 
  While this is a factually true statement, the smoothing algorithm   requires far more than 3x3 pixels on the original image to operate.

Our response:

In the new version of the manuscript, this paragraph has been moved to section 6, paragraph 6. 
We agree with the referee that smoothing algorithm requires information far more than the 3x3 pixels 
on the original image. We dropped that sentence that claims the fixed Gaussian polynomial centroiding 
(previously noted as default Gaussian centroiding) only uses information in the 3x3 region. 
Furthermore, we drop all the sentences that discuss the effect of smoothing on sampling.

  Referee comment:

  - Section 6, paragraph 6: If PSF-fitting is to be argued against for speed reasons, the authors should compare the speed of PSF-fitting 
  astrometry and flux estimates against matched filter astrometry plus PSF-fitting flux   estimation. It is not clear that the PSF-fitting 
  only approach would be slower, given that the matched filter requires a convolution as   well as something with the accuracy of PSF-fitting to estimate flux.

Our response:

We do not wish to argue against PSF-fitting for speed reasons. We only want to argue that for the purpose of centroiding stars, 
fast and approximate methods such as matched-filter polynomial centroiding (and in some cases the fixed Gaussian polynomial method) 
can be as efficient as PSF-fitting in terms of saturating the CRLB. But we agree with the referee that the way section 6, paragraph 6 was written 
may imply that we are arguing against use of PSF-fitting.

  Referee comment:

  - Section 6, paragraphs 7-8: These paragraphs are hard to follow, as many readers won't equate functions on values in 2D images to dot-products between 1D vectors without some explanation. 
  An equation or two would be helpful,   for example
  chi^2 = [ F^2 dot(PSF,PSF) - 2*F*dot(PSF,image) + dot(PSF,image) ] / sigma^2,
  and that the first and third terms are more or less constant when varying only the centroid, thus a chi^2 minimization is equivalent to finding the maximum of the match-filtered image.

Our response:

We have added equation (30) to clarify our point. This is now discussed in paragraphs 10 and 11 of the last section. 
The equation is added to paragraph 10. In paragraph 11, we explain how optimizing the modified chi-squared 
is equivalent to finding the peak of the matched-filter.

  Referee comment:

  - Section 6, paragraph 10: It should be noted that estimation of a PSF within a few tenths of a pixel is trivial from most images. 
  Thus, when dealing with realistic images, there is little if any difference between a true   matched filter and the default polynomial.

Our response:

We agree with the referee comment. The discussion is now included in paragraph 13 of this section. For many images, theres is very 
little difference between a true  matched filter and the fixed-Gaussian polynomial centroiding method. Therefore, in paragraph 13 of 
section 6, we first mention that PSF-fitting always saturates the CRLB, but in most cases a simple polynomial centroiding after 
convolving the image with a fixed-Gaussian kernel would perform as good (in terms of saturating the CRLB) as the case where we do 
know the PSF at the positions of stars. That is, there is little difference between the performance of a matched-filter and a fixed-Gaussian 
polynomial centroiding.

  Referee comment:

  - Figures: Is the Y-axis the error in the total centroid position (e.g., sqrt(dx^2+dy^2), or just the error in one axis? Given the derivation of the CRLB, I believe it to be one axis.

Our response:

We are sorry for not clarifying this. The Y-axis of the plots only show error in one axis. 
Furthermore, we have changed the Y-axis of the plots to the ratio between the x component of the 
centroiding error and the CRLB. We have clarified this in the captions of figures, the first paragraph of 
subsection 5.1, and the first paragraph of the subsection 5.2 .

  Referee comment:

  - Figures: Log-log plots have the ability to make the errors look smaller than they are. The authors may wish to consider plotting with (error/CRLB) on the Y axis.

Our response:

We agree with th referee and we have made relevant changes to the plots. 
We have changed the Y-axis to the ratio of error (in x-axis of the centroid positions) 
to the CRLB. We have removed the logarithmic scale of the Y-axis in all of the plots.

  Referee comment:

  - Figures 4 and 8: It seems that the use of a 17x17 postage stamp is artificially reducing the error at low SNR, given the large number of points with centroid errors near the limit of 7-8 pixels.

Our response:

The 7x7 moment methods fails to return reliable centroiding methods in the limit of low signal-to-noise ratio. 
As a result, we see a large number of outliers that correspond to centroiding errors near the limit of 7-8 pixels.
In the end of the 5th paragraph of section 6, we explicitly mention that in the case of SNR = 5, the errors arising from the 
7x7 moment method are suppressed by the fact that 17x17 postage-stamps are used to simulate images. 
We also add that we expect the deviation of the RMSE from the CRLB to be larger for this method.

In addition to the changes given above, we also made the following
small changes:

* Added references to Foreman-Mackey et al. 2015, Rowe et al. 2015, 
and Zuntz et al. 2013, 2014.

* Fixed a few typos.

* We have changed the color of plots.

* Added some acknowledgements, including one to the referee.

### 2017-05-31 ms/revision1/main.tex
first revision and response

\documentclass[twocolumn]{aastex61}
\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext}
\usepackage[T1]{fontenc}
\usepackage{apjfonts} 
\usepackage[figure,figure*]{hypcap}

\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

\definecolor{dred}{rgb}{0.75,0,0}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\hypersetup{ colorlinks,
linkcolor=darkblue,
filecolor=darkgreen,
urlcolor=darkred,
citecolor=darkblue}

\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\lang}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\vep}{\bm{\epsilon}}
\newcommand{\ep}{\epsilon}
\newcommand{\pars}{\vec{\theta}}
\newcommand{\dev}{\mathrm{d}}
\newcommand{\ngal}{n_{g}}
\newcommand{\gmf}{g(N)}
\newcommand{\mr}{M_{\rm r}}
\newcommand{\rpp}{r_{\rm p}}
\newcommand{\mzero}{\log M_{0}}
\newcommand{\mone}{\log M_{1}}
\newcommand{\mmin}{\log M_{\rm min}}
\newcommand{\sigmam}{\sigma_{\log \rm M}} 
\newcommand{\wpp}{w_{\rm p}}

\newcommand{\acen}{\mathcal{A}_{\rm cen}}
\newcommand{\asat}{\mathcal{A}_{\rm sat}}
\newcommand{\todo}[1]{{\textcolor{dred}{ #1}}}

\shorttitle{saturation of the Cram\'{e}r-Rao bound}
\shortauthors{Vakili \& Hogg}

\begin{document}

\title{Do fast stellar centroiding methods saturate the Cram\'{e}r-Rao lower bound?}

\author{Mohammadjavad Vakili}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY, 10003}
\author{David~W.~Hogg}

\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY, 10003}
\affiliation{Flatiron institute, 160 5th Avenue, New York, NY, 10010}
\affiliation{Center for Data Science, New York University, 60 5th Ave, New York, NY, 10010}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}

\begin{abstract}
One of the most demanding tasks in astronomical image processing---in terms of precision---is 
the centroiding of stars. Upcoming large surveys are going to take images of 
billions of point sources, including many faint stars, with short exposure times. 
Real-time estimation of the centroids of stars is crucial for real-time PSF estimation, 
and maximal precision is required for measurements of proper motion.

\todo{The fundamental Cram\'{e}r-Rao lower bound sets a limit on the root-mean-squared-error 
achievable by optimal estimators. In this work, we aim to compare 
the performance of various centroiding methods, in terms of saturating the bound, when they 
are applied to relatively low signal-to-noise ratio unsaturated stars assuming zero-mean 
constant Gaussian noise. In order to make this comparison, we present the ratio of the root-mean-squared-errors of these estimators to their corresponding Cram\'{e}r-Rao bound as a function of the signal-to-noise ratio and the full-width at half-maximum of faint stars.}

We discuss two general circumstances in centroiding of faint stars: (i) when we have a good estimate
of the PSF, (ii) when we do not know the PSF. \todo{In the case that we know the PSF, 
we show that a fast polynomial centroiding after smoothing the image by the PSF can be 
as efficient as the maximum-likelihood estimator at saturating the bound. 
In the case that we do not know the PSF, we demonstrate that although polynomial centroiding is not as optimal as PSF profile fitting, it comes very close to saturating the Cram\'{e}r-Rao lower bound in a wide range of conditions. We also show that the moment-based method of center-of-light 
never comes close to saturating the bound, and thus it does not deliver reliable estimates of centroids.}

\end{abstract}

\keywords{methods: statistical--- methods: data analysis--- techniques: image processing}

\section{Introduction}

Accurate estimates of the centers of point sources, which are convolved with telescope point spread function (PSF), and atmospheric PSF in case of ground based telescopes, and the pixel response function, are crucial to further steps of
astronomical image processing. 
For instance, proper measurement of the shapes of galaxies
requires interpolation of the PSF estimates from the positions of stars across the
image to the positions of galaxies. At the position of each star, the PSF is estimated by sub-pixel 
shifting of the star so that the PSF is centered on its centroid. If the sub-pixel shifts are wrong, then 
the PSF estimates will be biased. Moreover, measurements of the parallaxes and the proper motions of stars
depend on how well we can measure their centroids.

Ideally, we want a centroiding procedure that provides measurements as precise 
as possible without putting a huge computational burden on the photometric pipeline.
Reducing the computational cost becomes even more important in large surveys,
where we want to estimate the centroids of thousands of point sources detected
on the telescope's focal plane, for various real-time applications.

\todo{The Cram\'{e}r-Rao lower bound (CRLB) sets a lower limit on the root-mean-squared error of estimators. When the root-mean-squared error arising from an estimator approaches the bound, the bound is saturated by that estimator. In this paper, we study the optimality of various techniques for centroiding faint, unsaturated stars. Our requirement for optimality is saturation of the 
theoretically-set lower bound, known as the Cram\'{e}r-Rao lower bound, by the 
centroiding methods considered in this study.}

\todo{We apply a number of centroiding methods to a large number of simulated faint stars, assuming uncorrelated 
Gaussian noise, with different signal-to-noise ratio and size realizations. 
The Cram\'{e}r-Rao lower bound has an inverse relation with the signal-to-noise-ratio 
of stars. In the context of astrometry, the Cram\'{e}r-Rao lower bound saturation for least-squares estimators has been tested in specific limits in which the centroiding bias is negligible (\citealt{lobos}).}

\todo{Saturating the Cram\'{e}r-Rao lower bound in estimating the centroids of stars however, is limited
by the lack of knowledge about the exact shape of the PSF and presence of noise. There are many sources of noise such as the CCD readout noise, sky noise, errors resulting from 
incorrect flatfield corrections, and photon noise from the astronomical object itself. 
In this study, we limit our investigation to the simulated images that contain non-overlapping faint sources that are sky-limited.}

\todo{We focus the scope of this investigation to sky-limited images for which the sky level has been subtracted. Furthermore, we assume that any instrument gain has been calibrated out and that the 
simulated images are free of any contamination by cosmic rays, stray light from neighboring fields, or 
any other type of defect in real images. We expect these defects to move the centroiding errors further from the fundamental bound. We intend to investigate whether fast centroiding estimates can saturate the bound in a realistic range of low signal-to-noise ratio images that are sky-limited.}

Given an analytic expression for the PSF model adopted in this study,
we derive an expression for the fundamental lower bound on the centroiding error as
a function of the parameters of the PSF model (e.g. PSF size),
and signal-to-noise-ratio of stars. We create two sets of simulations for which we can 
compute the CRLB, one with variable signal-to-noise ratio and constant full width at half maximum (FWHM), and one 
with variable FWHM and constant signal-to-noise ratio. After applying
different centroiding methods to the simulations, we investigate how close 
these methods can get to saturating the CRLB for various ranges of background 
Gaussian noise level and PSF FWHM.

In this work, we focus on four centroiding methods. \todo{The first method is the maximum-likelihood 
estimator which involves fitting a PSF profile, assuming that we have a good PSF estimate, to the star.} 
The second method estimates the centroid of a star by fitting a 2d second-order polynomial to 
the 3$\times$3 patch around the brightest pixel of the image after convolution with the PSF. 
The third method centroids stars by
 smoothing the image of stars by a Gaussian kernel of a fixed size,
 and then applying the same 3$\times$3 polynomial trick to the smooth
 image. This method is fast and does not require any knowledge of the 
PSF. The last method we consider, is a center-of-light centroiding 
(measurement of a first moment), applied to the 7$\times$7 patch around the brightest pixel of the image.

This paper is structured as follows. In Section \ref{sec:CRLB},
we discuss the Cram\'{e}r-Rao lower bound and derive
an analytic expression for the lower bound on the centroiding error
of the simulated data. 
In Section \ref{sec:method} we give a brief overview of 
centroiding methods used in our investigation.
In Section \ref{sec:data} we discuss the Cram\'{e}r-Rao lower bound saturation
tests and their corresponding simulated data.
In Section \ref{sec:result}, we compare the performances of the methods
discussed in Section \ref{sec:method} with the CRLB derived in Section \ref{sec:CRLB}. Finally, we discuss and conclude in Section \ref{sec:discussion}.

%%%%%%%%%%%%%%%%%%%%Cram\'{e}r-Rao lower Bound %%%%%%%%%%%%%%

\section{The Cram\'{e}r-Rao lower bound}\label{sec:CRLB}

The Cram\'{e}r-Rao lower bound sets a limit, in some sense, on how well a measurement 
can be made in noisy data.  The bound can only be computed in the context of a 
generative model, or a probabilistic forward model of the data. That is, we can 
only compute the CRLB in the context of assumptions about the properties of the data. 
However, it makes sense for us to use centroiding methods that saturate the CRLB under 
some reasonable assumptions, even if we find that those assumptions are not strictly correct in real situations.
The closer an estimator is to saturating the CRLB, the more information about the quantity that we 
need to estimate is preserved. The closer the root-mean-squared-error (RMSE) of a given estimator is to the bound,  
the more optimal---in terms of preserving the information---the estimator is.

The Cram\'{e}r-Rao inequality \citep{crlb} sets a lower bound on the 
root-mean-squared error of unbiased estimators. The CRLB is given by the square-root of the inverse of 
the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB, it is sufficient to compute the Fisher matrix. 
This computation relies on a set of assumptions:

\begin{itemize}
%  \item Known, constant model observable with known dependence on the model parameters. 
%        In this work the model observables are the presumed known Moffat PSF profiles, 
%        and the model parameters are the centroids. 
  \item \todo{Known PSF model. In this work the presumed model is the Moffat PSF profile.}
  \item Known, stationary noise process. In the context of centroiding stars, this is equivalent to 
        having background limited noise from sky background and CCD readout noise.
  \item \todo{Images are calibrated correctly. Flat-field is correctly calibrated.}       
  \item Uncorrelated Gaussian noise with no outliers. 
\end{itemize}

%\todo{HOGG HELP: can you read the following paragraph and see whether it makes sense or not?}

\todo{Note that in this study, we explicitly focus on sky-limited images. In the sky-limited images, the contribution 
to the Poisson pixel noise is largely dominated by the sky rather than the objects. In sky-limited images, when the number of photons per pixel is large, the Poisson noise can be approximated by a Gaussian distribution. Therefore, the Gaussian noise assumption is only an approximation to the Poisson noise. This is a good approximation for a large set of astronomical images.}

\todo{A number of factors can produce correlation between pixels. These include detector imperfection, saturation, and post-processing of images such as smoothing, rotating, and shifting the images. In raw unsaturated images, pixel noise is close to uncorrelated. Instrument gain can introduce heteroscedasticity. In that case, the noise variance varies between pixels. In an upcoming publication on the inference of the HST WFC3-IR channel PSF (Vakili, Fadely, Hogg in preparation), we discuss proper treatment of centroiding in the presence of gain. For simplicity, we assume that per-pixel uncertainty remains constant across all pixels.}

%After subtraction of the 
%sky background level, distribution of the Poisson pixel noise can be approximated by a Gaussian %distribution with 
%zero mean. \todo{Also mention in the discussion: The assumption of uncorrelated Gaussian noise is only %an approximation 
%to a Poisson distribution which has broader tails than what we expect from a Gaussian!} 
%\todo{HOGG HELP: can you write a few words about uncorrelated noise?}

Let us assume that there are $M$ observables $\mathbf{f} = (f_{1}, ... , f_{M})$, each
related to $B$ model parameters $\boldsymbol{\mathbf{\theta}} = (\theta_{1} , ... , \theta_{B})$ 
\beq
f_{m} = f_{m}(\theta_{1} , ... , \theta_{B}).
\label{genmodel}
\eeq

Assuming uncorrelated Gaussian error with variance $\sigma^{2}_{m}$ for each observable $f_{m}$, elements
of the $B\times B$ Fisher matrix $\mathcal{F}_{ij}$ are given by
\beq
\mathcal{F}_{ij} = \sum_{m=1}^{M}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
\label{fisher}
\eeq
%Let us assume that, for each parameter $\theta_{i}$, there exists a set of 
%asymptotically unbiased estimators $\{\hat{\theta}_{i}\}$. 
Let us assume that we have computed the root-mean-squared error on the parameter $\theta_{i}$ arising from applying an estimator to a large number of data. The Cram\'{e}r-Rao inequality states that this root-mean-squared error is greater than or equal to the $i$-th diagonal element of the inverse of the Fisher information matrix:
\beq
%\text{RMSE}[\{\hat{\theta_{i}}\}] \geq \sqrt{[\mathcal{F}^{-1}]_{ii}},
\text{RMSE} \geq \sqrt{[\mathcal{F}^{-1}]_{ii}},
\label{inequality}
\eeq
where the left hand side of the inequality is called the Cram\'{e}r-Rao bound on 
the root-mean-squared error of estimating the parameter $\theta_{i}$. Note that 
the bound is computed assuming that the model (equation~\ref{genmodel}) generating the data 
is known, and that uncertainties are given by additive uncorrelated Gaussian noise.

Based on Cram\'{e}r-Rao inequality (\ref{inequality}), \citet{crlb} defines efficiency of optimal estimators as the ratio of the CRLB and the root-mean-squared-error such that the maximum efficiency 
achievable by an estimator is unity. The closer the RMSE to the CRLB, 
the more information about the parameter of interest is preserved, and thus the more efficient the estimator is.

Let us consider the case of a maximum likelihood estimate $\boldsymbol{\mathbf{\theta}}_{\text{ML}}$, 
where the likelihood function corresponds to the same generative assumptions that we used to compute the CRLB.

\begin{eqnarray}
\boldsymbol{\mathbf{\theta}}_{\text{ML}} &=& \argmax \mathcal{L}, \\
-2\ln \mathcal{L} &=& \sum_{m}\frac{1}{\sigma_{m}^{2}}( y_{m} - f_{m}(\boldsymbol{\mathbf{\theta}}))^{2}, \\
\end{eqnarray}
where $y_{m}$ is the $m$th component of the observed data $\mathbf{y}$
\beq
\mathbf{y} = \mathbf{f}(\boldsymbol{\mathbf{\theta}}_{\text{true}}) + \mathbf{n}.
\eeq

Maximum likelihood estimators can achieve maximum efficiency. \todo{That is, when a maximum likelihood %estimators are applied to a large number of data, the RMSE is greater than or equal to the CRLB (see
estimator is applied to a large number of data and RMSE is computed, the RMSE approaches the CRLB (see
\citealt{crlb}; \citealt{lecam} for proof) in which case the CRLB is saturated.} \todo{Therefore, we want to investigate the conditions under which the RMSE arising from a given fast centroiding method is close to the CRLB, or whether it can saturate the CRLB.}

In this investigation, the model observables for the noisy data are the pixel-convolved PSF (PSF profile evaluated at different pixel locations), and  
the model parameters under consideration are the centroid coordinates. Therefore, $\mathcal{F}$
is a 2$\times$2 matrix whose elements are given by

\beq
  \mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma^{2}}
                \frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}},
\label{fish}
\eeq
where the summation is over pixels, $f_{m}$ is the value of the PSF at pixel location $m$,
$\theta=\{x_{c},y_{c}\}$, and $\sigma^{2}$ is variance of the uncorrelated Gaussian noise map $n(\mathbf{x}_{m})$
\begin{eqnarray}
\mathbb{E}[n(\mathbf{x}_{m})] &=& 0, \\
\mathbb{E}[n(\mathbf{x}_{m})n(\mathbf{x}_{m^{\prime}})] &=& \sigma^{2}\delta_{m,m^{\prime}}. 
\end{eqnarray}

Derivation of an explicit expression for the Fisher matrix $\mathcal{F}$ requires 
specifying a presumed correct PSF model.
We use the Moffat profile \citep{moffat} for our PSF simulations. 
The Moffat profile is an analytic model for stellar PSFs. It has broader wings than
a simple Gaussian profile. The surface brightness of the Moffat profile is given by
\beq
I(r) = \frac{F(\beta -1)}{\pi \alpha^{2}}[1+(r/\alpha)^{2}]^{-\beta},
\label{mof}
\eeq
where $F$ is the total flux, $\beta$ is a dimensionless parameter, and $\alpha$ is
the scale radius of the Moffat profile, with FWHM (hereafter denoted by $\gamma$)
being $2\alpha\sqrt{2^{1/\beta}-1}$. \todo{The Moffat PSF profile has been used in the PSF modeling required for weak lensing galaxy shape measurements (see \citealt{im3shape,im3shape_code}). It has also been used as one of the methods for generation of the PSF in simulation of images needed for weak lensing systematic studies (\citealt{galsim}).}
At a fixed $\gamma$, Moffat profiles with lower values
of $\beta$ have broader tails. It is also important to note that for sufficiently large values of the 
parameter $\beta$, the Moffat PSF becomes arbitrarily close to a simple Gaussian PSF.

\todo{Note that in our data generation, we simulate images (in the pixel space) that are Nyquist-sampled or close to Nyquist-sampled. All pixels in the images are identical, and the stars are simulated 
by sampling from the pixel-convolved PSF. In well-sampled images, the center of 
the pixel-convolved PSF must be very close to the center of the optical PSF.}

In order to investigate the performance of centroiding methods for
 different background noise levels and different
values of the parameter $\gamma$, simulation of a large number of images of stars---for which the exact positions of centroids
and their corresponding lower bounds are known---is required.

Given the PSF model (\ref{mof}), an expression for the CRLB as a function of the size, and SNR of stars can be 
derived. For further simplicity, the flux of all stars in our simulations are set to unity and per-pixel 
uncertainties are assumed to be uncorrelated Gaussian.

Moreover, it is more convenient to work with the signal-to-noise ratio
(SNR) instead of the variance of the Gaussian noise.
We use the definition of SNR according to which SNR is given by the ratio
 of the mean and variance of the distribution
which the flux estimator is drawn from. Let us assume that the total flux from
the point source is $F$, and that the sub-pixel shifted PSF at the $i$-th pixel is given
by $P_{i}$. Therefore, the brightness of the $i$-th pixel $y_{i}$ is drawn from
a Gaussian distribution 
\beq
p(y_{i}) = \mathcal{N}(FP_{i},\sigma^{2}). 
\eeq

The optimal estimator of flux is the matched-filter flux estimator 
$\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
\beq
p(\tilde{F}) = \mathcal{N}(F , \frac{\sigma^{2}}{\sum_{i}P_{i}^{2}}),
\eeq  
which leads us to
\beq
\begin{array}{l}
\text{SNR} = \frac{F\sqrt{\sum_{i} P_{i}^{2}}}{\sigma}.
\end{array}
\label{snr}
\eeq

 In the case of Moffat profiles (\ref{mof}) with total flux of stars set to unity, 
the SNR given in (\ref{snr}) can be analytically 
expressed in terms of the per pixel uncertainty
$\sigma$, FWHM $\gamma$, and also $\beta$, \todo{the dimensionless parameter of (\ref{mof})}
\beq
\text{SNR} = \frac{2(\beta-1)(2^{1/\beta}-1)^{1/2}}{\pi^{1/2}(2\beta-1)^{1/2}}\frac{1}{\sigma \gamma}.
\label{snr2}
\eeq

Equation (\ref{snr2}) implies that at a fixed $\gamma$ and background Gaussian noise 
with variance $\sigma^{2}$, stars with broader tails (lower $\beta$) have lower SNR.
On the other hand, stars with higher $\beta$ have higher SNR. 
For sufficiently large $\beta$---where the PSF can be
approximated by Gaussian profile---SNR is approximately given by $0.664/(\sigma\gamma)$.
Furthermore, at a fixed $\beta$ and variance of the background noise $\sigma^{2}$,
observed stars with higher $\gamma$ have lower SNR.

Throughout this investigation, $\beta$ is held fixed at the fiducial value of $\beta=$ 2.5, where SNR
is given by the following expression
\beq
\text{SNR} \simeq \frac{0.478}{\sigma \gamma}\;\;\; \mathrm{for}\;\;\; \beta = 2.5.
\eeq

Given the analytic expression for the Moffat PSF model (\ref{mof}), and choice of $\beta=2.5$, 
the inverse of the Fisher matrix is given by
\beq
  \mathcal{F}^{-1} \simeq \Big(0.685 \frac{\gamma}{\text{SNR}}\Big)^{2} 
  \begin{pmatrix}
      1 & 0\\
      0 & 1\\
  \end{pmatrix}.
\label{crlbmoffat}
\eeq

Equation (\ref{crlbmoffat}) implies that at given SNR and $\gamma$,
CRLB for each component of centroid is approximately given by $0.685\gamma/\text{SNR}$,
and that a good centroiding technique delivers centroids with
root-mean-squared-error close to this.

It is worth noting that for any PSF model whose radial light profile is some function of 
$r/\gamma$, CRLB has the same functional form, in that it is proportional to the ratio
between $\gamma$ and the SNR. 
For PSF profiles with shorter tails (e.g., Gaussian), the prefactor of 0.685 in (\ref{crlbmoffat})
becomes smaller. In the particular case of Gaussian PSF, the prefactor is approximately 0.6.

\section{Centroiding methods}\label{sec:method}

\todo{In this section, we briefly discuss the approximate and the non-approximate centroiding methods considered in this 
study. The first two methods require knowledge of the PSF at the positions of stars. That is, the shape and the size of the PSF are known and the only unknown variables are the coordinates of the centroids of stars. 
Note that in practice however, size and shape of the PSF are also estimated along with the centroid. In the following, we assume that the size and shape of the PSF are known. For the last two methods, we do not use any information about the PSF.}

\todo{\subsection{Centroiding by fitting a correct PSF profile}}

We examine fitting an exact PSF profile to the stars. That is, 
in our Cram\'{e}r-Rao bound saturation tests, we find the best
estimates of flux and centroid by maximizing the likelihood using 
the correct PSF model. \todo{In the model, the size of the Moffat PSF is 
assumed to be correct.} We expect this method to perform best in 
determining the centroids of stars, and deliver RMSE equal to 
Cram\'{e}r-Rao bound.

\todo{\subsection{Matched-filter polynomial centroiding}}

Let us consider the case in which we have a good estimate of the pixel-convolved PSF at
the position of the faint star under consideration. 
We can smooth the image of the star, by correlating it with the 
full PSF $\mathcal{P}$ at the position of the star.
\begin{eqnarray}
Y^{(s)} &=& Y \star \mathcal{P}, \\
Y^{(s)}_{[i,j]} &=& \sum_{k,l}Y_{[i-k,j-l]}\mathcal{P}_{[k,l]},
\end{eqnarray}
where $Y$ is the image of the star, and $Y^{(s)}$ is sometimes called a matched filter. 
A matched filter is a method in which the data $Y$ is correlated (convolved in the 
case of symmetrical PSF) with the PSF $\mathcal{P}$. It is equivalent to optimizing the 
likelihood and therefore provides an optimal map 
where the peak of the map is the likely position of the 
point source (Lang \emph{et al.}, in preparation).

Then, we fit a simple 2d second-order polynomial 
$P(x,y)=a+bx+cy+dx^2+exy+fy^2$ 
to the 3$\times$3 patch centered on the brightest pixel of the
matched-filter image $Y^{s}$.
Upon constructing a universal 9$\times$6 design matrix
\begin{equation}
    \mathbf{A} = 
    \begin{bmatrix}
        1 & x_{1} & y_{1} & x_{1}^{2} & x_{1}y_{1} & y_{1}^{2} \\
        . & . & . & . & . & .  \\
        . & . & . & . & . & .  \\
        . & . & . & . & . & .  \\
        1 & x_{9} & y_{9} & x_{9}^{2} & x_{9}y_{9} & y_{9}^{2}
    \end{bmatrix},
\end{equation}
the free parameters $\{a,b,c,d,e,f\}$
(hereafter compactly denoted by $\mathbf{X}$) can be determined by 
\beq
\mathbf{X} = (\mathbf{A}^{T}\mathbf{A})^{-1}\mathbf{A}^{T}\mathbf{Z},
\label{linearfit}
\eeq
where $\mathbf{Z}$ is given by $(z_{1},...,z_{9})^{T}$,
with $z_{i}$ being the brightness of the $i-$th pixel of the 3$\times$3 patch centered on the brightest pixel of $Y^{(s)}$.
Afterwards, the best fit parameters can be used to compute the centroid coordinate

\beq
  \begin{bmatrix}
      x_{c}\\
      y_{c}\\
  \end{bmatrix} = 
  \begin{bmatrix}
      2d & e\\
      e & 2f\\
  \end{bmatrix}^{-1}
  \begin{bmatrix}
      -b\\
      -c\\
  \end{bmatrix}.
\label{center}
\eeq

It is important to note that the algebraic operation in (\ref{center}) involves 
inverting a 2$\times$2 curvature matrix
\beq
  D = 
  \begin{bmatrix}
      2d & e\\
      e & 2f\\
  \end{bmatrix}.
\eeq

When the curvature matrix $D$ has a zero (or very close to zero) determinant,
centroid estimates obtained from equation (\ref{center}) can become arbitrarily 
large, which leads to catastrophic outliers. 
In order to tackle this issue, we add a soft regularization term
proportional to $\sigma$ to the diagonals of $D$ prior to inversion.

The procedure of convolving the image of star with the PSF results in a
smoother image. Therefore, a simple second-order polynomial will provide a better fit 
since convolution with the PSF makes the variation of the brightness of the image 
across the 3$\times$3 patch very smooth.

%We should nonlinearly optimize a PSF to saturate the bound.
%But because optimization is done through a chi-squared fitting, 
%this is equivalent to optimizing a matched filter. 
%And if the image is well sampled (in the PSF-convolved image) this
%is equivalent to interpolating a matched filter on a grid. 
%Therefore we expect the matched filter centroiding method to 
%saturate the bound in cases where the image is well sampled.

\todo{\subsection{Fixed-Gaussian polynomial centroiding}}
In the case that we do not know the PSF at the position of star, we change 
the smoothing step in the following way. Instead of smoothing the image 
by convolving it with the PSF, smoothing is done by convolving the image 
with a \todo{fixed Gaussian kernel with a fixed size} 
\beq
k(\mathbf{x}) = \frac{1}{2\pi w^2}\exp(-\mathbf{x}^{2}/2w^{2}),
\label{eq:gauss}
\eeq
where throughout this study, the full-width at half-maximum of the Gaussian kernel is held at
a fixed value of 2.8 pixels (corresponding to $w \simeq$ 1.2 pixels). The smoothing step is done as follows
\begin{eqnarray}
Y^{(s)} &=& Y \star \mathcal{K}, \\
Y^{(s)}_{[i,j]} &=& \sum_{k,l}Y_{[i-k,j-l]}\mathcal{K}_{[k,l]},
\end{eqnarray}
where $Y$ is the image of the star, $Y^{(s)}$ is the smooth image, \todo{and $\mathcal{K}$ is an
array whose elements are given by the Gaussian kernel}
\beq
\mathcal{K}_{[k,l]} = k(x_{k},y_{l}).
\eeq
\todo{Note that the size of the kernel $\mathcal{K}$ is equal to the size of the kernel $\mathcal{P}$ used in 
the matched-filter polynomial centroiding.} Then we apply the same 2d second-order polynomial method (see Eqs. \ref{linearfit}, \ref{center}) to the 3$\times$3 patch centered on the brightest
pixel of the smooth image $Y^{(s)}$. Therefore, for a given star and a smoothing kernel,
the outcome of equation \ref{linearfit} can be
plugged into equation \ref{center} to find the centroid estimate
of the star. This is inspired by the 3$\times$3 quartic approximation 
used in the \textsl{Sloan Digital Sky Surveys} photometric pipeline \citep{sdss}.

\todo{\subsection{Center-of-light centroiding}}
In addition to the fitting methods 
mentioned so far, we examine centroiding 
stars by computing their first moments
in a 7$\times$7 patch around the brightest pixel of the image.

\begin{eqnarray}
x_{c} &=& \frac{\sum_{m}x_{m}Y_{m}}{\sum_{m}Y_{m}}, \\
y_{c} &=& \frac{\sum_{m}y_{m}Y_{m}}{\sum_{m}Y_{m}},
\end{eqnarray}
where the summation is done over all the pixels of the 7$\times$7 patch, and $x_{m}$, 
$y_{m}$, and $Y_{m}$, are the $x$ coordinate, $y$ coordinate, and the brightness
of pixel $m$ respectively.

In terms of saturating the Cram\'{e}r-Rao lower bound, we expect this simple 
center-of-light centroiding to perform worse than all other methods mentioned in 
this section. Hereafter, we call this method $7\times7$ moment centroiding.

\section{Tests}\label{sec:data}

We perform two sets of simulations. In the first set, we choose four values of
2, 2.8, 4, and 5.6 pixels for $\gamma$. For each $\gamma$, we generate 100,000 
17 $\times$ 17 postage-stamps of Moffat profiles with centroids randomly drawn
within the central pixel of the 17 $\times$ 17 postage-stamps. Moreover, zero-mean 
uncorrelated Gaussian noise is added to each postage-stamp such that the simulated 
stars are uniformly distributed in log-SNR between SNR = 5 to SNR = 100.

In the second set, we generate 100,000 17$\times$17 postage-stamps
of Moffat profile, with values of $\gamma$ uniformly distributed 
between 2 and 6 pixels, and with centroids drawn randomly within 
the central pixel. We choose four values for SNR: 5, 10, 20, and 40. 
For each SNR, and for each postage-stamp with a given $\gamma$, 
zero-mean uncorrelated Gaussian noise, with standard deviation corresponding 
to SNR and $\gamma$ through equation (\ref{snr2}), is added to each postage-stamp.

In the first experiment, we study how the centroiding error behaves with changing
SNR, while $\gamma$ is held constant. In the second experiment, we study 
how the centroiding error behaves with changing $\gamma$ while SNR is held constant.

\section{Results}\label{sec:result}

\todo{\subsection{Experiment 1 : variable SNR; constant $\gamma$}}

In this experiment, after finding the centroiding errors for each method,
we compute the RMSE in bins of SNR in order to compare it to the CRLB. 
Results of the first experiment are shown in Figures~\ref{1},~\ref{2},~\ref{3},~\ref{4}. \todo{Note that the centroid errors, the CRLB, and the RMSE values shown in these figures are computed for only one component. As we expected, the RMSE from centroiding by fitting the exact PSF model (Figure~\ref{1}) lies on the CRLB.}

%except for simulations with SNR $\la$ 10 where the RMSE gets slightly pulled away
%from the CRLB due to presence of a few outliers. 
\todo{Figure~\ref{2} demonstrates that even the matched filter polynomial centroiding is able deliver centroiding estimates as efficient as the PSF fitting method in terms of saturating the bound for the simulated stars with $\gamma = 2.8, 4, 5.6$ pixels. For stars with $\gamma$ = 2 pixels, although this method gets very close to saturating the CRLB, the RMSE arising from this method shows slight deviations from the CRLB since the images of stars are not sufficiently smooth even after correlation of these images with the PSF. For simulated images with higher $\gamma$, convolving the data with the PSF results in images that are smooth around the brightest pixel. This enables the polynomial centroiding to deliver estimates that can saturate the CRLB.}

\todo{The RMSE from the fixed-Gaussian polynomial centroiding (Figure~\ref{3}),
is very close to the CRLB. As we increase $\gamma$ from 2 pixels to 2.8 pixels, RMSE approaches the CRLB. For stars with $\gamma$ = 2 pixels, the rate at which the RMSE from this method drops
eventually becomes smaller than the constant rate at which the CRLB
decreases with increasing SNR. The reason for this is that even after smoothing
the data with a Gaussian kernel, the images are not smooth enough
for a second-order polynomial fitting to deliver estimates with RMSE close to the bound. For stars with $\gamma$ = 2.8 pixels, a significant fraction of information is in the 3$\times$3 patch of the smooth image and this method is able to saturate the bound. When we increase $\gamma$ to 4 and 5.6 pixels, the mismatch between the width of the Gaussian kernel and the PSF increases and the RMSE deviates from the CRLB. The deviation is largest for the simulated stars with $\gamma$ = 5.6 pixels.}

\todo{On the other hand, Figure~\ref{4} shows that in case of 7$\times$7 moment method, the RMSE becomes quite large as we move toward fainter stars in our simulation.
For stars with larger $\gamma$, centroid estimates from the naive center-of-light 
centroiding do not even come close to saturating the CRLB. As $\gamma$ increases, the 
RMSE deviates further from the CRLB.}

\todo{\subsection{Experiment 2 : constant SNR; variable $\gamma$}}

In this experiment, after finding the centroiding errors for each method, we
compute the RMSE in bins of $\gamma$ in order to compare it to the CRLB. 
Behavior of error as a function of $\gamma$ for different values of SNR,
is shown in Figures~\ref{5},~\ref{6},~\ref{7}, and~\ref{8}. \todo{Note that the centroid errors, the CRLB, and the RMSE values shown in these figures are computed for only one component.}

Once again, the RMSE from centroiding by fitting the exact PSF model as a function of FWHM lies on the CRLB (see Figure~\ref{5}). 
Thus, centroid estimates from fitting the exact PSF model always saturate the CRLB. Once again, we observe that the centroid estimates found by the matched-filter polynomial centroiding saturate the CRLB with the
exception of simulated stars with $\gamma$ very close to 2 pixels (see Figure~\ref{6}).

Figure~\ref{7} illustrates that the \todo{fixed-Gaussian} polynomial method results in RMSE very close to the CRLB. For all four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels, the RMSE gets closer to the CRLB since the method starts to perform
slightly better as we move away from undersampled stars and as the FWHM of the smoothing kernel gets closer to that of the simulated images.
After approximately 3 pixels, increasing $\gamma$ results in deviation of the RMSE of the method from the CRLB. \todo{This is a characteristic of the fixed-Gaussian polynomial method as we apply it to a smooth image in which some fraction of the available information is lost in the 3$\times$3 patch around the brightest pixel.} Furthermore, increasing the SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) closer to the CRLB. 
\todo{In the case of extremely faint stars (SNR = 5), the fixed-Gaussian polynomial centroiding fails to saturate the bound.}

The centroid estimates obtained from the naive 7$\times$7 moment method (see Figure ~\ref{8}) result in RMSE much larger than the CRLB in all ranges of FWHM and for all four values of SNR in this experiment.

\section{Discussion}\label{sec:discussion}

An efficient stellar centroiding algorithm must saturate---or come close to saturating---the fundamental 
Cram\'{e}r-Rao lower bound. That is, in all ranges of background noise level, size, radial light profile,
and shape, it must preserve information about the centroids of stars. In practice however,
this is only achievable when we have a reasonably good estimate of the PSF. Since we do not always 
know the exact PSF profile, we must make use of approximate centroiding algorithms. \todo{In this work, we
studied how close we get to saturating the CRLB with approximate methods acting on relatively low 
signal-to-noise ratio unsaturated stars.}

We focused on examples from two classes of centroiding algorithms. The first class contains fast and approximate
methods that do not require any knowledge of the PSF at the positions of stars. Of methods that belong to this class,
we consider centroiding stars based on fitting a second-order
polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel of fixed width, and finding the center of light 
of a 7$\times$7 patch around the brightest pixel of the star.

\todo{The second class of centroiding algorithms make use of the PSF (or some good estimate of the PSF)
at the positions of stars. In our investigation, it is assumed that the size and the shape of the PSF are known prior to applying these algorithms to the images of stars.} We considered two examples from this class. The first example is the matched filter polynomial centroiding, and the
second example is the PSF fitting. \todo{In the PSF fitting method, we find the maximum likelihood estimates of the flux and centroids of stars by fitting a PSF model that has the correct shape and size.}

%The second class of centroiding algorithms contains methods that require knowledge of the PSF (or %having a good estimate
%of the PSF) at the positions of stars. We considered two examples from this class. The first example
%is the matched-filter polynomial centroiding, and the
%second example is the full PSF profile fitting. In terms of saturating the Cram\'{e}r-Rao bound, we %compared the performances of these methods against each other.

\todo{In terms of saturating the Cram\'{e}r-Rao bound, we compared the performances of these methods against each other. Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
centroid estimates that saturate the CRLB. This confirms our expectation that maximum-likelihood estimators saturate the Cram\'{e}r-Rao lower bound.}

\todo{We note that the estimates found by the 7$\times$7 moment method, except in the case of
very high SNR values and small values of $\gamma$, do not come close to
saturating the CRLB. In a considerable range of PSF sizes and background noise levels, 
this method fails to deliver any centroiding estimate close to saturating the bound. When applied to stars with $\gamma = 2.8, \; 4$ pixels, we find deviation of RMSE from the CRLB as large as $600\%-800\%$ below signal-to-noise ratio of 10. For the simulated stars with $\gamma = 5.6$ pixels, we find deviations as large as $500 \%$ for SNR below 10 and as large as $200 \%$ for SNR $\sim$ 100. It can be noted in Figure~\ref{8} that in the simulations with the lowest SNR (SNR $\sim$ 5), the errors arising from the 7$\times$7 moment method are suppressed by the fact that 17$\times$17 postage-stamps are used to simulate images. Therefore in the case of SNR $\sim$ 5, we expect the deviation of the RMSE from the CRLB to be larger for this method.}

\todo{On the other hand, the RMSE of centroid estimates of the fixed-Gaussian polynomial centroiding are much closer to saturating the CRLB in all ranges of signal-to-noise ratio even though this method does not require knowledge of the PSF at the positions of stars. We note that when the FWHM of the stars are close to 2.8 pixels (the FWHM of the Gaussian kernel), the fixed-Gaussian polynomial method saturates the CRLB. Deviation of the RMSE of this method from the CRLB is larger for the simulated stars with larger values of FWHM ($\gamma \simeq 5$ pixels). Presence of noise is another limiting factor.
Although this method is able to get very close to saturating the bound in a wide range of
signal-to-noise ratios, it is not reliable in the case of centroiding extremely faint stars ($5<\mathrm{S/N}<10$).}
%This is partly due to the fact that in the presence of noise, 
%the brightest pixel of image does not necessarily contain the centroid of stars even %after smoothing 
%the image.

%The fixed-Gaussian polynomial centroiding technique only takes advantage of the information 
%contained in a 3$\times$3 patch centered on the brightest pixel of the smoothed image which is only 
%well-sampled when the FWHM of the simulated image of star 
%matches that of the smoothing kernel. Thus, when we apply 
%this method to find the centroids of stars with larger FWHM, a certain amount of
%information (encoded in the Cram\'{e}r-Rao lower bound) is lost, and therefore the RMSE
%of these methods deviates from the CRLB. This deviation becomes larger at lower
%signal-to-noise ratios. Besides, the performance of this method slightly degrades
%in the case of undersampled stars (with FWHM close two 2 pixels).

\todo{In matched-filter polynomial centroiding, the fixed-Gaussian polynomial method is modified by convolving the image with the correct PSF. Our results on the simulated stars show that the matched-filter estimator saturates the CRLB for all PSF sizes and noise levels.  
This is due to the fact that once the images of stars are convolved with the correct PSF, they become smooth that fitting a second-order polynomial to the 3$\times$3 patch centered on the brightest pixel of the smooth image is sufficient for us to obtain results as accurate as those from fitting a PSF profile.}

\todo{The Gaussian kernel (see equation \ref{eq:gauss}) in the fixed-Gaussian polynomial centroiding is separable, and correlation of the kernel with an image of star can be performed \emph{exactly} in no time. Therefore in terms of computational cost, this method is more efficient than the matched-filter method in which the image of star is correlated with a PSF of arbitrary shape.}

\todo{In the case that we have a good estimate of the PSF, the matched-filter polynomial method can be faster than PSF fitting method for \emph{centroiding} \emph{purposes}. Additionally, this method is able to saturate the CRLB in a wide range of conditions. It is however important to note that in many cases, reliable estimation of the flux requires a technique as accurate as PSF fitting. However, in cases in which an investigator only needs an empirical estimates of the centroid offsets, fixed-Gaussian polynomial or matched-filter polynomial centroiding methods can be employed with negligible loss of information. For instance in modeling the stellar light curves in the \emph{K2} mission, \citet{dfm} uses a simple polynomial centroiding to marginalize out the systematic trends caused by centroid offsets.}

%However, this method has its own disadvantages. First, we do not %always know the the exact PSF. Second, finding 
%the centroid by profile fitting is computationally expensive, %whereas employing any of the 3$\times$3 polynomial techniques %considered in this study in large scale astronomical surveys %reduces the computational cost of initial astrometry of the %point sources considerably.

\todo{Moreover, we note that the PSF fitting method can be made faster by only keeping the term proportional to the dot product of the PSF model and the image in $\chi^2$:
\beq
\chi^{2} = \big(\mathbf{y} \cdot \mathbf{y} -2F\mathbf{y} \cdot \mathbf{m} + F^{2}\mathbf{m} \cdot \mathbf{m}\big)/\sigma^{2},
\eeq
where $F$ is the flux, $\sigma$ is the per-pixel uncertainty, the dot product between two vectors is denoted by $(\cdot)$, and the image of star and the normalized shifted PSF model are denoted by $\mathbf{y}$ and $\mathbf{m}$ respectively. Upon varying only the centroid, the terms $\mathbf{y}.\mathbf{y}$ and $\mathbf{m}.\mathbf{m}$ remain approximately constant. However, this only allows us to vary the position of centroid, and not the flux, while fitting the PSF model to the star.}

Finding a centroid coordinate that maximizes the dot product of the PSF and the star image is equivalent to finding the peak of the correlation of the PSF and the image. Therefore optimizing the modified $\chi^2$ is equivalent to finding the location of the peak of the matched filter.

\todo{In the initial smoothing step of the fixed-Gaussian polynomial method, the image of the star is correlated with an approximate Gaussian PSF.} When there is mismatch between the widths of the smoothing kernel and the that of the PSF, we loose some information by employing a 3$\times$3 polynomial fitting. When we have the advantage of knowing the PSF, this issue can be resolved by employing the matched-filter polynomial method.

\todo{In this investigation we showed that PSF fitting always performs better---in terms of saturating the CRLB---at centroiding stars.} Having a reasonable PSF model always helps us obtain more reliable centroid estimates, but over a certain range of low signal-to-noise ratios and PSF sizes, one can achieve sensibly accurate results by employing a simple 3$\times$3 method after smoothing the image with a Gaussian kernel of a fixed width, and without making any assumption about the PSF model at the positions of stars.

In this investigation we narrowed our focus on a set of data simulated from a particular PSF profile. Although there are various cases where Moffat profiles provide reasonable representations of the point spread function, these profiles are not generic enough to let us reach a more general conclusion.

\acknowledgments

Acknowledgments: we thank Jo~Bovy, Robert~Lupton, Michael~Blanton, Dustin~Lang, and Alex~Malz for discussions related to this work. 
We appreciate the comments by the anonymous referee.
We are also grateful to Dustin~Lang and Alex~Malz for reading 
and commenting on the earlier version of this manuscript.

This work was partially supported by the NSF (grants IIS-1124794 and AST-1517237), NASA (grant NNX12AI50G), and the Moore-Sloan Data Science Environment at NYU.

\bibliographystyle{yahapj}
\bibliography{references}

%%%%%%%%%%%%%%%% FIGURES %%%%%%%%%%%%%%
\clearpage

\begin{figure*}[p]~\\
\begin{center}
%\minipage{.8\textwidth}
\includegraphics[width=0.85\linewidth]{new_psf.pdf}
%\endminipage
\caption{\todo{Scatter plots showing the relation between the ratio of error (in x-axis of the centroid positions) to the CRLB and the signal-to-noise ratio of stars. 
Errors are found from fitting the exact PSF model to the stars,
with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right)
pixels. In each scatter plot, the blue solid line represents the ratio of the root-mean-squared-error to the CRLB, and the red line represents the ratio achievable by an optimal estimator.}}\label{1}
\end{center}
\end{figure*}

\begin{figure*}[p]~\\
\begin{center}
 \includegraphics[width=0.85\linewidth]{new_matchedfilter.pdf}
%\endminipage
 \caption{\todo{Scatter plots showing the relation between the ratio of error (in x-axis of the centroid positions) to the CRLB and the signal-to-noise ratio of stars. 
Errors are found from applying the matched filter polynomial centroiding to the stars,
with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue solid line represents the ratio of the root-mean-squared-error to the CRLB, and the red line represents the ratio achievable by an optimal estimator.}}\label{2}
\end{center}
\end{figure*}

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=0.85\linewidth]{new_polynomial.pdf}
%\endminipage 
\caption{\todo{Scatter plots showing the relation between the ratio of error (in x-axis of the centroid positions) to the CRLB and the signal-to-noise ratio of stars. 
Errors are found from applying the fixed-Gaussian polynomial centroiding to the stars,
with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue solid line represents the ratio of the root-mean-squared-error to the CRLB, and the red line represents the ratio achievable by an optimal estimator.}}\label{3}
\end{center}
\end{figure*}

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=0.85\linewidth]{new_moment.pdf}
\caption{\todo{Scatter plots showing the relation between the ratio of error (in x-axis of the centroid positions) to the CRLB and the signal-to-noise ratio of stars. 
Errors are found from applying the 7$\times$7 moment method to the stars,
with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue solid line represents the ratio of the root-mean-squared-error to the CRLB, and the red line represents the ratio achievable by an optimal estimator.}}\label{4}
\end{center}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FWHM PLOTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=0.65\linewidth]{new_fwhm_psf.pdf}
\caption{\todo{Scatter plots showing the relation between the ratio of error (in x-axis of the centroid positions) to the CRLB and the FWHM of stars.
Errors are found from fitting the exact PSF model to the stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue solid line represents the ratio of the root-mean-squared-error to the CRLB, and the red line represents the ratio achievable by an optimal estimator.}}\label{5}
\end{center}
\end{figure*}

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=0.65\linewidth]{new_fwhm_matchedfilter.pdf}
%\endminipage
\caption{\todo{Scatter plots showing the relation between the ratio of error (in x-axis of the centroid positions) to the CRLB and the FWHM of stars.
Errors are found from applying the matched filter polynomial centroiding to the stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue solid line represents the ratio of the root-mean-squared-error to the CRLB, and the red line represents the ratio achievable by an optimal estimator.}}\label{6}
\end{center}
\end{figure*}

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=0.65\linewidth]{new_fwhm_polynomial.pdf}
%\endminipage
\caption{\todo{Scatter plots showing the relation between the ratio of error (in x-axis of the centroid positions) to the CRLB and the FWHM of stars.
Errors are found from applying the fixed-Gaussian polynomial centroiding to the stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue solid line represents the ratio of the root-mean-squared-error to the CRLB, and the red line represents the ratio achievable by an optimal estimator.}}\label{7}
\end{center}
\end{figure*}

\begin{figure*}[p]~\\
\begin{center}
\includegraphics[width=0.65\linewidth]{new_fwhm_moment.pdf}
%\endminipage
\caption{\todo{Scatter plots showing the relation between the ratio of error (in x-axis of the centroid positions) to the CRLB and the FWHM of stars.
Errors are found from applying the 7$\times$7 moment method to the stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue solid line represents the ratio of the root-mean-squared-error to the CRLB, and the red line represents the ratio achievable by an optimal estimator.}}\label{8}
\end{center}
\end{figure*}

\end{document}

### 2017-06-14 ms/revision2/main.tex
generalizing the likelihood function in the second revision

--- 2017-05-31 ms/revision1/main.tex
@@
-\documentclass[twocolumn]{aastex61}
+\documentclass[onecolumn]{aastex61}
 \pdfoutput=1 %for arXiv submission
@@
 becomes smaller. In the particular case of Gaussian PSF, the prefactor is approximately 0.6.
+
+\section{Poisson likelihood}
+
+Now let us consider the case in which case the brightness of every pixel is determined by Poisson statistics. That is, the forward model for the brightness of $i$-th pixel $y_{i}$ is given by
+
+\beq
+y_{i} = g X_{i} + e_i,
+\eeq
+where $X_{i}$ is the number of photons arrived at the $i$-th pixel at a given time interval. This quantity is a random draw from a Poisson probability distribution 
+\beq
+X_{i} \sim \mathrm{Poissoin}(\lambda_{i}), 
+\eeq
+where $\lambda_{i}$ is the mean and standard deviation of the Poisson distribution.
+In other words, $\lambda_{i}$ is the expected value for the number of photons arrived at a given time interval at the $i$-th pixel and is given by
+\beq
+\lambda_{i} = fP_{i} + b_{i}.
+\eeq
+In this relation, $f$ is the flux of the star under consideration, $P_{i}$ is the pixel-convolved PSF, and $b_i$ is the background sky.
+Now let us derive the statistical properties of the number of photons accumulated in a time interval $(0,t)$ where $t=N\Delta t$.
+
+\subsection{Gaussian approximation in the limit of large number of photons}
+
+In the limit $N \rightarrow \infty$, the central limit theorem guarantees that the quantity $X_{i}(t) = \sum_{n=1}^{N} X_{i,n}$ is a random draw 
+from a Gaussian distribution with the mean $N\lambda_i$ and the variance $N\lambda_i$. Therefore, in the limit of a large number of photons, the quantity $y_{i}$ 
+is a draw from the following Gaussian distribution:
+
+\begin{eqnarray}
+y_{i} &\sim& \mathcal{N}(\mu_i , \sigma_i^2), \\
+\mu_i &=& N g (f_iP_i + b_i), \\
+\sigma_i^{2} &=& \sigma_{g}^{2} + N g (f_iP_i + b_i).
+\end{eqnarray}
+
+\subsection{Photon-dominated noise}
+
+Let us consider the situation in which the noise is dominated by the photons from the astronomical objects themselves. In this case, the likelihood is given by
+\beq
+\mathcal{L} \; = \; \prod_{i} p(y_{i}|m_i),
+\label{eq:poisson_likelihood}
+\eeq
+where 
+\begin{eqnarray}
+p(y_i|m_i) \; &=& \; \mathrm{Poisson}(m_i),\\
+m_i &=& g(fP_i+b_i).
+\end{eqnarray}
+
+It can be shown that with the choice of Poisson likelihood (Eq~\ref{eq:poisson_likelihood}) the inverse of the Fisher information matrix is given by
+
+\beq
+  \mathcal{F}^{-1} = \sum_i \frac{\Big(fgdP_{i}/dx_c\Big)^{2}}{fP_i + b_i} 
+  \begin{pmatrix}
+      1 & 0\\
+      0 & 1\\
+  \end{pmatrix}.
+\label{crlbmoffat}
+\eeq
 

### 2017-06-14 ms/revision2/main.tex
adding more words to Poisson likelihood

@@
 
-The optimal estimator of flux is the matched-filter flux estimator 
-$\tilde{F}=\sum_{i}y_{i}P_{i}$. It can be shown that 
+%The optimal estimator of flux is the matched-filter flux estimator 
+\todo{The optimal estimator of flux is proportional to the matched-filter flux
+$\tilde{F}=\sum_{i}y_{i}P_{i}/\sum_{i}P_{i}^{2}$.} It can be shown that 
 \beq
@@
 \label{crlbmoffat}
+\eeq
+
+The optimal estimator of flux in this case, is given by
+\beq
+F^{\star} = \frac{\sum_i \Big(y_i - gb\Big)P_i}{\sum_i gP_i^2}.
+\label{eq:optimalf}
+\eeq
+SNR is the ratio of the mean and variance of the distribution function that $F^{\star}$ is drawn from.
+Combining Eqs.~\ref{eq:poisson_likelihood} and~\ref{eq:optimalf}, one can show that the SNR is given by
+\beq
+\text{SNR} = \frac{F\sqrt{\sum_i P_i^2}}{\sqrt{\sum_i(FP_i+b)}}
+\eeq
+
+Following the assumptions of previous section: normalized flux and correctly subtracted background sky, we have
+
+\beq
+\text{SNR} = \frac{2(\beta-1)(2^{1/\beta}-1)^{1/2}}{\pi^{1/2}(2\beta-1)^{1/2}}\frac{1}{\gamma}.
+\label{snr3}
 \eeq
